### 2021-06-11 Paper_Figure_code.Rmd
Add files via upload

---
title: "R Notebook"
output: html_notebook
---

################ Methylation paper Figure ################

################ Start Figure 2 and Figure S1-S2################

############# 100 WB GSE132203_100 samples methylation ###############

###############   BPmet  ###################

```{r}
library(Metrics)
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

load("~/deconvolution/Final methylation paper/figure/Figure2 and S1_S2/Figure2_RawData.RData")

out.l <- epidish(GSE132203_100, BPmet, "RPC", maxit = 100)
GSE132203_100_BPmet <- data.frame(out.l$estF[,c(2,3,4,1,6,5)])

melt_FACS_GSE132203_100 <- melt(FACS_GSE132203_100)

melt_GSE132203_100_BPmet <- melt(GSE132203_100_BPmet) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_BPmet) <- c("FACS","cell_type","ALL")

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPmet") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

#### each cell types

GSE132203_100_BPmet <- cbind(GSE132203_100_BPmet, FACS_GSE132203_100)

colnames(GSE132203_100_BPmet)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK","Neu")

melt_GSE132203_100_BPmet <- list()
rmse <- list()
p_GSE132203_100_BPmet <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE132203_100_BPmet[,i], FACS_GSE132203_100[,i])

    melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[,c(i, i+6)],  id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

p_GSE132203_100_BPmet[[1]] <-  ggplot(melt_GSE132203_100_BPmet[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL ) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.42, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[3]] <-  ggplot(melt_GSE132203_100_BPmet[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.248, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[6]] <-ggplot(melt_GSE132203_100_BPmet[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.82, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]],p_GSE132203_100_BPmet[[2]],p_GSE132203_100_BPmet[[3]],p_GSE132203_100_BPmet[[4]],p_GSE132203_100_BPmet[[5]],p_GSE132203_100_BPmet[[6]], ncol = 2, nrow=3)

figure_GSE132203_100_BPmet_each_together <- ggarrange(p_GSE132203_100_BPmet_all, p_GSE132203_100_BPmet_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE132203_100_BPmet_each_together <- annotate_figure(figure_GSE132203_100_BPmet_each_together, left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))

```

###############   MethylCIBERSORT  ##################

```{r}

out.l <- epidish(GSE132203_100, MethylCIBERSORT_WB, "RPC", maxit = 100)

GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[,3] + out.l$estF[,10], out.l$estF[,5], out.l$estF[,1], out.l$estF[,2], out.l$estF[,4], out.l$estF[,9]))

colnames(GSE132203_100_MethylCIBERSORT_WB) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")

# melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB)

melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS","cell_type","MethylCIBERSORT")

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "MethylCIBERSORT") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, labels =NULL, breaks = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
#### each cell types

GSE132203_100_MethylCIBERSORT_WB <- cbind(GSE132203_100_MethylCIBERSORT_WB, FACS_GSE132203_100)

colnames(GSE132203_100_MethylCIBERSORT_WB)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK", "Neu")

melt_GSE132203_100_MethylCIBERSORT_WB <- list()
rmse <- list()
p_GSE132203_100_MethylCIBERSORT <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[,i], GSE132203_100_MethylCIBERSORT_WB[,i+6])

    melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[,c(i, i+6)],  id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.245, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.335, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.335, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.077, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[5]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[6]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.825, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.26, y = 0.685, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT_each <- ggarrange(p_GSE132203_100_MethylCIBERSORT[[1]],p_GSE132203_100_MethylCIBERSORT[[2]],p_GSE132203_100_MethylCIBERSORT[[3]],p_GSE132203_100_MethylCIBERSORT[[4]],p_GSE132203_100_MethylCIBERSORT[[5]], p_GSE132203_100_MethylCIBERSORT[[6]], ncol = 2, nrow=3)

figure_GSE132203_100_MethylCIBERSORT_together <- ggarrange(p_GSE132203_100_MethylCIBERSORT_WB_all, p_GSE132203_100_MethylCIBERSORT_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE132203_100_MethylCIBERSORT_together <- annotate_figure(figure_GSE132203_100_MethylCIBERSORT_together, left = text_grob("MethylCIBERSORT estimate", color = "black", size = 20, rot = 90))

```

###############   DHS  ##################

```{r}

out.l <- epidish(GSE132203_100, centDHSbloodDMC.m, "RPC", maxit = 100)
GSE132203_100_DHS <- data.frame(out.l$estF[,c(3,4,5,1,2,6)])
colnames(GSE132203_100_DHS) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")

#melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS)

melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_DHS) <- c("FACS","cell_type","DHS")

p_melt_GSE132203_100_DHS_all <- ggplot(melt_GSE132203_100_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2,6)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

p_melt_GSE132203_100_DHS_all_longly <- ggplot(melt_GSE132203_100_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "DHS") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL,labels =NULL, breaks = NULL ) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2,6)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

#### each cell types

GSE132203_100_DHS <- cbind(GSE132203_100_DHS, FACS_GSE132203_100)

colnames(GSE132203_100_DHS)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK", "Neu")

melt_GSE132203_100_DHS <- list()
rmse <- list()
p_GSE132203_100_DHS <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE132203_100_DHS[,i], GSE132203_100_DHS[,i+6])

    melt_GSE132203_100_DHS[[i]] <- melt(GSE132203_100_DHS[,c(i, i+6)],  id.vars = colnames(GSE132203_100_DHS)[i], measure.vars = colnames(GSE132203_100_DHS)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

p_GSE132203_100_DHS[[1]] <- ggplot(melt_GSE132203_100_DHS[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS[[2]] <- ggplot(melt_GSE132203_100_DHS[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS[[3]] <- ggplot(melt_GSE132203_100_DHS[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS[[4]] <- ggplot(melt_GSE132203_100_DHS[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS[[5]] <- ggplot(melt_GSE132203_100_DHS[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.039, y = 0.215, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS[[6]] <-ggplot(melt_GSE132203_100_DHS[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.925, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.253, y = 0.78, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE132203_100_DHS_each <- ggarrange(p_GSE132203_100_DHS[[1]],p_GSE132203_100_DHS[[2]],p_GSE132203_100_DHS[[3]],p_GSE132203_100_DHS[[4]],p_GSE132203_100_DHS[[5]], p_GSE132203_100_DHS[[6]], ncol = 2, nrow = 3)

figure_GSE132203_100_DHS_all_together <- ggarrange(p_melt_GSE132203_100_DHS_all, p_GSE132203_100_DHS_each, ncol = 2, nrow=1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE132203_100_DHS_all_together <- annotate_figure(figure_GSE132203_100_DHS_all_together, left = text_grob("DHS estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))

```

############## methylation 6 WB samples GSE77797 ##############

############## BPmet ###################

```{r}

out.l <- epidish(GSE77797_six, BPmet, "RPC", maxit = 100)
GSE77797_six_BPmet <- data.frame(out.l$estF[,c(2,3,4,1,6)])
#melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet)
melt_facs_GSE77797_six <- melt(facs_GSE77797_six[,-6])

melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_BPmet) <- c("FACS","cell_type","BPmet")

p_GSE77797_six_BPmet_all <- ggplot(melt_GSE77797_six_BPmet,aes(x=FACS, y=BPmet, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)

p_GSE77797_six_BPmet_all_longly <- ggplot(melt_GSE77797_six_BPmet,aes(x=FACS, y=BPmet, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPmet") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)

#### each cell types

GSE77797_six_BPmet <- cbind(GSE77797_six_BPmet, facs_GSE77797_six[,-6])

colnames(GSE77797_six_BPmet)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")

melt_GSE77797_six_BPmet <- list()
rmse <- list()
G6_BPmet <- list()

for (i in c(1:5)) {

    rmse[[i]] <- rmse(GSE77797_six_BPmet[,i], GSE77797_six_BPmet[,i+5])

    melt_GSE77797_six_BPmet[[i]] <- melt(GSE77797_six_BPmet[,c(i, i+5)],  id.vars = colnames(GSE77797_six_BPmet)[i], measure.vars = colnames(GSE77797_six_BPmet)[i+5])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
                   rmse = unlist(rmse))

G6_BPmet[[1]] <- ggplot(melt_GSE77797_six_BPmet[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0, 0.3)) + scale_y_continuous(name = NULL, limits = c(0, 0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.08, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

G6_BPmet[[2]] <- ggplot(melt_GSE77797_six_BPmet[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.25, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.04, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

G6_BPmet[[3]] <- ggplot(melt_GSE77797_six_BPmet[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

G6_BPmet[[4]] <- ggplot(melt_GSE77797_six_BPmet[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

G6_BPmet[[5]] <- ggplot(melt_GSE77797_six_BPmet[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0138, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]],G6_BPmet[[2]],G6_BPmet[[3]],G6_BPmet[[4]],G6_BPmet[[5]], ncol = 2, nrow=3)

figure_GSE77797_six_BPmet_together <- ggarrange(p_GSE77797_six_BPmet_all, p_GSE77797_six_BPmet_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE77797_six_BPmet_together <- annotate_figure(figure_GSE77797_six_BPmet_together,  left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))

```

###################### MethylCIBERSORT_WB #########################

```{r}

out.l <- epidish(GSE77797_six, MethylCIBERSORT_WB, "RPC", maxit = 100)
GSE77797_six_MethylCIBERSORT_WB <- data.frame(out.l$estF[,c(3,5,1,2,4)])

# melt_GSE77797_six_MethylCIBERSORT_WB <- melt(GSE77797_six_MethylCIBERSORT_WB)

melt_GSE77797_six_MethylCIBERSORT_WB <- melt(GSE77797_six_MethylCIBERSORT_WB) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_MethylCIBERSORT_WB) <- c("FACS","cell_type","MethylCIBERSORT")

p_GSE77797_six_MethylCIBERSORT_all <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)

p_GSE77797_six_MethylCIBERSORT_all_longly <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "MethylCIBERSORT") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05,  label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
#### each cell types

GSE77797_six_MethylCIBERSORT_WB <- cbind(GSE77797_six_MethylCIBERSORT_WB, facs_GSE77797_six[,-6])

colnames(GSE77797_six_MethylCIBERSORT_WB)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")

melt_GSE77797_six_MethylCIBERSORT_WB <- list()
rmse <- list()
G6_MethylCIBERSORT_WB <- list()

for (i in c(1:5)) {

    rmse[[i]] <- rmse(GSE77797_six_MethylCIBERSORT_WB[,i], GSE77797_six_MethylCIBERSORT_WB[,i+5])

    melt_GSE77797_six_MethylCIBERSORT_WB[[i]] <- melt(GSE77797_six_MethylCIBERSORT_WB[,c(i, i+5)],  id.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i+5])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
                   rmse = unlist(rmse))

G6_MethylCIBERSORT_WB[[1]] <-  ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0, 0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.082, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

G6_MethylCIBERSORT_WB[[2]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

G6_MethylCIBERSORT_WB[[3]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

G6_MethylCIBERSORT_WB[[4]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.026, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

G6_MethylCIBERSORT_WB[[5]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0138, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE77797_six_MethylCIBERSORT_WB_each <- ggarrange(G6_MethylCIBERSORT_WB[[1]],G6_MethylCIBERSORT_WB[[2]],G6_MethylCIBERSORT_WB[[3]],G6_MethylCIBERSORT_WB[[4]],G6_MethylCIBERSORT_WB[[5]], ncol = 2, nrow = 3)

figure_GSE77797_six_MethylCIBERSORT_WB_together <- ggarrange(p_GSE77797_six_MethylCIBERSORT_all, p_GSE77797_six_MethylCIBERSORT_WB_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE77797_six_MethylCIBERSORT_WB_together <- annotate_figure(figure_GSE77797_six_MethylCIBERSORT_WB_together, left = text_grob("MethylCIBERSORT estimate", color = "black", size = 20, rot = 90))

# p_GSE77797_six_MethylCIBERSORT_each <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ cell_type) + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.position="none")  + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.28, size = 6, color = "black") + geom_text(data = RMSE, aes(x = 0.065, y = 0.24, label = paste('RMSE =', round(rmse,2))), color = "black", size = 5.5)
# 
# figure_GSE77797_six_MethylCIBERSORT_each <- ggarrange(p_GSE77797_six_MethylCIBERSORT_all, p_GSE77797_six_MethylCIBERSORT_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2.5))
# 
# annotate_figure(figure_GSE77797_six_MethylCIBERSORT_each, bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("EpiDISH estimate", color = "black", size = 20, rot = 90))
```

###################### DHS #########################

```{r}

out.l <- epidish(GSE77797_six, centDHSbloodDMC.m, "RPC", maxit = 100)
GSE77797_six_DHS <- data.frame(out.l$estF[,c(3,4,5,1,2)])
colnames(GSE77797_six_DHS) <- c("CD4", "CD8", "Mono", "B", "NK")

#melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS)

melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_DHS) <- c("FACS","cell_type","DHS")

p_GSE77797_six_DHS_all <- ggplot(melt_GSE77797_six_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)

p_GSE77797_six_DHS_all_longly <- ggplot(melt_GSE77797_six_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "DHS") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)

#################################################################################

#### each cell types

GSE77797_six_DHS <- cbind(GSE77797_six_DHS, facs_GSE77797_six[,-6])

colnames(GSE77797_six_DHS)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")

melt_GSE77797_six_DHS <- list()
rmse <- list()
G6_DHS <- list()

for (i in c(1:5)) {

    rmse[[i]] <- rmse(GSE77797_six_DHS[,i], GSE77797_six_DHS[,i+5])

    melt_GSE77797_six_DHS[[i]] <- melt(GSE77797_six_DHS[,c(i, i+5)],  id.vars = colnames(GSE77797_six_DHS)[i], measure.vars = colnames(GSE77797_six_DHS)[i+5])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
                   rmse = unlist(rmse))

G6_DHS[[1]] <- ggplot(melt_GSE77797_six_DHS[[1]],aes(x = value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.34, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.082, y = 0.285, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

G6_DHS[[2]] <- ggplot(melt_GSE77797_six_DHS[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

G6_DHS[[3]] <- ggplot(melt_GSE77797_six_DHS[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

G6_DHS[[4]] <- ggplot(melt_GSE77797_six_DHS[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

G6_DHS[[5]] <- ggplot(melt_GSE77797_six_DHS[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.06)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.017, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]],G6_DHS[[2]],G6_DHS[[3]],G6_DHS[[4]],G6_DHS[[5]], ncol = 2, nrow=3)

figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow=1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE77797_six_DHS_together <- annotate_figure(figure_GSE77797_six_DHS_together,  left = text_grob("DHS estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))

figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together,figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow=3)

annotate_figure(figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together, bottom = text_grob("Gold standard", color = "black", size = 20))

# p_GSE77797_six_DHS_each <- ggplot(melt_GSE77797_six_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ cell_type) + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.position="none")  + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.28, size = 6, color = "black") + geom_text(data = RMSE, aes(x = 0.065, y = 0.24, label = paste('RMSE =', round(rmse,2))), color = "black", size = 5.5)
# 
# figure_GSE77797_six_DHS_each <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow=1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1,2.5))
# 
# annotate_figure(figure_GSE77797_six_DHS_each, bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("EpiDISH estimate", color = "black", size = 20, rot = 90))

```

########## Figure 2 and Figure S1-S2  ############

```{r}

figure_GSE132203_100_all_together <- ggarrange(p_GSE132203_100_BPmet_all_longly,p_GSE132203_100_MethylCIBERSORT_WB_all_lonly ,p_melt_GSE132203_100_DHS_all_longly, ncol = 3, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))

figure_GSE77797_all_together <- ggarrange(p_GSE77797_six_BPmet_all_longly,p_GSE77797_six_MethylCIBERSORT_all_longly ,p_GSE77797_six_DHS_all_longly, ncol = 3, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"))

Figure2 <- annotate_figure(ggarrange(figure_GSE132203_100_all_together, figure_GSE77797_all_together, ncol = 1, nrow = 2), bottom = text_grob("Gold standard", color = "black", size = 20))

Figure_S1a <- figure_GSE132203_100_BPmet_each_together
Figure_S1b <- figure_GSE132203_100_MethylCIBERSORT_together
Figure_S1c <- figure_GSE132203_100_DHS_all_together

Figure_S2a <- figure_GSE77797_six_BPmet_together
Figure_S2b <- figure_GSE77797_six_MethylCIBERSORT_WB_together
Figure_S2c <- figure_GSE77797_six_DHS_together

# figure_GSE132203_100_all_signatures <- ggarrange( figure_GSE132203_100_BPmet_each_together, figure_GSE132203_100_MethylCIBERSORT_together, figure_GSE132203_100_DHS_all_together, ncol = 1, nrow = 3)
# 
# figure_GSE132203_100_DHS_all_together <- annotate_figure(figure_GSE132203_100_DHS_all_together, bottom = text_grob("Gold standard", color = "black", size = 20))

```

############################ Start Figure 3 ############################

##########  methylation TCGA-LUAD with previous tumor purity methods ############

############## BPmetCan and MethylCIBERSORT_Luad ###################

```{r}
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

load("/home/ting/deconvolution/Final methylation paper/figure/Figure3 and S3/Figure3_and_S3.RData")

out.l <- epidish(ABSOLUTE.LUAD.Aran, BPmetCan, "RPC", maxit = 100)
TCGA_LUAD_BPmetCan <- data.frame(out.l$estF)

out.l <- epidish(ABSOLUTE.LUAD.Aran, MethylCIBERSORT_LUAD, "RPC", maxit = 100)
TCGA_LUAD_MethylCIBERSORT_LUAD <- data.frame(out.l$estF)

TCGA_LUAD_BPmetCan_MethylCIBERSORT<-as.data.frame(cbind(FACS.ABSOLUTE.LUAD.Aran$ABSOLUTE,TCGA_LUAD_BPmetCan$cancer, TCGA_LUAD_MethylCIBERSORT_LUAD$Cancer, FACS.ABSOLUTE.LUAD.Aran$ESTIMATE,FACS.ABSOLUTE.LUAD.Aran$LUMP,FACS.ABSOLUTE.LUAD.Aran$IHC))

colnames(TCGA_LUAD_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC")

melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT<-melt(TCGA_LUAD_BPmetCan_MethylCIBERSORT,  id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC"))

p_TCGA_LUAD_BPmetCan_MethylCIBERSORT <-  ggplot(melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT,aes(x=value, y = ABSOLUTE)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable, ncol = 2) + scale_x_continuous(name = "Method purity estimate", limits = c(0,1)) + scale_y_continuous(name = "ABSOLUTE estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.9, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.68, size = 6) + theme(axis.title.x = element_text(vjust = -0.5)) + theme(axis.title.y = element_text(vjust = 1.5)) #+ labs(tag = "a")

```

##########  methylation TCGA-BRCA with previous tumor purity methods ##########

############## BPmetCan and MethylCIBERSORT_breast ###################

```{r}

out.l <- epidish(TCGA_BRCA_450k, BPmetCan, "RPC", maxit = 100)
TCGA_BRCA_BPmetCan <- data.frame(out.l$estF)

out.l <- epidish(TCGA_BRCA_450k, MethylCIBERSORT_brest, "RPC", maxit = 100)
TCGA_BRCA_MethylCIBERSORT <- data.frame(out.l$estF)

TCGA_BRCA_BPmetCan_MethylCIBERSORT<-as.data.frame(cbind(FACS_Aran_BRCA$ABSOLUTE,TCGA_BRCA_BPmetCan$cancer, TCGA_BRCA_MethylCIBERSORT$Cancer, FACS_Aran_BRCA$ESTIMATE,FACS_Aran_BRCA$LUMP,FACS_Aran_BRCA$IHC))

colnames(TCGA_BRCA_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC")

melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT <- melt(TCGA_BRCA_BPmetCan_MethylCIBERSORT,  id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC"))

p_TCGA_BRCA_BPmetCan_MethylCIBERSORT <-  ggplot(melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT,aes(x = value, y = ABSOLUTE)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable, ncol = 2) + scale_x_continuous(name = "Method purity estimate", limits = c(0,1)) + scale_y_continuous(name = "ABSOLUTE estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0.6, label.y = 0.1, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0.6, label.y = 0, size = 6) + theme(axis.title.x = element_text(vjust = -0.5)) + theme(axis.title.y = element_text(vjust=1.5)) #+ labs(tag = "b")

```

############################ DNA methylation lymphocytes ###################################

############################ BPmetCan ###################################

# Lymphocytes: CD4 + Tregs + CD8 + B + NK

# Monocytes/Macrophages lineage: M0 + M1 + M2 + Monocytes

# Neutrophiles: Neutrophils

```{r}

out.l <- epidish(TCGA_LUAD_Methylation, BPmetCan, "RPC")
TCGA_LUAD_BPmetCan_lymphocytes_deconv <- data.frame(out.l$estF)

TCGA_LUAD_BPmetCan_lymphocytes <- cbind((TCGA_LUAD_BPmetCan_lymphocytes_deconv$B + TCGA_LUAD_BPmetCan_lymphocytes_deconv$CD4 + TCGA_LUAD_BPmetCan_lymphocytes_deconv$CD8 + TCGA_LUAD_BPmetCan_lymphocytes_deconv$NK + TCGA_LUAD_BPmetCan_lymphocytes_deconv$Treg), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Lymphocytes)
colnames(TCGA_LUAD_BPmetCan_lymphocytes) <- c("estimate", "facs")

TCGA_LUAD_BPmetCan_Macrophages <- cbind((TCGA_LUAD_BPmetCan_lymphocytes_deconv$M0 + TCGA_LUAD_BPmetCan_lymphocytes_deconv$M1 + TCGA_LUAD_BPmetCan_lymphocytes_deconv$M2 + TCGA_LUAD_BPmetCan_lymphocytes_deconv$Mono), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Macrophages)
colnames(TCGA_LUAD_BPmetCan_Macrophages) <- c("estimate", "facs")

TCGA_LUAD_BPmetCan_Neutrophils <- cbind((TCGA_LUAD_BPmetCan_lymphocytes_deconv$Neu), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Neutrophils)
colnames(TCGA_LUAD_BPmetCan_Neutrophils) <- c("estimate", "facs")

p_TCGA_LUAD_BPmetCan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.72, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_BPmetCan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_BPmetCan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Neutrophils[-144,]),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

```

############## MethylCIBERSORT #####################

# Lymphocytes: CD4 + Tregs + CD8 + B + NK

# Monocytes/Macrophages lineage: Monocytes

# Neutrophiles: Neutrophils
```{r}

out.l <- epidish(TCGA_LUAD_Methylation, MethylCIBERSORT_LUAD, "RPC")
TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv <- data.frame(out.l$estF)

TCGA_LUAD_MethylCIBERSORT_lymphocytes <- cbind(( TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD4 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD8 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$NK + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$B + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$Treg), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Lymphocytes)
colnames(TCGA_LUAD_MethylCIBERSORT_lymphocytes) <- c("estimate", "facs")

TCGA_LUAD_MethylCIBERSORT_Macrophages <- cbind((TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$Mono), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Macrophages)
colnames(TCGA_LUAD_MethylCIBERSORT_Macrophages) <- c("estimate", "facs")

TCGA_LUAD_MethylCIBERSORT_Neutrophils <- cbind((TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$Neu), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Neutrophils)
colnames(TCGA_LUAD_MethylCIBERSORT_Neutrophils) <- c("estimate", "facs")

p_TCGA_LUAD_MethylCIBERSORT_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_lymphocytes), aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.72, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_MethylCIBERSORT_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Macrophages),aes(x=facs, y=estimate )) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_MethylCIBERSORT_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow=1, labels = "c", font.label = list(size = 20, color = "black"))

# annotate_figure_TCGA_LUAD_MethylCIBERSORT <- annotate_figure(figure_TCGA_LUAD_MethylCIBERSORT, left = text_grob("MethylCIBERSORT estimate", color = "black", size = 20, rot = 90))
# 
# 
# annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- ggarrange(annotate_figure_TCGA_LUAD_BPmetCan, annotate_figure_TCGA_LUAD_MethylCIBERSORT, ncol = 1, nrow = 2)
# 
# annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- annotate_figure(annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT, bottom = text_grob("H&E estimate", color = "black", size = 20))

```

############## Options DHS #####################

# Lymphocytes: CD4 + CD8 + B + NK

# Monocytes/Macrophages lineage: Monocytes

# Neutrophiles: Neutrophils

```{r}
# out.l <- epidish(TCGA_LUAD_Mthylation, centDHSbloodDMC.m, "RPC", maxit = 100)
# TCGA_LUAD_Methylation_DHS_lymphocytes_deconv <- data.frame(out.l$estF)
# TCGA_LUAD_Methylation_DHS_lymphocytes_deconv <- TCGA_LUAD_Methylation_DHS_lymphocytes_deconv[rownames(TCGA_LUAD_Methylation_DHS_lymphocytes_deconv)%in%rownames(FACS_TCGA_LUAD_BPmetCan_lymphocytes),]
# 
# 
# TCGA_LUAD_DHS_lymphocytes <- cbind((TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$CD4T + TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$CD8T + TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$NK + TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$B), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Lymphocytes)
# colnames(TCGA_LUAD_DHS_lymphocytes) <- c("estimate", "facs")
# 
# TCGA_LUAD_DHS_Macrophages <- cbind((TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$Mono), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Macrophages)
# colnames(TCGA_LUAD_DHS_Macrophages) <- c("estimate", "facs")
# 
# TCGA_LUAD_DHS_Neutrophils <- cbind((TCGA_LUAD_Methylation_DHS_lymphocytes_deconv$Neu), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Neutrophils)
# colnames(TCGA_LUAD_DHS_Neutrophils) <- c("estimate", "facs")
# 
# p_TCGA_LUAD_DHS_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_DHS_lymphocytes), aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 1.05, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
# 
# p_TCGA_LUAD_DHS_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_DHS_Macrophages),aes(x=facs, y=estimate )) + geom_point(colour = c("yellow2")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.73, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
# 
# p_TCGA_LUAD_DHS_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_DHS_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.73, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
# 
# figure_TCGA_LUAD_DHS <- ggarrange(p_TCGA_LUAD_DHS_lymphocytes, p_TCGA_LUAD_DHS_Macrophages, p_TCGA_LUAD_DHS_Neutrophils, ncol = 3, nrow=1, labels = "c", font.label = list(size = 20, color = "black"))
# 
# annotate_figure(figure_TCGA_LUAD_DHS, left = text_grob("DHS estimates", color = "black", size = 20, rot = 90), bottom = text_grob("H&E estimates", color = "black", size = 20))
# 
```

########### Figure 3 and Figure S3  #################
```{r}

#### Figure 3 #####

figure_LUAD_methy <- ggarrange(p_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow =1, labels = "a", font.label = list(size = 20, color = "black"))

figure_TCGA_LUAD_BPmetCan <- ggarrange(p_TCGA_LUAD_BPmetCan_lymphocytes, p_TCGA_LUAD_BPmetCan_Macrophages, p_TCGA_LUAD_BPmetCan_Neutrophils, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))

figure_TCGA_LUAD_BPmetCan <- annotate_figure(figure_TCGA_LUAD_BPmetCan, left = text_grob("BPmetCan estimate", color = "black", size = 20, rot = 90))

figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))

figure_TCGA_LUAD_MethylCIBERSORT <- annotate_figure(figure_TCGA_LUAD_MethylCIBERSORT, left = text_grob("MethylCIBERSORT estimate", color = "black", size = 20, rot = 90))

TCGA_LUAD_BPmetCan_MethylCIBERSORT <- ggarrange(figure_TCGA_LUAD_BPmetCan, figure_TCGA_LUAD_MethylCIBERSORT, ncol = 1, nrow = 2, labels = "b", font.label = list(size = 20, color = "black"))

annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- annotate_figure(TCGA_LUAD_BPmetCan_MethylCIBERSORT, bottom = text_grob("H&E estimate", color = "black", size = 20))

Figure3 <- ggarrange(figure_LUAD_methy, annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 2)

#### Figure S3 #####

Figure_S3 <- ggarrange(p_TCGA_BRCA_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 1)

```

############################ Start Figure 4 ############################

############################ RNAseq lymphocytes ###################################

##########  RNAseq GSE107011 PBMC Monaco ############

############## BPRNA ###################

```{r}
library(Metrics)

load("~/deconvolution/Final methylation paper/figure/Figure4/GSE107011_PBMCs_Fig4.RData")

out.l <- epidish(GSE107011, as.matrix(BPRNA), "RPC", maxit = 100)
BPRNA_EpiDISH <- data.frame(out.l$estF)

GSE107011_BPRNA_EpiDISH_modify <- cbind(BPRNA_EpiDISH[, c(2,3,4,1,6,5)])

#melt_GSE107011_BPRNA_EpiDISH_modify <- melt(GSE107011_BPRNA_EpiDISH_modify)
melt_FACS_GSE107011 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

melt_GSE107011_BPRNA_EpiDISH_modify_FACS <- melt(GSE107011_BPRNA_EpiDISH_modify) %>% cbind(melt_FACS_GSE107011$value, .)
colnames(melt_GSE107011_BPRNA_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")

p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0, 0.4)) + scale_y_continuous(name = NULL, limits = c(0, 0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]))$est,2)), parse = F, size = 8)

p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPRNA") + scale_x_continuous(name = NULL, limits = NULL) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]))$est,2)), parse = F, size = 8)

#### each cell types

GSE107011_BPRNA_EpiDISH_modify <- cbind(GSE107011_BPRNA_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

colnames(GSE107011_BPRNA_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")

melt_GSE107011_BPRNA_EpiDISH_modify <- list()
rmse <- list()
melt_GSE107011_BPRNA_EpiDISH <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE107011_BPRNA_EpiDISH_modify[,i], GSE107011_BPRNA_EpiDISH_modify[,i+6])

    melt_GSE107011_BPRNA_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNA_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

melt_GSE107011_BPRNA_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0, 0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.74, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.62, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.088, y = 0.52, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNA_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.14, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.117, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.068, y = 0.097, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNA_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.475, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.405, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.088, y = 0.345, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNA_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.475, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.405, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0345, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNA_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.19, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.045, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNA_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.04)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.038, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.033, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.018, y = 0.0275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

# left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90),

```

############## Figure 4  #####################
```{r}

library(cowplot)
library(dplyr)

p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]],melt_GSE107011_BPRNA_EpiDISH[[2]],melt_GSE107011_BPRNA_EpiDISH[[3]],melt_GSE107011_BPRNA_EpiDISH[[4]],melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3)

figure_GSE107011_BPRNA_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_GSE107011_BPRNA_EpiDISH_each, ncol = 2, labels = "a", nrow=1, font.label = list(size = 20, color = "black"), widths = c(1,2.5)) #, labels = "b"

Fig_4a <- annotate_figure(figure_GSE107011_BPRNA_EpiDISH_together,  bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90))

# GSE107011_PBMCs <- read.table("~/paper1.txt", row.names = 1, header = T)
# GSE107011_PBMCs_pvalue <- read.table("~/paper1.txt", row.names = 1, header = T)

melt_PBMCs <- melt(GSE107011_PBMCs)
melt_PBMCs_Pvalue <- melt(GSE107011_PBMCs_pvalue)

merge_melt_PBMCs <- cbind(melt_PBMCs, melt_PBMCs_Pvalue) %>% .[,-3]

melt_merge_melt_PBMCs <- merge_melt_PBMCs %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_melt_PBMCs$new_Var2 <- rownames(GSE107011_PBMCs_pvalue)
melt_merge_melt_PBMCs$new_Var2 <- factor(melt_merge_melt_PBMCs$new_Var2, levels = unique(melt_merge_melt_PBMCs$new_Var2))

PBMCs_figure <- ggplot(melt_merge_melt_PBMCs, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 8) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 20),
          legend.text=element_text(size = 20),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 20, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 20, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("Pearson correlation") + theme(plot.title = element_text(hjust = 0.5, size = 20 ))

Figure_4b <- ggarrange(PBMCs_figure, ncol = 1, labels = "b", nrow=1, font.label = list(size = 20, color = "black"))

# Figure_4 <- ggarrange(figure_GSE107011_BPRNA_EpiDISH_together ,PBMCs_figure, ncol = 1, nrow=2, font.label = list(size = 20, color = "black"))

# ggdraw()+ draw_plot(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, x=0, y=0.6, width=0.5, height = 0.4)+
#     draw_plot(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, x=0.5, y= 0.6, width=0.5, height = 0.4) +
#     draw_plot(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, x=1, y=0.6, width = 0.5, height = 0.4)+ 
#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.6)+ 
#     draw_plot_label(label = c("a", "b", "c", "d"), size = 18, x=c(0, 0.5, 1, 0), y=c(1, 1, 1, 0.58))
# 
# 
# ggdraw()+ draw_plot(figure_GSE107011_all_together, x = 0.05, y = 0.5, width = 0.9, height = 0.5)+
#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.5) + 
#     draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y=c(1, 0.5))
#   
# 
# ggarrange(PBMCs_figure, labels = "b", nrow=1, ncol = 1, font.label = list(size = 20, color = "black"), widths = c(1,1))

```

######### Not Run #####

######### CCLE_TIL10 ###################

```{r}
library(dplyr)

GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind((GSE107011_CCLE_TIL10_EpiDISH$T.cells.CD4 + GSE107011_CCLE_TIL10_EpiDISH$Tregs),GSE107011_CCLE_TIL10_EpiDISH[, c(9,5,2,7,6)])

colnames(GSE107011_CCLE_TIL10_EpiDISH_modify) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")

# melt_GSE107011_CCLE_TIL10_EpiDISH_modify <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify)
# melt_FACS_GSE107011 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

  melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify) %>% cbind(melt_FACS_GSE107011$value, .)
  colnames(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")

p_GSE107011_CCLE_TIL10_EpiDISH_modify_all <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "CCLE_TIL10 estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)

p_GSE107011_CCLE_TIL10_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "CCLE_TIL10") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)

#### each cell types

GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind(GSE107011_CCLE_TIL10_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

colnames(GSE107011_CCLE_TIL10_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")

melt_GSE107011_CCLE_TIL10_EpiDISH_modify <- list()
rmse <- list()
melt_GSE107011_CCLE_TIL10_EpiDISH <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE107011_CCLE_TIL10_EpiDISH_modify[,i], GSE107011_CCLE_TIL10_EpiDISH_modify[,i+6])

    melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[i]] <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

melt_GSE107011_CCLE_TIL10_EpiDISH[[1]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

melt_GSE107011_CCLE_TIL10_EpiDISH[[2]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.273, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.08, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

melt_GSE107011_CCLE_TIL10_EpiDISH[[3]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.092, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

melt_GSE107011_CCLE_TIL10_EpiDISH[[4]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.182, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

melt_GSE107011_CCLE_TIL10_EpiDISH[[5]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.182, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

melt_GSE107011_CCLE_TIL10_EpiDISH[[6]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0735, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.0676, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE107011_CCLE_TIL10_EpiDISH_each <- ggarrange(melt_GSE107011_CCLE_TIL10_EpiDISH[[1]],melt_GSE107011_CCLE_TIL10_EpiDISH[[2]],melt_GSE107011_CCLE_TIL10_EpiDISH[[3]],melt_GSE107011_CCLE_TIL10_EpiDISH[[4]],melt_GSE107011_CCLE_TIL10_EpiDISH[[5]], melt_GSE107011_CCLE_TIL10_EpiDISH[[6]], ncol = 3, nrow = 2)

figure_GSE107011_CCLE_TIL10_EpiDISH_each_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_GSE107011_CCLE_TIL10_EpiDISH_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE107011_CCLE_TIL10_EpiDISH_each_together <- annotate_figure(figure_GSE107011_CCLE_TIL10_EpiDISH_each_together, left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))

```

############## BPRNACan ###################

```{r}
GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH[, c(3,4,8,1,10,9)])

# melt_GSE107011_BPRNACan_EpiDISH_modify <- melt(GSE107011_BPRNACan_EpiDISH_modify)
# melt_FACS_107 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

melt_GSE107011_BPRNACan_EpiDISH_modify_FACS <- melt(GSE107011_BPRNACan_EpiDISH_modify) %>% cbind(melt_FACS_107$value, .)
colnames(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")

p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)

p_melt_GSE107011_BPRNACan_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPRNACan") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.25, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)

#### each cell types

GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

colnames(GSE107011_BPRNACan_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")

melt_GSE107011_BPRNACan_EpiDISH_modify <- list()
rmse <- list()
melt_GSE107011_BPRNACan_EpiDISH <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE107011_BPRNACan_EpiDISH_modify[,i], GSE107011_BPRNACan_EpiDISH_modify[,i+6])

    melt_GSE107011_BPRNACan_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNACan_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

melt_GSE107011_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.138, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0842, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.108, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.276, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.138, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

melt_GSE107011_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0735, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.0673, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE107011_BPRNACan_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNACan_EpiDISH[[1]],melt_GSE107011_BPRNACan_EpiDISH[[2]],melt_GSE107011_BPRNACan_EpiDISH[[3]],melt_GSE107011_BPRNACan_EpiDISH[[4]],melt_GSE107011_BPRNACan_EpiDISH[[5]], melt_GSE107011_BPRNACan_EpiDISH[[6]], ncol = 3, nrow = 2)

figure_GSE107011_BPRNACan_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, p_GSE107011_BPRNACan_EpiDISH_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE107011_BPRNACan_EpiDISH_together <- annotate_figure(figure_GSE107011_BPRNACan_EpiDISH_together, left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))

```

############## PBMC GSE107011  ###################

```{r}
figure_GSE107011_all_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))

figure_GSE107011_all_together <- annotate_figure(figure_GSE107011_all_together, bottom = text_grob("Gold standard", color = "black", size = 20))
```

######### Not Run #####

############################ Start Figure S4 ############################

############################ 1700 in-silico mixture RNAseq benchmark ############################

############################ CCLE_TIL10 ############################

```{r}

load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S4/Silico_1700_RNAseq.RData")

out.l <- epidish(Silico_1700, CCLE_TIL10, "RPC", maxit = 200)
benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[,c(1,8,9,5,3,4,2,7,6,10,11)])
benchmarker_CCLE_TIL10 <- cbind(benchmarker_CCLE_TIL10, Facs_Silico_1700)

colnames(benchmarker_CCLE_TIL10)<-c("V","V","V","V","V","V","V","V","V","V","V","Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs")

melt_benchmarker_CCLE_TIL10 <- list()
rmse <- list()
p_benchmarker_CCLE_TIL10 <- list()

for (i in c(1:11)) {

    rmse <- rmse(benchmarker_CCLE_TIL10[,i], Facs_Silico_1700[,i])
    melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[,c(i, i+11)],  id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i+11])

RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs"),
                   rmse = unlist(rmse))

p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]],aes(x=value, y= V)) + geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1","deeppink","darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL,limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.915, size = 6) + annotate("text", x = 0.22, y = 0.832, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)  
}

for (i in c(2:11)) {

    rmse <- rmse(benchmarker_CCLE_TIL10[,i], Facs_Silico_1700[,i])
    melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[,c(i, i+11)],  id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i+11])

    RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs"),
                   rmse = unlist(rmse))

p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]],aes(x=value, y= V)) + geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1","deeppink","darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) + theme_bw() + stat_smooth(method = lm, color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL,limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6) + annotate("text", x = 0.062, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) 
}

```

############################ BPRNACan ############################

```{r}

out.l <- epidish(Silico_1700, BPRNACan, "RPC", maxit = 200)
benchmarker_BPRNACan_150 <- data.frame(out.l$estF[,c(2,3,4,8,6,7,1,10,9)])
benchmarker_BPRNACan_150 <- cbind(benchmarker_BPRNACan_150, Facs_Silico_1700[,-c(10,11)])

colnames(benchmarker_BPRNACan_150)<-c("V","V","V","V","V","V","V","V", "V","Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu")

melt_benchmarker_BPRNACan_150 <- list()
rmse <- list()
bench_BPRNACan <- list()

for (i in c(1:9)) {

    rmse[[i]] <- rmse(benchmarker_BPRNACan_150[,i], benchmarker_BPRNACan_150[,i+9])

    melt_benchmarker_BPRNACan_150[[i]] <- melt(benchmarker_BPRNACan_150[,c(i, i+9)],  id.vars = colnames(benchmarker_BPRNACan_150)[i], measure.vars = colnames(benchmarker_BPRNACan_150)[i+9])
}

RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu"),
                   rmse = unlist(rmse))

bench_BPRNACan[[1]] <- ggplot(melt_benchmarker_BPRNACan_150[[1]],aes(x=value, y= V)) + geom_point(colour = c("cyan1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.935, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.22, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[2]] <- ggplot(melt_benchmarker_BPRNACan_150[[2]],aes(x=value, y= V)) + geom_point(colour = c("red")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text",  x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[3]] <- ggplot(melt_benchmarker_BPRNACan_150[[3]],aes(x=value, y= V)) + geom_point(colour = c("green")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.185, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[4]] <- ggplot(melt_benchmarker_BPRNACan_150[[4]],aes(x=value, y= V)) + geom_point(colour = c("blue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[5]] <- ggplot(melt_benchmarker_BPRNACan_150[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkorange1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.037, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.065, y = 0.034, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[6]] <- ggplot(melt_benchmarker_BPRNACan_150[[6]],aes(x=value, y= V)) + geom_point(colour = c("deeppink")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 4e-04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 3.7e-04, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.092, y = 3.4e-04, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[7]] <- ggplot(melt_benchmarker_BPRNACan_150[[7]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[7],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[8]] <- ggplot(melt_benchmarker_BPRNACan_150[[8]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.185, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[8],2))))), parse = TRUE, size = 6)

bench_BPRNACan[[9]] <- ggplot(melt_benchmarker_BPRNACan_150[[9]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3) ) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[9],2))))), parse = TRUE, size = 6)

```

################# Figure 4S #######################

```{r}

Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow=4, labels = "a", font.label = list(size = 18, color = "black"))

Figure_4Sa <- annotate_figure(Figure_4Sa,
                bottom = text_grob("Gold standard", color = "black", size = 20),
                left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))

Figure_S4b <- ggarrange(bench_BPRNACan[[1]],bench_BPRNACan[[2]],bench_BPRNACan[[3]],bench_BPRNACan[[4]],bench_BPRNACan[[5]],bench_BPRNACan[[6]],bench_BPRNACan[[7]],bench_BPRNACan[[8]],bench_BPRNACan[[9]], ncol = 3, nrow=3,labels = "b", font.label = list(size = 18, color = "black"))

Figure_S4b <- annotate_figure(Figure_S4b,
                bottom = text_grob("Gold standard", color = "black", size = 20),
                left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))

```

############################ Start Figure 5 ############################

#############  H&E #####################

############## CCLE_TIL10 #####################

# Lymphocytes: CD4 + CD8 + B + NK + Tregs

# Monocytes/Macrophages lineage: Monocytes + M1 + M2

# Neutrophiles: Neutrophils

```{r}

load("/home/ting/deconvolution/Final methylation paper/figure/figure5/Figure_5.RData")

library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

out.l <- epidish(LUAD_RNAseq_TPM, CCLE_TIL10, "RPC", maxit = 100)
TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- data.frame(out.l$estF)
TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[sort(rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv)),]
TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify),]

TCGA_LUAD_CCLE_TIL10_lymphocytes <- cbind((TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$B + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$CD4 + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$CD8 + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$NK + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$Tregs), HE_TCGA_LUAD_lymphocytes_modify$Lymphocytes)
colnames(TCGA_LUAD_CCLE_TIL10_lymphocytes) <- c("estimate", "facs")

TCGA_LUAD_CCLE_TIL10_Macrophages <- cbind((TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$M1 + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$M2 + TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$Mono), HE_TCGA_LUAD_lymphocytes_modify$Macrophages)
colnames(TCGA_LUAD_CCLE_TIL10_Macrophages) <- c("estimate", "facs")

TCGA_LUAD_CCLE_TIL10_Neutrophils <- cbind((TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv$Neu), HE_TCGA_LUAD_lymphocytes_modify$Neutrophils)
colnames(TCGA_LUAD_CCLE_TIL10_Neutrophils) <- c("estimate", "facs")

p_TCGA_LUAD_CCLE_TIL10_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.46, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_CCLE_TIL10_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_CCLE_TIL10_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.05)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.05, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.046, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

figure_TCGA_LUAD_CCLE_TIL10 <- ggarrange(p_TCGA_LUAD_CCLE_TIL10_lymphocytes, p_TCGA_LUAD_CCLE_TIL10_Macrophages, p_TCGA_LUAD_CCLE_TIL10_Neutrophils, ncol = 3, nrow=1)

annotate_figure_TCGA_LUAD_CCLE_TIL10 <- annotate_figure(figure_TCGA_LUAD_CCLE_TIL10, left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))

```

############## BPRNACan #####################

# Lymphocytes: CD4 + CD8 + B + NK

# Monocytes/Macrophages lineage: Monocytes + M0 + M1 + M2

# Neutrophiles: Neutrophils

```{r}

library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

out.l <- epidish(LUAD_RNAseq_TPM, BPRNACan, "RPC", maxit = 100)
TCGA_LUAD_BPRNACan_lymphocytes_deconv <- data.frame(out.l$estF)
TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[sort(rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv)),]
TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify),]

TCGA_LUAD_BPRNACan_lymphocytes <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$B + TCGA_LUAD_BPRNACan_lymphocytes_deconv$CD4 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$CD8 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$NK), HE_TCGA_LUAD_lymphocytes_modify$Lymphocytes)
colnames(TCGA_LUAD_BPRNACan_lymphocytes) <- c("estimate", "facs")

TCGA_LUAD_BPRNACan_Macrophages <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$M0 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$M1 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$M2 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$Mono), HE_TCGA_LUAD_lymphocytes_modify$Macrophages)
colnames(TCGA_LUAD_BPRNACan_Macrophages) <- c("estimate", "facs")

TCGA_LUAD_BPRNACan_Macrophages_NoM0 <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$M1 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$M2 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$Mono), HE_TCGA_LUAD_lymphocytes_modify$Macrophages)
colnames(TCGA_LUAD_BPRNACan_Macrophages_NoM0) <- c("estimate", "facs")

TCGA_LUAD_BPRNACan_Macrophages_Only_Mono <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$Mono), HE_TCGA_LUAD_lymphocytes_modify$Macrophages)
colnames(TCGA_LUAD_BPRNACan_Macrophages_Only_Mono) <- c("estimate", "facs")

TCGA_LUAD_BPRNACan_Macrophages_M1_m2 <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$M1 + TCGA_LUAD_BPRNACan_lymphocytes_deconv$M2), HE_TCGA_LUAD_lymphocytes_modify$Macrophages)
colnames(TCGA_LUAD_BPRNACan_Macrophages_M1_m2) <- c("estimate", "facs")

TCGA_LUAD_BPRNACan_Neutrophils <- cbind((TCGA_LUAD_BPRNACan_lymphocytes_deconv$Neu), HE_TCGA_LUAD_lymphocytes_modify$Neutrophils)
colnames(TCGA_LUAD_BPRNACan_Neutrophils) <- c("estimate", "facs")

p_TCGA_LUAD_BPRNACan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.073, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_BPRNACan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

p_TCGA_LUAD_BPRNACan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.008)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.008, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0074, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))

figure_TCGA_LUAD_BPRNACan <- ggarrange(p_TCGA_LUAD_BPRNACan_lymphocytes, p_TCGA_LUAD_BPRNACan_Macrophages, p_TCGA_LUAD_BPRNACan_Neutrophils, ncol = 3, nrow=1,  font.label = list(size = 20, color = "black"))

annotate_figure_TCGA_LUAD_BPRNACan <- annotate_figure(figure_TCGA_LUAD_BPRNACan, left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))

annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow=2, labels = "a", font.label = list(size = 20, color = "black"))

annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- annotate_figure(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, bottom = text_grob("H&E estimate", color = "black", size = 20))

```

##########  RNAseq Ludo's data 59 multiple myeloma TME patients ############

############## BPRNACan ###################

```{r}

out.l <- epidish(Thomas_RNAseq_part, BPRNACan, "RPC", maxit = 100)
Thomas_RNAseq_BPRNACan_150 <- data.frame(out.l$estF[,c(3,4,10)])

FACS_Thomas_mean_M <- FACS_Thomas_mean[,c(3,4,2)]/100

Thomas_RNAseq_BPRNACan_150 <- cbind(Thomas_RNAseq_BPRNACan_150, FACS_Thomas_mean_M)
colnames(Thomas_RNAseq_BPRNACan_150)<-c("V","V","V","CD4","CD8","NK")

melt_Thomas_RNAseq_BPRNACan_150 <- list()
rmse <- list()
Th <- list()

for (i in c(1:3)) {

    rmse[[i]] <- rmse(Thomas_RNAseq_BPRNACan_150[,i], FACS_Thomas_mean_M[,i])

    melt_Thomas_RNAseq_BPRNACan_150[[i]] <- melt(Thomas_RNAseq_BPRNACan_150[,c(i, i+3)],  id.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i], measure.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i+3])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
                   rmse = unlist(rmse))

Th[[1]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "CD4")+ scale_x_continuous(name = NULL, limits = c(0,0.18)) + scale_y_continuous(name = NULL, limits = c(0,0.25)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.25, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.235, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.048, y = 0.22, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

Th[[2]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[2]][-9,],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "CD8")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.05)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.05, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.047, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.023, y = 0.044, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

Th[[3]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.04)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0375, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 0.035, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

```

############## quanTIseq ###################

```{r}
library(immunedeconv)
library(textshape)
library(dplyr)

Thomas_quantiseq = deconvolute(Thomas_RNAseq_part, "quantiseq", tumor = FALSE)

          Thomas_quantiseq <- as.data.frame(t(column_to_rownames(Thomas_quantiseq)))

          colnames(Thomas_quantiseq) <- c("B", "M1", "M2", "Mono", "Neu", "NK", "CD4", "CD8", "Tregs", "DCs", "UnCharcs")

Thomas_quanTIseq_M <- Thomas_quantiseq[,c(7,8,6)]

Thomas_quanTIseq_M <- cbind(Thomas_quanTIseq_M, FACS_Thomas_mean_M)
colnames(Thomas_quanTIseq_M)<-c("V","V","V","CD4","CD8","NK")

melt_Thomas_quanTIseq_M <- list()
rmse <- list()
Thq <- list()

for (i in c(1:3)) {

    rmse[[i]] <- rmse(Thomas_quanTIseq_M[,i], FACS_Thomas_mean_M[,i])

    melt_Thomas_quanTIseq_M[[i]] <- melt(Thomas_quanTIseq_M[,c(i, i+3)],  id.vars = colnames(Thomas_quanTIseq_M)[i], measure.vars = colnames(Thomas_quanTIseq_M)[i+3])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
                   rmse = unlist(rmse))

Thq[[1]] <- ggplot(melt_Thomas_quanTIseq_M[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.12)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.12, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.112, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.058, y = 0.105, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

Thq[[2]] <- ggplot(melt_Thomas_quanTIseq_M[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.075, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.023, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

Thq[[3]] <-  ggplot(melt_Thomas_quanTIseq_M[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.075, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

 # Mix_figure_BPRNACan_quanTIseq_M <- ggarrange(figure_Thomas_BPRNACan_150, figure_Thomas_quanTIseq_M, ncol = 1, nrow=2)
 # annotate_figure(Mix_figure_BPRNACan_quanTIseq_M,
 #                 bottom = text_grob("Gold standard", color = "black", size = 20))
```

######################### MCP-counter ######################################

```{r}
Thomas_MCP_counter = deconvolute(Thomas_RNAseq_part, "mcp_counter")

Thomas_MCP_counter <- as.data.frame(t(column_to_rownames(Thomas_MCP_counter)))

Thomas_MCP_counter <- Thomas_MCP_counter[,-6]

colnames(Thomas_MCP_counter) <- c("T", "CD8", "CytotoxicityScore", "NK", "B", "Macrophage/Monocyte", "DCs", "Neu", "Endothelial", "CAFs")

Thomas_Thomas_MCP_counter_M <- Thomas_MCP_counter[,c(1,2,4)]
Thomas_Thomas_MCP_counter_M <- cbind((Thomas_Thomas_MCP_counter_M[,1]-Thomas_Thomas_MCP_counter_M[,2]),Thomas_Thomas_MCP_counter_M[,2], Thomas_Thomas_MCP_counter_M[,3])
Thomas_Thomas_MCP_counter_M <- pmax(Thomas_Thomas_MCP_counter_M, 0)

Thomas_Thomas_MCP_counter_M <- cbind(Thomas_Thomas_MCP_counter_M, FACS_Thomas_mean_M)
colnames(Thomas_Thomas_MCP_counter_M)<-c("V","V","V","CD4","CD8","NK")

melt_Thomas_Thomas_MCP_counter_M <- list()
rmse <- list()
Thm <- list()

for (i in c(1:3)) {

#     rmse[[i]] <- rmse(Thomas_Thomas_MCP_counter_M[,i], Thomas_Thomas_MCP_counter_M[,i+3])
#     
#     melt_Thomas_Thomas_MCP_counter_M[[i]] <- melt(Thomas_Thomas_MCP_counter_M[,c(i, i+3)],  id.vars = colnames(Thomas_Thomas_MCP_counter_M)[i], measure.vars = colnames(Thomas_Thomas_MCP_counter_M)[i+3])
# }

 rmse[[i]] <- rmse(Thomas_Thomas_MCP_counter_M[,i], FACS_Thomas_mean_M[,i])

    melt_Thomas_Thomas_MCP_counter_M[[i]] <- melt(Thomas_Thomas_MCP_counter_M[,c(i, i+3)],  id.vars = colnames(Thomas_Thomas_MCP_counter_M)[i], measure.vars = colnames(Thomas_Thomas_MCP_counter_M)[i+3])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
                   rmse = unlist(rmse))

Thm[[1]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 30, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 27.5, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.051, y = 25.5, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

Thm[[2]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 50, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 46, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.024, y = 43, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

Thm[[3]] <-  ggplot(melt_Thomas_Thomas_MCP_counter_M[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 6, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 5.55, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 5.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

```

############## scRNAseq GSE72056  ###################

############## BPRNACan ###################

```{r}
library(Metrics)

load("/home/ting/deconvolution/Final methylation paper/RNAseq/melanoma_scRNAseq_GSE72056_and_GSE93722/Two_datasets/Melanoma_GSE72056_RNAseq.RData")

out.l <- epidish(Melanoma_GSE72056_no_malighant, BPRNACan, "RPC", maxit = 100)
GSE72056_BPRNACan <- data.frame(cbind(out.l$estF[,2:4], out.l$estF[,5] + out.l$estF[,6]+out.l$estF[,7]+out.l$estF[,8],out.l$estF[,1],out.l$estF[,10])) 
colnames(GSE72056_BPRNACan)[4:6] <- c("Macrophages","B","NK")

GSE72056_BPRNACan_EpiDISH <- cbind(GSE72056_BPRNACan, Facs_Melanoma_GSE72056[,c(10,3,4,6,1,7)])

colnames(GSE72056_BPRNACan_EpiDISH) <- c("V","V","V","V","V","V", "cancer", "CD4", "CD8", "Macrophages", "B", "NK")

melt_GSE72056_BPRNACan_EpiDISH <- list()
rmse <- list()
p_GSE72056_BPRNACan_EpiDISH <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE72056_BPRNACan_EpiDISH[,i], GSE72056_BPRNACan_EpiDISH[,i + 6])

    melt_GSE72056_BPRNACan_EpiDISH[[i]] <- melt(GSE72056_BPRNACan_EpiDISH[,c(i, i + 6)],  id.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i], measure.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i + 6])
}

RMSE <- data.frame(cell_type = c("cancer", "CD4", "CD8", "Macrophages", "B", "NK"),
                   rmse = unlist(rmse))

p_GSE72056_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[1]],aes(x = value, y = V)) + geom_point(colour = c("cyan1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[2]],aes(x = value, y = V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.172, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.093, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0335, y = 0.087, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.75, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.103, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.015)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.015, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.014, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0185, y = 0.013, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

# figure_GSE72056_BPRNACan_EpiDISH <- ggarrange(p_GSE72056_BPRNACan_EpiDISH[[1]], p_GSE72056_BPRNACan_EpiDISH[[2]], p_GSE72056_BPRNACan_EpiDISH[[3]], p_GSE72056_BPRNACan_EpiDISH[[4]], p_GSE72056_BPRNACan_EpiDISH[[5]], p_GSE72056_BPRNACan_EpiDISH[[6]], ncol = 3, nrow = 2, labels = "c", font.label = list(size = 20, color = "black"))
# 
# figure_GSE72056_BPRNACan_EpiDISH <- annotate_figure(figure_GSE72056_BPRNACan_EpiDISH, left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Ture cell fractions", color = "black", size = 20))

# 
# 
# 
# 
# # melt_CCLE_TIL10_mel_non_malighant_M <- melt(CCLE_TIL10_mel_non_malighant_M)
# melt_FACS_GSE72056_CCLE_TIL10 <- melt(FACS_GSE72056_CCLE_TIL10)
# 
# melt_CCLE_TIL10_mel_non_malighant_M_FACS <- melt(CCLE_TIL10_mel_non_malighant_M) %>% cbind(melt_FACS_GSE72056_CCLE_TIL10$value, .)
# colnames(melt_CCLE_TIL10_mel_non_malighant_M_FACS) <- c("FACS","samples","cell_type","ALL")
# 
# p_CCLE_TIL10_mel_non_malighant_M_all <- ggplot(melt_CCLE_TIL10_mel_non_malighant_M_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=3) + theme_bw() + scale_color_manual(values = c("cyan1", "red", "green", "darkorange1","deeppink", "blue", "lightsalmon2","coral", "darkgoldenrod1", "darkmagenta", "darkgreen")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.4, y = 0.07, label = paste("R = ", round(cor.test(CCLE_TIL10_mel_non_malighant_M, as.matrix(FACS_GSE72056_CCLE_TIL10))$est,2)), parse = F, size = 8)

```

############## quanTIseq ###################

```{r}
library(immunedeconv)
library(textshape)

GSE72056_quanTIseq = deconvolute(Melanoma_GSE72056_no_malighant, "quantiseq", tumor = TRUE)
GSE72056_quanTIseq_TIL10 <- as.data.frame(t(column_to_rownames(GSE72056_quanTIseq,"cell_type")))
GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10[,7], GSE72056_quanTIseq_TIL10[,8], GSE72056_quanTIseq_TIL10[,2] + GSE72056_quanTIseq_TIL10[,3] + GSE72056_quanTIseq_TIL10[,4], GSE72056_quanTIseq_TIL10[,1], GSE72056_quanTIseq_TIL10[,6],GSE72056_quanTIseq_TIL10[,9])
colnames(GSE72056_quanTIseq_TIL10) <- c("CD4","CD8","Macrophages","B","NK","Tregs")

GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10, Facs_Melanoma_GSE72056[,c(3,4,6,1,7,9)])

colnames(GSE72056_quanTIseq_TIL10) <- c("V","V","V","V","V","V",  "CD4", "CD8", "Macrophages", "B", "NK", "Tregs")

melt_GSE72056_quanTIseq <- list()
rmse <- list()
p_GSE72056_quanTIseq <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE72056_quanTIseq_TIL10[,i], GSE72056_quanTIseq_TIL10[,i + 6])

    melt_GSE72056_quanTIseq[[i]] <- melt(GSE72056_quanTIseq_TIL10[,c(i, i + 6)],  id.vars = colnames(GSE72056_quanTIseq_TIL10)[i], measure.vars = colnames(GSE72056_quanTIseq_TIL10)[i + 6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Macrophages", "B", "NK", "Tregs"),
                   rmse = unlist(rmse))

p_GSE72056_quanTIseq[[1]] <- ggplot(melt_GSE72056_quanTIseq[[1]],aes(x = value, y = V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.163, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.21, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.093, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0335, y = 0.0865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.105, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.016, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[6]] <- ggplot(melt_GSE72056_quanTIseq[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkgreen"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0175, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

# figure_GSE72056_quanTIseq <- ggarrange(p_GSE72056_quanTIseq[[1]], p_GSE72056_quanTIseq[[2]], p_GSE72056_quanTIseq[[3]], p_GSE72056_quanTIseq[[4]], p_GSE72056_quanTIseq[[5]], p_GSE72056_quanTIseq[[6]], ncol = 3, nrow = 2, labels = "c", font.label = list(size = 20, color = "black"))
# 
# figure_GSE72056_quanTIseq <- annotate_figure(figure_GSE72056_quanTIseq, left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Ture cell fractions", color = "black", size = 20))

```

############## MCP-counter ###################

```{r}

GSE72056_MCP_counter = as.data.frame(deconvolute(Melanoma_GSE72056_no_malighant, "mcp_counter"))
GSE72056_MCPcounter <- as.data.frame(t(column_to_rownames(GSE72056_MCP_counter,"cell_type")))

GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter[,2], GSE72056_MCPcounter[,6], GSE72056_MCPcounter[,5],  GSE72056_MCPcounter[,4], GSE72056_MCPcounter[,c(10:11)])

colnames(GSE72056_MCPcounter) <- c("CD8","Macrophages","B","NK", "Endothelial","CAFs")

GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter, Facs_Melanoma_GSE72056[, c(4,6,1,7,5,2)])

colnames(GSE72056_MCPcounter) <- c("V","V","V","V", "V","V", "CD8", "Macrophages", "B", "NK", "Endothelial","CAFs")

melt_GSE72056_MCPcounter <- list()
rmse <- list()
p_GSE72056_MCPcounter <- list()

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE72056_MCPcounter[,i], GSE72056_MCPcounter[,i + 6])

    melt_GSE72056_MCPcounter[[i]] <- melt(GSE72056_MCPcounter[,c(i, i + 6)],  id.vars = colnames(GSE72056_MCPcounter)[i], measure.vars = colnames(GSE72056_MCPcounter)[i + 6])
}

RMSE <- data.frame(cell_type = c("CD8", "Macrophages", "B", "NK", "Endothelial","CAFs"),
                   rmse = unlist(rmse))

p_GSE72056_MCPcounter[[1]] <- ggplot( melt_GSE72056_MCPcounter[[1]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 4.7, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.195, y = 4.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.75, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.042, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,2.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 2.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.35, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 2.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.375, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0165, y = 0.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[5]] <- ggplot(melt_GSE72056_MCPcounter[[5]],aes(x = value, y = V)) + geom_point(colour = c("chartreuse"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.28, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0165, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[6]] <- ggplot(melt_GSE72056_MCPcounter[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkorchid"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.12)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.8, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0242, y = 2.625, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

# figure_GSE72056_MCPcounter <- ggarrange(p_GSE72056_MCPcounter[[1]], p_GSE72056_MCPcounter[[2]], p_GSE72056_MCPcounter[[3]], p_GSE72056_MCPcounter[[4]], p_GSE72056_MCPcounter[[5]], p_GSE72056_MCPcounter[[6]], ncol = 3, nrow = 2, labels = "c", font.label = list(size = 20, color = "black"))
# 
# figure_GSE72056_MCPcounter <- annotate_figure(figure_GSE72056_MCPcounter, left = text_grob("MCP_counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Ture cell fractions", color = "black", size = 20))

```

################# Figure 5 #######################

###################### Lymphocytes Figure_5a_b ###########################

```{r}
###################### Lymphocytes Figure_5a_b ###########################
library(cowplot)

annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow=2,  labels = "a", font.label = list(size = 20, color = "black"))

Fig_5a <- annotate_figure(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, bottom = text_grob("H&E estimate", color = "black", size = 20))

Figure_5b <-

  ggdraw()+ draw_plot(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, x = 0.05, y = 0.5, width = 0.9, height = 0.5)+
    draw_plot(All_Methods_TCGA_LUAD_HE, x=0, y= 0, width = 1, height = 0.5) + 
    draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y=c(1, 0.5))
```

###################### Figure_5c ###########################

```{r}
###################### Ludo's Figure_5c ###########################

figure_Thomas_BPRNACan_150 <- ggarrange(Th[[1]],Th[[2]],Th[[3]], ncol = 3, nrow=1, labels = "c", font.label = list(size = 20, color = "black"))

figure_Thomas_BPRNACan_150 <- annotate_figure(figure_Thomas_BPRNACan_150,
               # bottom = text_grob("Gold standard", color = "black", size = 20),
                left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))

figure_Thomas_quanTIseq_M <- ggarrange(Thq[[1]],Thq[[2]],Thq[[3]], ncol = 3, nrow=1, font.label = list(size = 18, color = "black"))

figure_Thomas_quanTIseq_M <- annotate_figure(figure_Thomas_quanTIseq_M,
               # bottom = text_grob("Gold standard", color = "black", size = 20),
                left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90))

figure_Thomas_MCP_counter_M <- ggarrange(Thm[[1]],Thm[[2]],Thm[[3]], ncol = 3, nrow=1, font.label = list(size = 18, color = "black"))

figure_Thomas_MCP_counter_M <- annotate_figure(figure_Thomas_MCP_counter_M,
               # bottom = text_grob("Gold standard", color = "black", size = 20),
                left = text_grob("MCP-counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))

 Mix_figure_BPRNACan_quanTIseq_M_MCP_counter <- ggarrange(figure_Thomas_BPRNACan_150, figure_Thomas_quanTIseq_M, figure_Thomas_MCP_counter_M,ncol = 1, nrow=3)

Figure_5c <- annotate_figure(Mix_figure_BPRNACan_quanTIseq_M_MCP_counter,
                 bottom = text_grob("Gold standard", color = "black", size = 20))

```

###################### scRNA-seq melanoma Figure_5d ###########################

```{r}
###################### scRNAseq ###########################
################ BPRNAseq #######################

p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.85, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.085, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.65, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.084, y = 0.53, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.015)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.015, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0125, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0138, y = 0.010, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

figure_GSE72056_BPRNACan_EpiDISH_c <- ggarrange(p_GSE72056_BPRNACan_EpiDISH[[3]], p_GSE72056_BPRNACan_EpiDISH[[4]], p_GSE72056_BPRNACan_EpiDISH[[5]], p_GSE72056_BPRNACan_EpiDISH[[6]], ncol = 2, nrow = 2, labels = "d", font.label = list(size = 20, color = "black"))

figure_GSE72056_BPRNACan_EpiDISH_c <- annotate_figure(figure_GSE72056_BPRNACan_EpiDISH_c, left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))

############### quanTIseq #######################

p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.85, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.085, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.168, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.078, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.168, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.013, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

figure_GSE72056_quanTIseq_c <- ggarrange(p_GSE72056_quanTIseq[[2]], p_GSE72056_quanTIseq[[3]], p_GSE72056_quanTIseq[[4]], p_GSE72056_quanTIseq[[5]], ncol = 2, nrow = 2, font.label = list(size = 20, color = "black"))

figure_GSE72056_quanTIseq_c <- annotate_figure(figure_GSE72056_quanTIseq_c, left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90))

################ MCP-counter #######################

p_GSE72056_MCPcounter[[1]] <- ggplot( melt_GSE72056_MCPcounter[[1]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 6, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 5.15, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.161, y = 4.3, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.692, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0325, y = 0.575, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.6, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 2.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.435, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.013, y = 0.37, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

figure_GSE72056_MCPcounter_c <- ggarrange(p_GSE72056_MCPcounter[[1]], p_GSE72056_MCPcounter[[2]], p_GSE72056_MCPcounter[[3]], p_GSE72056_MCPcounter[[4]], ncol = 2, nrow = 2, font.label = list(size = 20, color = "black"))

figure_GSE72056_MCPcounter_c <- annotate_figure(figure_GSE72056_MCPcounter_c, left = text_grob("MCP_counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Cell fraction estimates", color = "black", size = 20))

figure5d <- annotate_figure(ggarrange(figure_GSE72056_BPRNACan_EpiDISH_c, figure_GSE72056_quanTIseq_c, figure_GSE72056_MCPcounter_c, ncol = 1, nrow = 3, font.label = list(size = 20, color = "black")), bottom = text_grob("Cell fraction estimates", color = "black", size = 20))

```

############################ Start Figure S5 ############################

##########  RNAseq TCGA-LUAD with previous tumor purity methods ############

############## CCLE_TIL10 and BPRNACan ###################

```{r}

load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S5/Figure_S5.RData")

out.l <- epidish(TCGA_LUADRNAseq_TumorPurity_Aran, CCLE_TIL10, "RPC", maxit = 100)
TCGA_LUAD_RNAseq_CCLE_TIL10 <- data.frame(out.l$estF)
TCGA_LUAD_RNAseq_CCLE_TIL10<-as.data.frame(cbind( TCGA_LUAD_RNAseq_CCLE_TIL10$Cancer.cells, Facs_LUAD_Aran$ABSOLUTE,  Facs_LUAD_Aran$ESTIMATE, Facs_LUAD_Aran$LUMP, Facs_LUAD_Aran$IHC))
colnames(TCGA_LUAD_RNAseq_CCLE_TIL10) <- c("CCLE_TIL10", "ABSOLUTE", "ESTIMATE","LUMP","IHC")

melt_CCLE_TIL10 <- melt(TCGA_LUAD_RNAseq_CCLE_TIL10,  id.vars = "CCLE_TIL10", measure.vars = c("ABSOLUTE", "ESTIMATE","LUMP","IHC"))

p_CCLE_TIL10 <- ggplot(melt_CCLE_TIL10,aes(x=value, y=CCLE_TIL10)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = "CCLE_TIL10 estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.86, size = 6) + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + labs(tag = "a")

```

########### BPRNACan ####################

```{r}

out.l <- epidish(TCGA_LUADRNAseq_TumorPurity_Aran, BPRNACan, "RPC", maxit = 100)
TCGA_LUAD_RNAseq_BPRNACan_150 <- data.frame(out.l$estF)
TCGA_LUAD_RNAseq_BPRNACan_150<-as.data.frame(cbind(TCGA_LUAD_RNAseq_BPRNACan_150$cancer, Facs_LUAD_Aran$ABSOLUTE, Facs_LUAD_Aran$ESTIMATE,Facs_LUAD_Aran$LUMP,Facs_LUAD_Aran$IHC))
colnames(TCGA_LUAD_RNAseq_BPRNACan_150) <- c("BPRNACan", "ABSOLUTE", "ESTIMATE","LUMP","IHC")

melt_BPRNACan <- melt(TCGA_LUAD_RNAseq_BPRNACan_150,  id.vars = "BPRNACan", measure.vars = c("ABSOLUTE", "ESTIMATE","LUMP","IHC"))

p_BPRNACan <- ggplot(melt_BPRNACan,aes(x=value, y=BPRNACan)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0.8,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor( aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0.5, label.y = 0.83, size = 6) + stat_cor( aes(label = paste(..p.label..)), label.x = 0.5, label.y = 0.81, size = 6) + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + labs(tag = "b")

```

############################ Figure S5 ############################

```{r}

Figure_S5 <- ggarrange(p_CCLE_TIL10, p_BPRNACan, ncol = 1, nrow=2, font.label = list(size = 20, color = "black"))

Figure_S5 <- annotate_figure(Figure_S5,
                bottom = text_grob("Method purity estimate", color = "black", size = 20))

```

############################ Start Figure S6 #################################### 
############ Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)

### silico_1700

```{r}
load("~/deconvolution/Final methylation paper/figure/Figure_S6/Figure_S6.RData")

library(dplyr)

melt_silico_1700 <- melt(silico_1700)

melt_silico_1700_Pvalue <- melt(silico_1700_Pvalue)

merge_melt_silico_1700 <- cbind(melt_silico_1700, melt_silico_1700_Pvalue) %>% .[,-3]

melt_merge_melt_silico_1700 <- merge_melt_silico_1700 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_melt_silico_1700$new_Var2 <- rownames(silico_1700_Pvalue)
melt_merge_melt_silico_1700$new_Var2 <- factor(melt_merge_melt_silico_1700$new_Var2, levels = unique(melt_merge_melt_silico_1700$new_Var2))

silico_1700_figure <- ggplot(melt_merge_melt_silico_1700, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("1700 simulated RNA-seq data sets (ID: 6)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

Figure_S6a <- ggarrange(silico_1700_figure, ncol = 1, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))

```

### LUAD H&E RNAseq ###

```{r}

melt_TCGA_LUAD_Lymphocytes_RNAseq <- melt(TCGA_LUAD_Lymphocytes_RNAseq)

melt_TCGA_LUAD_Lymphocytes_RNAseq_Pvalue <- melt(TCGA_LUAD_Lymphocytes_RNAseq_Pvalue)

merge_TCGA_LUAD_Lymphocytes_RNAseq <- cbind(melt_TCGA_LUAD_Lymphocytes_RNAseq, melt_TCGA_LUAD_Lymphocytes_RNAseq_Pvalue) %>% .[,-3]

melt_merge_TCGA_LUAD_Lymphocytes_RNAseq <- merge_TCGA_LUAD_Lymphocytes_RNAseq %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_TCGA_LUAD_Lymphocytes_RNAseq$new_Var2 <- rownames(TCGA_LUAD_Lymphocytes_RNAseq_Pvalue)
melt_merge_TCGA_LUAD_Lymphocytes_RNAseq$new_Var2 <- factor(melt_merge_TCGA_LUAD_Lymphocytes_RNAseq$new_Var2, levels = unique(melt_merge_TCGA_LUAD_Lymphocytes_RNAseq$new_Var2))

TCGA_LUAD_Lymphocytes_RNAseq_figure <- ggplot(melt_merge_TCGA_LUAD_Lymphocytes_RNAseq, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("H&E stained (ID: 4)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

Figure_S6b <- ggarrange(TCGA_LUAD_Lymphocytes_RNAseq_figure, ncol = 1, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"))
```

### Melanoma_GSE72056 ###

```{r}

melt_Melanoma_GSE72056 <- melt(Melanoma_GSE72056)

melt_Melanoma_GSE72056_Pvalue <- melt(Melanoma_GSE72056_Pvalue)

merge_Melanoma_GSE72056 <- cbind(melt_Melanoma_GSE72056, melt_Melanoma_GSE72056_Pvalue) %>% .[,-3]

melt_merge_Melanoma_GSE72056 <- merge_Melanoma_GSE72056 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_Melanoma_GSE72056$new_Var2 <- rownames(Melanoma_GSE72056)
melt_merge_Melanoma_GSE72056$new_Var2 <- factor(melt_merge_Melanoma_GSE72056$new_Var2, levels = unique(melt_merge_Melanoma_GSE72056$new_Var2))

Melanoma_GSE72056_figure <- ggplot(melt_merge_Melanoma_GSE72056, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

Figure_S6c <- ggarrange(Melanoma_GSE72056_figure, ncol = 1, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"))

```

### Melanoma_GSE93722 ###

```{r}

melt_Melanoma_GSE93722 <- melt(Melanoma_GSE93722)

melt_Melanoma_GSE93722_Pvalue <- melt(Melanoma_GSE93722_Pvalue)

merge_Melanoma_GSE93722 <- cbind(melt_Melanoma_GSE93722, melt_Melanoma_GSE93722_Pvalue) %>% .[,-3]

melt_merge_Melanoma_GSE93722 <- merge_Melanoma_GSE93722 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_Melanoma_GSE93722$new_Var2 <- rownames(Melanoma_GSE93722)
melt_merge_Melanoma_GSE93722$new_Var2 <- factor(melt_merge_Melanoma_GSE93722$new_Var2, levels = unique(melt_merge_Melanoma_GSE93722$new_Var2))

Melanoma_GSE93722_figure <- ggplot(melt_merge_Melanoma_GSE93722, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 malignant melanoma (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

Figure_S6d <- ggarrange(Melanoma_GSE93722_figure, ncol = 1, nrow = 1, labels = "d", font.label = list(size = 20, color = "black"))

```

### 2021-06-11 Paper_Figure_code.Rmd
code_for_figures

@@
 melt_merge_melt_silico_1700 <- merge_melt_silico_1700 %>%
-    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
+    mutate(text = case_when(  
         is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
@@
         value.1 >= 0.05 ~ paste(value, "\n"),
-        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
+        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
         value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
@@
     geom_text(aes(label=text),col ="black",size = 5) +
-    theme_minimal() + # 不要背景
-    theme(axis.title.x=element_blank(), # 去掉 title
-          axis.ticks.x=element_blank(), # 去掉x 轴
-          axis.title.y=element_blank(), # 去掉 y 轴
+    theme_minimal() + 
+    theme(axis.title.x=element_blank(),
+          axis.ticks.x=element_blank(), 
+          axis.title.y=element_blank(), 
           legend.title=element_text(size = 14),
           legend.text=element_text(size = 14),
-          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
+          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
           axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("1700 simulated RNA-seq data sets (ID: 6)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
@@
 melt_merge_TCGA_LUAD_Lymphocytes_RNAseq <- merge_TCGA_LUAD_Lymphocytes_RNAseq %>%
-    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
+    mutate(text = case_when(  
         is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
@@
     geom_text(aes(label=text),col ="black",size = 5) +
-    theme_minimal() + # 不要背景
-    theme(axis.title.x=element_blank(), # 去掉 title
-          axis.ticks.x=element_blank(), # 去掉x 轴
-          axis.title.y=element_blank(), # 去掉 y 轴
+    theme_minimal() + 
+    theme(axis.title.x=element_blank(), 
+          axis.ticks.x=element_blank(), 
+          axis.title.y=element_blank(), 
           legend.title=element_text(size = 14),
           legend.text=element_text(size = 14),
-          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
+          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
           axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("H&E stained (ID: 4)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
@@
 melt_merge_Melanoma_GSE72056 <- merge_Melanoma_GSE72056 %>%
-    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
+    mutate(text = case_when(  
         is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
@@
     geom_text(aes(label=text),col ="black",size = 5) +
-    theme_minimal() + # 不要背景
-    theme(axis.title.x=element_blank(), # 去掉 title
-          axis.ticks.x=element_blank(), # 去掉x 轴
-          axis.title.y=element_blank(), # 去掉 y 轴
+    theme_minimal() + 
+    theme(axis.title.x=element_blank(),
+          axis.ticks.x=element_blank(), 
+          axis.title.y=element_blank(), 
           legend.title=element_text(size = 14),
           legend.text=element_text(size = 14),
-          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
+          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
           axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
@@
 melt_merge_Melanoma_GSE93722 <- merge_Melanoma_GSE93722 %>%
-    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
+    mutate(text = case_when(  
         is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
@@
     geom_text(aes(label=text),col ="black",size = 5) +
-    theme_minimal() + # 不要背景
-    theme(axis.title.x=element_blank(), # 去掉 title
-          axis.ticks.x=element_blank(), # 去掉x 轴
-          axis.title.y=element_blank(), # 去掉 y 轴
+    theme_minimal() + 
+    theme(axis.title.x=element_blank(), 
+          axis.ticks.x=element_blank(), 
+          axis.title.y=element_blank(), 
           legend.title=element_text(size = 14),
           legend.text=element_text(size = 14),
-          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
+          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
           axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 malignant melanoma (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

### 2021-07-26 Paper_Figure_code.Rmd
Updates
Removes legend background on Figure 3
Figures are properly labelled in the code
Add titles for better navigation
Other things probably

@@
 output: html_notebook
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-################ Start Figure 2 and Figure S1-S2################
+# Start Figure 3 and Figure S1-S2
 
@@
 
-load("~/deconvolution/Final methylation paper/figure/Figure2 and S1_S2/Figure2_RawData.RData")
+load("~/Documents/Ting_paper/Code/all_figures/Figure2 and S1_S2/Figure2_RawData.RData")
 
 out.l <- epidish(GSE132203_100, BPmet, "RPC", maxit = 100)
-GSE132203_100_BPmet <- data.frame(out.l$estF[,c(2,3,4,1,6,5)])
+GSE132203_100_BPmet <- data.frame(out.l$estF[, c(2, 3, 4, 1, 6, 5)])
 
@@
 melt_GSE132203_100_BPmet <- melt(GSE132203_100_BPmet) %>% cbind(melt_FACS_GSE132203_100$value, .)
-colnames(melt_GSE132203_100_BPmet) <- c("FACS","cell_type","ALL")
-
-p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
-
-p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPmet") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
+colnames(melt_GSE132203_100_BPmet) <- c("FACS", "cell_type", "ALL")
+
+p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
+
+p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"BPmet") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
 
@@
 
-colnames(GSE132203_100_BPmet)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK","Neu")
+colnames(GSE132203_100_BPmet) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE132203_100_BPmet[,i], FACS_GSE132203_100[,i])
-
-    melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[,c(i, i+6)],  id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i+6])
+  rmse[[i]] <- rmse(GSE132203_100_BPmet[, i], FACS_GSE132203_100[, i])
+
+  melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[, c(i, i + 6)], id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-p_GSE132203_100_BPmet[[1]] <-  ggplot(melt_GSE132203_100_BPmet[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL ) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.42, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet[[3]] <-  ggplot(melt_GSE132203_100_BPmet[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.248, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet[[6]] <-ggplot(melt_GSE132203_100_BPmet[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.82, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]],p_GSE132203_100_BPmet[[2]],p_GSE132203_100_BPmet[[3]],p_GSE132203_100_BPmet[[4]],p_GSE132203_100_BPmet[[5]],p_GSE132203_100_BPmet[[6]], ncol = 2, nrow=3)
-
-figure_GSE132203_100_BPmet_each_together <- ggarrange(p_GSE132203_100_BPmet_all, p_GSE132203_100_BPmet_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+p_GSE132203_100_BPmet[[1]] <- ggplot(melt_GSE132203_100_BPmet[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.42, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet[[3]] <- ggplot(melt_GSE132203_100_BPmet[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.248, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet[[6]] <- ggplot(melt_GSE132203_100_BPmet[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.82, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]], p_GSE132203_100_BPmet[[2]], p_GSE132203_100_BPmet[[3]], p_GSE132203_100_BPmet[[4]], p_GSE132203_100_BPmet[[5]], p_GSE132203_100_BPmet[[6]], ncol = 2, nrow = 3)
+
+figure_GSE132203_100_BPmet_each_together <- ggarrange(p_GSE132203_100_BPmet_all, p_GSE132203_100_BPmet_each, ncol = 2, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE132203_100_BPmet_each_together <- annotate_figure(figure_GSE132203_100_BPmet_each_together, left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))
-
 ```
@@
 
-GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[,3] + out.l$estF[,10], out.l$estF[,5], out.l$estF[,1], out.l$estF[,2], out.l$estF[,4], out.l$estF[,9]))
+GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[, 3] + out.l$estF[, 10], out.l$estF[, 5], out.l$estF[, 1], out.l$estF[, 2], out.l$estF[, 4], out.l$estF[, 9]))
 
@@
 melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB) %>% cbind(melt_FACS_GSE132203_100$value, .)
-colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS","cell_type","MethylCIBERSORT")
-
-p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
-
-p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "MethylCIBERSORT") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, labels =NULL, breaks = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
+colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS", "cell_type", "MethylCIBERSORT")
+
+p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
+
+p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"MethylCIBERSORT") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, labels = NULL, breaks = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
 #### each cell types
@@
 
-colnames(GSE132203_100_MethylCIBERSORT_WB)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK", "Neu")
+colnames(GSE132203_100_MethylCIBERSORT_WB) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[,i], GSE132203_100_MethylCIBERSORT_WB[,i+6])
-
-    melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[,c(i, i+6)],  id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i+6])
+  rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[, i], GSE132203_100_MethylCIBERSORT_WB[, i + 6])
+
+  melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[, c(i, i + 6)], id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.245, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.335, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.335, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.077, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT[[5]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT[[6]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.825, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.26, y = 0.685, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_MethylCIBERSORT_each <- ggarrange(p_GSE132203_100_MethylCIBERSORT[[1]],p_GSE132203_100_MethylCIBERSORT[[2]],p_GSE132203_100_MethylCIBERSORT[[3]],p_GSE132203_100_MethylCIBERSORT[[4]],p_GSE132203_100_MethylCIBERSORT[[5]], p_GSE132203_100_MethylCIBERSORT[[6]], ncol = 2, nrow=3)
-
-figure_GSE132203_100_MethylCIBERSORT_together <- ggarrange(p_GSE132203_100_MethylCIBERSORT_WB_all, p_GSE132203_100_MethylCIBERSORT_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.245, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.077, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT[[5]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT[[6]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.825, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.26, y = 0.685, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_MethylCIBERSORT_each <- ggarrange(p_GSE132203_100_MethylCIBERSORT[[1]], p_GSE132203_100_MethylCIBERSORT[[2]], p_GSE132203_100_MethylCIBERSORT[[3]], p_GSE132203_100_MethylCIBERSORT[[4]], p_GSE132203_100_MethylCIBERSORT[[5]], p_GSE132203_100_MethylCIBERSORT[[6]], ncol = 2, nrow = 3)
+
+figure_GSE132203_100_MethylCIBERSORT_together <- ggarrange(p_GSE132203_100_MethylCIBERSORT_WB_all, p_GSE132203_100_MethylCIBERSORT_each, ncol = 2, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE132203_100_MethylCIBERSORT_together <- annotate_figure(figure_GSE132203_100_MethylCIBERSORT_together, left = text_grob("MethylCIBERSORT estimate", color = "black", size = 20, rot = 90))
-
 ```
@@
 out.l <- epidish(GSE132203_100, centDHSbloodDMC.m, "RPC", maxit = 100)
-GSE132203_100_DHS <- data.frame(out.l$estF[,c(3,4,5,1,2,6)])
+GSE132203_100_DHS <- data.frame(out.l$estF[, c(3, 4, 5, 1, 2, 6)])
 colnames(GSE132203_100_DHS) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")
 
-#melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS)
+# melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS)
 
 melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS) %>% cbind(melt_FACS_GSE132203_100$value, .)
-colnames(melt_GSE132203_100_DHS) <- c("FACS","cell_type","DHS")
-
-p_melt_GSE132203_100_DHS_all <- ggplot(melt_GSE132203_100_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2,6)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
-
-p_melt_GSE132203_100_DHS_all_longly <- ggplot(melt_GSE132203_100_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "DHS") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL,labels =NULL, breaks = NULL ) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2,6)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
+colnames(melt_GSE132203_100_DHS) <- c("FACS", "cell_type", "DHS")
+
+p_melt_GSE132203_100_DHS_all <- ggplot(melt_GSE132203_100_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 4, 5, 1, 2, 6)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
+
+p_melt_GSE132203_100_DHS_all_longly <- ggplot(melt_GSE132203_100_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"DHS") +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, labels = NULL, breaks = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 4, 5, 1, 2, 6)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
 
@@
 
-colnames(GSE132203_100_DHS)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK", "Neu")
+colnames(GSE132203_100_DHS) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE132203_100_DHS[,i], GSE132203_100_DHS[,i+6])
-
-    melt_GSE132203_100_DHS[[i]] <- melt(GSE132203_100_DHS[,c(i, i+6)],  id.vars = colnames(GSE132203_100_DHS)[i], measure.vars = colnames(GSE132203_100_DHS)[i+6])
+  rmse[[i]] <- rmse(GSE132203_100_DHS[, i], GSE132203_100_DHS[, i + 6])
+
+  melt_GSE132203_100_DHS[[i]] <- melt(GSE132203_100_DHS[, c(i, i + 6)], id.vars = colnames(GSE132203_100_DHS)[i], measure.vars = colnames(GSE132203_100_DHS)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-p_GSE132203_100_DHS[[1]] <- ggplot(melt_GSE132203_100_DHS[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS[[2]] <- ggplot(melt_GSE132203_100_DHS[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS[[3]] <- ggplot(melt_GSE132203_100_DHS[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS[[4]] <- ggplot(melt_GSE132203_100_DHS[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS[[5]] <- ggplot(melt_GSE132203_100_DHS[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.039, y = 0.215, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS[[6]] <-ggplot(melt_GSE132203_100_DHS[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.925, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.253, y = 0.78, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-p_GSE132203_100_DHS_each <- ggarrange(p_GSE132203_100_DHS[[1]],p_GSE132203_100_DHS[[2]],p_GSE132203_100_DHS[[3]],p_GSE132203_100_DHS[[4]],p_GSE132203_100_DHS[[5]], p_GSE132203_100_DHS[[6]], ncol = 2, nrow = 3)
-
-figure_GSE132203_100_DHS_all_together <- ggarrange(p_melt_GSE132203_100_DHS_all, p_GSE132203_100_DHS_each, ncol = 2, nrow=1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+p_GSE132203_100_DHS[[1]] <- ggplot(melt_GSE132203_100_DHS[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS[[2]] <- ggplot(melt_GSE132203_100_DHS[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS[[3]] <- ggplot(melt_GSE132203_100_DHS[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0776, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS[[4]] <- ggplot(melt_GSE132203_100_DHS[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS[[5]] <- ggplot(melt_GSE132203_100_DHS[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.255, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.039, y = 0.215, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS[[6]] <- ggplot(melt_GSE132203_100_DHS[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1.1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1.1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.925, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.253, y = 0.78, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+p_GSE132203_100_DHS_each <- ggarrange(p_GSE132203_100_DHS[[1]], p_GSE132203_100_DHS[[2]], p_GSE132203_100_DHS[[3]], p_GSE132203_100_DHS[[4]], p_GSE132203_100_DHS[[5]], p_GSE132203_100_DHS[[6]], ncol = 2, nrow = 3)
+
+figure_GSE132203_100_DHS_all_together <- ggarrange(p_melt_GSE132203_100_DHS_all, p_GSE132203_100_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE132203_100_DHS_all_together <- annotate_figure(figure_GSE132203_100_DHS_all_together, left = text_grob("DHS estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))
-
 ```
@@
 out.l <- epidish(GSE77797_six, BPmet, "RPC", maxit = 100)
-GSE77797_six_BPmet <- data.frame(out.l$estF[,c(2,3,4,1,6)])
-#melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet)
-melt_facs_GSE77797_six <- melt(facs_GSE77797_six[,-6])
+GSE77797_six_BPmet <- data.frame(out.l$estF[, c(2, 3, 4, 1, 6)])
+# melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet)
+melt_facs_GSE77797_six <- melt(facs_GSE77797_six[, -6])
 
 melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet) %>% cbind(melt_facs_GSE77797_six$value, .)
-colnames(melt_GSE77797_six_BPmet) <- c("FACS","cell_type","BPmet")
-
-p_GSE77797_six_BPmet_all <- ggplot(melt_GSE77797_six_BPmet,aes(x=FACS, y=BPmet, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
-
-p_GSE77797_six_BPmet_all_longly <- ggplot(melt_GSE77797_six_BPmet,aes(x=FACS, y=BPmet, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPmet") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
+colnames(melt_GSE77797_six_BPmet) <- c("FACS", "cell_type", "BPmet")
+
+p_GSE77797_six_BPmet_all <- ggplot(melt_GSE77797_six_BPmet, aes(x = FACS, y = BPmet, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
+
+p_GSE77797_six_BPmet_all_longly <- ggplot(melt_GSE77797_six_BPmet, aes(x = FACS, y = BPmet, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"BPmet") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
 
@@
 
-GSE77797_six_BPmet <- cbind(GSE77797_six_BPmet, facs_GSE77797_six[,-6])
-
-colnames(GSE77797_six_BPmet)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")
+GSE77797_six_BPmet <- cbind(GSE77797_six_BPmet, facs_GSE77797_six[, -6])
+
+colnames(GSE77797_six_BPmet) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")
 
@@
 for (i in c(1:5)) {
-
-    rmse[[i]] <- rmse(GSE77797_six_BPmet[,i], GSE77797_six_BPmet[,i+5])
-
-    melt_GSE77797_six_BPmet[[i]] <- melt(GSE77797_six_BPmet[,c(i, i+5)],  id.vars = colnames(GSE77797_six_BPmet)[i], measure.vars = colnames(GSE77797_six_BPmet)[i+5])
+  rmse[[i]] <- rmse(GSE77797_six_BPmet[, i], GSE77797_six_BPmet[, i + 5])
+
+  melt_GSE77797_six_BPmet[[i]] <- melt(GSE77797_six_BPmet[, c(i, i + 5)], id.vars = colnames(GSE77797_six_BPmet)[i], measure.vars = colnames(GSE77797_six_BPmet)[i + 5])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
-                   rmse = unlist(rmse))
-
-G6_BPmet[[1]] <- ggplot(melt_GSE77797_six_BPmet[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0, 0.3)) + scale_y_continuous(name = NULL, limits = c(0, 0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.08, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-G6_BPmet[[2]] <- ggplot(melt_GSE77797_six_BPmet[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.25, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.04, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-G6_BPmet[[3]] <- ggplot(melt_GSE77797_six_BPmet[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-G6_BPmet[[4]] <- ggplot(melt_GSE77797_six_BPmet[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-G6_BPmet[[5]] <- ggplot(melt_GSE77797_six_BPmet[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0138, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]],G6_BPmet[[2]],G6_BPmet[[3]],G6_BPmet[[4]],G6_BPmet[[5]], ncol = 2, nrow=3)
-
-figure_GSE77797_six_BPmet_together <- ggarrange(p_GSE77797_six_BPmet_all, p_GSE77797_six_BPmet_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
+  rmse = unlist(rmse)
+)
+
+G6_BPmet[[1]] <- ggplot(melt_GSE77797_six_BPmet[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.255, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.08, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+G6_BPmet[[2]] <- ggplot(melt_GSE77797_six_BPmet[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.25, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.04, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+G6_BPmet[[3]] <- ggplot(melt_GSE77797_six_BPmet[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.09)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.17, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.025, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+G6_BPmet[[4]] <- ggplot(melt_GSE77797_six_BPmet[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.09)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+G6_BPmet[[5]] <- ggplot(melt_GSE77797_six_BPmet[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.05)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0138, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 2, nrow = 3)
+
+figure_GSE77797_six_BPmet_together <- ggarrange(p_GSE77797_six_BPmet_all, p_GSE77797_six_BPmet_each, ncol = 2, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE77797_six_BPmet_together <- annotate_figure(figure_GSE77797_six_BPmet_together, left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))
-
 ```
@@
 out.l <- epidish(GSE77797_six, MethylCIBERSORT_WB, "RPC", maxit = 100)
-GSE77797_six_MethylCIBERSORT_WB <- data.frame(out.l$estF[,c(3,5,1,2,4)])
+GSE77797_six_MethylCIBERSORT_WB <- data.frame(out.l$estF[, c(3, 5, 1, 2, 4)])
 
@@
 melt_GSE77797_six_MethylCIBERSORT_WB <- melt(GSE77797_six_MethylCIBERSORT_WB) %>% cbind(melt_facs_GSE77797_six$value, .)
-colnames(melt_GSE77797_six_MethylCIBERSORT_WB) <- c("FACS","cell_type","MethylCIBERSORT")
-
-p_GSE77797_six_MethylCIBERSORT_all <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
-
-p_GSE77797_six_MethylCIBERSORT_all_longly <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "MethylCIBERSORT") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05,  label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
+colnames(melt_GSE77797_six_MethylCIBERSORT_WB) <- c("FACS", "cell_type", "MethylCIBERSORT")
+
+p_GSE77797_six_MethylCIBERSORT_all <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
+
+p_GSE77797_six_MethylCIBERSORT_all_longly <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"MethylCIBERSORT") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
 #### each cell types
 
-GSE77797_six_MethylCIBERSORT_WB <- cbind(GSE77797_six_MethylCIBERSORT_WB, facs_GSE77797_six[,-6])
-
-colnames(GSE77797_six_MethylCIBERSORT_WB)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")
+GSE77797_six_MethylCIBERSORT_WB <- cbind(GSE77797_six_MethylCIBERSORT_WB, facs_GSE77797_six[, -6])
+
+colnames(GSE77797_six_MethylCIBERSORT_WB) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")
 
@@
 for (i in c(1:5)) {
-
-    rmse[[i]] <- rmse(GSE77797_six_MethylCIBERSORT_WB[,i], GSE77797_six_MethylCIBERSORT_WB[,i+5])
-
-    melt_GSE77797_six_MethylCIBERSORT_WB[[i]] <- melt(GSE77797_six_MethylCIBERSORT_WB[,c(i, i+5)],  id.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i+5])
+  rmse[[i]] <- rmse(GSE77797_six_MethylCIBERSORT_WB[, i], GSE77797_six_MethylCIBERSORT_WB[, i + 5])
+
+  melt_GSE77797_six_MethylCIBERSORT_WB[[i]] <- melt(GSE77797_six_MethylCIBERSORT_WB[, c(i, i + 5)], id.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i + 5])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
-                   rmse = unlist(rmse))
-
-G6_MethylCIBERSORT_WB[[1]] <-  ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0, 0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.255, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.082, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-G6_MethylCIBERSORT_WB[[2]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-G6_MethylCIBERSORT_WB[[3]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-G6_MethylCIBERSORT_WB[[4]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.026, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-G6_MethylCIBERSORT_WB[[5]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0138, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE77797_six_MethylCIBERSORT_WB_each <- ggarrange(G6_MethylCIBERSORT_WB[[1]],G6_MethylCIBERSORT_WB[[2]],G6_MethylCIBERSORT_WB[[3]],G6_MethylCIBERSORT_WB[[4]],G6_MethylCIBERSORT_WB[[5]], ncol = 2, nrow = 3)
-
-figure_GSE77797_six_MethylCIBERSORT_WB_together <- ggarrange(p_GSE77797_six_MethylCIBERSORT_all, p_GSE77797_six_MethylCIBERSORT_WB_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
+  rmse = unlist(rmse)
+)
+
+G6_MethylCIBERSORT_WB[[1]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.255, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.082, y = 0.21, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+G6_MethylCIBERSORT_WB[[2]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.17, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+G6_MethylCIBERSORT_WB[[3]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.09)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+G6_MethylCIBERSORT_WB[[4]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.09)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.026, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+G6_MethylCIBERSORT_WB[[5]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.05)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.17, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0138, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE77797_six_MethylCIBERSORT_WB_each <- ggarrange(G6_MethylCIBERSORT_WB[[1]], G6_MethylCIBERSORT_WB[[2]], G6_MethylCIBERSORT_WB[[3]], G6_MethylCIBERSORT_WB[[4]], G6_MethylCIBERSORT_WB[[5]], ncol = 2, nrow = 3)
+
+figure_GSE77797_six_MethylCIBERSORT_WB_together <- ggarrange(p_GSE77797_six_MethylCIBERSORT_all, p_GSE77797_six_MethylCIBERSORT_WB_each, ncol = 2, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
@@
 out.l <- epidish(GSE77797_six, centDHSbloodDMC.m, "RPC", maxit = 100)
-GSE77797_six_DHS <- data.frame(out.l$estF[,c(3,4,5,1,2)])
+GSE77797_six_DHS <- data.frame(out.l$estF[, c(3, 4, 5, 1, 2)])
 colnames(GSE77797_six_DHS) <- c("CD4", "CD8", "Mono", "B", "NK")
 
-#melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS)
+# melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS)
 
 melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS) %>% cbind(melt_facs_GSE77797_six$value, .)
-colnames(melt_GSE77797_six_DHS) <- c("FACS","cell_type","DHS")
-
-p_GSE77797_six_DHS_all <- ggplot(melt_GSE77797_six_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
-
-p_GSE77797_six_DHS_all_longly <- ggplot(melt_GSE77797_six_DHS,aes(x=FACS, y=DHS, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "DHS") + scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[,c(3,4,5,1,2)], facs_GSE77797_six[,-6])$est,2)), parse = F, size = 8)
+colnames(melt_GSE77797_six_DHS) <- c("FACS", "cell_type", "DHS")
+
+p_GSE77797_six_DHS_all <- ggplot(melt_GSE77797_six_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 4, 5, 1, 2)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
+
+p_GSE77797_six_DHS_all_longly <- ggplot(melt_GSE77797_six_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"DHS") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
+  annotate("text", x = 0.24, y = 0.05, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 4, 5, 1, 2)], facs_GSE77797_six[, -6])$est, 2)), parse = F, size = 8)
 
@@
 
-GSE77797_six_DHS <- cbind(GSE77797_six_DHS, facs_GSE77797_six[,-6])
-
-colnames(GSE77797_six_DHS)<-c("V","V","V","V","V","CD4","CD8","Mono","B","NK")
+GSE77797_six_DHS <- cbind(GSE77797_six_DHS, facs_GSE77797_six[, -6])
+
+colnames(GSE77797_six_DHS) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")
 
@@
 for (i in c(1:5)) {
-
-    rmse[[i]] <- rmse(GSE77797_six_DHS[,i], GSE77797_six_DHS[,i+5])
-
-    melt_GSE77797_six_DHS[[i]] <- melt(GSE77797_six_DHS[,c(i, i+5)],  id.vars = colnames(GSE77797_six_DHS)[i], measure.vars = colnames(GSE77797_six_DHS)[i+5])
+  rmse[[i]] <- rmse(GSE77797_six_DHS[, i], GSE77797_six_DHS[, i + 5])
+
+  melt_GSE77797_six_DHS[[i]] <- melt(GSE77797_six_DHS[, c(i, i + 5)], id.vars = colnames(GSE77797_six_DHS)[i], measure.vars = colnames(GSE77797_six_DHS)[i + 5])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
-                   rmse = unlist(rmse))
-
-G6_DHS[[1]] <- ggplot(melt_GSE77797_six_DHS[[1]],aes(x = value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.34, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.082, y = 0.285, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-G6_DHS[[2]] <- ggplot(melt_GSE77797_six_DHS[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.17, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-G6_DHS[[3]] <- ggplot(melt_GSE77797_six_DHS[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.09)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-G6_DHS[[4]] <- ggplot(melt_GSE77797_six_DHS[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-G6_DHS[[5]] <- ggplot(melt_GSE77797_six_DHS[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.06)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.13, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.017, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]],G6_DHS[[2]],G6_DHS[[3]],G6_DHS[[4]],G6_DHS[[5]], ncol = 2, nrow=3)
-
-figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow=1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
+  rmse = unlist(rmse)
+)
+
+G6_DHS[[1]] <- ggplot(melt_GSE77797_six_DHS[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.34, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.082, y = 0.285, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+G6_DHS[[2]] <- ggplot(melt_GSE77797_six_DHS[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.17, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.043, y = 0.145, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+G6_DHS[[3]] <- ggplot(melt_GSE77797_six_DHS[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.09)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.025, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+G6_DHS[[4]] <- ggplot(melt_GSE77797_six_DHS[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.022, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+G6_DHS[[5]] <- ggplot(melt_GSE77797_six_DHS[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.06)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.13, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.017, y = 0.11, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 2, nrow = 3)
+
+figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
@@
 
-figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together,figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow=3)
+figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together, figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow = 3)
 
@@
 # annotate_figure(figure_GSE77797_six_DHS_each, bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("EpiDISH estimate", color = "black", size = 20, rot = 90))
-
-```
-
-########## Figure 2 and Figure S1-S2  ############
-
-```{r}
-
-figure_GSE132203_100_all_together <- ggarrange(p_GSE132203_100_BPmet_all_longly,p_GSE132203_100_MethylCIBERSORT_WB_all_lonly ,p_melt_GSE132203_100_DHS_all_longly, ncol = 3, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))
-
-figure_GSE77797_all_together <- ggarrange(p_GSE77797_six_BPmet_all_longly,p_GSE77797_six_MethylCIBERSORT_all_longly ,p_GSE77797_six_DHS_all_longly, ncol = 3, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"))
-
-Figure2 <- annotate_figure(ggarrange(figure_GSE132203_100_all_together, figure_GSE77797_all_together, ncol = 1, nrow = 2), bottom = text_grob("Gold standard", color = "black", size = 20))
+```
+
+# Figure 3 and Figure S1-S2
+
+```{r}
+
+figure_GSE132203_100_all_together <- ggarrange(p_GSE132203_100_BPmet_all_longly, p_GSE132203_100_MethylCIBERSORT_WB_all_lonly, p_melt_GSE132203_100_DHS_all_longly, ncol = 3, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))
+
+figure_GSE77797_all_together <- ggarrange(p_GSE77797_six_BPmet_all_longly, p_GSE77797_six_MethylCIBERSORT_all_longly, p_GSE77797_six_DHS_all_longly, ncol = 3, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"))
+
+Figure3 <- annotate_figure(ggarrange(figure_GSE132203_100_all_together, figure_GSE77797_all_together, ncol = 1, nrow = 2), bottom = text_grob("Gold standard", color = "black", size = 20))
 
@@
 # figure_GSE132203_100_DHS_all_together <- annotate_figure(figure_GSE132203_100_DHS_all_together, bottom = text_grob("Gold standard", color = "black", size = 20))
-
-```
-
-############################ Start Figure 3 ############################
+```
+
+# Start Figure 4
 
@@
 
-load("/home/ting/deconvolution/Final methylation paper/figure/Figure3 and S3/Figure3_and_S3.RData")
+load("~/Documents/Ting_paper/Code/all_figures/Figure3 and S3/Figure3_and_S3.RData")
 
@@
 
-TCGA_LUAD_BPmetCan_MethylCIBERSORT<-as.data.frame(cbind(FACS.ABSOLUTE.LUAD.Aran$ABSOLUTE,TCGA_LUAD_BPmetCan$cancer, TCGA_LUAD_MethylCIBERSORT_LUAD$Cancer, FACS.ABSOLUTE.LUAD.Aran$ESTIMATE,FACS.ABSOLUTE.LUAD.Aran$LUMP,FACS.ABSOLUTE.LUAD.Aran$IHC))
-
-colnames(TCGA_LUAD_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC")
-
-melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT<-melt(TCGA_LUAD_BPmetCan_MethylCIBERSORT,  id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC"))
-
-p_TCGA_LUAD_BPmetCan_MethylCIBERSORT <-  ggplot(melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT,aes(x=value, y = ABSOLUTE)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable, ncol = 2) + scale_x_continuous(name = "Method purity estimate", limits = c(0,1)) + scale_y_continuous(name = "ABSOLUTE estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.9, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.68, size = 6) + theme(axis.title.x = element_text(vjust = -0.5)) + theme(axis.title.y = element_text(vjust = 1.5)) #+ labs(tag = "a")
-
+TCGA_LUAD_BPmetCan_MethylCIBERSORT <- as.data.frame(cbind(FACS.ABSOLUTE.LUAD.Aran$ABSOLUTE, TCGA_LUAD_BPmetCan$cancer, TCGA_LUAD_MethylCIBERSORT_LUAD$Cancer, FACS.ABSOLUTE.LUAD.Aran$ESTIMATE, FACS.ABSOLUTE.LUAD.Aran$LUMP, FACS.ABSOLUTE.LUAD.Aran$IHC))
+
+colnames(TCGA_LUAD_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT", "ESTIMATE", "LUMP", "IHC")
+
+melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- melt(TCGA_LUAD_BPmetCan_MethylCIBERSORT, id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT", "ESTIMATE", "LUMP", "IHC"))
+
+p_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- ggplot(melt_TCGA_LUAD_BPmetCan_MethylCIBERSORT, aes(x = value, y = ABSOLUTE)) +
+  geom_point(colour = "brown") +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable, ncol = 2) +
+  scale_x_continuous(name = "Method purity estimate", limits = c(0, 1)) +
+  scale_y_continuous(name = "ABSOLUTE estimate", limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.9, size = 6) +
+  stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.68, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) #+ labs(tag = "a")
 ```
@@
 
-TCGA_BRCA_BPmetCan_MethylCIBERSORT<-as.data.frame(cbind(FACS_Aran_BRCA$ABSOLUTE,TCGA_BRCA_BPmetCan$cancer, TCGA_BRCA_MethylCIBERSORT$Cancer, FACS_Aran_BRCA$ESTIMATE,FACS_Aran_BRCA$LUMP,FACS_Aran_BRCA$IHC))
-
-colnames(TCGA_BRCA_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC")
-
-melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT <- melt(TCGA_BRCA_BPmetCan_MethylCIBERSORT,  id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT","ESTIMATE","LUMP","IHC"))
-
-p_TCGA_BRCA_BPmetCan_MethylCIBERSORT <-  ggplot(melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT,aes(x = value, y = ABSOLUTE)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable, ncol = 2) + scale_x_continuous(name = "Method purity estimate", limits = c(0,1)) + scale_y_continuous(name = "ABSOLUTE estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size = 18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0.6, label.y = 0.1, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0.6, label.y = 0, size = 6) + theme(axis.title.x = element_text(vjust = -0.5)) + theme(axis.title.y = element_text(vjust=1.5)) #+ labs(tag = "b")
-
+TCGA_BRCA_BPmetCan_MethylCIBERSORT <- as.data.frame(cbind(FACS_Aran_BRCA$ABSOLUTE, TCGA_BRCA_BPmetCan$cancer, TCGA_BRCA_MethylCIBERSORT$Cancer, FACS_Aran_BRCA$ESTIMATE, FACS_Aran_BRCA$LUMP, FACS_Aran_BRCA$IHC))
+
+colnames(TCGA_BRCA_BPmetCan_MethylCIBERSORT) <- c("ABSOLUTE", "BPmetCan", "MethylCIBERSORT", "ESTIMATE", "LUMP", "IHC")
+
+melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT <- melt(TCGA_BRCA_BPmetCan_MethylCIBERSORT, id.vars = "ABSOLUTE", measure.vars = c("BPmetCan", "MethylCIBERSORT", "ESTIMATE", "LUMP", "IHC"))
+
+p_TCGA_BRCA_BPmetCan_MethylCIBERSORT <- ggplot(melt_TCGA_BRCA_BPmetCan_MethylCIBERSORT, aes(x = value, y = ABSOLUTE)) +
+  geom_point(colour = "brown") +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable, ncol = 2) +
+  scale_x_continuous(name = "Method purity estimate", limits = c(0, 1)) +
+  scale_y_continuous(name = "ABSOLUTE estimate", limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0.6, label.y = 0.1, size = 6) +
+  stat_cor(aes(label = paste(..p.label..)), label.x = 0.6, label.y = 0, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) #+ labs(tag = "b")
 ```
@@
 
-p_TCGA_LUAD_BPmetCan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.72, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_BPmetCan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_BPmetCan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Neutrophils[-144,]),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
+p_TCGA_LUAD_BPmetCan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_lymphocytes), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("darkslategrey")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"lymphocytes") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.72, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_BPmetCan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Macrophages), aes(x = estimate, y = facs)) +
+  geom_point(colour = c("coral")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Macrophages") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.36, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_BPmetCan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPmetCan_Neutrophils[-144, ]), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("deepskyblue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Neutrophils") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.03)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.36, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
 ```
@@
 
-TCGA_LUAD_MethylCIBERSORT_lymphocytes <- cbind(( TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD4 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD8 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$NK + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$B + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$Treg), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Lymphocytes)
+TCGA_LUAD_MethylCIBERSORT_lymphocytes <- cbind((TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD4 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$CD8 + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$NK + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$B + TCGA_LUAD_MethylCIBERSORT_lymphocytes_deconv$Treg), FACS_TCGA_LUAD_BPmetCan_lymphocytes$Lymphocytes)
 colnames(TCGA_LUAD_MethylCIBERSORT_lymphocytes) <- c("estimate", "facs")
@@
 
-p_TCGA_LUAD_MethylCIBERSORT_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_lymphocytes), aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.72, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_MethylCIBERSORT_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Macrophages),aes(x=facs, y=estimate )) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_MethylCIBERSORT_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.36, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow=1, labels = "c", font.label = list(size = 20, color = "black"))
+p_TCGA_LUAD_MethylCIBERSORT_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_lymphocytes), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("darkslategrey")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"lymphocytes") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.72, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_MethylCIBERSORT_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Macrophages), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("coral")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Macrophages") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.36, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_MethylCIBERSORT_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_MethylCIBERSORT_Neutrophils), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("deepskyblue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Neutrophils") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.03)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.36, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"))
 
@@
 # annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT <- annotate_figure(annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT, bottom = text_grob("H&E estimate", color = "black", size = 20))
-
 ```
@@
 
-########### Figure 3 and Figure S3  #################
+# Figure 4 and Figure S3  
 ```{r}
@@
 
-figure_LUAD_methy <- ggarrange(p_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow =1, labels = "a", font.label = list(size = 20, color = "black"))
-
-figure_TCGA_LUAD_BPmetCan <- ggarrange(p_TCGA_LUAD_BPmetCan_lymphocytes, p_TCGA_LUAD_BPmetCan_Macrophages, p_TCGA_LUAD_BPmetCan_Neutrophils, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))
+figure_LUAD_methy <- ggarrange(p_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))
+
+figure_TCGA_LUAD_BPmetCan <- ggarrange(p_TCGA_LUAD_BPmetCan_lymphocytes, p_TCGA_LUAD_BPmetCan_Macrophages, p_TCGA_LUAD_BPmetCan_Neutrophils, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
 
@@
 
-figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))
+figure_TCGA_LUAD_MethylCIBERSORT <- ggarrange(p_TCGA_LUAD_MethylCIBERSORT_lymphocytes, p_TCGA_LUAD_MethylCIBERSORT_Macrophages, p_TCGA_LUAD_MethylCIBERSORT_Neutrophils, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
 
@@
 
-Figure3 <- ggarrange(figure_LUAD_methy, annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 2)
+Figure4 <- ggarrange(figure_LUAD_methy, annotate_TCGA_LUAD_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 2)
 
@@
 Figure_S3 <- ggarrange(p_TCGA_BRCA_BPmetCan_MethylCIBERSORT, ncol = 1, nrow = 1)
-
-```
-
-############################ Start Figure 4 ############################
+```
+
+# Start Figure 5
 
@@
 
-load("~/deconvolution/Final methylation paper/figure/Figure4/GSE107011_PBMCs_Fig4.RData")
+# load("~/deconvolution/Final methylation paper/figure/Figure4/GSE107011_PBMCs_Fig4.RData")
 
@@
 
-GSE107011_BPRNA_EpiDISH_modify <- cbind(BPRNA_EpiDISH[, c(2,3,4,1,6,5)])
-
-#melt_GSE107011_BPRNA_EpiDISH_modify <- melt(GSE107011_BPRNA_EpiDISH_modify)
-melt_FACS_GSE107011 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
+GSE107011_BPRNA_EpiDISH_modify <- cbind(BPRNA_EpiDISH[, c(2, 3, 4, 1, 6, 5)])
+
+# melt_GSE107011_BPRNA_EpiDISH_modify <- melt(GSE107011_BPRNA_EpiDISH_modify)
+melt_FACS_GSE107011 <- melt(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100)
 
 melt_GSE107011_BPRNA_EpiDISH_modify_FACS <- melt(GSE107011_BPRNA_EpiDISH_modify) %>% cbind(melt_FACS_GSE107011$value, .)
-colnames(melt_GSE107011_BPRNA_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")
-
-p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0, 0.4)) + scale_y_continuous(name = NULL, limits = c(0, 0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]))$est,2)), parse = F, size = 8)
-
-p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPRNA") + scale_x_continuous(name = NULL, limits = NULL) + scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]))$est,2)), parse = F, size = 8)
+colnames(melt_GSE107011_BPRNA_EpiDISH_modify_FACS) <- c("FACS", "cell_type", "ALL")
+
+p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)
+
+p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"BPRNA") +
+  scale_x_continuous(name = NULL, limits = NULL) +
+  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)
 
@@
 
-GSE107011_BPRNA_EpiDISH_modify <- cbind(GSE107011_BPRNA_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
-
-colnames(GSE107011_BPRNA_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")
+GSE107011_BPRNA_EpiDISH_modify <- cbind(GSE107011_BPRNA_EpiDISH_modify, FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100)
+
+colnames(GSE107011_BPRNA_EpiDISH_modify) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE107011_BPRNA_EpiDISH_modify[,i], GSE107011_BPRNA_EpiDISH_modify[,i+6])
-
-    melt_GSE107011_BPRNA_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNA_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i+6])
+  rmse[[i]] <- rmse(GSE107011_BPRNA_EpiDISH_modify[, i], GSE107011_BPRNA_EpiDISH_modify[, i + 6])
+
+  melt_GSE107011_BPRNA_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNA_EpiDISH_modify[, c(i, i + 6)], id.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNA_EpiDISH_modify)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-melt_GSE107011_BPRNA_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0, 0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.74, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.62, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.088, y = 0.52, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNA_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.14, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.117, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.068, y = 0.097, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNA_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.475, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.405, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.088, y = 0.345, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNA_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.475, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.405, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0345, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNA_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.19, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.045, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNA_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.04)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 18, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.038, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.033, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.018, y = 0.0275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+melt_GSE107011_BPRNA_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.74, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.62, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.088, y = 0.52, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNA_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.14, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.117, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.068, y = 0.097, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNA_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.475, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.405, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.088, y = 0.345, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNA_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.475, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.405, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0345, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNA_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.19, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.045, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNA_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.04)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 18, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.038, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.033, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.018, y = 0.0275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
 
 # left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90),
-
-```
-
-############## Figure 4  #####################
+```
+
+# Figure 5
+
 ```{r}
@@
 
-p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]],melt_GSE107011_BPRNA_EpiDISH[[2]],melt_GSE107011_BPRNA_EpiDISH[[3]],melt_GSE107011_BPRNA_EpiDISH[[4]],melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3)
-
-figure_GSE107011_BPRNA_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_GSE107011_BPRNA_EpiDISH_each, ncol = 2, labels = "a", nrow=1, font.label = list(size = 20, color = "black"), widths = c(1,2.5)) #, labels = "b"
-
-Fig_4a <- annotate_figure(figure_GSE107011_BPRNA_EpiDISH_together,  bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90))
+p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]], melt_GSE107011_BPRNA_EpiDISH[[2]], melt_GSE107011_BPRNA_EpiDISH[[3]], melt_GSE107011_BPRNA_EpiDISH[[4]], melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3)
+
+figure_GSE107011_BPRNA_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_GSE107011_BPRNA_EpiDISH_each, ncol = 2, labels = "a", nrow = 1, font.label = list(size = 20, color = "black"), widths = c(1, 2.5)) # , labels = "b"
+
+Fig_5a <- annotate_figure(figure_GSE107011_BPRNA_EpiDISH_together, bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90))
 
@@
 
-merge_melt_PBMCs <- cbind(melt_PBMCs, melt_PBMCs_Pvalue) %>% .[,-3]
+merge_melt_PBMCs <- cbind(melt_PBMCs, melt_PBMCs_Pvalue) %>% .[, -3]
 
@@
     value.1 >= 0.05 ~ paste(value, "\n"),
-        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
+    value.1 >= 0.01 & value.1 < 0.05 ~ paste(value, "\n*"), # round() 只保留两位小数
     value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
-        value.1 < 0.001 ~ paste(value, "\n***")))
+    value.1 < 0.001 ~ paste(value, "\n***")
+  ))
 
@@
 PBMCs_figure <- ggplot(melt_merge_melt_PBMCs, aes(new_Var2, variable)) +
-    geom_tile(aes(fill = value), colour = "grey", size = 1)+
-    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +
-
-    geom_text(aes(label=text),col ="black",size = 8) +
+  geom_tile(aes(fill = value), colour = "grey", size = 1) +
+  scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
+  geom_text(aes(label = text), col = "black", size = 8) +
   theme_minimal() + # 不要背景
-    theme(axis.title.x=element_blank(), # 去掉 title
-          axis.ticks.x=element_blank(), # 去掉x 轴
-          axis.title.y=element_blank(), # 去掉 y 轴
-          legend.title=element_text(size = 20),
-          legend.text=element_text(size = 20),
+  theme(
+    axis.title.x = element_blank(), # 去掉 title
+    axis.ticks.x = element_blank(), # 去掉x 轴
+    axis.title.y = element_blank(), # 去掉 y 轴
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 20),
     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 20, colour = "black"), # 调整x轴文字，字体加粗
-          axis.text.y = element_text(size = 20, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("Pearson correlation") + theme(plot.title = element_text(hjust = 0.5, size = 20 ))
-
-Figure_4b <- ggarrange(PBMCs_figure, ncol = 1, labels = "b", nrow=1, font.label = list(size = 20, color = "black"))
+    axis.text.y = element_text(size = 20, colour = "black")
+  ) +
+  labs(fill = paste0("Correlation")) +
+  ggtitle("Pearson correlation") +
+  theme(plot.title = element_text(hjust = 0.5, size = 20))
+
+Figure_5b <- ggarrange(PBMCs_figure, ncol = 1, labels = "b", nrow = 1, font.label = list(size = 20, color = "black"))
 
@@
 # ggarrange(PBMCs_figure, labels = "b", nrow=1, ncol = 1, font.label = list(size = 20, color = "black"), widths = c(1,1))
-
 ```
@@
 
-GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind((GSE107011_CCLE_TIL10_EpiDISH$T.cells.CD4 + GSE107011_CCLE_TIL10_EpiDISH$Tregs),GSE107011_CCLE_TIL10_EpiDISH[, c(9,5,2,7,6)])
+GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind((GSE107011_CCLE_TIL10_EpiDISH$T.cells.CD4 + GSE107011_CCLE_TIL10_EpiDISH$Tregs), GSE107011_CCLE_TIL10_EpiDISH[, c(9, 5, 2, 7, 6)])
 
@@
 melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify) %>% cbind(melt_FACS_GSE107011$value, .)
-  colnames(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")
-
-p_GSE107011_CCLE_TIL10_EpiDISH_modify_all <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "CCLE_TIL10 estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)
-
-p_GSE107011_CCLE_TIL10_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "CCLE_TIL10") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)
+colnames(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS) <- c("FACS", "cell_type", "ALL")
+
+p_GSE107011_CCLE_TIL10_EpiDISH_modify_all <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = "CCLE_TIL10 estimate", limits = c(0, 0.6)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100))$est, 2)), parse = F, size = 8)
+
+p_GSE107011_CCLE_TIL10_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"CCLE_TIL10") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.3, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_CCLE_TIL10_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100))$est, 2)), parse = F, size = 8)
 
@@
 
-GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind(GSE107011_CCLE_TIL10_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
-
-colnames(GSE107011_CCLE_TIL10_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")
+GSE107011_CCLE_TIL10_EpiDISH_modify <- cbind(GSE107011_CCLE_TIL10_EpiDISH_modify, FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100)
+
+colnames(GSE107011_CCLE_TIL10_EpiDISH_modify) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE107011_CCLE_TIL10_EpiDISH_modify[,i], GSE107011_CCLE_TIL10_EpiDISH_modify[,i+6])
-
-    melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[i]] <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i+6])
+  rmse[[i]] <- rmse(GSE107011_CCLE_TIL10_EpiDISH_modify[, i], GSE107011_CCLE_TIL10_EpiDISH_modify[, i + 6])
+
+  melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[i]] <- melt(GSE107011_CCLE_TIL10_EpiDISH_modify[, c(i, i + 6)], id.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_CCLE_TIL10_EpiDISH_modify)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[1]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[2]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.273, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.08, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[3]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.092, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[4]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.182, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[5]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.182, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_CCLE_TIL10_EpiDISH[[6]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0735, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.0676, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-p_GSE107011_CCLE_TIL10_EpiDISH_each <- ggarrange(melt_GSE107011_CCLE_TIL10_EpiDISH[[1]],melt_GSE107011_CCLE_TIL10_EpiDISH[[2]],melt_GSE107011_CCLE_TIL10_EpiDISH[[3]],melt_GSE107011_CCLE_TIL10_EpiDISH[[4]],melt_GSE107011_CCLE_TIL10_EpiDISH[[5]], melt_GSE107011_CCLE_TIL10_EpiDISH[[6]], ncol = 3, nrow = 2)
-
-figure_GSE107011_CCLE_TIL10_EpiDISH_each_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_GSE107011_CCLE_TIL10_EpiDISH_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[1]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.455, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.105, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[2]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.273, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.08, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[3]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.455, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.092, y = 0.415, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[4]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.182, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[5]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.182, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.055, y = 0.166, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_CCLE_TIL10_EpiDISH[[6]] <- ggplot(melt_GSE107011_CCLE_TIL10_EpiDISH_modify[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.08)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.08, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.0735, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.022, y = 0.0676, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+p_GSE107011_CCLE_TIL10_EpiDISH_each <- ggarrange(melt_GSE107011_CCLE_TIL10_EpiDISH[[1]], melt_GSE107011_CCLE_TIL10_EpiDISH[[2]], melt_GSE107011_CCLE_TIL10_EpiDISH[[3]], melt_GSE107011_CCLE_TIL10_EpiDISH[[4]], melt_GSE107011_CCLE_TIL10_EpiDISH[[5]], melt_GSE107011_CCLE_TIL10_EpiDISH[[6]], ncol = 3, nrow = 2)
+
+figure_GSE107011_CCLE_TIL10_EpiDISH_each_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_GSE107011_CCLE_TIL10_EpiDISH_each, ncol = 2, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE107011_CCLE_TIL10_EpiDISH_each_together <- annotate_figure(figure_GSE107011_CCLE_TIL10_EpiDISH_each_together, left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))
-
 ```
@@
 ```{r}
-GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH[, c(3,4,8,1,10,9)])
+GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH[, c(3, 4, 8, 1, 10, 9)])
 
@@
 melt_GSE107011_BPRNACan_EpiDISH_modify_FACS <- melt(GSE107011_BPRNACan_EpiDISH_modify) %>% cbind(melt_FACS_107$value, .)
-colnames(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS) <- c("FACS","cell_type","ALL")
-
-p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)
-
-p_melt_GSE107011_BPRNACan_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPRNACan") + scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0,0.6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.25, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1,2,4,3,5,6)]/100))$est,2)), parse = F, size = 8)
+colnames(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS) <- c("FACS", "cell_type", "ALL")
+
+p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- p_melt_GSE107011_BPRNACan_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"ALL") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = "BPRNACan estimate", limits = c(0, 0.6)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100))$est, 2)), parse = F, size = 8)
+
+p_melt_GSE107011_BPRNACan_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
+  geom_point(shape = 19, size = 4) +
+  theme_bw() +
+  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"BPRNACan") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = "BPRNACan estimate", limits = c(0, 0.6)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  annotate("text", x = 0.25, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNACan_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100))$est, 2)), parse = F, size = 8)
 
@@
 
-GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH_modify, FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
-
-colnames(GSE107011_BPRNACan_EpiDISH_modify) <- c("V","V","V","V","V","V", "CD4","CD8","Mono","B","NK", "Neu")
+GSE107011_BPRNACan_EpiDISH_modify <- cbind(GSE107011_BPRNACan_EpiDISH_modify, FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)] / 100)
+
+colnames(GSE107011_BPRNACan_EpiDISH_modify) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE107011_BPRNACan_EpiDISH_modify[,i], GSE107011_BPRNACan_EpiDISH_modify[,i+6])
-
-    melt_GSE107011_BPRNACan_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNACan_EpiDISH_modify[,c(i, i+6)],  id.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i+6])
+  rmse[[i]] <- rmse(GSE107011_BPRNACan_EpiDISH_modify[, i], GSE107011_BPRNACan_EpiDISH_modify[, i + 6])
+
+  melt_GSE107011_BPRNACan_EpiDISH_modify[[i]] <- melt(GSE107011_BPRNACan_EpiDISH_modify[, c(i, i + 6)], id.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i], measure.vars = colnames(GSE107011_BPRNACan_EpiDISH_modify)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
-                   rmse = unlist(rmse))
-
-melt_GSE107011_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.138, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0842, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL,limits = c(0,0.4)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.455, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.108, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.276, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.052, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.15)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.15, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.138, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.055, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-melt_GSE107011_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0735, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.022, y = 0.0673, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-p_GSE107011_BPRNACan_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNACan_EpiDISH[[1]],melt_GSE107011_BPRNACan_EpiDISH[[2]],melt_GSE107011_BPRNACan_EpiDISH[[3]],melt_GSE107011_BPRNACan_EpiDISH[[4]],melt_GSE107011_BPRNACan_EpiDISH[[5]], melt_GSE107011_BPRNACan_EpiDISH[[6]], ncol = 3, nrow = 2)
-
-figure_GSE107011_BPRNACan_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, p_GSE107011_BPRNACan_EpiDISH_each, ncol = 2, nrow=1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1,2))
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+melt_GSE107011_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.455, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.105, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.138, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0842, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.455, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.108, y = 0.412, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.276, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.052, y = 0.25, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.15, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.138, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.055, y = 0.125, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+melt_GSE107011_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNACan_EpiDISH_modify[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.08)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.08, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.0735, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.022, y = 0.0673, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+p_GSE107011_BPRNACan_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNACan_EpiDISH[[1]], melt_GSE107011_BPRNACan_EpiDISH[[2]], melt_GSE107011_BPRNACan_EpiDISH[[3]], melt_GSE107011_BPRNACan_EpiDISH[[4]], melt_GSE107011_BPRNACan_EpiDISH[[5]], melt_GSE107011_BPRNACan_EpiDISH[[6]], ncol = 3, nrow = 2)
+
+figure_GSE107011_BPRNACan_EpiDISH_together <- ggarrange(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, p_GSE107011_BPRNACan_EpiDISH_each, ncol = 2, nrow = 1, labels = "b", font.label = list(size = 20, color = "black"), widths = c(1, 2))
 
 figure_GSE107011_BPRNACan_EpiDISH_together <- annotate_figure(figure_GSE107011_BPRNACan_EpiDISH_together, left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))
-
 ```
@@
 ```{r}
-figure_GSE107011_all_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, ncol = 3, nrow=1, font.label = list(size = 20, color = "black"))
+figure_GSE107011_all_together <- ggarrange(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, p_melt_GSE107011_BPRNA_EpiDISH_modify_all, p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
 
@@
 
-############################ Start Figure S4 ############################
+# Start Figure S4
 
@@
 
-load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S4/Silico_1700_RNAseq.RData")
-
-out.l <- epidish(Silico_1700, CCLE_TIL10, "RPC", maxit = 200)
-benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[,c(1,8,9,5,3,4,2,7,6,10,11)])
+# load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S4/Silico_1700_RNAseq.RData")
+
+out.l <- epidish(silico_1700, CCLE_TIL10, "RPC", maxit = 200)
+benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[, c(1, 8, 9, 5, 3, 4, 2, 7, 6, 10, 11)])
 benchmarker_CCLE_TIL10 <- cbind(benchmarker_CCLE_TIL10, Facs_Silico_1700)
 
-colnames(benchmarker_CCLE_TIL10)<-c("V","V","V","V","V","V","V","V","V","V","V","Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs")
+colnames(benchmarker_CCLE_TIL10) <- c("V", "V", "V", "V", "V", "V", "V", "V", "V", "V", "V", "Cancer", "CD4", "CD8", "Mono", "M1", "M2", "B", "NK", "Neu", "Tregs", "DCs")
 
@@
 for (i in c(1:11)) {
-
-    rmse <- rmse(benchmarker_CCLE_TIL10[,i], Facs_Silico_1700[,i])
-    melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[,c(i, i+11)],  id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i+11])
-
-RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs"),
-                   rmse = unlist(rmse))
-
-p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]],aes(x=value, y= V)) + geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1","deeppink","darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL,limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.915, size = 6) + annotate("text", x = 0.22, y = 0.832, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
+  rmse <- rmse(benchmarker_CCLE_TIL10[, i], Facs_Silico_1700[, i])
+  melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[, c(i, i + 11)], id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i + 11])
+
+  RMSE <- data.frame(
+    cell_type = c("Cancer", "CD4", "CD8", "Mono", "M1", "M2", "B", "NK", "Neu", "Tregs", "DCs"),
+    rmse = unlist(rmse)
+  )
+
+  p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]], aes(x = value, y = V)) +
+    geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1", "deeppink", "darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) +
+    theme_bw() +
+    stat_smooth(method = lm, color = "black") +
+    facet_wrap(~variable) +
+    scale_x_continuous(name = NULL, limits = c(0, 1)) +
+    scale_y_continuous(name = NULL, limits = c(0, 1)) +
+    theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+    font("xy.text", size = 16, color = "black") +
+    stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+    stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.915, size = 6) +
+    annotate("text", x = 0.22, y = 0.832, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
 }
@@
 for (i in c(2:11)) {
-
-    rmse <- rmse(benchmarker_CCLE_TIL10[,i], Facs_Silico_1700[,i])
-    melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[,c(i, i+11)],  id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i+11])
-
-    RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu", "Tregs", "DCs"),
-                   rmse = unlist(rmse))
-
-p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]],aes(x=value, y= V)) + geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1","deeppink","darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) + theme_bw() + stat_smooth(method = lm, color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL,limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6) + annotate("text", x = 0.062, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))
+  rmse <- rmse(benchmarker_CCLE_TIL10[, i], Facs_Silico_1700[, i])
+  melt_benchmarker_CCLE_TIL10[[i]] <- melt(benchmarker_CCLE_TIL10[, c(i, i + 11)], id.vars = colnames(benchmarker_CCLE_TIL10)[i], measure.vars = colnames(benchmarker_CCLE_TIL10)[i + 11])
+
+  RMSE <- data.frame(
+    cell_type = c("Cancer", "CD4", "CD8", "Mono", "M1", "M2", "B", "NK", "Neu", "Tregs", "DCs"),
+    rmse = unlist(rmse)
+  )
+
+  p_benchmarker_CCLE_TIL10[[i]] <- ggplot(melt_benchmarker_CCLE_TIL10[[i]], aes(x = value, y = V)) +
+    geom_point(colour = c("cyan1", "red", "green", "blue", "darkorange1", "deeppink", "darkgoldenrod1", "darkmagenta", "deepskyblue", "darkgreen", "midnightblue")[i]) +
+    theme_bw() +
+    stat_smooth(method = lm, color = "black") +
+    facet_wrap(~variable) +
+    scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+    scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+    theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+    font("xy.text", size = 16, color = "black") +
+    stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+    stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+    annotate("text", x = 0.062, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6) +
+    theme(axis.title.x = element_text(vjust = -0.5)) +
+    theme(axis.title.y = element_text(vjust = 1.5))
 }
-
 ```
@@
 out.l <- epidish(Silico_1700, BPRNACan, "RPC", maxit = 200)
-benchmarker_BPRNACan_150 <- data.frame(out.l$estF[,c(2,3,4,8,6,7,1,10,9)])
-benchmarker_BPRNACan_150 <- cbind(benchmarker_BPRNACan_150, Facs_Silico_1700[,-c(10,11)])
-
-colnames(benchmarker_BPRNACan_150)<-c("V","V","V","V","V","V","V","V", "V","Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu")
+benchmarker_BPRNACan_150 <- data.frame(out.l$estF[, c(2, 3, 4, 8, 6, 7, 1, 10, 9)])
+benchmarker_BPRNACan_150 <- cbind(benchmarker_BPRNACan_150, Facs_Silico_1700[, -c(10, 11)])
+
+colnames(benchmarker_BPRNACan_150) <- c("V", "V", "V", "V", "V", "V", "V", "V", "V", "Cancer", "CD4", "CD8", "Mono", "M1", "M2", "B", "NK", "Neu")
 
@@
 for (i in c(1:9)) {
-
-    rmse[[i]] <- rmse(benchmarker_BPRNACan_150[,i], benchmarker_BPRNACan_150[,i+9])
-
-    melt_benchmarker_BPRNACan_150[[i]] <- melt(benchmarker_BPRNACan_150[,c(i, i+9)],  id.vars = colnames(benchmarker_BPRNACan_150)[i], measure.vars = colnames(benchmarker_BPRNACan_150)[i+9])
+  rmse[[i]] <- rmse(benchmarker_BPRNACan_150[, i], benchmarker_BPRNACan_150[, i + 9])
+
+  melt_benchmarker_BPRNACan_150[[i]] <- melt(benchmarker_BPRNACan_150[, c(i, i + 9)], id.vars = colnames(benchmarker_BPRNACan_150)[i], measure.vars = colnames(benchmarker_BPRNACan_150)[i + 9])
 }
 
-RMSE <- data.frame(cell_type = c("Cancer","CD4","CD8","Mono","M1","M2","B","NK", "Neu"),
-                   rmse = unlist(rmse))
-
-bench_BPRNACan[[1]] <- ggplot(melt_benchmarker_BPRNACan_150[[1]],aes(x=value, y= V)) + geom_point(colour = c("cyan1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.935, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.22, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[2]] <- ggplot(melt_benchmarker_BPRNACan_150[[2]],aes(x=value, y= V)) + geom_point(colour = c("red")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text",  x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[3]] <- ggplot(melt_benchmarker_BPRNACan_150[[3]],aes(x=value, y= V)) + geom_point(colour = c("green")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.185, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[4]] <- ggplot(melt_benchmarker_BPRNACan_150[[4]],aes(x=value, y= V)) + geom_point(colour = c("blue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[5]] <- ggplot(melt_benchmarker_BPRNACan_150[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkorange1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.037, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.065, y = 0.034, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[6]] <- ggplot(melt_benchmarker_BPRNACan_150[[6]],aes(x=value, y= V)) + geom_point(colour = c("deeppink")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.4)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 4e-04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 3.7e-04, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.092, y = 3.4e-04, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[7]] <- ggplot(melt_benchmarker_BPRNACan_150[[7]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[7],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[8]] <- ggplot(melt_benchmarker_BPRNACan_150[[8]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.185, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[8],2))))), parse = TRUE, size = 6)
-
-bench_BPRNACan[[9]] <- ggplot(melt_benchmarker_BPRNACan_150[[9]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3) ) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[9],2))))), parse = TRUE, size = 6)
-
-```
-
-################# Figure 4S #######################
-
-```{r}
-
-Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow=4, labels = "a", font.label = list(size = 18, color = "black"))
+RMSE <- data.frame(
+  cell_type = c("Cancer", "CD4", "CD8", "Mono", "M1", "M2", "B", "NK", "Neu"),
+  rmse = unlist(rmse)
+)
+
+bench_BPRNACan[[1]] <- ggplot(melt_benchmarker_BPRNACan_150[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("cyan1")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.935, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.22, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[2]] <- ggplot(melt_benchmarker_BPRNACan_150[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("red")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[3]] <- ggplot(melt_benchmarker_BPRNACan_150[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("green")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.185, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[4]] <- ggplot(melt_benchmarker_BPRNACan_150[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("blue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[5]] <- ggplot(melt_benchmarker_BPRNACan_150[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkorange1")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.04, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.037, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.065, y = 0.034, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[6]] <- ggplot(melt_benchmarker_BPRNACan_150[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("deeppink")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 4e-04, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 3.7e-04, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.092, y = 3.4e-04, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[7]] <- ggplot(melt_benchmarker_BPRNACan_150[[7]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[7], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[8]] <- ggplot(melt_benchmarker_BPRNACan_150[[8]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.185, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.066, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[8], 2))))), parse = TRUE, size = 6)
+
+bench_BPRNACan[[9]] <- ggplot(melt_benchmarker_BPRNACan_150[[9]], aes(x = value, y = V)) +
+  geom_point(colour = c("deepskyblue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.062, y = 0.342, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[9], 2))))), parse = TRUE, size = 6)
+```
+
+# Figure S4
+
+```{r}
+
+Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow = 4, labels = "a", font.label = list(size = 18, color = "black"))
 
@@
   bottom = text_grob("Gold standard", color = "black", size = 20),
-                left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))
-
-Figure_S4b <- ggarrange(bench_BPRNACan[[1]],bench_BPRNACan[[2]],bench_BPRNACan[[3]],bench_BPRNACan[[4]],bench_BPRNACan[[5]],bench_BPRNACan[[6]],bench_BPRNACan[[7]],bench_BPRNACan[[8]],bench_BPRNACan[[9]], ncol = 3, nrow=3,labels = "b", font.label = list(size = 18, color = "black"))
+  left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90)
+)
+
+Figure_S4b <- ggarrange(bench_BPRNACan[[1]], bench_BPRNACan[[2]], bench_BPRNACan[[3]], bench_BPRNACan[[4]], bench_BPRNACan[[5]], bench_BPRNACan[[6]], bench_BPRNACan[[7]], bench_BPRNACan[[8]], bench_BPRNACan[[9]], ncol = 3, nrow = 3, labels = "b", font.label = list(size = 18, color = "black"))
 
@@
   bottom = text_grob("Gold standard", color = "black", size = 20),
-                left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))
-
-```
-
-############################ Start Figure 5 ############################
+  left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90)
+)
+```
+
+# Start Figure 6
 
@@
 
-load("/home/ting/deconvolution/Final methylation paper/figure/figure5/Figure_5.RData")
+load("/home/julien/Documents/Ting_paper/Code/all_figures/figure5/Figure_5.RData")
 
@@
 TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- data.frame(out.l$estF)
-TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[sort(rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv)),]
-TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify),]
+TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[sort(rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv)), ]
+TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv <- TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv[rownames(TCGA_LUAD_CCLE_TIL10_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify), ]
 
@@
 
-p_TCGA_LUAD_CCLE_TIL10_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.46, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_CCLE_TIL10_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_CCLE_TIL10_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.05)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.05, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.046, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-figure_TCGA_LUAD_CCLE_TIL10 <- ggarrange(p_TCGA_LUAD_CCLE_TIL10_lymphocytes, p_TCGA_LUAD_CCLE_TIL10_Macrophages, p_TCGA_LUAD_CCLE_TIL10_Neutrophils, ncol = 3, nrow=1)
+p_TCGA_LUAD_CCLE_TIL10_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_lymphocytes), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("darkslategrey")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Lymphocytes") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.46, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_CCLE_TIL10_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Macrophages), aes(x = estimate, y = facs)) +
+  geom_point(colour = c("coral")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Macrophages") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.8)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_CCLE_TIL10_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_CCLE_TIL10_Neutrophils), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("deepskyblue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Neutrophils") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.03)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.05)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.05, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.046, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+figure_TCGA_LUAD_CCLE_TIL10 <- ggarrange(p_TCGA_LUAD_CCLE_TIL10_lymphocytes, p_TCGA_LUAD_CCLE_TIL10_Macrophages, p_TCGA_LUAD_CCLE_TIL10_Neutrophils, ncol = 3, nrow = 1)
 
 annotate_figure_TCGA_LUAD_CCLE_TIL10 <- annotate_figure(figure_TCGA_LUAD_CCLE_TIL10, left = text_grob("CCLE_TIL10 estimate", color = "black", size = 20, rot = 90))
-
 ```
@@
 TCGA_LUAD_BPRNACan_lymphocytes_deconv <- data.frame(out.l$estF)
-TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[sort(rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv)),]
-TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify),]
+TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[sort(rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv)), ]
+TCGA_LUAD_BPRNACan_lymphocytes_deconv <- TCGA_LUAD_BPRNACan_lymphocytes_deconv[rownames(TCGA_LUAD_BPRNACan_lymphocytes_deconv) %in% rownames(HE_TCGA_LUAD_lymphocytes_modify), ]
 
@@
 
-p_TCGA_LUAD_BPRNACan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_lymphocytes),aes(x = facs, y= estimate)) + geom_point(colour = c("darkslategrey")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Lymphocytes")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.073, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_BPRNACan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Macrophages),aes(x=estimate, y= facs)) + geom_point(colour = c("coral")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Macrophages")+ scale_x_continuous(name = NULL, limits = c(0,0.05)) + scale_y_continuous(name = NULL, limits = c(0, 0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-p_TCGA_LUAD_BPRNACan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Neutrophils),aes(x = facs, y = estimate )) + geom_point(colour = c("deepskyblue")) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "Neutrophils")+ scale_x_continuous(name = NULL, limits = c(0,0.03)) + scale_y_continuous(name = NULL, limits = c(0,0.008)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.008, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0074, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5))
-
-figure_TCGA_LUAD_BPRNACan <- ggarrange(p_TCGA_LUAD_BPRNACan_lymphocytes, p_TCGA_LUAD_BPRNACan_Macrophages, p_TCGA_LUAD_BPRNACan_Neutrophils, ncol = 3, nrow=1,  font.label = list(size = 20, color = "black"))
+p_TCGA_LUAD_BPRNACan_lymphocytes <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_lymphocytes), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("darkslategrey")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Lymphocytes") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.08, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.073, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_BPRNACan_Macrophages <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Macrophages), aes(x = estimate, y = facs)) +
+  geom_point(colour = c("coral")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Macrophages") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.05)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+p_TCGA_LUAD_BPRNACan_Neutrophils <- ggplot(as.data.frame(TCGA_LUAD_BPRNACan_Neutrophils), aes(x = facs, y = estimate)) +
+  geom_point(colour = c("deepskyblue")) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"Neutrophils") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.03)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.008)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.008, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.0074, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5))
+
+figure_TCGA_LUAD_BPRNACan <- ggarrange(p_TCGA_LUAD_BPRNACan_lymphocytes, p_TCGA_LUAD_BPRNACan_Macrophages, p_TCGA_LUAD_BPRNACan_Neutrophils, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
 
@@
 
-annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow=2, labels = "a", font.label = list(size = 20, color = "black"))
+annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow = 2, labels = "a", font.label = list(size = 20, color = "black"))
 
 annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- annotate_figure(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, bottom = text_grob("H&E estimate", color = "black", size = 20))
-
 ```
@@
 out.l <- epidish(Thomas_RNAseq_part, BPRNACan, "RPC", maxit = 100)
-Thomas_RNAseq_BPRNACan_150 <- data.frame(out.l$estF[,c(3,4,10)])
-
-FACS_Thomas_mean_M <- FACS_Thomas_mean[,c(3,4,2)]/100
+Thomas_RNAseq_BPRNACan_150 <- data.frame(out.l$estF[, c(3, 4, 10)])
+
+FACS_Thomas_mean_M <- FACS_Thomas_mean[, c(3, 4, 2)] / 100
 
 Thomas_RNAseq_BPRNACan_150 <- cbind(Thomas_RNAseq_BPRNACan_150, FACS_Thomas_mean_M)
-colnames(Thomas_RNAseq_BPRNACan_150)<-c("V","V","V","CD4","CD8","NK")
+colnames(Thomas_RNAseq_BPRNACan_150) <- c("V", "V", "V", "CD4", "CD8", "NK")
 
@@
 for (i in c(1:3)) {
-
-    rmse[[i]] <- rmse(Thomas_RNAseq_BPRNACan_150[,i], FACS_Thomas_mean_M[,i])
-
-    melt_Thomas_RNAseq_BPRNACan_150[[i]] <- melt(Thomas_RNAseq_BPRNACan_150[,c(i, i+3)],  id.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i], measure.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i+3])
+  rmse[[i]] <- rmse(Thomas_RNAseq_BPRNACan_150[, i], FACS_Thomas_mean_M[, i])
+
+  melt_Thomas_RNAseq_BPRNACan_150[[i]] <- melt(Thomas_RNAseq_BPRNACan_150[, c(i, i + 3)], id.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i], measure.vars = colnames(Thomas_RNAseq_BPRNACan_150)[i + 3])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
-                   rmse = unlist(rmse))
-
-Th[[1]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "CD4")+ scale_x_continuous(name = NULL, limits = c(0,0.18)) + scale_y_continuous(name = NULL, limits = c(0,0.25)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.25, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.235, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.048, y = 0.22, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-Th[[2]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[2]][-9,],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ "CD8")+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.05)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.05, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.047, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.023, y = 0.044, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-Th[[3]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.04)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.04, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0375, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 0.035, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "NK"),
+  rmse = unlist(rmse)
+)
+
+Th[[1]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"CD4") +
+  scale_x_continuous(name = NULL, limits = c(0, 0.18)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.25)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.25, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.235, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.048, y = 0.22, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+Th[[2]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[2]][-9, ], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~"CD8") +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.05)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.05, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.047, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.023, y = 0.044, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+Th[[3]] <- ggplot(melt_Thomas_RNAseq_BPRNACan_150[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.04)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.04, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.0375, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.022, y = 0.035, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
 ```
@@
 
-Thomas_quantiseq = deconvolute(Thomas_RNAseq_part, "quantiseq", tumor = FALSE)
+Thomas_quantiseq <- deconvolute(Thomas_RNAseq_part, "quantiseq", tumor = FALSE)
 
@@
 
-Thomas_quanTIseq_M <- Thomas_quantiseq[,c(7,8,6)]
+Thomas_quanTIseq_M <- Thomas_quantiseq[, c(7, 8, 6)]
 
 Thomas_quanTIseq_M <- cbind(Thomas_quanTIseq_M, FACS_Thomas_mean_M)
-colnames(Thomas_quanTIseq_M)<-c("V","V","V","CD4","CD8","NK")
+colnames(Thomas_quanTIseq_M) <- c("V", "V", "V", "CD4", "CD8", "NK")
 
@@
 for (i in c(1:3)) {
-
-    rmse[[i]] <- rmse(Thomas_quanTIseq_M[,i], FACS_Thomas_mean_M[,i])
-
-    melt_Thomas_quanTIseq_M[[i]] <- melt(Thomas_quanTIseq_M[,c(i, i+3)],  id.vars = colnames(Thomas_quanTIseq_M)[i], measure.vars = colnames(Thomas_quanTIseq_M)[i+3])
+  rmse[[i]] <- rmse(Thomas_quanTIseq_M[, i], FACS_Thomas_mean_M[, i])
+
+  melt_Thomas_quanTIseq_M[[i]] <- melt(Thomas_quanTIseq_M[, c(i, i + 3)], id.vars = colnames(Thomas_quanTIseq_M)[i], measure.vars = colnames(Thomas_quanTIseq_M)[i + 3])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
-                   rmse = unlist(rmse))
-
-Thq[[1]] <- ggplot(melt_Thomas_quanTIseq_M[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.12)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.12, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.112, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.058, y = 0.105, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-Thq[[2]] <- ggplot(melt_Thomas_quanTIseq_M[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.075, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.023, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-Thq[[3]] <-  ggplot(melt_Thomas_quanTIseq_M[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.08)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.08, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.075, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "NK"),
+  rmse = unlist(rmse)
+)
+
+Thq[[1]] <- ggplot(melt_Thomas_quanTIseq_M[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.12)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.12, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.112, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.058, y = 0.105, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+Thq[[2]] <- ggplot(melt_Thomas_quanTIseq_M[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.08)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.08, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.075, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.023, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+Thq[[3]] <- ggplot(melt_Thomas_quanTIseq_M[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.08)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.08, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.075, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.022, y = 0.0705, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
 
@@
 ```{r}
-Thomas_MCP_counter = deconvolute(Thomas_RNAseq_part, "mcp_counter")
+Thomas_MCP_counter <- deconvolute(Thomas_RNAseq_part, "mcp_counter")
 
@@
 
-Thomas_MCP_counter <- Thomas_MCP_counter[,-6]
+Thomas_MCP_counter <- Thomas_MCP_counter[, -6]
 
@@
 
-Thomas_Thomas_MCP_counter_M <- Thomas_MCP_counter[,c(1,2,4)]
-Thomas_Thomas_MCP_counter_M <- cbind((Thomas_Thomas_MCP_counter_M[,1]-Thomas_Thomas_MCP_counter_M[,2]),Thomas_Thomas_MCP_counter_M[,2], Thomas_Thomas_MCP_counter_M[,3])
+Thomas_Thomas_MCP_counter_M <- Thomas_MCP_counter[, c(1, 2, 4)]
+Thomas_Thomas_MCP_counter_M <- cbind((Thomas_Thomas_MCP_counter_M[, 1] - Thomas_Thomas_MCP_counter_M[, 2]), Thomas_Thomas_MCP_counter_M[, 2], Thomas_Thomas_MCP_counter_M[, 3])
 Thomas_Thomas_MCP_counter_M <- pmax(Thomas_Thomas_MCP_counter_M, 0)
@@
 Thomas_Thomas_MCP_counter_M <- cbind(Thomas_Thomas_MCP_counter_M, FACS_Thomas_mean_M)
-colnames(Thomas_Thomas_MCP_counter_M)<-c("V","V","V","CD4","CD8","NK")
+colnames(Thomas_Thomas_MCP_counter_M) <- c("V", "V", "V", "CD4", "CD8", "NK")
 
@@
 
- rmse[[i]] <- rmse(Thomas_Thomas_MCP_counter_M[,i], FACS_Thomas_mean_M[,i])
-
-    melt_Thomas_Thomas_MCP_counter_M[[i]] <- melt(Thomas_Thomas_MCP_counter_M[,c(i, i+3)],  id.vars = colnames(Thomas_Thomas_MCP_counter_M)[i], measure.vars = colnames(Thomas_Thomas_MCP_counter_M)[i+3])
+  rmse[[i]] <- rmse(Thomas_Thomas_MCP_counter_M[, i], FACS_Thomas_mean_M[, i])
+
+  melt_Thomas_Thomas_MCP_counter_M[[i]] <- melt(Thomas_Thomas_MCP_counter_M[, c(i, i + 3)], id.vars = colnames(Thomas_Thomas_MCP_counter_M)[i], measure.vars = colnames(Thomas_Thomas_MCP_counter_M)[i + 3])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8",  "NK"),
-                   rmse = unlist(rmse))
-
-Thm[[1]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[1]], aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 30, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 27.5, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.051, y = 25.5, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-Thm[[2]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 50, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 46, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.024, y = 43, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-Thm[[3]] <-  ggplot(melt_Thomas_Thomas_MCP_counter_M[[3]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 6, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 5.55, size = 6) +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.022, y = 5.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "NK"),
+  rmse = unlist(rmse)
+)
+
+Thm[[1]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 30, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 27.5, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.051, y = 25.5, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+Thm[[2]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 50, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 46, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.024, y = 43, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+Thm[[3]] <- ggplot(melt_Thomas_Thomas_MCP_counter_M[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 6)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 6, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 5.55, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  annotate("text", x = 0.022, y = 5.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
 ```
@@
 
-load("/home/ting/deconvolution/Final methylation paper/RNAseq/melanoma_scRNAseq_GSE72056_and_GSE93722/Two_datasets/Melanoma_GSE72056_RNAseq.RData")
-
 out.l <- epidish(Melanoma_GSE72056_no_malighant, BPRNACan, "RPC", maxit = 100)
-GSE72056_BPRNACan <- data.frame(cbind(out.l$estF[,2:4], out.l$estF[,5] + out.l$estF[,6]+out.l$estF[,7]+out.l$estF[,8],out.l$estF[,1],out.l$estF[,10])) 
-colnames(GSE72056_BPRNACan)[4:6] <- c("Macrophages","B","NK")
-
-GSE72056_BPRNACan_EpiDISH <- cbind(GSE72056_BPRNACan, Facs_Melanoma_GSE72056[,c(10,3,4,6,1,7)])
-
-colnames(GSE72056_BPRNACan_EpiDISH) <- c("V","V","V","V","V","V", "cancer", "CD4", "CD8", "Macrophages", "B", "NK")
+GSE72056_BPRNACan <- data.frame(cbind(out.l$estF[, 2:4], out.l$estF[, 5] + out.l$estF[, 6] + out.l$estF[, 7] + out.l$estF[, 8], out.l$estF[, 1], out.l$estF[, 10]))
+colnames(GSE72056_BPRNACan)[4:6] <- c("Macrophages", "B", "NK")
+
+GSE72056_BPRNACan_EpiDISH <- cbind(GSE72056_BPRNACan, Facs_Melanoma_GSE72056[, c(10, 3, 4, 6, 1, 7)])
+
+colnames(GSE72056_BPRNACan_EpiDISH) <- c("V", "V", "V", "V", "V", "V", "cancer", "CD4", "CD8", "Macrophages", "B", "NK")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE72056_BPRNACan_EpiDISH[,i], GSE72056_BPRNACan_EpiDISH[,i + 6])
-
-    melt_GSE72056_BPRNACan_EpiDISH[[i]] <- melt(GSE72056_BPRNACan_EpiDISH[,c(i, i + 6)],  id.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i], measure.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i + 6])
+  rmse[[i]] <- rmse(GSE72056_BPRNACan_EpiDISH[, i], GSE72056_BPRNACan_EpiDISH[, i + 6])
+
+  melt_GSE72056_BPRNACan_EpiDISH[[i]] <- melt(GSE72056_BPRNACan_EpiDISH[, c(i, i + 6)], id.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i], measure.vars = colnames(GSE72056_BPRNACan_EpiDISH)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("cancer", "CD4", "CD8", "Macrophages", "B", "NK"),
-                   rmse = unlist(rmse))
-
-p_GSE72056_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[1]],aes(x = value, y = V)) + geom_point(colour = c("cyan1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[2]],aes(x = value, y = V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.172, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.093, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0335, y = 0.087, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.75, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.103, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.015)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.015, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.014, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0185, y = 0.013, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
+RMSE <- data.frame(
+  cell_type = c("cancer", "CD4", "CD8", "Macrophages", "B", "NK"),
+  rmse = unlist(rmse)
+)
+
+p_GSE72056_BPRNACan_EpiDISH[[1]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("cyan1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.93, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[2]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.8)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.93, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.172, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.93, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.21, y = 0.87, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.093, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0335, y = 0.087, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.75, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.103, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.015)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.015, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.014, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0185, y = 0.013, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
 
@@
 # p_CCLE_TIL10_mel_non_malighant_M_all <- ggplot(melt_CCLE_TIL10_mel_non_malighant_M_FACS,aes(x = FACS, y = ALL, colour = cell_type)) + geom_point(shape = 19 ,size=3) + theme_bw() + scale_color_manual(values = c("cyan1", "red", "green", "darkorange1","deeppink", "blue", "lightsalmon2","coral", "darkgoldenrod1", "darkmagenta", "darkgreen")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.4, y = 0.07, label = paste("R = ", round(cor.test(CCLE_TIL10_mel_non_malighant_M, as.matrix(FACS_GSE72056_CCLE_TIL10))$est,2)), parse = F, size = 8)
-
 ```
@@
 
-GSE72056_quanTIseq = deconvolute(Melanoma_GSE72056_no_malighant, "quantiseq", tumor = TRUE)
-GSE72056_quanTIseq_TIL10 <- as.data.frame(t(column_to_rownames(GSE72056_quanTIseq,"cell_type")))
-GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10[,7], GSE72056_quanTIseq_TIL10[,8], GSE72056_quanTIseq_TIL10[,2] + GSE72056_quanTIseq_TIL10[,3] + GSE72056_quanTIseq_TIL10[,4], GSE72056_quanTIseq_TIL10[,1], GSE72056_quanTIseq_TIL10[,6],GSE72056_quanTIseq_TIL10[,9])
-colnames(GSE72056_quanTIseq_TIL10) <- c("CD4","CD8","Macrophages","B","NK","Tregs")
-
-GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10, Facs_Melanoma_GSE72056[,c(3,4,6,1,7,9)])
-
-colnames(GSE72056_quanTIseq_TIL10) <- c("V","V","V","V","V","V",  "CD4", "CD8", "Macrophages", "B", "NK", "Tregs")
+GSE72056_quanTIseq <- deconvolute(Melanoma_GSE72056_no_malighant, "quantiseq", tumor = TRUE)
+GSE72056_quanTIseq_TIL10 <- as.data.frame(t(column_to_rownames(GSE72056_quanTIseq, "cell_type")))
+GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10[, 7], GSE72056_quanTIseq_TIL10[, 8], GSE72056_quanTIseq_TIL10[, 2] + GSE72056_quanTIseq_TIL10[, 3] + GSE72056_quanTIseq_TIL10[, 4], GSE72056_quanTIseq_TIL10[, 1], GSE72056_quanTIseq_TIL10[, 6], GSE72056_quanTIseq_TIL10[, 9])
+colnames(GSE72056_quanTIseq_TIL10) <- c("CD4", "CD8", "Macrophages", "B", "NK", "Tregs")
+
+GSE72056_quanTIseq_TIL10 <- cbind(GSE72056_quanTIseq_TIL10, Facs_Melanoma_GSE72056[, c(3, 4, 6, 1, 7, 9)])
+
+colnames(GSE72056_quanTIseq_TIL10) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Macrophages", "B", "NK", "Tregs")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE72056_quanTIseq_TIL10[,i], GSE72056_quanTIseq_TIL10[,i + 6])
-
-    melt_GSE72056_quanTIseq[[i]] <- melt(GSE72056_quanTIseq_TIL10[,c(i, i + 6)],  id.vars = colnames(GSE72056_quanTIseq_TIL10)[i], measure.vars = colnames(GSE72056_quanTIseq_TIL10)[i + 6])
+  rmse[[i]] <- rmse(GSE72056_quanTIseq_TIL10[, i], GSE72056_quanTIseq_TIL10[, i + 6])
+
+  melt_GSE72056_quanTIseq[[i]] <- melt(GSE72056_quanTIseq_TIL10[, c(i, i + 6)], id.vars = colnames(GSE72056_quanTIseq_TIL10)[i], measure.vars = colnames(GSE72056_quanTIseq_TIL10)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD4", "CD8", "Macrophages", "B", "NK", "Tregs"),
-                   rmse = unlist(rmse))
-
-p_GSE72056_quanTIseq[[1]] <- ggplot(melt_GSE72056_quanTIseq[[1]],aes(x = value, y = V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.8)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.37, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.163, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.93, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.21, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.093, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0335, y = 0.0865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.105, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.016, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[6]] <- ggplot(melt_GSE72056_quanTIseq[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkgreen"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.187, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0175, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
+RMSE <- data.frame(
+  cell_type = c("CD4", "CD8", "Macrophages", "B", "NK", "Tregs"),
+  rmse = unlist(rmse)
+)
+
+p_GSE72056_quanTIseq[[1]] <- ggplot(melt_GSE72056_quanTIseq[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("red"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.8)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.37, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.163, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.93, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.21, y = 0.865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.093, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0335, y = 0.0865, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.187, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.105, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.187, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.016, y = 0.173, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[6]] <- ggplot(melt_GSE72056_quanTIseq[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgreen"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.187, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0175, y = 0.17, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
 
@@
 # figure_GSE72056_quanTIseq <- annotate_figure(figure_GSE72056_quanTIseq, left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Ture cell fractions", color = "black", size = 20))
-
 ```
@@
 
-GSE72056_MCP_counter = as.data.frame(deconvolute(Melanoma_GSE72056_no_malighant, "mcp_counter"))
-GSE72056_MCPcounter <- as.data.frame(t(column_to_rownames(GSE72056_MCP_counter,"cell_type")))
-
-GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter[,2], GSE72056_MCPcounter[,6], GSE72056_MCPcounter[,5],  GSE72056_MCPcounter[,4], GSE72056_MCPcounter[,c(10:11)])
-
-colnames(GSE72056_MCPcounter) <- c("CD8","Macrophages","B","NK", "Endothelial","CAFs")
-
-GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter, Facs_Melanoma_GSE72056[, c(4,6,1,7,5,2)])
-
-colnames(GSE72056_MCPcounter) <- c("V","V","V","V", "V","V", "CD8", "Macrophages", "B", "NK", "Endothelial","CAFs")
+GSE72056_MCP_counter <- as.data.frame(deconvolute(Melanoma_GSE72056_no_malighant, "mcp_counter"))
+GSE72056_MCPcounter <- as.data.frame(t(column_to_rownames(GSE72056_MCP_counter, "cell_type")))
+
+GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter[, 2], GSE72056_MCPcounter[, 6], GSE72056_MCPcounter[, 5], GSE72056_MCPcounter[, 4], GSE72056_MCPcounter[, c(10:11)])
+
+colnames(GSE72056_MCPcounter) <- c("CD8", "Macrophages", "B", "NK", "Endothelial", "CAFs")
+
+GSE72056_MCPcounter <- cbind(GSE72056_MCPcounter, Facs_Melanoma_GSE72056[, c(4, 6, 1, 7, 5, 2)])
+
+colnames(GSE72056_MCPcounter) <- c("V", "V", "V", "V", "V", "V", "CD8", "Macrophages", "B", "NK", "Endothelial", "CAFs")
 
@@
 for (i in c(1:6)) {
-
-    rmse[[i]] <- rmse(GSE72056_MCPcounter[,i], GSE72056_MCPcounter[,i + 6])
-
-    melt_GSE72056_MCPcounter[[i]] <- melt(GSE72056_MCPcounter[,c(i, i + 6)],  id.vars = colnames(GSE72056_MCPcounter)[i], measure.vars = colnames(GSE72056_MCPcounter)[i + 6])
+  rmse[[i]] <- rmse(GSE72056_MCPcounter[, i], GSE72056_MCPcounter[, i + 6])
+
+  melt_GSE72056_MCPcounter[[i]] <- melt(GSE72056_MCPcounter[, c(i, i + 6)], id.vars = colnames(GSE72056_MCPcounter)[i], measure.vars = colnames(GSE72056_MCPcounter)[i + 6])
 }
 
-RMSE <- data.frame(cell_type = c("CD8", "Macrophages", "B", "NK", "Endothelial","CAFs"),
-                   rmse = unlist(rmse))
-
-p_GSE72056_MCPcounter[[1]] <- ggplot( melt_GSE72056_MCPcounter[[1]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 4.7, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.195, y = 4.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.75, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.042, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,2.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 2.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.35, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.105, y = 2.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.375, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0165, y = 0.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[5]] <- ggplot(melt_GSE72056_MCPcounter[[5]],aes(x = value, y = V)) + geom_point(colour = c("chartreuse"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.28, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0165, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[6]] <- ggplot(melt_GSE72056_MCPcounter[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkorchid"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.12)) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.8, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0242, y = 2.625, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
+RMSE <- data.frame(
+  cell_type = c("CD8", "Macrophages", "B", "NK", "Endothelial", "CAFs"),
+  rmse = unlist(rmse)
+)
+
+p_GSE72056_MCPcounter[[1]] <- ggplot(melt_GSE72056_MCPcounter[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 4.7, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.195, y = 4.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.75, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.042, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 2.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 2.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 2.35, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.105, y = 2.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.375, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0165, y = 0.35, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[5]] <- ggplot(melt_GSE72056_MCPcounter[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("chartreuse"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.28, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0165, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[6]] <- ggplot(melt_GSE72056_MCPcounter[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkorchid"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.12)) +
+  scale_y_continuous(name = NULL) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 2.8, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0242, y = 2.625, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
 
@@
 # figure_GSE72056_MCPcounter <- annotate_figure(figure_GSE72056_MCPcounter, left = text_grob("MCP_counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Ture cell fractions", color = "black", size = 20))
-
-```
-
-################# Figure 5 #######################
-
-###################### Lymphocytes Figure_5a_b ###########################
-
-```{r}
-###################### Lymphocytes Figure_5a_b ###########################
+```
+
+# Figure 6
+
+###################### Lymphocytes Figure_6a_b ###########################
+
+```{r}
+###################### Lymphocytes Figure_6a_b ###########################
 library(cowplot)
 
-annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow=2,  labels = "a", font.label = list(size = 20, color = "black"))
-
-Fig_5a <- annotate_figure(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, bottom = text_grob("H&E estimate", color = "black", size = 20))
-
-Figure_5b <-
-
-  ggdraw()+ draw_plot(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, x = 0.05, y = 0.5, width = 0.9, height = 0.5)+
-    draw_plot(All_Methods_TCGA_LUAD_HE, x=0, y= 0, width = 1, height = 0.5) + 
-    draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y=c(1, 0.5))
-```
-
-###################### Figure_5c ###########################
-
-```{r}
-###################### Ludo's Figure_5c ###########################
-
-figure_Thomas_BPRNACan_150 <- ggarrange(Th[[1]],Th[[2]],Th[[3]], ncol = 3, nrow=1, labels = "c", font.label = list(size = 20, color = "black"))
+annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan <- ggarrange(annotate_figure_TCGA_LUAD_CCLE_TIL10, annotate_figure_TCGA_LUAD_BPRNACan, ncol = 1, nrow = 2, labels = "a", font.label = list(size = 20, color = "black"))
+
+Fig_6a <- annotate_figure(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, bottom = text_grob("H&E estimate", color = "black", size = 20))
+
+Figure_6b <-
+  ggdraw() + draw_plot(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, x = 0.05, y = 0.5, width = 0.9, height = 0.5) +
+  draw_plot(All_Methods_TCGA_LUAD_HE, x = 0, y = 0, width = 1, height = 0.5) +
+  draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y = c(1, 0.5))
+```
+
+###################### Figure_6c ###########################
+
+```{r}
+###################### Ludo's Figure_6c ###########################
+
+figure_Thomas_BPRNACan_150 <- ggarrange(Th[[1]], Th[[2]], Th[[3]], ncol = 3, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"))
 
@@
   # bottom = text_grob("Gold standard", color = "black", size = 20),
-                left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90))
-
-figure_Thomas_quanTIseq_M <- ggarrange(Thq[[1]],Thq[[2]],Thq[[3]], ncol = 3, nrow=1, font.label = list(size = 18, color = "black"))
+  left = text_grob("BPRNACan estimate", color = "black", size = 20, rot = 90)
+)
+
+figure_Thomas_quanTIseq_M <- ggarrange(Thq[[1]], Thq[[2]], Thq[[3]], ncol = 3, nrow = 1, font.label = list(size = 18, color = "black"))
 
@@
   # bottom = text_grob("Gold standard", color = "black", size = 20),
-                left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90))
-
-figure_Thomas_MCP_counter_M <- ggarrange(Thm[[1]],Thm[[2]],Thm[[3]], ncol = 3, nrow=1, font.label = list(size = 18, color = "black"))
+  left = text_grob("quanTIseq estimate", color = "black", size = 20, rot = 90)
+)
+
+figure_Thomas_MCP_counter_M <- ggarrange(Thm[[1]], Thm[[2]], Thm[[3]], ncol = 3, nrow = 1, font.label = list(size = 18, color = "black"))
 
@@
   # bottom = text_grob("Gold standard", color = "black", size = 20),
-                left = text_grob("MCP-counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20))
-
- Mix_figure_BPRNACan_quanTIseq_M_MCP_counter <- ggarrange(figure_Thomas_BPRNACan_150, figure_Thomas_quanTIseq_M, figure_Thomas_MCP_counter_M,ncol = 1, nrow=3)
-
-Figure_5c <- annotate_figure(Mix_figure_BPRNACan_quanTIseq_M_MCP_counter,
-                 bottom = text_grob("Gold standard", color = "black", size = 20))
-
-```
-
-###################### scRNA-seq melanoma Figure_5d ###########################
+  left = text_grob("MCP-counter estimate", color = "black", size = 20, rot = 90), bottom = text_grob("Gold standard", color = "black", size = 20)
+)
+
+Mix_figure_BPRNACan_quanTIseq_M_MCP_counter <- ggarrange(figure_Thomas_BPRNACan_150, figure_Thomas_quanTIseq_M, figure_Thomas_MCP_counter_M, ncol = 1, nrow = 3)
+
+Figure_6c <- annotate_figure(Mix_figure_BPRNACan_quanTIseq_M_MCP_counter,
+  bottom = text_grob("Gold standard", color = "black", size = 20)
+)
+```
+
+###################### scRNA-seq melanoma Figure_6d ###########################
 
@@
 
-p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.85, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.085, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.65, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.084, y = 0.53, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.015)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.015, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.0125, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.0138, y = 0.010, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)
+p_GSE72056_BPRNACan_EpiDISH[[3]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.85, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[4]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.085, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[5]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.65, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.084, y = 0.53, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_BPRNACan_EpiDISH[[6]] <- ggplot(melt_GSE72056_BPRNACan_EpiDISH[[6]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.015)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.015, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.0125, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0138, y = 0.010, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
 
@@
 
-p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.85, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.085, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.168, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.078, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.168, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.013, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)
+p_GSE72056_quanTIseq[[2]] <- ggplot(melt_GSE72056_quanTIseq[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.85, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.17, y = 0.7, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[3]] <- ggplot(melt_GSE72056_quanTIseq[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.1, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.085, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.026, y = 0.071, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[4]] <- ggplot(melt_GSE72056_quanTIseq[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.168, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.078, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_quanTIseq[[5]] <- ggplot(melt_GSE72056_quanTIseq[[5]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.168, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.013, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)
 
@@
 
-p_GSE72056_MCPcounter[[1]] <- ggplot( melt_GSE72056_MCPcounter[[1]],aes(x = value, y = V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,6)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 6, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 5.15, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.161, y = 4.3, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]],aes(x = value, y = V)) + geom_point(colour = c("coral"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.8)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.8, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.692, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.0325, y = 0.575, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]],aes(x = value, y = V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.5)) + scale_y_continuous(name = NULL, limits = c(0,3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 2.6, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 2.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)
-
-p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]],aes(x = value, y = V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color = "black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,0.08)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.435, size = 6)  + theme(axis.title.y = element_text(vjust = 1.5)) +  theme(axis.title.x = element_text(vjust = -0.5)) + annotate("text", x = 0.013, y = 0.37, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)
+p_GSE72056_MCPcounter[[1]] <- ggplot(melt_GSE72056_MCPcounter[[1]], aes(x = value, y = V)) +
+  geom_point(colour = c("green"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = NULL, limits = c(0, 6)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 6, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 5.15, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.161, y = 4.3, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[2]] <- ggplot(melt_GSE72056_MCPcounter[[2]], aes(x = value, y = V)) +
+  geom_point(colour = c("coral"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.8, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.692, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.0325, y = 0.575, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[3]] <- ggplot(melt_GSE72056_MCPcounter[[3]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkgoldenrod1"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 3)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 3, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 2.6, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.078, y = 2.15, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)
+
+p_GSE72056_MCPcounter[[4]] <- ggplot(melt_GSE72056_MCPcounter[[4]], aes(x = value, y = V)) +
+  geom_point(colour = c("darkmagenta"), size = 6) +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
+  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.435, size = 6) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  annotate("text", x = 0.013, y = 0.37, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
 
@@
 
-figure5d <- annotate_figure(ggarrange(figure_GSE72056_BPRNACan_EpiDISH_c, figure_GSE72056_quanTIseq_c, figure_GSE72056_MCPcounter_c, ncol = 1, nrow = 3, font.label = list(size = 20, color = "black")), bottom = text_grob("Cell fraction estimates", color = "black", size = 20))
-
-```
-
-############################ Start Figure S5 ############################
+figure6d <- annotate_figure(ggarrange(figure_GSE72056_BPRNACan_EpiDISH_c, figure_GSE72056_quanTIseq_c, figure_GSE72056_MCPcounter_c, ncol = 1, nrow = 3, font.label = list(size = 20, color = "black")), bottom = text_grob("Cell fraction estimates", color = "black", size = 20))
+```
+
+# Start Figure S5
 
@@
 
-load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S5/Figure_S5.RData")
+load("~/Documents/Ting_paper/Code/all_figures/Figure_S5/Figure_S5.RData")
 
@@
 TCGA_LUAD_RNAseq_CCLE_TIL10 <- data.frame(out.l$estF)
-TCGA_LUAD_RNAseq_CCLE_TIL10<-as.data.frame(cbind( TCGA_LUAD_RNAseq_CCLE_TIL10$Cancer.cells, Facs_LUAD_Aran$ABSOLUTE,  Facs_LUAD_Aran$ESTIMATE, Facs_LUAD_Aran$LUMP, Facs_LUAD_Aran$IHC))
-colnames(TCGA_LUAD_RNAseq_CCLE_TIL10) <- c("CCLE_TIL10", "ABSOLUTE", "ESTIMATE","LUMP","IHC")
-
-melt_CCLE_TIL10 <- melt(TCGA_LUAD_RNAseq_CCLE_TIL10,  id.vars = "CCLE_TIL10", measure.vars = c("ABSOLUTE", "ESTIMATE","LUMP","IHC"))
-
-p_CCLE_TIL10 <- ggplot(melt_CCLE_TIL10,aes(x=value, y=CCLE_TIL10)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = "CCLE_TIL10 estimate",limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.86, size = 6) + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + labs(tag = "a")
-
+TCGA_LUAD_RNAseq_CCLE_TIL10 <- as.data.frame(cbind(TCGA_LUAD_RNAseq_CCLE_TIL10$Cancer.cells, Facs_LUAD_Aran$ABSOLUTE, Facs_LUAD_Aran$ESTIMATE, Facs_LUAD_Aran$LUMP, Facs_LUAD_Aran$IHC))
+colnames(TCGA_LUAD_RNAseq_CCLE_TIL10) <- c("CCLE_TIL10", "ABSOLUTE", "ESTIMATE", "LUMP", "IHC")
+
+melt_CCLE_TIL10 <- melt(TCGA_LUAD_RNAseq_CCLE_TIL10, id.vars = "CCLE_TIL10", measure.vars = c("ABSOLUTE", "ESTIMATE", "LUMP", "IHC"))
+
+p_CCLE_TIL10 <- ggplot(melt_CCLE_TIL10, aes(x = value, y = CCLE_TIL10)) +
+  geom_point(colour = "brown") +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = "CCLE_TIL10 estimate", limits = c(0, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
+  stat_cor(aes(label = paste(..p.label..)), label.x = 0, label.y = 0.86, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  labs(tag = "a")
 ```
@@
 TCGA_LUAD_RNAseq_BPRNACan_150 <- data.frame(out.l$estF)
-TCGA_LUAD_RNAseq_BPRNACan_150<-as.data.frame(cbind(TCGA_LUAD_RNAseq_BPRNACan_150$cancer, Facs_LUAD_Aran$ABSOLUTE, Facs_LUAD_Aran$ESTIMATE,Facs_LUAD_Aran$LUMP,Facs_LUAD_Aran$IHC))
-colnames(TCGA_LUAD_RNAseq_BPRNACan_150) <- c("BPRNACan", "ABSOLUTE", "ESTIMATE","LUMP","IHC")
-
-melt_BPRNACan <- melt(TCGA_LUAD_RNAseq_BPRNACan_150,  id.vars = "BPRNACan", measure.vars = c("ABSOLUTE", "ESTIMATE","LUMP","IHC"))
-
-p_BPRNACan <- ggplot(melt_BPRNACan,aes(x=value, y=BPRNACan)) + geom_point(colour = "brown") + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable) + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = "BPRNACan estimate", limits = c(0.8,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor( aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0.5, label.y = 0.83, size = 6) + stat_cor( aes(label = paste(..p.label..)), label.x = 0.5, label.y = 0.81, size = 6) + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + labs(tag = "b")
-
-```
-
-############################ Figure S5 ############################
-
-```{r}
-
-Figure_S5 <- ggarrange(p_CCLE_TIL10, p_BPRNACan, ncol = 1, nrow=2, font.label = list(size = 20, color = "black"))
+TCGA_LUAD_RNAseq_BPRNACan_150 <- as.data.frame(cbind(TCGA_LUAD_RNAseq_BPRNACan_150$cancer, Facs_LUAD_Aran$ABSOLUTE, Facs_LUAD_Aran$ESTIMATE, Facs_LUAD_Aran$LUMP, Facs_LUAD_Aran$IHC))
+colnames(TCGA_LUAD_RNAseq_BPRNACan_150) <- c("BPRNACan", "ABSOLUTE", "ESTIMATE", "LUMP", "IHC")
+
+melt_BPRNACan <- melt(TCGA_LUAD_RNAseq_BPRNACan_150, id.vars = "BPRNACan", measure.vars = c("ABSOLUTE", "ESTIMATE", "LUMP", "IHC"))
+
+p_BPRNACan <- ggplot(melt_BPRNACan, aes(x = value, y = BPRNACan)) +
+  geom_point(colour = "brown") +
+  theme_bw() +
+  stat_smooth(method = lm, color = "black") +
+  facet_wrap(~variable) +
+  scale_x_continuous(name = NULL, limits = c(0, 1)) +
+  scale_y_continuous(name = "BPRNACan estimate", limits = c(0.8, 1)) +
+  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
+  font("xy.text", size = 16, color = "black") +
+  stat_cor(aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0.5, label.y = 0.83, size = 6) +
+  stat_cor(aes(label = paste(..p.label..)), label.x = 0.5, label.y = 0.81, size = 6) +
+  theme(axis.title.x = element_text(vjust = -0.5)) +
+  theme(axis.title.y = element_text(vjust = 1.5)) +
+  labs(tag = "b")
+```
+
+# Figure S5
+
+```{r}
+
+Figure_S5 <- ggarrange(p_CCLE_TIL10, p_BPRNACan, ncol = 1, nrow = 2, font.label = list(size = 20, color = "black"))
 
 Figure_S5 <- annotate_figure(Figure_S5,
-                bottom = text_grob("Method purity estimate", color = "black", size = 20))
-
-```
-
-############################ Start Figure S6 #################################### 
-############ Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)
+  bottom = text_grob("Method purity estimate", color = "black", size = 20)
+)
+```
+
+# Start Figure S6 
+Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)
 
@@
 ```{r}
-load("~/deconvolution/Final methylation paper/figure/Figure_S6/Figure_S6.RData")
+load("~/Documents/Ting_paper/Code/all_figures/Figure_S6/Figure_S6.RData")
 
@@
 
-merge_melt_silico_1700 <- cbind(melt_silico_1700, melt_silico_1700_Pvalue) %>% .[,-3]
+merge_melt_silico_1700 <- cbind(melt_silico_1700, melt_silico_1700_Pvalue) %>% .[, -3]
 
@@
     value.1 >= 0.05 ~ paste(value, "\n"),
-        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
+    value.1 >= 0.01 & value.1 < 0.05 ~ paste(value, "\n*"),
     value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
-        value.1 < 0.001 ~ paste(value, "\n***")))
+    value.1 < 0.001 ~ paste(value, "\n***")
+  ))
 
@@
 silico_1700_figure <- ggplot(melt_merge_melt_silico_1700, aes(new_Var2, variable)) +
-    geom_tile(aes(fill = value), colour = "grey", size = 1)+
-    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +
-
-    geom_text(aes(label=text),col ="black",size = 5) +
+  geom_tile(aes(fill = value), colour = "grey", size = 1) +
+  scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
+  geom_text(aes(label = text), col = "black", size = 5) +
   theme_minimal() +
-    theme(axis.title.x=element_blank(),
-          axis.ticks.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.title=element_text(size = 14),
-          legend.text=element_text(size = 14),
+  theme(
+    axis.title.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.y = element_blank(),
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 14),
     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
-          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("1700 simulated RNA-seq data sets (ID: 6)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
+    axis.text.y = element_text(size = 14, colour = "black")
+  ) +
+  labs(fill = paste0("Correlation")) +
+  ggtitle("1700 simulated RNA-seq data sets (ID: 6)") +
+  theme(plot.title = element_text(hjust = 0.5, size = 16))
 
 Figure_S6a <- ggarrange(silico_1700_figure, ncol = 1, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"))
-
 ```
@@
 
-merge_TCGA_LUAD_Lymphocytes_RNAseq <- cbind(melt_TCGA_LUAD_Lymphocytes_RNAseq, melt_TCGA_LUAD_Lymphocytes_RNAseq_Pvalue) %>% .[,-3]
+merge_TCGA_LUAD_Lymphocytes_RNAseq <- cbind(melt_TCGA_LUAD_Lymphocytes_RNAseq, melt_TCGA_LUAD_Lymphocytes_RNAseq_Pvalue) %>% .[, -3]
 
@@
 TCGA_LUAD_Lymphocytes_RNAseq_figure <- ggplot(melt_merge_TCGA_LUAD_Lymphocytes_RNAseq, aes(new_Var2, variable)) +
-    geom_tile(aes(fill = value), colour = "grey", size = 1)+
-    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +
-
-    geom_text(aes(label=text),col ="black",size = 5) +
+  geom_tile(aes(fill = value), colour = "grey", size = 1) +
+  scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
+  geom_text(aes(label = text), col = "black", size = 5) +
   theme_minimal() +
-    theme(axis.title.x=element_blank(), 
-          axis.ticks.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.title=element_text(size = 14),
-          legend.text=element_text(size = 14),
+  theme(
+    axis.title.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.y = element_blank(),
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 14),
     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
-          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("H&E stained (ID: 4)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
+    axis.text.y = element_text(size = 14, colour = "black")
+  ) +
+  labs(fill = paste0("Correlation")) +
+  ggtitle("H&E stained (ID: 4)") +
+  theme(plot.title = element_text(hjust = 0.5, size = 16))
 
@@
 
-merge_Melanoma_GSE72056 <- cbind(melt_Melanoma_GSE72056, melt_Melanoma_GSE72056_Pvalue) %>% .[,-3]
+merge_Melanoma_GSE72056 <- cbind(melt_Melanoma_GSE72056, melt_Melanoma_GSE72056_Pvalue) %>% .[, -3]
 
@@
 Melanoma_GSE72056_figure <- ggplot(melt_merge_Melanoma_GSE72056, aes(new_Var2, variable)) +
-    geom_tile(aes(fill = value), colour = "grey", size = 1)+
-    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +
-
-    geom_text(aes(label=text),col ="black",size = 5) +
+  geom_tile(aes(fill = value), colour = "grey", size = 1) +
+  scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
+  geom_text(aes(label = text), col = "black", size = 5) +
   theme_minimal() +
-    theme(axis.title.x=element_blank(),
-          axis.ticks.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.title=element_text(size = 14),
-          legend.text=element_text(size = 14),
+  theme(
+    axis.title.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.y = element_blank(),
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 14),
     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
-          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
+    axis.text.y = element_text(size = 14, colour = "black")
+  ) +
+  labs(fill = paste0("Correlation")) +
+  ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") +
+  theme(plot.title = element_text(hjust = 0.5, size = 16))
 
 Figure_S6c <- ggarrange(Melanoma_GSE72056_figure, ncol = 1, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"))
-
 ```
@@
 
-merge_Melanoma_GSE93722 <- cbind(melt_Melanoma_GSE93722, melt_Melanoma_GSE93722_Pvalue) %>% .[,-3]
+merge_Melanoma_GSE93722 <- cbind(melt_Melanoma_GSE93722, melt_Melanoma_GSE93722_Pvalue) %>% .[, -3]
 
@@
 Melanoma_GSE93722_figure <- ggplot(melt_merge_Melanoma_GSE93722, aes(new_Var2, variable)) +
-    geom_tile(aes(fill = value), colour = "grey", size = 1)+
-    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +
-
-    geom_text(aes(label=text),col ="black",size = 5) +
+  geom_tile(aes(fill = value), colour = "grey", size = 1) +
+  scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
+  geom_text(aes(label = text), col = "black", size = 5) +
   theme_minimal() +
-    theme(axis.title.x=element_blank(), 
-          axis.ticks.x=element_blank(), 
-          axis.title.y=element_blank(), 
-          legend.title=element_text(size = 14),
-          legend.text=element_text(size = 14),
+  theme(
+    axis.title.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.y = element_blank(),
+    legend.title = element_text(size = 14),
+    legend.text = element_text(size = 14),
     axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
-          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 malignant melanoma (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
+    axis.text.y = element_text(size = 14, colour = "black")
+  ) +
+  labs(fill = paste0("Correlation")) +
+  ggtitle("4 malignant melanoma (ID: 8)") +
+  theme(plot.title = element_text(hjust = 0.5, size = 16))
 
 Figure_S6d <- ggarrange(Melanoma_GSE93722_figure, ncol = 1, nrow = 1, labels = "d", font.label = list(size = 20, color = "black"))
-
-```
+```

### 2021-07-27 Paper_Figure_code.Rmd
Upgrades
Fix according to comments on figure 5 & 6

@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"ALL") +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"BPmet") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~variable) +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"MethylCIBERSORT") +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"DHS") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~variable, ncol = 2) +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"lymphocytes") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"Macrophages") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"Neutrophils") +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"BPRNA") +
@@
 
-PBMCs_figure <- ggplot(melt_merge_melt_PBMCs, aes(new_Var2, variable)) +
+PBMCs_figure <- ggplot(melt_merge_melt_PBMCs, aes(variable, new_Var2)) +
   geom_tile(aes(fill = value), colour = "grey", size = 1) +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"CCLE_TIL10") +
@@
   scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"BPRNACan") +
@@
     theme_bw() +
-    stat_smooth(method = lm, color = "black") +
+    stat_smooth(method = lm, color = "black", fullrange = T) +
     facet_wrap(~variable) +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"Lymphocytes") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"CD4") +
@@
   theme_bw() +
-  stat_smooth(method = lm, color = "black") +
+  stat_smooth(method = lm, color = "black", fullrange = T) +
   facet_wrap(~"CD8") +
@@
   ggdraw() + draw_plot(annotate_TCGA_LUAD_CCLE_TIL10_BPRNACan, x = 0.05, y = 0.5, width = 0.9, height = 0.5) +
-  draw_plot(All_Methods_TCGA_LUAD_HE, x = 0, y = 0, width = 1, height = 0.5) +
+  draw_plot(All_Methods_TCGA_LUAD_HE, x = 0, y = 0, width = 1, height = 0.5) + # reverse x and y on this
   draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y = c(1, 0.5))

### 2021-08-12 Paper_Figure_code.Rmd
Add files via upload

@@
 
-################ Methylation paper Figure ################
+################ Methylation paper Figure
 
@@
 
-############# 100 WB GSE132203_100 samples methylation ###############
-
-###############   BPmet  ###################
+############# 100 WB GSE132203_100 samples methylation
+
+############### BPmet
 
@@
 
-###############   MethylCIBERSORT  ##################
+############### MethylCIBERSORT
 
@@
 
-###############   DHS  ##################
+############### DHS
 
@@
 
-############## methylation 6 WB samples GSE77797 ##############
-
-############## BPmet ###################
+############## methylation 6 WB samples GSE77797
+
+############## BPmet
 
@@
 
-###################### MethylCIBERSORT_WB #########################
+###################### MethylCIBERSORT_WB
 
@@
 
-###################### DHS #########################
+###################### DHS
 
@@
 
-##########  methylation TCGA-LUAD with previous tumor purity methods ############
-
-############## BPmetCan and MethylCIBERSORT_Luad ###################
-
-```{r}
-library(reshape2)
-library(scales)
-library(ggpubr)
-library(EpiDISH)
-
+########## methylation TCGA-LUAD with previous tumor purity methods
+
+############## BPmetCan and MethylCIBERSORT_Luad
+
+```{r}
 load("~/Documents/Ting_paper/Code/all_figures/Figure3 and S3/Figure3_and_S3.RData")
@@
 
-##########  methylation TCGA-BRCA with previous tumor purity methods ##########
-
-############## BPmetCan and MethylCIBERSORT_breast ###################
+########## methylation TCGA-BRCA with previous tumor purity methods
+
+############## BPmetCan and MethylCIBERSORT_breast
 
@@
 
-############################ DNA methylation lymphocytes ###################################
-
-############################ BPmetCan ###################################
+############################ DNA methylation lymphocytes
+
+############################ BPmetCan
 
@@
 
-############## MethylCIBERSORT #####################
+############## MethylCIBERSORT
 
@@
 # Neutrophiles: Neutrophils
+
 ```{r}
@@
 
-############## Options DHS #####################
+############## Options DHS
 
@@
 # Figure 4 and Figure S3
-```{r}
-
-#### Figure 3 #####
+
+```{r}
+
+#### Figure 4 #####
 
@@
 
-############################ RNAseq lymphocytes ###################################
-
-##########  RNAseq GSE107011 PBMC Monaco ############
-
-############## BPRNA ###################
-
-```{r}
-library(Metrics)
-
-# load("~/deconvolution/Final methylation paper/figure/Figure4/GSE107011_PBMCs_Fig4.RData")
+############################ RNAseq lymphocytes
+
+########## RNAseq GSE107011 PBMC Monaco
+
+############## BPRNA
+
+```{r}
+load("~/Documents/Ting_paper/Code/all_figures/Figure4/GSE107011_PBMCs_Fig4.RData")
 
@@
   theme(axis.title.y = element_text(vjust = 1.5)) +
-  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
   annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)
@@
   theme(axis.title.y = element_text(vjust = 1.5)) +
-  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
+  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
   annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)
@@
 
-# left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90),
 ```
@@
 Fig_5a <- annotate_figure(figure_GSE107011_BPRNA_EpiDISH_together, bottom = text_grob("Gold standard", color = "black", size = 20), left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90))
-
-# GSE107011_PBMCs <- read.table("~/paper1.txt", row.names = 1, header = T)
-# GSE107011_PBMCs_pvalue <- read.table("~/paper1.txt", row.names = 1, header = T)
 
@@
 
-# Figure_4 <- ggarrange(figure_GSE107011_BPRNA_EpiDISH_together ,PBMCs_figure, ncol = 1, nrow=2, font.label = list(size = 20, color = "black"))
-
-# ggdraw()+ draw_plot(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, x=0, y=0.6, width=0.5, height = 0.4)+
-#     draw_plot(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, x=0.5, y= 0.6, width=0.5, height = 0.4) +
-#     draw_plot(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, x=1, y=0.6, width = 0.5, height = 0.4)+
-#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.6)+
-#     draw_plot_label(label = c("a", "b", "c", "d"), size = 18, x=c(0, 0.5, 1, 0), y=c(1, 1, 1, 0.58))
-#
-#
-# ggdraw()+ draw_plot(figure_GSE107011_all_together, x = 0.05, y = 0.5, width = 0.9, height = 0.5)+
-#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.5) +
-#     draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y=c(1, 0.5))
-#
-#
-# ggarrange(PBMCs_figure, labels = "b", nrow=1, ncol = 1, font.label = list(size = 20, color = "black"), widths = c(1,1))
-```
-
-######### Not Run #####
-
-######### CCLE_TIL10 ###################
+```
+
+######### Not Run
+
+######### CCLE_TIL10
 
@@
 
-############## BPRNACan ###################
+############## BPRNACan
 
@@
 
-############## PBMC GSE107011  ###################
+############## PBMC GSE107011
 
@@
 
-######### Not Run #####
+######### Not Run
 
@@
 
-############################ 1700 in-silico mixture RNAseq benchmark ############################
-
-############################ CCLE_TIL10 ############################
-
-```{r}
-
-# load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S4/Silico_1700_RNAseq.RData")
-
-out.l <- epidish(silico_1700, CCLE_TIL10, "RPC", maxit = 200)
+############################ 1700 in-silico mixture RNAseq benchmark
+
+############################ CCLE_TIL10
+
+```{r}
+
+load("~/Documents/Ting_paper/Code/all_figures/Figure_S4/Figure_S4.RData")
+
+out.l <- epidish(Silico_1700, CCLE_TIL10, "RPC", maxit = 200)
 benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[, c(1, 8, 9, 5, 3, 4, 2, 7, 6, 10, 11)])
@@
 
-############################ BPRNACan ############################
+############################ BPRNACan
 
@@
 
-#############  H&E #####################
-
-############## CCLE_TIL10 #####################
+############# H&E
+
+############## CCLE_TIL10
 
@@
 load("/home/julien/Documents/Ting_paper/Code/all_figures/figure5/Figure_5.RData")
-
-library(reshape2)
-library(scales)
-library(ggpubr)
-library(EpiDISH)
 
@@
 
-############## BPRNACan #####################
+############## BPRNACan
 
@@
 ```{r}
-
-library(reshape2)
-library(scales)
-library(ggpubr)
-library(EpiDISH)
 
@@
 
-##########  RNAseq Ludo's data 59 multiple myeloma TME patients ############
-
-############## BPRNACan ###################
+########## RNAseq Ludo's data 59 multiple myeloma TME patients
+
+############## BPRNACan
 
@@
 
-############## quanTIseq ###################
-
-```{r}
-library(immunedeconv)
-library(textshape)
-library(dplyr)
+############## quanTIseq
+
+```{r}
 
@@
 
-######################### MCP-counter ######################################
+######################### MCP-counter
 
@@
 
-############## scRNAseq GSE72056  ###################
-
-############## BPRNACan ###################
-
-```{r}
-library(Metrics)
+############## scRNAseq GSE72056
+
+############## BPRNACan
+
+```{r}
 
@@
 
-############## quanTIseq ###################
-
-```{r}
-library(immunedeconv)
-library(textshape)
+############## quanTIseq
+
+```{r}
 
@@
 
-############## MCP-counter ###################
+############## MCP-counter
 
@@
 
+###################### Lymphocytes Figure_6a_b
+
+```{r}
 ###################### Lymphocytes Figure_6a_b ###########################
-
-```{r}
-###################### Lymphocytes Figure_6a_b ###########################
-library(cowplot)
 
@@
 
-###################### Figure_6c ###########################
+###################### Figure_6c
 
@@
 
-###################### scRNA-seq melanoma Figure_6d ###########################
+###################### scRNA-seq melanoma Figure_6d
 
@@
 
-##########  RNAseq TCGA-LUAD with previous tumor purity methods ############
-
-############## CCLE_TIL10 and BPRNACan ###################
+########## RNAseq TCGA-LUAD with previous tumor purity methods
+
+############## CCLE_TIL10 and BPRNACan
 
@@
 
-########### BPRNACan ####################
+########### BPRNACan
 
@@
 # Start Figure S6
+
 Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)
@@
 load("~/Documents/Ting_paper/Code/all_figures/Figure_S6/Figure_S6.RData")
-
-library(dplyr)
 
@@
 
-### LUAD H&E RNAseq ###
+### LUAD H&E RNAseq
 
@@
 
-### Melanoma_GSE72056 ###
+### Melanoma_GSE72056
 
@@
 
-### Melanoma_GSE93722 ###
+### Melanoma_GSE93722
 

### 2021-08-12 Paper_Figure_code.Rmd
tweaking figures

@@
 
-p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 2, nrow = 3)
+p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 2, nrow = 3, align = "hv")
 
@@
 
-p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 2, nrow = 3)
-
-figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2))
+p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 2, nrow = 3, align = "hv")
+
+figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2), align = "hv")
 
@@
 
-figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together, figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow = 3)
+figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together, figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow = 3, align = "hv")
 
@@
   scale_x_continuous(name = NULL, limits = NULL) +
-  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
+  scale_y_continuous(name = NULL, limits = c(0, 0.50)) +
   theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
@@
 
-p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]], melt_GSE107011_BPRNA_EpiDISH[[2]], melt_GSE107011_BPRNA_EpiDISH[[3]], melt_GSE107011_BPRNA_EpiDISH[[4]], melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3)
+p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]], melt_GSE107011_BPRNA_EpiDISH[[2]], melt_GSE107011_BPRNA_EpiDISH[[3]], melt_GSE107011_BPRNA_EpiDISH[[4]], melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3, align = "hv")
 
@@
 
-Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow = 4, labels = "a", font.label = list(size = 18, color = "black"))
+Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow = 4, labels = "a", font.label = list(size = 18, color = "black"), align = "hv")
 
@@
 
-Figure_S4b <- ggarrange(bench_BPRNACan[[1]], bench_BPRNACan[[2]], bench_BPRNACan[[3]], bench_BPRNACan[[4]], bench_BPRNACan[[5]], bench_BPRNACan[[6]], bench_BPRNACan[[7]], bench_BPRNACan[[8]], bench_BPRNACan[[9]], ncol = 3, nrow = 3, labels = "b", font.label = list(size = 18, color = "black"))
+Figure_S4b <- ggarrange(bench_BPRNACan[[1]], bench_BPRNACan[[2]], bench_BPRNACan[[3]], bench_BPRNACan[[4]], bench_BPRNACan[[5]], bench_BPRNACan[[6]], bench_BPRNACan[[7]], bench_BPRNACan[[8]], bench_BPRNACan[[9]], ncol = 3, nrow = 3, labels = "b", font.label = list(size = 18, color = "black"), align = "hv")
 

### 2021-08-13 Paper_Figure_code.Rmd
small upgrades

@@
 title: "R Notebook"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
 editor_options:
@@
 library(EpiDISH)
+library(tidyverse)
+library(immunedeconv)
 
@@
 
-# melt_GSE107011_BPRNACan_EpiDISH_modify <- melt(GSE107011_BPRNACan_EpiDISH_modify)
-# melt_FACS_107 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
+melt_GSE107011_BPRNACan_EpiDISH_modify <- melt(GSE107011_BPRNACan_EpiDISH_modify)
+melt_FACS_107 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)
 
@@
 
-Thomas_quantiseq <- as.data.frame(t(column_to_rownames(Thomas_quantiseq)))
+Thomas_quantiseq <- as.data.frame(t(column_to_rownames(Thomas_quantiseq, var = "cell_type")))
 
@@
 
-Thomas_MCP_counter <- as.data.frame(t(column_to_rownames(Thomas_MCP_counter)))
+Thomas_MCP_counter <- as.data.frame(t(column_to_rownames(Thomas_MCP_counter, var = "cell_type")))
 

### 2021-08-16 Paper_Figure_code.Rmd
Fig5

@@
   scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
-  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
+  scale_y_continuous(name = NULL, limits = NULL) +
   theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
@@
   scale_x_continuous(name = NULL, limits = NULL) +
-  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
+  scale_y_continuous(name = NULL, limits = NULL) +
   theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
@@
   scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
-  scale_y_continuous(name = NULL, limits = c(0, 0.04)) +
+  scale_y_continuous(name = NULL, limits = NULL) +
   theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +

### 2021-11-30 Figures/Paper_Figures_final.Rmd
Create Paper_Figures_final.Rmd

---
title: "Gem-DeCan Figures"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
suppressPackageStartupMessages({
  library(reshape2)
  library(ggpubr)
  library(tidyverse)
  library(Hmisc)
  library(ggridges)
})
knitr::opts_chunk$set(fig.width=15, fig.height=10) 
```

# Figure 3

## Non-tumoral multiple myeloma

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

# Load data
myeloma = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_GSE104171.txt")
myeloma_facs = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/FACS_GSE104171.txt")
rownames(myeloma_facs) = myeloma_facs$Name
myeloma_facs = myeloma_facs[,-1]

colnames(myeloma) = colnames(myeloma) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(myeloma) = colnames(myeloma) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(myeloma) = colnames(myeloma) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(myeloma) = colnames(myeloma) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")

# Select cell types available in facs data. Here NK, CD4, CD8
myeloma = myeloma %>% select(c("Samples",
  "Quantiseq_NK_cell", "Quantiseq_T_cell_CD4._.non.regulatory.", "Quantiseq_T_cell_CD8.",
  "MCP_NK_cells", "MCP_CD8_T_cells",
  "Epidish_BPRNACan_NK", "Epidish_BPRNACan_CD4", "Epidish_BPRNACan_CD8", 
  "DeconRNASeq_BPRNACan_NK", "DeconRNASeq_BPRNACan_CD4", "DeconRNASeq_BPRNACan_CD8", 
  "Epidish_BPRNACanProMet_NK", "Epidish_BPRNACanProMet_CD4", "Epidish_BPRNACanProMet_CD8",
  "DeconRNASeq_BPRNACanProMet_NK", "DeconRNASeq_BPRNACanProMet_CD4", "DeconRNASeq_BPRNACanProMet_CD8", 
  "Epidish_BPRNACan3DProMet_NK", "Epidish_BPRNACan3DProMet_CD4", "Epidish_BPRNACan3DProMet_CD8",
  "DeconRNASeq_BPRNACan3DProMet_NK", "DeconRNASeq_BPRNACan3DProMet_CD4", "DeconRNASeq_BPRNACan3DProMet_CD8",
  "Epidish_CBSX.NSCLC_NK.cells", "Epidish_CBSX.NSCLC_T.cells.CD4", "Epidish_CBSX.NSCLC_T.cells.CD8",
 "DeconRNASeq_CBSX.NSCLC_NK.cells", "DeconRNASeq_CBSX.NSCLC_T.cells.CD4", "DeconRNASeq_CBSX.NSCLC_T.cells.CD8",
  "Epidish_CBSX.HNSCC_T.cells.CD4", "Epidish_CBSX.HNSCC_T.cells.CD8", 
  "DeconRNASeq_CBSX.HNSCC_T.cells.CD4", "DeconRNASeq_CBSX.HNSCC_T.cells.CD8",
  "Epidish_CBSX.melanoma_NK.cells", "Epidish_CBSX.melanoma_T.cells.CD4", "Epidish_CBSX.melanoma_T.cells.CD8",
  "DeconRNASeq_CBSX.melanoma_NK.cells", "DeconRNASeq_CBSX.melanoma_T.cells.CD4", "DeconRNASeq_CBSX.melanoma_T.cells.CD8",
 "Epidish_CBSX_LM22_NK.cells.activated", "Epidish_CBSX_LM22_T.cells.CD4.memory.activated", "Epidish_CBSX_LM22_T.cells.CD8",
 "DeconRNASeq_CBSX_LM22_NK.cells.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD8",
  "CBSX.NSCLC_NK_cells", "CBSX.NSCLC_T_cells_CD4", "CBSX.NSCLC_T_cells_CD8",
  "CBSX.HNSCC_T_cells_CD4", "CBSX.HNSCC_T_cells_CD8",
  "CBSX.melanoma_NK_cells", "CBSX.melanoma_T_cells_CD4", "CBSX.melanoma_T_cells_CD8",
 "CBSX.LM22_NK_cells_activated",  "CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD8"
 ))
rownames(myeloma) = myeloma$Samples 
myeloma = myeloma[,-1]

# Get correlation and Pvalue for each cell type with facs
myeloma.corr = rcorr(as.matrix(myeloma), as.matrix(myeloma_facs))
myeloma.pval = myeloma.corr$P[, 57:59]
myeloma.corr = myeloma.corr$r[, 57:59]

# Create the table for the heatmap
myeloma_all_signs = data.frame(
                               "quanTIseq" = c(myeloma.corr[1,1], myeloma.corr[2,2], myeloma.corr[3,3]),
                               "MCPcounter" = c(myeloma.corr[4,1], NA, myeloma.corr[5,3]),
                               "EpiDISH BPRNACan" = c(myeloma.corr[6,1], myeloma.corr[7,2], myeloma.corr[8,3]),
                               "EpiDISH BPRNACanProMet" = c(myeloma.corr[18,1], myeloma.corr[19,2], myeloma.corr[20,3]),
                               "EpiDISH BPRNACan3DProMet" = c(myeloma.corr[12,1], myeloma.corr[13,2], myeloma.corr[14,3]),
                               "EpiDISH Melanoma" = c(myeloma.corr[34,1], myeloma.corr[35,2], myeloma.corr[36,3]),
                               "EpiDISH HNSCC" = c(NA, myeloma.corr[30,2], myeloma.corr[31,3]),
                               "EpiDISH NSCLC" = c(myeloma.corr[24,1], myeloma.corr[25,2], myeloma.corr[26,3]),
                               "EpiDISH LM22" = c(myeloma.corr[40,1], myeloma.corr[41,2], myeloma.corr[42,3]),

                               "DeconRNASeq BPRNACan" = c(myeloma.corr[9,1], myeloma.corr[10,2], myeloma.corr[11,3]),
                               "DeconRNASeq BPRNACanProMet" = c(myeloma.corr[21,1], myeloma.corr[22,2], myeloma.corr[23,3]),
                               "DeconRNASeq BPRNACan3DProMet" = c(myeloma.corr[15,1], myeloma.corr[16,2], myeloma.corr[17,3]),
                               "DeconRNASeq Melanoma" = c(myeloma.corr[37,1], myeloma.corr[38,2], myeloma.corr[39,3]),
                               "DeconRNASeq HNSCC" = c(NA, myeloma.corr[32,2], myeloma.corr[33,3]),
                               "DeconRNASeq NSCLC" = c(myeloma.corr[27,1], myeloma.corr[28,2], myeloma.corr[29,3]),
                               "DeconRNASeq LM22" = c(myeloma.corr[43,1], myeloma.corr[44,2], myeloma.corr[45,3]),

                               "CIBERSORTx Melanoma" = c(myeloma.corr[51,1], myeloma.corr[52,2], myeloma.corr[53,3]),
                               "CIBERSORTx HNSCC" = c(NA, myeloma.corr[49,2], myeloma.corr[50,3]),
                               "CIBERSORTx NSCLC" = c(myeloma.corr[46,1], myeloma.corr[47,2], myeloma.corr[48,3]),
                               "CIBERSORTx LM22" = c(myeloma.corr[54,1], myeloma.corr[55,2], myeloma.corr[56,3])
                               ) %>% 
  round(., 2) %>% t(.) %>% as.data.frame(.)
colnames(myeloma_all_signs) = c("NK", "CD4", "CD8")

myeloma_all_signs_p  = data.frame(
                               "quanTIseq" = c(myeloma.pval[1,1], myeloma.pval[2,2], myeloma.pval[3,3]),
                               "MCPcounter" = c(myeloma.pval[4,1], NA, myeloma.pval[5,3]),
                               "EpiDISH BPRNACan" = c(myeloma.pval[6,1], myeloma.pval[7,2], myeloma.pval[8,3]),
                               "EpiDISH BPRNACanProMet" = c(myeloma.pval[18,1], myeloma.pval[19,2], myeloma.pval[20,3]),
                               "EpiDISH BPRNACan3DProMet" = c(myeloma.pval[12,1], myeloma.pval[13,2], myeloma.pval[14,3]),
                               "EpiDISH Melanoma" = c(myeloma.pval[34,1], myeloma.pval[35,2], myeloma.pval[36,3]),
                               "EpiDISH HNSCC" = c(NA, myeloma.pval[30,2], myeloma.pval[31,3]),
                               "EpiDISH NSCLC" = c(myeloma.pval[24,1], myeloma.pval[25,2], myeloma.pval[26,3]),
                               "EpiDISH LM22" = c(myeloma.pval[40,1], myeloma.pval[41,2], myeloma.pval[42,3]),

                               "DeconRNASeq BPRNACan" = c(myeloma.pval[9,1], myeloma.pval[10,2], myeloma.pval[11,3]),
                               "DeconRNASeq BPRNACanProMet" = c(myeloma.pval[21,1], myeloma.pval[22,2], myeloma.pval[23,3]),
                               "DeconRNASeq BPRNACan3DProMet" = c(myeloma.pval[15,1], myeloma.pval[16,2], myeloma.pval[17,3]),
                               "DeconRNASeq Melanoma" = c(myeloma.pval[37,1], myeloma.pval[38,2], myeloma.pval[39,3]),
                               "DeconRNASeq HNSCC" = c(NA, myeloma.pval[32,2], myeloma.pval[33,3]),
                               "DeconRNASeq NSCLC" = c(myeloma.pval[27,1], myeloma.pval[28,2], myeloma.pval[29,3]),
                               "DeconRNASeq LM22" = c(myeloma.pval[43,1], myeloma.pval[44,2], myeloma.pval[45,3]),

                               "CIBERSORTx Melanoma" = c(myeloma.pval[51,1], myeloma.pval[52,2], myeloma.pval[53,3]),
                               "CIBERSORTx HNSCC" = c(NA, myeloma.pval[49,2], myeloma.pval[50,3]),
                               "CIBERSORTx NSCLC" = c(myeloma.pval[46,1], myeloma.pval[47,2], myeloma.pval[48,3]),
                               "CIBERSORTx LM22" = c(myeloma.pval[54,1], myeloma.pval[55,2], myeloma.pval[56,3])
                               ) %>% 
  round(., 2) %>% t(.) %>% as.data.frame(.)
colnames(myeloma_all_signs_p) = c("NK", "CD4", "CD8")

myeloma_all_signs["Mean", ] = colMeans(myeloma_all_signs, na.rm = T) %>% round(., 3)
myeloma_all_signs_p["Mean", ] = colMeans(myeloma_all_signs_p, na.rm = T)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

melt_myeloma_RNAseq <- melt(myeloma_all_signs)

melt_myeloma_RNAseq_Pvalue <- melt(myeloma_all_signs_p)

merge_myeloma_RNAseq <- cbind(melt_myeloma_RNAseq, melt_myeloma_RNAseq_Pvalue) %>% .[,-3]

melt_merge_myeloma_RNAseq <- merge_myeloma_RNAseq %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_myeloma_RNAseq$new_Var2 <- rownames(myeloma_all_signs)
melt_merge_myeloma_RNAseq$new_Var2 <- factor(melt_merge_myeloma_RNAseq$new_Var2, levels = unique(melt_merge_myeloma_RNAseq$new_Var2))

myeloma_RNAseq_figure <- ggplot(melt_merge_myeloma_RNAseq, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") + 
    geom_text(aes(label=text),col ="black",size = 4) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5, 
                                     size = 14, colour = "black"), 
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("59 Non-tumoral multiple myeloma (ID: 7)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
myeloma_RNAseq_figure
```

## Melanoma non metastatic
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# Load data
nonMeta = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt")
nonMeta_facs = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt")
rownames(nonMeta_facs) = nonMeta_facs$Name
nonMeta_facs = nonMeta_facs[,-1]

colnames(nonMeta) = colnames(nonMeta) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(nonMeta) = colnames(nonMeta) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(nonMeta) = colnames(nonMeta) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(nonMeta) = colnames(nonMeta) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")

# Select cell types available in facs data. Here Macro, NK, CD4, CD8, Cancer
nonMeta = nonMeta %>% select(c( "Samples",
  "Quantiseq_B_cell", "Quantiseq_Macrophage_M1", "Quantiseq_Macrophage_M2", "Quantiseq_Monocyte", "Quantiseq_NK_cell", "Quantiseq_T_cell_CD4._.non.regulatory.", "Quantiseq_T_cell_CD8.",
  "MCP_B_lineage", "MCP_Monocytic_lineage", "MCP_NK_cells", "MCP_CD8_T_cells",
  "Epidish_BPRNACan_B", "Epidish_BPRNACan_M0", "Epidish_BPRNACan_M1", "Epidish_BPRNACan_M2", "Epidish_BPRNACan_Mono", "Epidish_BPRNACan_NK", "Epidish_BPRNACan_CD4", "Epidish_BPRNACan_CD8", "Epidish_BPRNACan_cancer",
  "DeconRNASeq_BPRNACan_B", "DeconRNASeq_BPRNACan_M0", "DeconRNASeq_BPRNACan_M1", "DeconRNASeq_BPRNACan_M2", "DeconRNASeq_BPRNACan_Mono", "DeconRNASeq_BPRNACan_NK", "DeconRNASeq_BPRNACan_CD4", "DeconRNASeq_BPRNACan_CD8", "DeconRNASeq_BPRNACan_cancer",
  "Epidish_BPRNACanProMet_B", "Epidish_BPRNACanProMet_M0", "Epidish_BPRNACanProMet_M1", "Epidish_BPRNACanProMet_M2", "Epidish_BPRNACanProMet_Mono", "Epidish_BPRNACanProMet_NK", "Epidish_BPRNACanProMet_CD4", "Epidish_BPRNACanProMet_CD8", "Epidish_BPRNACanProMet_cancer",
  "DeconRNASeq_BPRNACanProMet_B", "DeconRNASeq_BPRNACanProMet_M0", "DeconRNASeq_BPRNACanProMet_M1", "DeconRNASeq_BPRNACanProMet_M2", "DeconRNASeq_BPRNACanProMet_Mono", "DeconRNASeq_BPRNACanProMet_NK", "DeconRNASeq_BPRNACanProMet_CD4", "DeconRNASeq_BPRNACanProMet_CD8", "DeconRNASeq_BPRNACanProMet_cancer",
  "Epidish_BPRNACan3DProMet_B", "Epidish_BPRNACan3DProMet_M0", "Epidish_BPRNACan3DProMet_M1", "Epidish_BPRNACan3DProMet_M2", "Epidish_BPRNACan3DProMet_Mono", "Epidish_BPRNACan3DProMet_NK", "Epidish_BPRNACan3DProMet_CD4", "Epidish_BPRNACan3DProMet_CD8", "Epidish_BPRNACan3DProMet_cancer",
  "DeconRNASeq_BPRNACan3DProMet_B", "DeconRNASeq_BPRNACan3DProMet_M0", "DeconRNASeq_BPRNACan3DProMet_M1", "DeconRNASeq_BPRNACan3DProMet_M2", "DeconRNASeq_BPRNACan3DProMet_Mono", "DeconRNASeq_BPRNACan3DProMet_NK", "DeconRNASeq_BPRNACan3DProMet_CD4", "DeconRNASeq_BPRNACan3DProMet_CD8", "DeconRNASeq_BPRNACan3DProMet_cancer",
  "Epidish_CBSX.NSCLC_B.cells", "Epidish_CBSX.NSCLC_Monocytes", "Epidish_CBSX.NSCLC_NK.cells", "Epidish_CBSX.NSCLC_T.cells.CD4", "Epidish_CBSX.NSCLC_T.cells.CD8",
  "DeconRNASeq_CBSX.NSCLC_B.cells", "DeconRNASeq_CBSX.NSCLC_Monocytes", "DeconRNASeq_CBSX.NSCLC_NK.cells", "DeconRNASeq_CBSX.NSCLC_T.cells.CD4", "DeconRNASeq_CBSX.NSCLC_T.cells.CD8",
  "Epidish_CBSX.HNSCC_B.cells", "Epidish_CBSX.HNSCC_Macrophages", "Epidish_CBSX.HNSCC_T.cells.CD4", "Epidish_CBSX.HNSCC_T.cells.CD8", "Epidish_CBSX.HNSCC_Malignant.cells",
  "DeconRNASeq_CBSX.HNSCC_B.cells", "DeconRNASeq_CBSX.HNSCC_Macrophages", "DeconRNASeq_CBSX.HNSCC_T.cells.CD4", "DeconRNASeq_CBSX.HNSCC_T.cells.CD8", "DeconRNASeq_CBSX.HNSCC_Malignant.cells",
  "Epidish_CBSX.melanoma_B.cells", "Epidish_CBSX.melanoma_Macrophages", "Epidish_CBSX.melanoma_T.cells.CD4", "Epidish_CBSX.melanoma_T.cells.CD8", "Epidish_CBSX.melanoma_Malignant",
  "DeconRNASeq_CBSX.melanoma_B.cells", "DeconRNASeq_CBSX.melanoma_Macrophages", "DeconRNASeq_CBSX.melanoma_T.cells.CD4", "DeconRNASeq_CBSX.melanoma_T.cells.CD8", "DeconRNASeq_CBSX.melanoma_Malignant",
  "Epidish_CBSX_LM22_Monocytes", "Epidish_CBSX_LM22_Macrophages.M0", "Epidish_CBSX_LM22_Macrophages.M1", "Epidish_CBSX_LM22_Macrophages.M2", "Epidish_CBSX_LM22_NK.cells.activated", "Epidish_CBSX_LM22_T.cells.CD4.memory.activated", "Epidish_CBSX_LM22_T.cells.CD8",
  "DeconRNASeq_CBSX_LM22_Monocytes", "DeconRNASeq_CBSX_LM22_Macrophages.M0", "DeconRNASeq_CBSX_LM22_Macrophages.M1", "DeconRNASeq_CBSX_LM22_Macrophages.M2", "DeconRNASeq_CBSX_LM22_NK.cells.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD8",
  "CBSX.NSCLC_B_cells", "CBSX.NSCLC_Monocytes", "CBSX.NSCLC_NK_cells", "CBSX.NSCLC_T_cells_CD4", "CBSX.NSCLC_T_cells_CD8",
  "CBSX.HNSCC_B_cells", "CBSX.HNSCC_Macrophages", "CBSX.HNSCC_T_cells_CD4", "CBSX.HNSCC_T_cells_CD8", "CBSX.HNSCC_Malignant_cells",
  "CBSX.melanoma_B_cells", "CBSX.melanoma_Macrophages", "CBSX.melanoma_T_cells_CD4", "CBSX.melanoma_T_cells_CD8", "CBSX.melanoma_Malignant",
  "CBSX.LM22_Monocytes", "CBSX.LM22_Macrophages_M0", "CBSX.LM22_Macrophages_M1", "CBSX.LM22_Macrophages_M2", "CBSX.LM22_NK_cells_activated", "CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD8"
                               ))
rownames(nonMeta) = nonMeta$Samples
nonMeta = nonMeta[,-1]

nonMeta$Quantiseq_Macrophages = nonMeta$Quantiseq_Macrophage_M1 + nonMeta$Quantiseq_Macrophage_M2 + nonMeta$Quantiseq_Monocyte
nonMeta$Epidish_BPRNACan_Macro = nonMeta$Epidish_BPRNACan_M0 + nonMeta$Epidish_BPRNACan_M1 + nonMeta$Epidish_BPRNACan_M2 + nonMeta$Epidish_BPRNACan_Mono
nonMeta$Epidish_BPRNACanProMet_Macro = nonMeta$Epidish_BPRNACanProMet_M0 + nonMeta$Epidish_BPRNACanProMet_M1 + nonMeta$Epidish_BPRNACanProMet_M2 + nonMeta$Epidish_BPRNACanProMet_Mono
nonMeta$Epidish_BPRNACan3DProMet_Macro = nonMeta$Epidish_BPRNACan3DProMet_M0 + nonMeta$Epidish_BPRNACan3DProMet_M1 + nonMeta$Epidish_BPRNACan3DProMet_M2 + nonMeta$Epidish_BPRNACan3DProMet_Mono
nonMeta$Epidish_CBSX_LM22_Macrophages = nonMeta$Epidish_CBSX_LM22_Macrophages.M0 + nonMeta$Epidish_CBSX_LM22_Macrophages.M1 + nonMeta$Epidish_CBSX_LM22_Macrophages.M2 + nonMeta$Epidish_CBSX_LM22_Monocytes
nonMeta$DeconRNASeq_BPRNACan_Macro = nonMeta$DeconRNASeq_BPRNACan_M0 + nonMeta$DeconRNASeq_BPRNACan_M1 + nonMeta$DeconRNASeq_BPRNACan_M2 + nonMeta$DeconRNASeq_BPRNACan_Mono
nonMeta$DeconRNASeq_BPRNACanProMet_Macro = nonMeta$DeconRNASeq_BPRNACanProMet_M0 + nonMeta$DeconRNASeq_BPRNACanProMet_M1 + nonMeta$DeconRNASeq_BPRNACanProMet_M2 + nonMeta$DeconRNASeq_BPRNACanProMet_Mono
nonMeta$DeconRNASeq_BPRNACan3DProMet_Macro = nonMeta$DeconRNASeq_BPRNACan3DProMet_M0 + nonMeta$DeconRNASeq_BPRNACan3DProMet_M1 + nonMeta$DeconRNASeq_BPRNACan3DProMet_M2 + nonMeta$DeconRNASeq_BPRNACan3DProMet_Mono
nonMeta$DeconRNASeq_CBSX_LM22_Macrophages = nonMeta$DeconRNASeq_CBSX_LM22_Macrophages.M0 + nonMeta$DeconRNASeq_CBSX_LM22_Macrophages.M1 + nonMeta$DeconRNASeq_CBSX_LM22_Macrophages.M2 + nonMeta$DeconRNASeq_CBSX_LM22_Monocytes
nonMeta$CBSX.LM22_Macrophages = nonMeta$CBSX.LM22_Macrophages_M0 + nonMeta$CBSX.LM22_Macrophages_M1 + nonMeta$CBSX.LM22_Macrophages_M2 + nonMeta$CBSX.LM22_Monocytes

# Get correlation and Pvalue for each cell type with facs CBSX.NSCLC_B.cells
nonMeta.corr = rcorr(as.matrix(nonMeta), as.matrix(nonMeta_facs))
nonMeta.pval = nonMeta.corr$P[, 143:150]
nonMeta.corr = nonMeta.corr$r[, 143:150]

# Create the table for the heatmap Macro, NK, CD4, CD8, Cancer
Melanoma_GSE72056_all_signs = data.frame(
                               "quanTIseq" = c(nonMeta.corr[133,4], nonMeta.corr[5,5], nonMeta.corr[6,1], nonMeta.corr[7,2], NA),
                               "MCPcounter" = c(nonMeta.corr[9,4], nonMeta.corr[10,5], NA, nonMeta.corr[11,2], NA),
                               "EpiDISH BPRNACan" = c(nonMeta.corr[133,4], nonMeta.corr[17,5], nonMeta.corr[18,1], nonMeta.corr[19,2], nonMeta.corr[20,8]),
                               "EpiDISH BPRNACanProMet" = c(nonMeta.corr[134,4], nonMeta.corr[35,5], nonMeta.corr[36,1], nonMeta.corr[37,2], nonMeta.corr[38,8]),
                               "EpiDISH BPRNACan3DProMet" = c(nonMeta.corr[135,4], nonMeta.corr[53,5], nonMeta.corr[54,1], nonMeta.corr[55,2], nonMeta.corr[56,8]),
                               "EpiDISH Melanoma" = c(nonMeta.corr[87,4], NA, nonMeta.corr[88,1], nonMeta.corr[89,2], nonMeta.corr[90,8]),
                               "EpiDISH HNSCC" = c(nonMeta.corr[77,4], NA, nonMeta.corr[78,1], nonMeta.corr[79,2], nonMeta.corr[80,8]),
                               "EpiDISH NSCLC" = c(nonMeta.corr[67,4], nonMeta.corr[68,5], nonMeta.corr[69,1], nonMeta.corr[70,2],NA),
                               "EpiDISH LM22" = c(nonMeta.corr[136,4], nonMeta.corr[100,5], nonMeta.corr[101,1], nonMeta.corr[102,2], NA),

                               "DeconRNASeq BPRNACan" = c(nonMeta.corr[137,4], nonMeta.corr[26,5], nonMeta.corr[27,1], nonMeta.corr[28,2], nonMeta.corr[29,8]),
                               "DeconRNASeq BPRNACanProMet" = c(nonMeta.corr[138,4], nonMeta.corr[44,5], nonMeta.corr[45,1], nonMeta.corr[46,2], nonMeta.corr[47,8]),
                               "DeconRNASeq BPRNACan3DProMet" = c(nonMeta.corr[139,4], nonMeta.corr[62,5], nonMeta.corr[63,1], nonMeta.corr[64,2], nonMeta.corr[65,8]),
                               "DeconRNASeq Melanoma" = c(nonMeta.corr[92,4], NA, nonMeta.corr[93,1], nonMeta.corr[94,2], nonMeta.corr[95,8]),
                               "DeconRNASeq HNSCC" = c(nonMeta.corr[82,4], NA, nonMeta.corr[83,1], nonMeta.corr[84,2], nonMeta.corr[85,8]),
                               "DeconRNASeq NSCLC" = c(nonMeta.corr[72,4], nonMeta.corr[73,5], nonMeta.corr[74,1], nonMeta.corr[75,2],NA),
                               "DeconRNASeq LM22" = c(nonMeta.corr[140,4], nonMeta.corr[100,5], nonMeta.corr[101,1], nonMeta.corr[102,2], NA),

                               "CIBERSORTx Melanoma" = c(nonMeta.corr[121,4], NA, nonMeta.corr[122,1], nonMeta.corr[123,2], nonMeta.corr[124,8]),
                               "CIBERSORTx HNSCC" = c(nonMeta.corr[116,4], NA, nonMeta.corr[117,1], nonMeta.corr[118,2], nonMeta.corr[119,8]),
                               "CIBERSORTx NSCLC" = c(nonMeta.corr[111,4], nonMeta.corr[112,5], nonMeta.corr[113,1], nonMeta.corr[114,2], NA),
                               "CIBERSORTx LM22" = c(nonMeta.corr[141,4], nonMeta.corr[129,5], nonMeta.corr[130,1], nonMeta.corr[131,2], NA)
                               ) %>% 
  round(., 2) %>% t(.) %>% as.data.frame(.)
colnames(Melanoma_GSE72056_all_signs) = c("Macrophages", "NK", "CD4", "CD8", "Cancer")

Melanoma_GSE72056_all_signs_p  = data.frame(
                               "quanTIseq" = c(nonMeta.pval[133,4], nonMeta.pval[5,5], nonMeta.pval[6,1], nonMeta.pval[7,2], NA),
                               "MCPcounter" = c(nonMeta.pval[9,4], nonMeta.pval[10,5], NA, nonMeta.pval[11,2], NA),
                               "EpiDISH BPRNACan" = c(nonMeta.pval[133,4], nonMeta.pval[17,5], nonMeta.pval[18,1], nonMeta.pval[19,2], nonMeta.pval[20,8]),
                               "EpiDISH BPRNACanProMet" = c(nonMeta.pval[134,4], nonMeta.pval[35,5], nonMeta.pval[36,1], nonMeta.pval[37,2], nonMeta.pval[38,8]),
                               "EpiDISH BPRNACan3DProMet" = c(nonMeta.pval[135,4], nonMeta.pval[53,5], nonMeta.pval[54,1], nonMeta.pval[55,2], nonMeta.pval[56,8]),
                               "EpiDISH Melanoma" = c(nonMeta.pval[87,4], NA, nonMeta.pval[88,1], nonMeta.pval[89,2], nonMeta.pval[90,8]),
                               "EpiDISH HNSCC" = c(nonMeta.pval[77,4], NA, nonMeta.pval[78,1], nonMeta.pval[79,2], nonMeta.pval[80,8]),
                               "EpiDISH NSCLC" = c(nonMeta.pval[67,4], nonMeta.pval[68,5], nonMeta.pval[69,1], nonMeta.pval[70,2],NA),
                               "EpiDISH LM22" = c(nonMeta.pval[136,4], nonMeta.pval[100,5], nonMeta.pval[101,1], nonMeta.pval[102,2], NA),

                               "DeconRNASeq BPRNACan" = c(nonMeta.pval[137,4], nonMeta.pval[26,5], nonMeta.pval[27,1], nonMeta.pval[28,2], nonMeta.pval[29,8]),
                               "DeconRNASeq BPRNACanProMet" = c(nonMeta.pval[138,4], nonMeta.pval[44,5], nonMeta.pval[45,1], nonMeta.pval[46,2], nonMeta.pval[47,8]),
                               "DeconRNASeq BPRNACan3DProMet" = c(nonMeta.pval[139,4], nonMeta.pval[62,5], nonMeta.pval[63,1], nonMeta.pval[64,2], nonMeta.pval[65,8]),
                               "DeconRNASeq Melanoma" = c(nonMeta.pval[92,4], NA, nonMeta.pval[93,1], nonMeta.pval[94,2], nonMeta.pval[95,8]),
                               "DeconRNASeq HNSCC" = c(nonMeta.pval[82,4], NA, nonMeta.pval[83,1], nonMeta.pval[84,2], nonMeta.pval[85,8]),
                               "DeconRNASeq NSCLC" = c(nonMeta.pval[72,4], nonMeta.pval[73,5], nonMeta.pval[74,1], nonMeta.pval[75,2],NA),
                               "DeconRNASeq LM22" = c(nonMeta.pval[140,4], nonMeta.pval[100,5], nonMeta.pval[101,1], nonMeta.pval[102,2], NA),

                               "CIBERSORTx Melanoma" = c(nonMeta.pval[121,4], NA, nonMeta.pval[122,1], nonMeta.pval[123,2], nonMeta.pval[124,8]),
                               "CIBERSORTx HNSCC" = c(nonMeta.pval[116,4], NA, nonMeta.pval[117,1], nonMeta.pval[118,2], nonMeta.pval[119,8]),
                               "CIBERSORTx NSCLC" = c(nonMeta.pval[111,4], nonMeta.pval[112,5], nonMeta.pval[113,1], nonMeta.pval[114,2], NA),
                               "CIBERSORTx LM22" = c(nonMeta.pval[141,4], nonMeta.pval[129,5], nonMeta.pval[130,1], nonMeta.pval[131,2], NA)
                               ) %>% 
  round(., 2) %>% t(.) %>% as.data.frame(.)
colnames(Melanoma_GSE72056_all_signs_p) = c("Macrophages", "NK", "CD4", "CD8", "Cancer")

Melanoma_GSE72056_all_signs["Mean", ] = colMeans(Melanoma_GSE72056_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE72056_all_signs_p["Mean", ] = colMeans(Melanoma_GSE72056_all_signs_p, na.rm = T)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

melt_Melanoma_GSE72056 <- melt(Melanoma_GSE72056_all_signs)

melt_Melanoma_GSE72056_Pvalue <- melt(Melanoma_GSE72056_all_signs_p)

merge_Melanoma_GSE72056 <- cbind(melt_Melanoma_GSE72056, melt_Melanoma_GSE72056_Pvalue) %>% .[,-3]

melt_merge_Melanoma_GSE72056 <- merge_Melanoma_GSE72056 %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA"),
        is.na(value.1) & (value == 0) ~ paste(value),
        value.1 >= 0.05 ~ paste(value),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_Melanoma_GSE72056$new_Var2 <- rownames(Melanoma_GSE72056_all_signs)
melt_merge_Melanoma_GSE72056$new_Var2 <- factor(melt_merge_Melanoma_GSE72056$new_Var2, levels = unique(melt_merge_Melanoma_GSE72056$new_Var2))

Melanoma_GSE72056_figure <- ggplot(melt_merge_Melanoma_GSE72056, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(),
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5, size = 14, colour = "black"), axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 Melanoma non-metastatic (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 )) 
Melanoma_GSE72056_figure
```

## Melanoma metastatic
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# Load data
meta = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_Melanoma_GSE93722.txt")
meta_facs = read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE93722.txt")

colnames(meta) = colnames(meta) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(meta) = colnames(meta) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(meta) = colnames(meta) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(meta) = colnames(meta) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")

# Select cell types available in facs data. Here B, NK, CD4, CD8, Cancer
meta = meta %>% select(c( "Samples",
  "Quantiseq_B_cell", "Quantiseq_NK_cell", "Quantiseq_T_cell_CD4._.non.regulatory.", "Quantiseq_T_cell_CD8.",
  "MCP_B_lineage", "MCP_NK_cells", "MCP_CD8_T_cells",
  "Epidish_BPRNACan_B", "Epidish_BPRNACan_NK", "Epidish_BPRNACan_CD4", "Epidish_BPRNACan_CD8", "Epidish_BPRNACan_cancer",
  "DeconRNASeq_BPRNACan_B", "DeconRNASeq_BPRNACan_NK", "DeconRNASeq_BPRNACan_CD4", "DeconRNASeq_BPRNACan_CD8", "DeconRNASeq_BPRNACan_cancer",
  "Epidish_BPRNACanProMet_B", "Epidish_BPRNACanProMet_NK", "Epidish_BPRNACanProMet_CD4", "Epidish_BPRNACanProMet_CD8", "Epidish_BPRNACanProMet_cancer",
  "DeconRNASeq_BPRNACanProMet_B", "DeconRNASeq_BPRNACanProMet_NK", "DeconRNASeq_BPRNACanProMet_CD4", "DeconRNASeq_BPRNACanProMet_CD8", "DeconRNASeq_BPRNACanProMet_cancer",
  "Epidish_BPRNACan3DProMet_B", "Epidish_BPRNACan3DProMet_NK", "Epidish_BPRNACan3DProMet_CD4", "Epidish_BPRNACan3DProMet_CD8", "Epidish_BPRNACan3DProMet_cancer",
  "DeconRNASeq_BPRNACan3DProMet_B", "DeconRNASeq_BPRNACan3DProMet_NK", "DeconRNASeq_BPRNACan3DProMet_CD4", "DeconRNASeq_BPRNACan3DProMet_CD8", "DeconRNASeq_BPRNACan3DProMet_cancer",
  "Epidish_CBSX.NSCLC_B.cells", "Epidish_CBSX.NSCLC_NK.cells", "Epidish_CBSX.NSCLC_T.cells.CD4", "Epidish_CBSX.NSCLC_T.cells.CD8",
  "DeconRNASeq_CBSX.NSCLC_B.cells", "DeconRNASeq_CBSX.NSCLC_NK.cells", "DeconRNASeq_CBSX.NSCLC_T.cells.CD4", "DeconRNASeq_CBSX.NSCLC_T.cells.CD8",
  "Epidish_CBSX.HNSCC_B.cells", "Epidish_CBSX.HNSCC_T.cells.CD4", "Epidish_CBSX.HNSCC_T.cells.CD8", "Epidish_CBSX.HNSCC_Malignant.cells",
  "DeconRNASeq_CBSX.HNSCC_B.cells", "DeconRNASeq_CBSX.HNSCC_T.cells.CD4", "DeconRNASeq_CBSX.HNSCC_T.cells.CD8", "DeconRNASeq_CBSX.HNSCC_Malignant.cells",
  "Epidish_CBSX.melanoma_B.cells", "Epidish_CBSX.melanoma_T.cells.CD4", "Epidish_CBSX.melanoma_T.cells.CD8", "Epidish_CBSX.melanoma_Malignant",
  "DeconRNASeq_CBSX.melanoma_B.cells","DeconRNASeq_CBSX.melanoma_T.cells.CD4", "DeconRNASeq_CBSX.melanoma_T.cells.CD8", "DeconRNASeq_CBSX.melanoma_Malignant",
  "Epidish_CBSX_LM22_B.cells.memory", "Epidish_CBSX_LM22_NK.cells.activated", "Epidish_CBSX_LM22_T.cells.CD4.memory.activated", "Epidish_CBSX_LM22_T.cells.CD8",
  "DeconRNASeq_CBSX_LM22_B.cells.memory", "DeconRNASeq_CBSX_LM22_NK.cells.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated", "DeconRNASeq_CBSX_LM22_T.cells.CD8",
  "CBSX.NSCLC_B_cells", "CBSX.NSCLC_NK_cells", "CBSX.NSCLC_T_cells_CD4", "CBSX.NSCLC_T_cells_CD8",
  "CBSX.HNSCC_B_cells", "CBSX.HNSCC_T_cells_CD4", "CBSX.HNSCC_T_cells_CD8", "CBSX.HNSCC_Malignant_cells",
  "CBSX.melanoma_B_cells", "CBSX.melanoma_T_cells_CD4", "CBSX.melanoma_T_cells_CD8", "CBSX.melanoma_Malignant",
  "CBSX.LM22_B_cells_memory", "CBSX.LM22_NK_cells_activated", "CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD8"
                               ))
rownames(meta) = meta$Samples
meta = meta[,-1]

# Get correlation and Pvalue for each cell type with facs CBSX.NSCLC_B.cells
# Create the table for the heatmap B, NK, CD4, CD8, Cancer
# Correlations one by one as there's only 4 samples
Melanoma_GSE93722_all_signs = data.frame(
                               "quanTIseq" = c(cor.test(meta$Quantiseq_B_cell, meta_facs$Bcells)$estimate, cor.test(meta$Quantiseq_NK_cell, meta_facs$NKcells)$estimate,
                                               cor.test(meta$Quantiseq_T_cell_CD4._.non.regulatory., meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$Quantiseq_T_cell_CD8., meta_facs$CD8_Tcells)$estimate, NA),
                               "MCPcounter" = c(cor.test(meta$MCP_B_lineage, meta_facs$Bcells)$estimate, cor.test(meta$MCP_NK_cells, meta_facs$NKcells)$estimate, NA,
                                               cor.test(meta$MCP_CD8_T_cells, meta_facs$CD8_Tcells)$estimate, NA),
                               "EpiDISH BPRNACan" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$estimate, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACan_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACan_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$Epidish_BPRNACan_cancer,meta_facs$Cancer_cells)$estimate),
                               "EpiDISH BPRNACanProMet" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$estimate, 
                                                              cor.test(meta$Epidish_BPRNACanProMet_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACanProMet_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACanProMet_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$Epidish_BPRNACanProMet_cancer,meta_facs$Cancer_cells)$estimate),
                               "EpiDISH BPRNACan3DProMet" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$estimate,
                                                                cor.test(meta$Epidish_BPRNACan3DProMet_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_cancer,meta_facs$Cancer_cells)$estimate),
                               "EpiDISH Melanoma" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$estimate,
                                                      NA, cor.test(meta$Epidish_CBSX.melanoma_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$Epidish_CBSX.melanoma_T.cells.CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$Epidish_CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$estimate),
                               "EpiDISH HNSCC" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$estimate,
                                                     NA, cor.test(meta$Epidish_CBSX.HNSCC_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$Epidish_CBSX.HNSCC_T.cells.CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$Epidish_CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$estimate),
                               "EpiDISH NSCLC" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$estimate,
                                                     cor.test(meta$Epidish_CBSX.NSCLC_NK.cells, meta_facs$NKcells)$estimate, 
                                                     cor.test(meta$Epidish_CBSX.NSCLC_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$Epidish_CBSX.NSCLC_T.cells.CD8, meta_facs$CD8_Tcells)$estimate, NA),
                               "EpiDISH LM22" = c(cor.test(meta$Epidish_CBSX_LM22_B.cells.memory, meta_facs$Bcells)$estimate,
                                                  cor.test(meta$Epidish_CBSX_LM22_NK.cells.activated, meta_facs$NKcells)$estimate,
                                                  cor.test(meta$Epidish_CBSX_LM22_T.cells.CD4.memory.activated, meta_facs$CD4_Tcells)$estimate,
                                                  cor.test(meta$Epidish_CBSX_LM22_T.cells.CD8, meta_facs$CD8_Tcells)$estimate, NA),

                               "DeconRNASeq BPRNACan" = c(cor.test(meta$DeconRNASeq_BPRNACan_B, meta_facs$Bcells)$estimate, 
                                                            cor.test(meta$DeconRNASeq_BPRNACan_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACan_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACan_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$DeconRNASeq_BPRNACan_cancer,meta_facs$Cancer_cells)$estimate),
                               "DeconRNASeq BPRNACanProMet" = c(cor.test(meta$DeconRNASeq_BPRNACanProMet_B, meta_facs$Bcells)$estimate, 
                                                              cor.test(meta$DeconRNASeq_BPRNACanProMet_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_cancer,meta_facs$Cancer_cells)$estimate),
                               "DeconRNASeq BPRNACan3DProMet" = c(cor.test(meta$DeconRNASeq_BPRNACan3DProMet_B, meta_facs$Bcells)$estimate,
                                                                cor.test(meta$DeconRNASeq_BPRNACan3DProMet_NK, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_CD4, meta_facs$CD4_Tcells)$estimate,
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_CD8, meta_facs$CD8_Tcells)$estimate, 
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_cancer,meta_facs$Cancer_cells)$estimate),
                               "DeconRNASeq Melanoma" = c(cor.test(meta$DeconRNASeq_CBSX.melanoma_B.cells, meta_facs$Bcells)$estimate,
                                                      NA, cor.test(meta$DeconRNASeq_CBSX.melanoma_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$DeconRNASeq_CBSX.melanoma_T.cells.CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$DeconRNASeq_CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$estimate),
                               "DeconRNASeq HNSCC" = c(cor.test(meta$DeconRNASeq_CBSX.HNSCC_B.cell, meta_facs$Bcells)$estimate,
                                                     NA, cor.test(meta$DeconRNASeq_CBSX.HNSCC_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$DeconRNASeq_CBSX.HNSCC_T.cells.CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$DeconRNASeq_CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$estimate),
                               "DeconRNASeq NSCLC" = c(cor.test(meta$DeconRNASeq_CBSX.NSCLC_B.cells, meta_facs$Bcells)$estimate,
                                                     cor.test(meta$DeconRNASeq_CBSX.NSCLC_NK.cells, meta_facs$NKcells)$estimate, 
                                                     cor.test(meta$DeconRNASeq_CBSX.NSCLC_T.cells.CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$DeconRNASeq_CBSX.NSCLC_T.cells.CD8, meta_facs$CD8_Tcells)$estimate, NA),
                               "DeconRNASeq LM22" = c(cor.test(meta$DeconRNASeq_CBSX_LM22_B.cells.memory, meta_facs$Bcells)$estimate,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_NK.cells.activated, meta_facs$NKcells)$estimate,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated, meta_facs$CD4_Tcells)$estimate,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_T.cells.CD8, meta_facs$CD8_Tcells)$estimate, NA),

                               "CIBERSORTx Melanoma" = c(cor.test(meta$CBSX.melanoma_B_cells, meta_facs$Bcells)$estimate,
                                                           NA, cor.test(meta$CBSX.melanoma_T_cells_CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$CBSX.melanoma_T_cells_CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$estimate),
                               "CIBERSORTx HNSCC" = c(cor.test(meta$CBSX.HNSCC_B_cell, meta_facs$Bcells)$estimate,
                                                        NA, cor.test(meta$CBSX.HNSCC_T_cells_CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$CBSX.HNSCC_T_cells_CD8, meta_facs$CD8_Tcells)$estimate,
                                               cor.test(meta$CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$estimate),
                               "CIBERSORTx NSCLC" = c(cor.test(meta$CBSX.NSCLC_B_cells, meta_facs$Bcells)$estimate,
                                                        cor.test(meta$CBSX.NSCLC_NK_cells, meta_facs$NKcells)$estimate,
                                                        cor.test(meta$CBSX.NSCLC_T_cells_CD4, meta_facs$CD4_Tcells)$estimate,
                                               cor.test(meta$CBSX.NSCLC_T_cells_CD8, meta_facs$CD8_Tcells)$estimate, NA),
                               "CIBERSORTx LM22" = c(cor.test(meta$CBSX.LM22_B_cells_memory, meta_facs$Bcells)$estimate,
                                                  cor.test(meta$CBSX.LM22_NK_cells_activated, meta_facs$NKcells)$estimate,
                                                  cor.test(meta$CBSX.LM22_T_cells_CD4_memory_activated, meta_facs$CD4_Tcells)$estimate,
                                                  cor.test(meta$CBSX.LM22_T_cells_CD8, meta_facs$CD8_Tcells)$estimate, NA)
                               ) %>% round(., 2) %>% t(.) %>% as.data.frame(.)
colnames(Melanoma_GSE93722_all_signs) = c("B", "NK", "CD4", "CD8", "Cancer")

Melanoma_GSE93722_all_signs_p  = data.frame(
  "quanTIseq" = c(cor.test(meta$Quantiseq_B_cell, meta_facs$Bcells)$p.value, cor.test(meta$Quantiseq_NK_cell, meta_facs$NKcells)$p.value,
                                               cor.test(meta$Quantiseq_T_cell_CD4._.non.regulatory., meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$Quantiseq_T_cell_CD8., meta_facs$CD8_Tcells)$p.value, NA),
                               "MCPcounter" = c(cor.test(meta$MCP_B_lineage, meta_facs$Bcells)$p.value, cor.test(meta$MCP_NK_cells, meta_facs$NKcells)$p.value, NA,
                                               cor.test(meta$MCP_CD8_T_cells, meta_facs$CD8_Tcells)$p.value, NA),
                               "EpiDISH (BPRNACan)" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$p.value, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACan_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACan_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$Epidish_BPRNACan_cancer,meta_facs$Cancer_cells)$p.value),
                               "EpiDISH (BPRNACanProMet)" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 
                                                              cor.test(meta$Epidish_BPRNACanProMet_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACanProMet_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACanProMet_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$Epidish_BPRNACanProMet_cancer,meta_facs$Cancer_cells)$p.value),
                               "EpiDISH (BPRNACan3DProMet)" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,
                                                                cor.test(meta$Epidish_BPRNACan3DProMet_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$Epidish_BPRNACan3DProMet_cancer,meta_facs$Cancer_cells)$p.value),
                               "EpiDISH (Melanoma)" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,
                                                      NA, cor.test(meta$Epidish_CBSX.melanoma_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$Epidish_CBSX.melanoma_T.cells.CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$Epidish_CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$p.value),
                               "EpiDISH (HNSCC)" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,
                                                     NA, cor.test(meta$Epidish_CBSX.HNSCC_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$Epidish_CBSX.HNSCC_T.cells.CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$Epidish_CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$p.value),
                               "EpiDISH (NSCLC)" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,
                                                     cor.test(meta$Epidish_CBSX.NSCLC_NK.cells, meta_facs$NKcells)$p.value, 
                                                     cor.test(meta$Epidish_CBSX.NSCLC_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$Epidish_CBSX.NSCLC_T.cells.CD8, meta_facs$CD8_Tcells)$p.value, NA),
                                "EpiDISH LM22" = c(cor.test(meta$Epidish_CBSX_LM22_B.cells.memory, meta_facs$Bcells)$p.value,
                                                  cor.test(meta$Epidish_CBSX_LM22_NK.cells.activated, meta_facs$NKcells)$p.value,
                                                  cor.test(meta$Epidish_CBSX_LM22_T.cells.CD4.memory.activated, meta_facs$CD4_Tcells)$p.value,
                                                  cor.test(meta$Epidish_CBSX_LM22_T.cells.CD8, meta_facs$CD8_Tcells)$p.value, NA),

                               "DeconRNASeq BPRNACan" = c(cor.test(meta$DeconRNASeq_BPRNACan_B, meta_facs$Bcells)$p.value, 
                                                            cor.test(meta$DeconRNASeq_BPRNACan_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACan_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACan_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$DeconRNASeq_BPRNACan_cancer,meta_facs$Cancer_cells)$p.value),
                               "DeconRNASeq BPRNACanProMet" = c(cor.test(meta$DeconRNASeq_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 
                                                              cor.test(meta$DeconRNASeq_BPRNACanProMet_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$DeconRNASeq_BPRNACanProMet_cancer,meta_facs$Cancer_cells)$p.value),
                               "DeconRNASeq BPRNACan3DProMet" = c(cor.test(meta$DeconRNASeq_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,
                                                                cor.test(meta$DeconRNASeq_BPRNACan3DProMet_NK, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_CD4, meta_facs$CD4_Tcells)$p.value,
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_CD8, meta_facs$CD8_Tcells)$p.value, 
                                                        cor.test(meta$DeconRNASeq_BPRNACan3DProMet_cancer,meta_facs$Cancer_cells)$p.value),
                               "DeconRNASeq Melanoma" = c(cor.test(meta$DeconRNASeq_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,
                                                      NA, cor.test(meta$DeconRNASeq_CBSX.melanoma_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$DeconRNASeq_CBSX.melanoma_T.cells.CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$DeconRNASeq_CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$p.value),
                               "DeconRNASeq HNSCC" = c(cor.test(meta$DeconRNASeq_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,
                                                     NA, cor.test(meta$DeconRNASeq_CBSX.HNSCC_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$DeconRNASeq_CBSX.HNSCC_T.cells.CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$DeconRNASeq_CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$p.value),
                               "DeconRNASeq NSCLC" = c(cor.test(meta$DeconRNASeq_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,
                                                     cor.test(meta$DeconRNASeq_CBSX.NSCLC_NK.cells, meta_facs$NKcells)$p.value, 
                                                     cor.test(meta$DeconRNASeq_CBSX.NSCLC_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$DeconRNASeq_CBSX.NSCLC_T.cells.CD8, meta_facs$CD8_Tcells)$p.value, NA),
                               "DeconRNASeq LM22" = c(cor.test(meta$DeconRNASeq_CBSX_LM22_B.cells.memory, meta_facs$Bcells)$p.value,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_NK.cells.activated, meta_facs$NKcells)$p.value,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated, meta_facs$CD4_Tcells)$p.value,
                                                  cor.test(meta$DeconRNASeq_CBSX_LM22_T.cells.CD8, meta_facs$CD8_Tcells)$p.value, NA),

                               "CIBERSORTx Melanoma" = c(cor.test(meta$CBSX.melanoma_B_cells, meta_facs$Bcells)$p.value,
                                                           NA, cor.test(meta$CBSX.melanoma_T_cells_CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$CBSX.melanoma_T_cells_CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$p.value),
                               "CIBERSORTx HNSCC" = c(cor.test(meta$CBSX.HNSCC_B_cell, meta_facs$Bcells)$p.value,
                                                        NA, cor.test(meta$CBSX.HNSCC_T_cells_CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$CBSX.HNSCC_T_cells_CD8, meta_facs$CD8_Tcells)$p.value,
                                               cor.test(meta$CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$p.value),
                               "CIBERSORTx NSCLC" = c(cor.test(meta$CBSX.NSCLC_B_cells, meta_facs$Bcells)$p.value,
                                                        cor.test(meta$CBSX.NSCLC_NK_cells, meta_facs$NKcells)$p.value,
                                                        cor.test(meta$CBSX.NSCLC_T_cells_CD4, meta_facs$CD4_Tcells)$p.value,
                                               cor.test(meta$CBSX.NSCLC_T_cells_CD8, meta_facs$CD8_Tcells)$p.value, NA),
                               "CIBERSORTx LM22" = c(cor.test(meta$CBSX.LM22_B_cells_memory, meta_facs$Bcells)$p.value,
                                                  cor.test(meta$CBSX.LM22_NK_cells_activated, meta_facs$NKcells)$p.value,
                                                  cor.test(meta$CBSX.LM22_T_cells_CD4_memory_activated, meta_facs$CD4_Tcells)$p.value,
                                                  cor.test(meta$CBSX.LM22_T_cells_CD8, meta_facs$CD8_Tcells)$p.value, NA)
  ) %>% 
  round(., 2) %>% t(.) %>% as.data.frame(.) 
colnames(Melanoma_GSE93722_all_signs_p) = c("B", "NK", "CD4", "CD8", "Cancer")

Melanoma_GSE93722_all_signs["Mean", ] = colMeans(Melanoma_GSE93722_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE93722_all_signs_p["Mean", ] = colMeans(Melanoma_GSE93722_all_signs_p, na.rm = T)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

melt_Melanoma_GSE93722 <- melt(Melanoma_GSE93722_all_signs)

melt_Melanoma_GSE93722_Pvalue <- melt(Melanoma_GSE93722_all_signs_p)

merge_Melanoma_GSE93722 <- cbind(melt_Melanoma_GSE93722, melt_Melanoma_GSE93722_Pvalue) %>% .[,-3]

melt_merge_Melanoma_GSE93722 <- merge_Melanoma_GSE93722 %>%
    mutate(text = case_when( 
        is.na(value.1) & is.na(value) ~ paste("NA"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

melt_merge_Melanoma_GSE93722$new_Var2 <- rownames(Melanoma_GSE93722_all_signs)
melt_merge_Melanoma_GSE93722$new_Var2 <- factor(melt_merge_Melanoma_GSE93722$new_Var2, levels = unique(melt_merge_Melanoma_GSE93722$new_Var2))

Melanoma_GSE93722_figure <- ggplot(melt_merge_Melanoma_GSE93722, aes(new_Var2, variable)) + 
    geom_tile(aes(fill = value), colour = "grey", size = 1)+
    scale_fill_gradient2(low = "#5C5DAF",mid = "white",high = "#EA2E2D") +

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5, size = 14, colour = "black"), 
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 Melanoma metastatic (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

#Figure_3c <- ggarrange(Melanoma_GSE93722_figure, ncol = 1, nrow = 1, labels = "e", font.label = list(size = 20, color = "black"))
Melanoma_GSE93722_figure
```

# Figure 4 :  TCGA all CibersortX comparison

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

# Load and parse data

tcga_deconv = read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_all_TCGA.txt", header=T)
Aran_all_facs <- read.csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv", sep = "\t")
HE_all_TCGA <- read.csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv", row.names = 1)

colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")

HE_all_TCGA$ParticipantBarcode <- HE_all_TCGA$ParticipantBarcode %>% str_replace_all(., "-", ".")

Aran_all_facs$Sample_ID <- Aran_all_facs$Sample_ID %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")
Aran_all_facs <- Aran_all_facs[Aran_all_facs$CPE != "NaN",]

tcga_deconv$Samples <- tcga_deconv$Samples %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")

Comm_samples <- Reduce(intersect, list(HE_all_TCGA$ParticipantBarcode, Aran_all_facs$Sample_ID, tcga_deconv$Samples))

Aran_all_facs <- Aran_all_facs %>% .[.$Sample_ID %in% Comm_samples, ] %>% .[order(.$Sample_ID), ]
HE_all_TCGA <- HE_all_TCGA %>% .[.$ParticipantBarcode %in% Comm_samples, ] %>% .[order(.$ParticipantBarcode),]
tcga_deconv <- tcga_deconv %>% .[.$Samples %in% Comm_samples, ]

# REMOVE NON UNIQUE SAMPLES IN TCGA CBX AND DECONV
tcga_deconv <- tcga_deconv %>%
  group_by(Samples) %>%
  summarise_all(mean)%>%
  as.data.frame()
rownames(tcga_deconv) = tcga_deconv$Samples
tcga_deconv <- tcga_deconv[,-1]

# Quantiseq
QT.lymph = tcga_deconv$Quantiseq_T_cell_CD4._.non.regulatory. + tcga_deconv$Quantiseq_T_cell_CD8. + tcga_deconv$Quantiseq_NK_cell
QT.macro = tcga_deconv$Quantiseq_Macrophage_M1 + tcga_deconv$Quantiseq_Macrophage_M2 + tcga_deconv$Quantiseq_Monocyte

# MCP
mcp.lymph = tcga_deconv$MCP_Cytotoxic_lymphocytes + tcga_deconv$MCP_CD8_T_cells + tcga_deconv$MCP_T_cells

# Epidish
epi_BPRNAcan.lymph = tcga_deconv$Epidish_BPRNACan_CD4 + tcga_deconv$Epidish_BPRNACan_CD8 + tcga_deconv$Epidish_BPRNACan_NK
epi_BPRNAcan.macro = tcga_deconv$Epidish_BPRNACan_M0 + tcga_deconv$Epidish_BPRNACan_M1 + tcga_deconv$Epidish_BPRNACan_M2 + tcga_deconv$Epidish_BPRNACan_Mono
# tcga_deconv$Epidish_BPRNACan_Neu

epi_BPRNAcanPro.lymph = tcga_deconv$Epidish_BPRNACanProMet_CD4 + tcga_deconv$Epidish_BPRNACanProMet_CD8 + tcga_deconv$Epidish_BPRNACanProMet_NK
epi_BPRNAcanPro.macro = tcga_deconv$Epidish_BPRNACanProMet_M0 + tcga_deconv$Epidish_BPRNACanProMet_M1 + tcga_deconv$Epidish_BPRNACanProMet_M2 + tcga_deconv$Epidish_BPRNACanProMet_Mono
# tcga_deconv$Epidish_BPRNACanProMet_Neu

epi_BPRNAcanPro3D.lymph = tcga_deconv$Epidish_BPRNACan3DProMet_CD4 + tcga_deconv$Epidish_BPRNACan3DProMet_CD8 + tcga_deconv$Epidish_BPRNACan3DProMet_NK
epi_BPRNAcanPro3D.macro = tcga_deconv$Epidish_BPRNACan3DProMet_M0 + tcga_deconv$Epidish_BPRNACan3DProMet_M1 + tcga_deconv$Epidish_BPRNACan3DProMet_M2 + tcga_deconv$Epidish_BPRNACan3DProMet_Mono
# tcga_deconv$Epidish_BPRNACan3DProMet_Neu

epi_CBX_mela.lymph = tcga_deconv$Epidish_CBSX.melanoma_T.cells.CD4 + tcga_deconv$Epidish_CBSX.melanoma_T.cells.CD8 + tcga_deconv$Epidish_CBSX.melanoma_NK.cells
epi_CBX_mela.macro = tcga_deconv$Epidish_CBSX.melanoma_Macrophages

epi_CBX_NSCLC.lymph = tcga_deconv$Epidish_CBSX.NSCLC_T.cells.CD4 + tcga_deconv$Epidish_CBSX.NSCLC_T.cells.CD8 + tcga_deconv$Epidish_CBSX.NSCLC_NK.cells + tcga_deconv$Epidish_CBSX.NSCLC_NKT.cells
epi_CBX_NSCLC.macro = tcga_deconv$Epidish_CBSX.NSCLC_Monocytes

epi_CBX_HNSCC.lymph = tcga_deconv$Epidish_CBSX.HNSCC_T.cells.CD4 + tcga_deconv$Epidish_CBSX.HNSCC_T.cells.CD8 
epi_CBX_HNSCC.macro = tcga_deconv$Epidish_CBSX.HNSCC_Macrophages

epi_LM22.lymph = tcga_deconv$Epidish_CBSX_LM22_T.cells.CD4.memory.activated + tcga_deconv$Epidish_CBSX_LM22_T.cells.CD4.naive + tcga_deconv$Epidish_CBSX_LM22_T.cells.CD4.memory.resting +
  tcga_deconv$Epidish_CBSX_LM22_T.cells.CD8 + tcga_deconv$Epidish_CBSX_LM22_NK.cells.resting + tcga_deconv$Epidish_CBSX_LM22_NK.cells.activated
epi_LM22.macro = tcga_deconv$Epidish_CBSX_LM22_Macrophages.M0 + tcga_deconv$Epidish_CBSX_LM22_Macrophages.M1 + tcga_deconv$Epidish_CBSX_LM22_Macrophages.M2

# DeconRNAseq
deconRNA_BPRNAcan.lymph = tcga_deconv$DeconRNASeq_BPRNACan_CD4 + tcga_deconv$DeconRNASeq_BPRNACan_CD8 + tcga_deconv$DeconRNASeq_BPRNACan_NK
deconRNA_BPRNAcan.macro = tcga_deconv$DeconRNASeq_BPRNACan_M0 + tcga_deconv$DeconRNASeq_BPRNACan_M1 + tcga_deconv$DeconRNASeq_BPRNACan_M2 + tcga_deconv$DeconRNASeq_BPRNACan_Mono
# tcga_deconv$DeconRNASeq_BPRNACan_Neu

deconRNA_BPRNAcanPro.lymph = tcga_deconv$DeconRNASeq_BPRNACanProMet_CD4 + tcga_deconv$DeconRNASeq_BPRNACanProMet_CD8 + tcga_deconv$DeconRNASeq_BPRNACanProMet_NK
deconRNA_BPRNAcanPro.macro = tcga_deconv$DeconRNASeq_BPRNACanProMet_M0 + tcga_deconv$DeconRNASeq_BPRNACanProMet_M1 + tcga_deconv$DeconRNASeq_BPRNACanProMet_M2 +
  tcga_deconv$DeconRNASeq_BPRNACanProMet_Mono
# tcga_deconv$DeconRNASeq_BPRNACanProMet_Neu

deconRNA_BPRNAcanPro3D.lymph = tcga_deconv$DeconRNASeq_BPRNACan3DProMet_CD4 + tcga_deconv$DeconRNASeq_BPRNACan3DProMet_CD8 + tcga_deconv$DeconRNASeq_BPRNACan3DProMet_NK
deconRNA_BPRNAcanPro3D.macro = tcga_deconv$DeconRNASeq_BPRNACan3DProMet_M0 + tcga_deconv$DeconRNASeq_BPRNACan3DProMet_M1 + tcga_deconv$DeconRNASeq_BPRNACan3DProMet_M2 +
  tcga_deconv$DeconRNASeq_BPRNACan3DProMet_Mono
# tcga_deconv$DeconRNASeq_BPRNACan3DProMet_Neu

deconRNA_CBX_mela.lymph = tcga_deconv$DeconRNASeq_CBSX.melanoma_T.cells.CD4 + tcga_deconv$DeconRNASeq_CBSX.melanoma_T.cells.CD8 + tcga_deconv$DeconRNASeq_CBSX.melanoma_NK.cells
deconRNA_CBX_mela.macro = tcga_deconv$DeconRNASeq_CBSX.melanoma_Macrophages

deconRNA_CBX_NSCLC.lymph = tcga_deconv$DeconRNASeq_CBSX.NSCLC_T.cells.CD4 + tcga_deconv$DeconRNASeq_CBSX.NSCLC_T.cells.CD8 + tcga_deconv$DeconRNASeq_CBSX.NSCLC_NK.cells + tcga_deconv$DeconRNASeq_CBSX.NSCLC_NKT.cells
deconRNA_CBX_NSCLC.macro = tcga_deconv$DeconRNASeq_CBSX.NSCLC_Monocytes

deconRNA_CBX_HNSCC.lymph = tcga_deconv$DeconRNASeq_CBSX.HNSCC_T.cells.CD4 + tcga_deconv$DeconRNASeq_CBSX.HNSCC_T.cells.CD8 
deconRNA_CBX_HNSCC.macro = tcga_deconv$DeconRNASeq_CBSX.HNSCC_Macrophages

deconRNA_LM22.lymph = tcga_deconv$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated + tcga_deconv$DeconRNASeq_CBSX_LM22_T.cells.CD4.naive + tcga_deconv$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting +
  tcga_deconv$DeconRNASeq_CBSX_LM22_T.cells.CD8 + tcga_deconv$DeconRNASeq_CBSX_LM22_NK.cells.resting + tcga_deconv$DeconRNASeq_CBSX_LM22_NK.cells.activated
deconRNA_LM22.macro = tcga_deconv$DeconRNASeq_CBSX_LM22_Macrophages.M0 + tcga_deconv$DeconRNASeq_CBSX_LM22_Macrophages.M1 + tcga_deconv$DeconRNASeq_CBSX_LM22_Macrophages.M2

# CBX NSCLC
cbx_NSCLC.lymph = tcga_deconv$CBSX.NSCLC_T_cells_CD4 + tcga_deconv$CBSX.NSCLC_T_cells_CD8 + tcga_deconv$CBSX.NSCLC_NK_cells + tcga_deconv$CBSX.NSCLC_NKT_cells
cbx_NSCLC.macro = tcga_deconv$CBSX.NSCLC_Monocytes

# CBX HNSCC
cbx_HNSCC.lymph = tcga_deconv$CBSX.HNSCC_T_cells_CD4 + tcga_deconv$CBSX.HNSCC_T_cells_CD8
cbx_HNSCC.macro = tcga_deconv$CBSX.HNSCC_Macrophage

# CBX Melanoma
cbx_mela.lymph = tcga_deconv$CBSX.melanoma_T_cells_CD4 + tcga_deconv$CBSX.melanoma_T_cells_CD8 + tcga_deconv$CBSX.melanoma_NK_cells
cbx_mela.macro = tcga_deconv$CBSX.melanoma_Macrophages

# CBX LM22
cbx_lm22.lymph = tcga_deconv$CBSX.LM22_T_cells_CD4_memory_activated + tcga_deconv$CBSX.LM22_T_cells_CD4_naive + tcga_deconv$CBSX.LM22_T_cells_CD4_memory_resting + 
  tcga_deconv$CBSX.LM22_NK_cells_activated + tcga_deconv$CBSX.LM22_NK_cells_resting
cbx_lm22.macro = tcga_deconv$CBSX.LM22_Monocytes + tcga_deconv$CBSX.LM22_Macrophages_M0 + tcga_deconv$CBSX.LM22_Macrophages_M1 + tcga_deconv$CBSX.LM22_Macrophages_M2

```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

# Create the DF with selected cell types

lymph = data.frame(HE_all_TCGA$Lymphocytes, QT.lymph, epi_BPRNAcan.lymph, epi_BPRNAcanPro.lymph, epi_BPRNAcanPro3D.lymph, epi_CBX_mela.lymph, epi_CBX_NSCLC.lymph, epi_CBX_HNSCC.lymph, epi_LM22.lymph,
                   deconRNA_BPRNAcan.lymph, deconRNA_BPRNAcanPro.lymph, deconRNA_BPRNAcanPro3D.lymph, deconRNA_CBX_mela.lymph, deconRNA_CBX_HNSCC.lymph, deconRNA_CBX_NSCLC.lymph, deconRNA_LM22.lymph, 
                   cbx_NSCLC.lymph, cbx_HNSCC.lymph, cbx_mela.lymph, cbx_lm22.lymph)
colnames(lymph) = c("H&E", "Quantiseq", "Epidish.BPRNACan", "Epidish.BPRNACanProMet", "Epidish.BPRNACan3DProMet", "Epidish.CBX_melanoma", "Epidish.CBX_NSCLC",  
                    "Epidish.CBX_HNSCC", "Epidish.CBX_LM22",
                    "DeconRNAseq.BPRNACan", "DeconRNAseq.BPRNACanProMet", "DeconRNAseq.BPRNACan3DProMet", "DeconRNAseq.CBX_melanoma", "DeconRNAseq.CBX_HNSCC",
                    "DeconRNAseq.CBX_NSCLC", "DeconRNAseq.CBX_LM22", 
                    "CBX.NSCLC", "CBX.HNSCC", "CBX.melanoma", "CBX.LM22")

macro = data.frame(HE_all_TCGA$Macrophages, QT.macro, epi_BPRNAcan.macro, epi_BPRNAcanPro.macro, epi_BPRNAcanPro3D.macro, epi_CBX_mela.macro,  
                   epi_CBX_HNSCC.macro, epi_CBX_NSCLC.macro, epi_LM22.macro, deconRNA_BPRNAcan.macro, deconRNA_BPRNAcanPro.macro, deconRNA_BPRNAcanPro3D.macro, 
                   deconRNA_CBX_mela.macro, deconRNA_CBX_HNSCC.macro, deconRNA_CBX_NSCLC.macro, deconRNA_LM22.macro, cbx_mela.macro, cbx_HNSCC.macro, cbx_NSCLC.macro, cbx_lm22.macro)
colnames(macro) = c("H&E", "Quantiseq", "Epidish.BPRNACan", "Epidish.BPRNACanProMet", "Epidish.BPRNACan3DProMet", "Epidish.CBX_melanoma", "Epidish.CBX_HNSCC",
                    "Epidish.CBX_NSCLC", "Epidish.CBX_LM22",
                    "DeconRNAseq.BPRNACan", "DeconRNAseq.BPRNACanProMet", "DeconRNAseq.BPRNACan3DProMet", "DeconRNAseq.CBX_melanoma", "DeconRNAseq.CBX_HNSCC",
                    "DeconRNAseq.CBX_NSCLC", "DeconRNAseq.CBX_LM22",
                    "CBX.melanoma", "CBX.HNSCC", "CBX.NSCLC", "CBX.LM22")

neutro = data.frame(HE_all_TCGA$Neutrophils, tcga_deconv$Quantiseq_Neutrophil, tcga_deconv$Epidish_BPRNACan_Neu, tcga_deconv$Epidish_BPRNACanProMet_Neu, 
                    tcga_deconv$Epidish_BPRNACan3DProMet_Neu, tcga_deconv$Epidish_CBSX_LM22_Neutrophils, tcga_deconv$DeconRNASeq_BPRNACan_Neu,
                    tcga_deconv$DeconRNASeq_BPRNACanProMet_Neu, tcga_deconv$DeconRNASeq_BPRNACan3DProMet_Neu, tcga_deconv$DeconRNASeq_CBSX_LM22_Neutrophils, tcga_deconv$CBSX.LM22_Neutrophils)
colnames(neutro) = c("H&E", "Quantiseq", "Epidish.BPRNACan", "Epidish.BPRNACanProMet", "Epidish.BPRNACan3DProMet", "Epidish.CBX_LM22", 
                     "DeconRNAseq.BPRNACan", "DeconRNAseq.BPRNACanProMet",  "DeconRNAseq.BPRNACan3DProMet", "DeconRNAseq.CBX_LM22", "CBX.LM22")
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

# Get correlation with ground truth

lymph.corr = rcorr(as.matrix(lymph), HE_all_TCGA$Lymphocytes)$r
lymph.corr = lymph.corr[1:20, 21] %>%  sort(., decreasing = T)

macro.corr = rcorr(as.matrix(macro), HE_all_TCGA$Macrophages)$r
macro.corr = macro.corr[1:20, 21] %>% sort(., decreasing = T)

neutro.corr = rcorr(as.matrix(neutro), HE_all_TCGA$Neutrophils)$r
neutro.corr = neutro.corr[1:11, 12] %>% sort(., decreasing = T)

```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
cols <- c("H&E" = "red", "Cibersort" = "yellow", "Epidish" = "blue", "Quantiseq" = "pink", "DeconRNAseq" = "green")

```

### Lymphocytes
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

lymph = lymph[names(lymph.corr)]

lymph.melt = melt(lymph)
lymph.melt = lymph.melt %>% mutate(method = 
                  substring(variable, 1, 1)) %>% 
  mutate(method = 
           case_when(
             method == "H" ~ "H&E",
             method == "C" ~ "Cibersort",
             method == "E" ~ "Epidish",
             method == "Q" ~ "Quantiseq",
             method == "D" ~ "DeconRNAseq"
           ))
lymph.melt$method = as.factor(lymph.melt$method)

ggplot(lymph.melt, aes(x = value, y = variable, colour = method)) +
  geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                       point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
  theme_ridges() + ggtitle("Lymphocytes") +
  annotate("text", x = 1, y = 1:20, label = paste0("R = ",round(lymph.corr, 2)), colour = "brown") +
  scale_colour_manual(values = cols) +
   theme(axis.text.x = element_text(color = "black", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 20, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "black", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.title = element_text(color = "black", size = 20)) +
  ylab("") + xlab("% of cell type")

```

### Macrophages
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
macro = macro[names(macro.corr)]

macro.melt = melt(macro)
macro.melt = macro.melt %>% mutate(method = 
                  substring(variable, 1, 1)) %>% 
  mutate(method = 
           case_when(
             method == "H" ~ "H&E",
             method == "C" ~ "Cibersort",
             method == "E" ~ "Epidish",
             method == "Q" ~ "Quantiseq",
             method == "D" ~ "DeconRNAseq"
           ))
macro.melt$method = as.factor(macro.melt$method)

ggplot(macro.melt, aes(x = value, y = variable, colour = method)) +
  geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                       point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
  theme_ridges() + ggtitle("Macrophages") +
  annotate("text", x = 1, y = 1:20, label = paste0("R = ",round(macro.corr, 2)), colour = "brown") +
  scale_colour_manual(values = cols) +
   theme(axis.text.x = element_text(color = "black", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 20, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "black", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.title = element_text(color = "black", size = 20)) +
  ylab("") + xlab("% of cell type")

```

### Neutrophils
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
neutro = neutro[names(neutro.corr)]

neutro.melt = melt(neutro)
neutro.melt = neutro.melt %>% mutate(method = 
                  substring(variable, 1, 1)) %>% 
  mutate(method = 
           case_when(
             method == "H" ~ "H&E",
             method == "C" ~ "Cibersort",
             method == "E" ~ "Epidish",
             method == "Q" ~ "Quantiseq",
             method == "D" ~ "DeconRNAseq"
           ))
neutro.melt$method = as.factor(neutro.melt$method)

ggplot(neutro.melt, aes(x = value, y = variable, colour = method)) +
  geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                       point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
  theme_ridges() + xlim(0, 0.5) + ggtitle("Neutrophils") +
  annotate("text", x = 0.5, y = 1:11, label = paste0("R = ",round(neutro.corr, 2)), colour = "brown") +
  scale_colour_manual(values = cols) +
   theme(axis.text.x = element_text(color = "black", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 20, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "black", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.title = element_text(color = "black", size = 20)) +
  ylab("") + xlab("% of cell type")

```

### 2021-11-30 Figures/Supp_fig4.Rmd
Initial commit figure 3, 4 and supp

---
title: "Supp figure 4"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
suppressPackageStartupMessages({
  library(reshape2)
  library(ggpubr)
  library(tidyverse)
  library(Hmisc)
  library(ggridges)
  library(gridExtra)
  library(grid)
})
knitr::opts_chunk$set(fig.width=15, fig.height=15) 
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

# Load and parse data

tcga_deconv = read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_all_TCGA.txt", header=T)
Aran_all_facs <- read.csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv", sep = "\t")
HE_all_TCGA <- read.csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv", row.names = 1)

colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")

HE_all_TCGA$ParticipantBarcode <- HE_all_TCGA$ParticipantBarcode %>% str_replace_all(., "-", ".")

Aran_all_facs$Sample_ID <- Aran_all_facs$Sample_ID %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")
Aran_all_facs <- Aran_all_facs[Aran_all_facs$CPE != "NaN",]

tcga_deconv$Samples <- tcga_deconv$Samples %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")

Comm_samples <- Reduce(intersect, list(HE_all_TCGA$ParticipantBarcode, Aran_all_facs$Sample_ID, tcga_deconv$Samples))

Aran_all_facs <- Aran_all_facs %>% .[.$Sample_ID %in% Comm_samples, ] %>% .[order(.$Sample_ID), ]
HE_all_TCGA <- HE_all_TCGA %>% .[.$ParticipantBarcode %in% Comm_samples, ] %>% .[order(.$ParticipantBarcode),]
tcga_deconv <- tcga_deconv %>% .[.$Samples %in% Comm_samples, ]
tcga_deconv <- tcga_deconv

# REMOVE NON UNIQUE SAMPLES IN TCGA DECONV and attribute cancer type
tcga_deconv <- tcga_deconv %>%
  group_by(Samples) %>%
  summarise_all(mean)%>%
  as.data.frame()
tcga_deconv <- merge(tcga_deconv, Aran_all_facs[,1:2], by.x = "Samples", by.y = "Sample_ID")
rownames(tcga_deconv) = tcga_deconv$Samples
tcga_deconv <- tcga_deconv[,-1]

# for each method_signature make a DF with all 3 cell type in H&E
make_df <- function(met_sign, DF){
  data = DF %>% select(colnames(DF)[grepl(met_sign, colnames(DF))])
  lymph = data %>% 
    select(colnames(data)[grepl("CD4", colnames(data))], colnames(data)[grepl("CD8", colnames(data))], 
           colnames(data)[grepl("NK", colnames(data))]) %>% 
    replace(is.na(.), 0) %>%
    mutate(sum = rowSums(across(where(is.numeric))))
  macro = data %>% 
    select(colnames(data)[grepl("M0", colnames(data))], colnames(data)[grepl("M1", colnames(data))], 
           colnames(data)[grepl("M2", colnames(data))], colnames(data)[grepl("Mono", colnames(data))],
           colnames(data)[grepl("Macro", colnames(data))]) %>% 
    replace(is.na(.), 0) %>%
    mutate(sum = rowSums(across(where(is.numeric))))
  neutro = data %>% 
    select(colnames(data)[grepl("Neu", colnames(data))]) %>% 
    replace(is.na(.), 0) %>%
    mutate(sum = rowSums(across(where(is.numeric))))

  final_df = data.frame(Lymphocytes = lymph$sum, Neutrophils = neutro$sum,
                        Macrophages = macro$sum, row.names = rownames(data))
  final_df
  }

colcol = c("darkslategrey", "green", "coral")
make_plot <- function(data, method_data, method){
  ploty = list()
  for (i in 1:3) {
    ploty[[i]] <- local({
      i <- i
      x = ggplot(data, aes(x = data_HE[, i], y = method_data[, i])) +
        geom_point(colour = colcol[i]) +
        stat_smooth(method = lm, size = 0.2, color = "black", se = F, fullrange = T) +
        scale_x_continuous(limits = c(0, max(method_data[,i]))) +
        scale_y_continuous(limits = c(0, max(method_data[,i]))) +
        theme(axis.title.x= element_text(size = 12, face="bold"), 
            axis.title.y= element_text(size = 12, face="bold") )  + 
        ylab(method) + xlab("FACS") + ggtitle(colnames(method_data)[i]) +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
        annotate("text", x = -Inf, y = Inf, hjust=-0.2, vjust=1, label = paste("italic(r)==", round(cor.test(method_data[, i], data_HE[, i])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
        annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=3, label = paste("RMSE =", round(sqrt(mean((method_data[, i] - data_HE[, i])^2, na.rm = T)), 2)), parse = F, size = 6) 
    })
  }
  grid.arrange(grobs = ploty, ncol = 3)
}

```

## LUAD
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "LUAD")
data_HE = HE_all_TCGA %>% filter(Study == "LUAD")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## LUSC
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "LUSC")
data_HE = HE_all_TCGA %>% filter(Study == "LUSC")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## PRAD
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "PRAD")
data_HE = HE_all_TCGA %>% filter(Study == "PRAD")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## BLCA
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "BLCA")
data_HE = HE_all_TCGA %>% filter(Study == "BLCA")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## CESC
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "CESC")
data_HE = HE_all_TCGA %>% filter(Study == "CESC")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## BRCA
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "BRCA")
data_HE = HE_all_TCGA %>% filter(Study == "BRCA")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## UCEC
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "UCEC")
data_HE = HE_all_TCGA %>% filter(Study == "UCEC")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## COAD
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "COAD")
data_HE = HE_all_TCGA %>% filter(Study == "COAD")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## READ
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "READ")
data_HE = HE_all_TCGA %>% filter(Study == "READ")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

## SKCM
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

data = tcga_deconv %>% filter(Cancer_type == "SKCM")
data_HE = HE_all_TCGA %>% filter(Study == "SKCM")
data_HE = data_HE[, 3:5]

QT = make_df("Quantiseq", data)
make_plot(data, QT, "QuantiSeq")

Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")

DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")

Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")

Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")

Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")

Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")

Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")

Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")

CBSX.LM22 = make_df("^CBSX.LM22", data)
make_plot(data, CBSX.LM22, "CBSX.LM22")
CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
CBSX.melanoma = make_df("^CBSX.melanoma", data)
make_plot(data, CBSX.melanoma, "CBSX.melanoma")
CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")

```

### 2021-11-30 Figures/Supp_figures.Rmd
Initial commit figure 3, 4 and supp

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(reshape2)
library(EpiDISH)
library(tidyverse)
library(Hmisc)
library(gridExtra)
library(grid)

knitr::opts_chunk$set(fig.width = 20, fig.height = 30, cache = T)
```

### Silico1700

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
silico1700_facs <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Silico_1700.txt")
silico1700_deconv <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_Silico_1700.txt")

colnames(silico1700_deconv) <- colnames(silico1700_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(silico1700_deconv) <- colnames(silico1700_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(silico1700_deconv) <- colnames(silico1700_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(silico1700_deconv) <- colnames(silico1700_deconv) %>% str_replace_all("CBSX__LM22_", "CBSX.LM22")

silico1700_deconv <- silico1700_deconv %>% select(-colnames(silico1700_deconv)[grepl("XCELL", colnames(silico1700_deconv))])
silico1700_deconv <- silico1700_deconv %>% select(-colnames(silico1700_deconv)[grepl("MCP", colnames(silico1700_deconv))])

# CD4
cd4 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("CD4", colnames(silico1700_deconv))])
# Regroup and remove different types of CD4 from LM22 signature
data$Epidish_CBSX_LM22_CD4 = data$Epidish_CBSX_LM22_T.cells.CD4.memory.activated + data$Epidish_CBSX_LM22_T.cells.CD4.memory.resting + data$Epidish_CBSX_LM22_T.cells.CD4.naive
data$DeconRNASeq_CBSX_LM22_CD4 = data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.naive
data$CBSX.LM22_CD4 = data$CBSX.LM22_T_cells_CD4_memory_activated + data$CBSX.LM22_T_cells_CD4_memory_resting + data$CBSX.LM22_T_cells_CD4_naive
data <- data %>% select(-c("CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD4_memory_resting", "CBSX.LM22_T_cells_CD4_naive", 
                           "Epidish_CBSX_LM22_T.cells.CD4.memory.activated" ,"Epidish_CBSX_LM22_T.cells.CD4.memory.resting" ,"Epidish_CBSX_LM22_T.cells.CD4.naive", 
                           "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated" ,"DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting" , "DeconRNASeq_CBSX_LM22_T.cells.CD4.naive"))

data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$T.cells.CD4)

for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# CD8
cd8 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("CD8", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$T.cells.CD8)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# Monocytes
mono <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Mono", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Monocytes)
for (i in 1:(ncol(data) - 1)) {
  mono[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Mono.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = mono, ncol = 3, top = textGrob("Monocytes", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# M1
m1 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("M1", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M1)
for (i in 1:(ncol(data) - 1)) {
  m1[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M1)|(_Macro.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = m1, ncol = 3, top = textGrob("Macrophages M1", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# M2
m2 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(_M2)|(\\.M2)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M2)
for (i in 1:(ncol(data) - 1)) {
  m2[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M2)|(_Macro.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = m2, ncol = 3, top = textGrob("Macrophages M2", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# B
b <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(B_cell)|(B.cell)|(B_lin)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$B.cells)
for (i in 1:(ncol(data) - 1)) {
  b[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(B_cell.*)|(_B.cell.*)|(_B_lin.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# NK
nk <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("NK", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$NK.cells)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# neutro
neutro <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Neu", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Neutrophils)
for (i in 1:(ncol(data) -1)) {
  neutro[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Neu.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = neutro, ncol = 3, top = textGrob("Neutrophils", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
```

### GSE104171 - multiple myeloma

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

GSE104171_deconv <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_GSE104171.txt")
GSE104171_facs <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/FACS_GSE104171.txt")
GSE104171_facs[ 2:4] <- GSE104171_facs[ 2:4] / 100
colnames(GSE104171_deconv) <- colnames(GSE104171_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(GSE104171_deconv) <- colnames(GSE104171_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(GSE104171_deconv) <- colnames(GSE104171_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(GSE104171_deconv) <- colnames(GSE104171_deconv) %>% str_replace_all("CBSX__LM22_", "CBSX.LM22")

GSE104171_deconv <- GSE104171_deconv %>% select(-colnames(GSE104171_deconv)[grepl("XCELL", colnames(GSE104171_deconv))])
GSE104171_deconv <- GSE104171_deconv %>% select(-colnames(GSE104171_deconv)[grepl("MCP", colnames(GSE104171_deconv))])

# CD4
cd4 <- list()
data <- GSE104171_deconv %>% select(colnames(GSE104171_deconv)[grepl("CD4", colnames(GSE104171_deconv))])
# Regroup and remove different types of CD4 from LM22 signature
data$Epidish_CBSX_LM22_CD4 = data$Epidish_CBSX_LM22_T.cells.CD4.memory.activated + data$Epidish_CBSX_LM22_T.cells.CD4.memory.resting + data$Epidish_CBSX_LM22_T.cells.CD4.naive
data$DeconRNASeq_CBSX_LM22_CD4 = data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.naive
data$CBSX.LM22_CD4 = data$CBSX.LM22_T_cells_CD4_memory_activated + data$CBSX.LM22_T_cells_CD4_memory_resting + data$CBSX.LM22_T_cells_CD4_naive
data <- data %>% select(-c("CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD4_memory_resting", "CBSX.LM22_T_cells_CD4_naive", 
                           "Epidish_CBSX_LM22_T.cells.CD4.memory.activated" ,"Epidish_CBSX_LM22_T.cells.CD4.memory.resting" ,"Epidish_CBSX_LM22_T.cells.CD4.naive", 
                           "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated" ,"DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting" , "DeconRNASeq_CBSX_LM22_T.cells.CD4.naive"))

data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE104171_facs$CD4)
for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# CD8
cd8 <- list()
data <- GSE104171_deconv %>% select(colnames(GSE104171_deconv)[grepl("CD8", colnames(GSE104171_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE104171_facs$CD8)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# NK
nk <- list()
data <- GSE104171_deconv %>% select(colnames(GSE104171_deconv)[grepl("NK", colnames(GSE104171_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE104171_facs$NK)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

```

### Melanoma_GSE93722

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

GSE72056_facs <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt")
GSE72056_deconv <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt")

colnames(GSE72056_deconv) <- colnames(GSE72056_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(GSE72056_deconv) <- colnames(GSE72056_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(GSE72056_deconv) <- colnames(GSE72056_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(GSE72056_deconv) <- colnames(GSE72056_deconv) %>% str_replace_all("CBSX__LM22_", "CBSX.LM22")

GSE72056_deconv <- GSE72056_deconv %>% select(-colnames(GSE72056_deconv)[grepl("XCELL", colnames(GSE72056_deconv))])
GSE72056_deconv <- GSE72056_deconv %>% select(-colnames(GSE72056_deconv)[grepl("MCP", colnames(GSE72056_deconv))])

# CD4
cd4 <- list()
data <- GSE72056_deconv %>% select(colnames(GSE72056_deconv)[grepl("CD4", colnames(GSE72056_deconv))])
# Regroup and remove different types of CD4 from LM22 signature
data$Epidish_CBSX_LM22_CD4 = data$Epidish_CBSX_LM22_T.cells.CD4.memory.activated + data$Epidish_CBSX_LM22_T.cells.CD4.memory.resting + data$Epidish_CBSX_LM22_T.cells.CD4.naive
data$DeconRNASeq_CBSX_LM22_CD4 = data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.naive
data$CBSX.LM22_CD4 = data$CBSX.LM22_T_cells_CD4_memory_activated + data$CBSX.LM22_T_cells_CD4_memory_resting + data$CBSX.LM22_T_cells_CD4_naive
data <- data %>% select(-c("CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD4_memory_resting", "CBSX.LM22_T_cells_CD4_naive", 
                           "Epidish_CBSX_LM22_T.cells.CD4.memory.activated" ,"Epidish_CBSX_LM22_T.cells.CD4.memory.resting" ,"Epidish_CBSX_LM22_T.cells.CD4.naive", 
                           "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated" ,"DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting" , "DeconRNASeq_CBSX_LM22_T.cells.CD4.naive"))

data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE72056_facs$CD4)
for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# CD8
cd8 <- list()
data <- GSE72056_deconv %>% select(colnames(GSE72056_deconv)[grepl("CD8", colnames(GSE72056_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE72056_facs$CD8)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# Macrophages
macro <- list()
data <- GSE72056_deconv %>% select(colnames(GSE72056_deconv)[grepl("Macro", colnames(GSE72056_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE72056_facs$Macrophages)
for (i in 1:(ncol(data) - 1)) {
  macro[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Macro.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = macro, ncol = 3, top = textGrob("Macrophages", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# B
b <- list()
data <- GSE72056_deconv %>% select(colnames(GSE72056_deconv)[grepl("(B_cell)|(B.cell)|(B_lin)", colnames(GSE72056_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE72056_facs$B)
for (i in 1:(ncol(data) - 1)) {
  b[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(B_cell.*)|(_B.cell.*)|(_B_lin.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# NK
nk <- list()
data <- GSE72056_deconv %>% select(colnames(GSE72056_deconv)[grepl("NK", colnames(GSE72056_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE72056_facs$NK)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

```

### Melanoma_GSE93722

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

GSE93722_facs <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE93722.txt")
GSE93722_deconv <- read.delim("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_Melanoma_GSE93722.txt")

colnames(GSE93722_deconv) <- colnames(GSE93722_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
colnames(GSE93722_deconv) <- colnames(GSE93722_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
colnames(GSE93722_deconv) <- colnames(GSE93722_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
colnames(GSE93722_deconv) <- colnames(GSE93722_deconv) %>% str_replace_all("CBSX__LM22_", "CBSX.LM22")

GSE93722_deconv <- GSE93722_deconv %>% select(-colnames(GSE93722_deconv)[grepl("XCELL", colnames(GSE93722_deconv))])
GSE93722_deconv <- GSE93722_deconv %>% select(-colnames(GSE93722_deconv)[grepl("MCP", colnames(GSE93722_deconv))])

# CD4
cd4 <- list()
data <- GSE93722_deconv %>% select(colnames(GSE93722_deconv)[grepl("CD4", colnames(GSE93722_deconv))])
# Regroup and remove different types of CD4 from LM22 signature
data$Epidish_CBSX_LM22_CD4 = data$Epidish_CBSX_LM22_T.cells.CD4.memory.activated + data$Epidish_CBSX_LM22_T.cells.CD4.memory.resting + data$Epidish_CBSX_LM22_T.cells.CD4.naive
data$DeconRNASeq_CBSX_LM22_CD4 = data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting + data$DeconRNASeq_CBSX_LM22_T.cells.CD4.naive
data$CBSX.LM22_CD4 = data$CBSX.LM22_T_cells_CD4_memory_activated + data$CBSX.LM22_T_cells_CD4_memory_resting + data$CBSX.LM22_T_cells_CD4_naive
data <- data %>% select(-c("CBSX.LM22_T_cells_CD4_memory_activated", "CBSX.LM22_T_cells_CD4_memory_resting", "CBSX.LM22_T_cells_CD4_naive", 
                           "Epidish_CBSX_LM22_T.cells.CD4.memory.activated" ,"Epidish_CBSX_LM22_T.cells.CD4.memory.resting" ,"Epidish_CBSX_LM22_T.cells.CD4.naive", 
                           "DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.activated" ,"DeconRNASeq_CBSX_LM22_T.cells.CD4.memory.resting" , "DeconRNASeq_CBSX_LM22_T.cells.CD4.naive"))

data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE93722_facs$CD4_Tcells)
for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# CD8
cd8 <- list()
data <- GSE93722_deconv %>% select(colnames(GSE93722_deconv)[grepl("CD8", colnames(GSE93722_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE93722_facs$CD8_Tcells)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# B
b <- list()
data <- GSE93722_deconv %>% select(colnames(GSE93722_deconv)[grepl("(B_cell)|(B.cell)|(B_lin)", colnames(GSE93722_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE93722_facs$Bcells)
for (i in 1:(ncol(data) - 1)) {
  b[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(B_cell.*)|(_B.cell.*)|(_B_lin.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# NK
nk <- list()
data <- GSE93722_deconv %>% select(colnames(GSE93722_deconv)[grepl("NK", colnames(GSE93722_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, GSE93722_facs$NKcells)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

```

### 2021-11-30 Figures/supp_figures_meth.Rmd
Initial commit figure 3, 4 and supp

---
title: "Supplementary Methylation figures"
output:
  html_document:
    df_print: paged
---

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(reshape2)
library(EpiDISH)
library(tidyverse)
library(Hmisc)
library(ggpubr)

knitr::opts_chunk$set(fig.width = 25, fig.height = 25, cache = T)
```

####  BPmet

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# Using an R object to load the data as the GSE matrix are heavy files.
# Signatures and facs data are available in the associated folder
load("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/GSE132203_100_and_GSE77797_6/methylation_figs.RData")

out.l <- epidish(GSE132203_100, BPmet, "RPC", maxit = 100)
GSE132203_100_BPmet <- data.frame(out.l$estF[, c(2, 3, 4, 1, 6, 5)])

melt_FACS_GSE132203_100 <- melt(FACS_GSE132203_100)

melt_GSE132203_100_BPmet <- melt(GSE132203_100_BPmet) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_BPmet) <- c("FACS", "cell_type", "ALL")

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_BPmet), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_BPmet) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("BPmet") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_BPmet), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_BPmet) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

#### each cell types

GSE132203_100_BPmet <- cbind(GSE132203_100_BPmet, FACS_GSE132203_100)

colnames(GSE132203_100_BPmet) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")

melt_GSE132203_100_BPmet <- list()
p_GSE132203_100_BPmet <- list()

for (i in c(1:6)) {

  # rmse[[i]] <- rmse(GSE132203_100_BPmet[,i], FACS_GSE132203_100[,i])

  melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[, c(i, i + 6)], id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i + 6])
}

# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
#                    rmse = unlist(rmse))

p_GSE132203_100_BPmet[[1]] <- ggplot(melt_GSE132203_100_BPmet[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.185, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[1]], FACS_GSE132203_100[, 1])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.113, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[1]] - FACS_GSE132203_100[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.072, y = 0.292, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[2]], FACS_GSE132203_100[, 2])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[2]] - FACS_GSE132203_100[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet[[3]] <- ggplot(melt_GSE132203_100_BPmet[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[3]], FACS_GSE132203_100[, 3])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[3]] - FACS_GSE132203_100[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.2), breaks = seq(0.0, 0.2, 0.05)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.095, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[4]], FACS_GSE132203_100[, 4])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.058, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[4]] - FACS_GSE132203_100[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.037, y = 0.218, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.073, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[5]], FACS_GSE132203_100[, 5])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.045, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[5]] - FACS_GSE132203_100[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0292, y = 0.15, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet[[6]] <- ggplot(melt_GSE132203_100_BPmet[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Neu") +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.45, y = 1.2, label = paste("italic(r)==", round(cor.test(GSE132203_100_BPmet[[6]], FACS_GSE132203_100[, 6])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_BPmet[[6]] - FACS_GSE132203_100[, 6])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_BPmet)), size = 6)

p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]], p_GSE132203_100_BPmet[[2]], p_GSE132203_100_BPmet[[3]], p_GSE132203_100_BPmet[[4]], p_GSE132203_100_BPmet[[5]], p_GSE132203_100_BPmet[[6]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black"))

p_GSE132203_100_BPmet_all_all <- ggarrange(p_GSE132203_100_BPmet_all, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
```

####   MethylCIBERSORT

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

out.l <- epidish(GSE132203_100, MethylCIBERSORT_WB, "RPC", maxit = 100)

GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[, 3] + out.l$estF[, 10], out.l$estF[, 5], out.l$estF[, 1], out.l$estF[, 2], out.l$estF[, 4], out.l$estF[, 9]))

colnames(GSE132203_100_MethylCIBERSORT_WB) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")

# melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB)

melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS", "cell_type", "MethylCIBERSORT")

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_MethylCIBERSORT_WB), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_MethylCIBERSORT_WB) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("MethylCIBERSORT") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_MethylCIBERSORT_WB), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_MethylCIBERSORT_WB) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

#### each cell types

GSE132203_100_MethylCIBERSORT_WB <- cbind(GSE132203_100_MethylCIBERSORT_WB, FACS_GSE132203_100)

colnames(GSE132203_100_MethylCIBERSORT_WB) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")

melt_GSE132203_100_MethylCIBERSORT_WB <- list()
rmse <- list()
p_GSE132203_100_MethylCIBERSORT <- list()

for (i in c(1:6)) {

  # rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[,i], GSE132203_100_MethylCIBERSORT_WB[,i+6])

  melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[, c(i, i + 6)], id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i + 6])
}

# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
#                    rmse = unlist(rmse))

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.185, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[1]], FACS_GSE132203_100[, 1])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.113, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[1]] - FACS_GSE132203_100[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.072, y = 0.292, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[2]], FACS_GSE132203_100[, 2])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[2]] - FACS_GSE132203_100[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[3]], FACS_GSE132203_100[, 3])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[3]] - FACS_GSE132203_100[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.2), breaks = seq(0.0, 0.2, 0.05)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.095, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[4]], FACS_GSE132203_100[, 4])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.058, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[4]] - FACS_GSE132203_100[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.037, y = 0.218, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT[[5]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.073, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[5]], FACS_GSE132203_100[, 5])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.045, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[5]] - FACS_GSE132203_100[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0292, y = 0.218, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT[[6]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Neu") +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +

  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.45, y = 1.2, label = paste("italic(r)==", round(cor.test(GSE132203_100_MethylCIBERSORT_WB[[6]], FACS_GSE132203_100[, 6])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_MethylCIBERSORT_WB[[6]] - FACS_GSE132203_100[, 6])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_MethylCIBERSORT_WB)), size = 6)

p_GSE132203_100_MethylCIBERSORT_each <- ggarrange(p_GSE132203_100_MethylCIBERSORT[[1]], p_GSE132203_100_MethylCIBERSORT[[2]], p_GSE132203_100_MethylCIBERSORT[[3]], p_GSE132203_100_MethylCIBERSORT[[4]], p_GSE132203_100_MethylCIBERSORT[[5]], p_GSE132203_100_MethylCIBERSORT[[6]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black"))

p_GSE132203_100_MethylCIBERSORT_all_all <- ggarrange(p_GSE132203_100_MethylCIBERSORT_WB_all, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
```

###   DHS

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

out.l <- epidish(GSE132203_100, centDHSbloodDMC.m, "RPC", maxit = 100)
GSE132203_100_DHS <- data.frame(out.l$estF[, c(3, 4, 5, 1, 2, 6)])
colnames(GSE132203_100_DHS) <- c("CD4", "CD8", "Mono", "B", "NK", "Neu")

# melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS)

melt_GSE132203_100_DHS <- melt(GSE132203_100_DHS) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_DHS) <- c("FACS", "cell_type", "DHS")

p_melt_GSE132203_100_DHS_all <- ggplot(melt_GSE132203_100_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_DHS), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_DHS) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_melt_GSE132203_100_DHS_all_longly <- ggplot(melt_GSE132203_100_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("DHS") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.48, y = 1.2, label = paste("italic(r)==", round(cor.test(as.matrix(GSE132203_100_DHS), as.matrix(FACS_GSE132203_100))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE132203_100_DHS) - as.matrix(FACS_GSE132203_100))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

#### each cell types

GSE132203_100_DHS <- cbind(GSE132203_100_DHS, FACS_GSE132203_100)

colnames(GSE132203_100_DHS) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")

melt_GSE132203_100_DHS <- list()
rmse <- list()
p_GSE132203_100_DHS <- list()

for (i in c(1:6)) {

  # rmse[[i]] <- rmse(GSE132203_100_DHS[,i], GSE132203_100_DHS[,i+6])

  melt_GSE132203_100_DHS[[i]] <- melt(GSE132203_100_DHS[, c(i, i + 6)], id.vars = colnames(GSE132203_100_DHS)[i], measure.vars = colnames(GSE132203_100_DHS)[i + 6])
}

# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
#                    rmse = unlist(rmse))

p_GSE132203_100_DHS[[1]] <- ggplot(melt_GSE132203_100_DHS[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.185, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[1]], FACS_GSE132203_100[, 1])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.113, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[1]] - FACS_GSE132203_100[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.072, y = 0.292, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS[[2]] <- ggplot(melt_GSE132203_100_DHS[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[2]], FACS_GSE132203_100[, 2])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[2]] - FACS_GSE132203_100[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS[[3]] <- ggplot(melt_GSE132203_100_DHS[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.135, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[3]], FACS_GSE132203_100[, 3])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.08, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[3]] - FACS_GSE132203_100[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.05, y = 0.292, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS[[4]] <- ggplot(melt_GSE132203_100_DHS[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.2), breaks = seq(0.0, 0.2, 0.05)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.095, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[4]], FACS_GSE132203_100[, 4])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.058, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[4]] - FACS_GSE132203_100[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.037, y = 0.218, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS[[5]] <- ggplot(melt_GSE132203_100_DHS[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.073, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[5]], FACS_GSE132203_100[, 5])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.045, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[5]] - FACS_GSE132203_100[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0292, y = 0.218, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS[[6]] <- ggplot(melt_GSE132203_100_DHS[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Neu") +
  scale_x_continuous(name = NULL, limits = c(0, 1), breaks = seq(0.0, 1.0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 1.2), breaks = seq(0.0, 1.2, 0.2)) +

  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.45, y = 1.2, label = paste("italic(r)==", round(cor.test(GSE132203_100_DHS[[6]], FACS_GSE132203_100[, 6])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.28, y = 1.05, label = paste("RMSE =", round(sqrt(mean((GSE132203_100_DHS[[6]] - FACS_GSE132203_100[, 6])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.175, y = 0.9, label = paste("n = ", nrow(GSE132203_100_DHS)), size = 6)

p_GSE132203_100_DHS_each <- ggarrange(p_GSE132203_100_DHS[[1]], p_GSE132203_100_DHS[[2]], p_GSE132203_100_DHS[[3]], p_GSE132203_100_DHS[[4]], p_GSE132203_100_DHS[[5]], p_GSE132203_100_DHS[[6]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black"))

p_GSE132203_100_DHS_all_all <- ggarrange(p_melt_GSE132203_100_DHS_all, ncol = 3, nrow = 1, font.label = list(size = 20, color = "black"))
```

## Methylation 6 WB samples GSE77797

### BPmet

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

out.l <- epidish(GSE77797_six, BPmet, "RPC", maxit = 100)
GSE77797_six_BPmet <- data.frame(out.l$estF[, c(2, 3, 4, 1, 6)])
# melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet)
melt_facs_GSE77797_six <- melt(facs_GSE77797_six[, -6])

melt_GSE77797_six_BPmet <- melt(GSE77797_six_BPmet) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_BPmet) <- c("FACS", "cell_type", "BPmet")

p_GSE77797_six_BPmet_all <- ggplot(melt_GSE77797_six_BPmet, aes(x = FACS, y = BPmet, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.108, y = 0.4, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_BPmet), as.matrix(facs_GSE77797_six[, -6]))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.345, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_BPmet) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.292, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

p_GSE77797_six_BPmet_all_longly <- ggplot(melt_GSE77797_six_BPmet, aes(x = FACS, y = BPmet, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("BPmet") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.108, y = 0.4, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_BPmet), as.matrix(facs_GSE77797_six[, -6]))$est, 3), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.345, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_BPmet) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.292, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

#### each cell types

GSE77797_six_BPmet <- cbind(GSE77797_six_BPmet, facs_GSE77797_six[, -6])

colnames(GSE77797_six_BPmet) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")

melt_GSE77797_six_BPmet <- list()
rmse <- list()
G6_BPmet <- list()

for (i in c(1:5)) {

  # rmse[[i]] <- rmse(GSE77797_six_BPmet[,i], GSE77797_six_BPmet[,i+5])

  melt_GSE77797_six_BPmet[[i]] <- melt(GSE77797_six_BPmet[, c(i, i + 5)], id.vars = colnames(GSE77797_six_BPmet)[i], measure.vars = colnames(GSE77797_six_BPmet)[i + 5])
}
#
# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
#                    rmse = unlist(rmse))

G6_BPmet[[1]] <- ggplot(melt_GSE77797_six_BPmet[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.102, y = 0.4, label = paste("italic(r)==", round(cor.test(GSE77797_six_BPmet[[1]], facs_GSE77797_six[, 1])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_BPmet[[1]], facs_GSE77797_six[, 1])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.345, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_BPmet[[1]] - facs_GSE77797_six[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.292, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

G6_BPmet[[2]] <- ggplot(melt_GSE77797_six_BPmet[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.05, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE77797_six_BPmet[[2]], facs_GSE77797_six[, 2])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_BPmet[[2]], facs_GSE77797_six[, 2])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.035, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_BPmet[[2]] - facs_GSE77797_six[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.018, y = 0.218, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

G6_BPmet[[3]] <- ggplot(melt_GSE77797_six_BPmet[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.1), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.035, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_BPmet[[3]], facs_GSE77797_six[, 3])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_BPmet[[3]], facs_GSE77797_six[, 3])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.023, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_BPmet[[3]] - facs_GSE77797_six[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0115, y = 0.145, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

G6_BPmet[[4]] <- ggplot(melt_GSE77797_six_BPmet[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.08), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.028, y = 0.15, label = paste("italic(r)==", round(cor.test(GSE77797_six_BPmet[[4]], facs_GSE77797_six[, 4])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_BPmet[[4]], facs_GSE77797_six[, 4])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.019, y = 0.13, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_BPmet[[4]] - facs_GSE77797_six[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.01, y = 0.11, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)

G6_BPmet[[5]] <- ggplot(melt_GSE77797_six_BPmet[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.06), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.022, y = 0.15, label = paste("italic(r)==", round(cor.test(GSE77797_six_BPmet[[5]], facs_GSE77797_six[, 5])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_BPmet[[5]], facs_GSE77797_six[, 5])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.015, y = 0.13, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_BPmet[[5]] - facs_GSE77797_six[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0082, y = 0.11, label = paste("n = ", nrow(GSE77797_six_BPmet)), size = 6)
```

#### MethylCIBERSORT_WB

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

out.l <- epidish(GSE77797_six, MethylCIBERSORT_WB, "RPC", maxit = 100)
GSE77797_six_MethylCIBERSORT_WB <- data.frame(out.l$estF[, c(3, 5, 1, 2, 4)])

# melt_GSE77797_six_MethylCIBERSORT_WB <- melt(GSE77797_six_MethylCIBERSORT_WB)

melt_GSE77797_six_MethylCIBERSORT_WB <- melt(GSE77797_six_MethylCIBERSORT_WB) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_MethylCIBERSORT_WB) <- c("FACS", "cell_type", "MethylCIBERSORT")

p_GSE77797_six_MethylCIBERSORT_all <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.115, y = 0.3, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_MethylCIBERSORT_WB), as.matrix(facs_GSE77797_six[, -6]))$est, 2), "~','", "~italic(P)<", round(cor.test(as.matrix(GSE77797_six_MethylCIBERSORT_WB), as.matrix(facs_GSE77797_six[, -6]))$p.value, 7)), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.257, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_MethylCIBERSORT_WB) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.218, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

p_GSE77797_six_MethylCIBERSORT_all_longly <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("MethylCIBERSORT") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.115, y = 0.3, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_MethylCIBERSORT_WB), as.matrix(facs_GSE77797_six[, -6]))$est, 2), "~','", "~italic(P)<", round(cor.test(as.matrix(GSE77797_six_MethylCIBERSORT_WB), as.matrix(facs_GSE77797_six[, -6]))$p.value, 7)), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.257, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_MethylCIBERSORT_WB) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.218, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

#### each cell types

GSE77797_six_MethylCIBERSORT_WB <- cbind(GSE77797_six_MethylCIBERSORT_WB, facs_GSE77797_six[, -6])

colnames(GSE77797_six_MethylCIBERSORT_WB) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")

melt_GSE77797_six_MethylCIBERSORT_WB <- list()
rmse <- list()
G6_MethylCIBERSORT_WB <- list()

for (i in c(1:5)) {

  # rmse[[i]] <- rmse(GSE77797_six_MethylCIBERSORT_WB[,i], GSE77797_six_MethylCIBERSORT_WB[,i+5])

  melt_GSE77797_six_MethylCIBERSORT_WB[[i]] <- melt(GSE77797_six_MethylCIBERSORT_WB[, c(i, i + 5)], id.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE77797_six_MethylCIBERSORT_WB)[i + 5])
}
#
# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
#                    rmse = unlist(rmse))

G6_MethylCIBERSORT_WB[[1]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.092, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[1]], facs_GSE77797_six[, 1])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[1]], facs_GSE77797_six[, 1])$p.value, 3)), parse = TRUE, size = 6) +
  annotate("text", x = 0.065, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_MethylCIBERSORT_WB[[1]] - facs_GSE77797_six[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.032, y = 0.218, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

G6_MethylCIBERSORT_WB[[2]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.045, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[2]], facs_GSE77797_six[, 2])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[2]], facs_GSE77797_six[, 2])$p.value, 3)), parse = TRUE, size = 6) +
  annotate("text", x = 0.035, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_MethylCIBERSORT_WB[[2]] - facs_GSE77797_six[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.018, y = 0.145, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

G6_MethylCIBERSORT_WB[[3]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.1), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.035, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[3]], facs_GSE77797_six[, 3])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[3]], facs_GSE77797_six[, 3])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.023, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_MethylCIBERSORT_WB[[3]] - facs_GSE77797_six[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0115, y = 0.145, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

G6_MethylCIBERSORT_WB[[4]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.08), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.028, y = 0.15, label = paste("italic(r)==", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[4]], facs_GSE77797_six[, 4])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[4]], facs_GSE77797_six[, 4])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.019, y = 0.13, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_MethylCIBERSORT_WB[[4]] - facs_GSE77797_six[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.01, y = 0.11, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)

G6_MethylCIBERSORT_WB[[5]] <- ggplot(melt_GSE77797_six_MethylCIBERSORT_WB[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.06), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.0205, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[5]], facs_GSE77797_six[, 5])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_MethylCIBERSORT_WB[[5]], facs_GSE77797_six[, 5])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.015, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_MethylCIBERSORT_WB[[5]] - facs_GSE77797_six[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0082, y = 0.145, label = paste("n = ", nrow(GSE77797_six_MethylCIBERSORT_WB)), size = 6)
```

### DHS

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

out.l <- epidish(GSE77797_six, centDHSbloodDMC.m, "RPC", maxit = 100)
GSE77797_six_DHS <- data.frame(out.l$estF[, c(3, 4, 5, 1, 2)])
colnames(GSE77797_six_DHS) <- c("CD4", "CD8", "Mono", "B", "NK")

# melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS)

melt_GSE77797_six_DHS <- melt(GSE77797_six_DHS) %>% cbind(melt_facs_GSE77797_six$value, .)
colnames(melt_GSE77797_six_DHS) <- c("FACS", "cell_type", "DHS")

p_GSE77797_six_DHS_all <- ggplot(melt_GSE77797_six_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("All cells") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.108, y = 0.3, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_DHS), as.matrix(facs_GSE77797_six[, -6]))$est, 2), "~','", "~italic(P)<", round(cor.test(as.matrix(GSE77797_six_DHS), as.matrix(facs_GSE77797_six[, -6]))$p.value, 10)), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.257, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_DHS) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.218, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

p_GSE77797_six_DHS_all_longly <- ggplot(melt_GSE77797_six_DHS, aes(x = FACS, y = DHS, colour = cell_type)) +
  geom_point(shape = 19, size = 2) +
  ggtitle("DHS") +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta")) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +

  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5), legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
  annotate("text", x = 0.115, y = 0.3, label = paste("italic(r)==", round(cor.test(as.matrix(GSE77797_six_DHS), as.matrix(facs_GSE77797_six[, -6]))$est, 2), "~','", "~italic(P)<", round(cor.test(as.matrix(GSE77797_six_DHS), as.matrix(facs_GSE77797_six[, -6]))$p.value, 10)), parse = TRUE, size = 6) +
  annotate("text", x = 0.07, y = 0.257, label = paste("RMSE =", round(sqrt(mean((as.matrix(GSE77797_six_DHS) - as.matrix(facs_GSE77797_six[, -6]))^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.035, y = 0.218, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

#################################################################################

#### each cell types

GSE77797_six_DHS <- cbind(GSE77797_six_DHS, facs_GSE77797_six[, -6])

colnames(GSE77797_six_DHS) <- c("V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK")

melt_GSE77797_six_DHS <- list()
rmse <- list()
G6_DHS <- list()

for (i in c(1:5)) {

  # rmse[[i]] <- rmse(GSE77797_six_DHS[,i], GSE77797_six_DHS[,i+5])

  melt_GSE77797_six_DHS[[i]] <- melt(GSE77797_six_DHS[, c(i, i + 5)], id.vars = colnames(GSE77797_six_DHS)[i], measure.vars = colnames(GSE77797_six_DHS)[i + 5])
}

# RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK"),
#                    rmse = unlist(rmse))

G6_DHS[[1]] <- ggplot(melt_GSE77797_six_DHS[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD4") +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.092, y = 0.3, label = paste("italic(r)==", round(cor.test(GSE77797_six_DHS[[1]], facs_GSE77797_six[, 1])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_DHS[[1]], facs_GSE77797_six[, 1])$p.value, 3)), parse = TRUE, size = 6) +
  annotate("text", x = 0.065, y = 0.257, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_DHS[[1]] - facs_GSE77797_six[, 1])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.032, y = 0.218, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

G6_DHS[[2]] <- ggplot(melt_GSE77797_six_DHS[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("CD8") +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.047, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_DHS[[2]], facs_GSE77797_six[, 2])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_DHS[[2]], facs_GSE77797_six[, 2])$p.value, 3)), parse = TRUE, size = 6) +
  annotate("text", x = 0.035, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_DHS[[2]] - facs_GSE77797_six[, 2])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.018, y = 0.145, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

G6_DHS[[3]] <- ggplot(melt_GSE77797_six_DHS[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("Mono") +
  scale_x_continuous(name = NULL, limits = c(0, 0.1), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.033, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_DHS[[3]], facs_GSE77797_six[, 3])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_DHS[[3]], facs_GSE77797_six[, 3])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.023, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_DHS[[3]] - facs_GSE77797_six[, 3])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0115, y = 0.145, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

G6_DHS[[4]] <- ggplot(melt_GSE77797_six_DHS[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("B") +
  scale_x_continuous(name = NULL, limits = c(0, 0.08), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.15)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.028, y = 0.15, label = paste("italic(r)==", round(cor.test(GSE77797_six_DHS[[4]], facs_GSE77797_six[, 4])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_DHS[[4]], facs_GSE77797_six[, 4])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.019, y = 0.13, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_DHS[[4]] - facs_GSE77797_six[, 4])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.01, y = 0.11, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)

G6_DHS[[5]] <- ggplot(melt_GSE77797_six_DHS[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 2) +
  stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
  ggtitle("NK") +
  scale_x_continuous(name = NULL, limits = c(0, 0.06), breaks = seq(0.0, 0.1, 0.02)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +

  annotate("text", x = 0.0215, y = 0.2, label = paste("italic(r)==", round(cor.test(GSE77797_six_DHS[[5]], facs_GSE77797_six[, 5])$est, 2), "~','", "~italic(P)<", round(cor.test(GSE77797_six_DHS[[5]], facs_GSE77797_six[, 5])$p.value, 4)), parse = TRUE, size = 6) +
  annotate("text", x = 0.015, y = 0.173, label = paste("RMSE =", round(sqrt(mean((GSE77797_six_DHS[[5]] - facs_GSE77797_six[, 5])^2, na.rm = T)), 2)), parse = F, size = 6) +
  annotate("text", x = 0.0082, y = 0.145, label = paste("n = ", nrow(GSE77797_six_DHS)), size = 6)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

Fig_S1a <- annotate_figure(ggarrange(p_GSE132203_100_BPmet_all_all, p_GSE132203_100_BPmet_each, ncol = 1, nrow = 2, heights = 1:3.5, font.label = list(size = 20, color = "black")), left = text_grob("BPmet estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "a", fig.lab.face = "bold", fig.lab.size = 16)

Fig_S1b <- annotate_figure(ggarrange(p_GSE132203_100_MethylCIBERSORT_all_all, p_GSE132203_100_MethylCIBERSORT_each, ncol = 1, nrow = 2, heights = 1:3.5, font.label = list(size = 20, color = "black")), left = text_grob("MethylCIBERSORT estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "b", fig.lab.face = "bold", fig.lab.size = 16)

Fig_S1c <- annotate_figure(ggarrange(p_GSE132203_100_DHS_all_all, p_GSE132203_100_DHS_each, ncol = 1, nrow = 2, heights = 1:3.5, font.label = list(size = 20, color = "black")), left = text_grob("DHS estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "c", fig.lab.face = "bold", fig.lab.size = 16)

Fig_S2a <- annotate_figure(ggarrange(p_GSE77797_six_BPmet_all, G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black")), left = text_grob("BPmet estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "a", fig.lab.face = "bold", fig.lab.size = 16)

Fig_S2b <- annotate_figure(ggarrange(p_GSE77797_six_MethylCIBERSORT_all, G6_MethylCIBERSORT_WB[[1]], G6_MethylCIBERSORT_WB[[2]], G6_MethylCIBERSORT_WB[[3]], G6_MethylCIBERSORT_WB[[4]], G6_MethylCIBERSORT_WB[[5]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black")), left = text_grob("MethylCIBERSORT estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "b", fig.lab.face = "bold", fig.lab.size = 16)

Fig_S2c <- annotate_figure(ggarrange(p_GSE77797_six_DHS_all, G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 3, nrow = 2, font.label = list(size = 20, color = "black")), left = text_grob("DHS estimate", color = "black", size = 14, rot = 90), bottom = text_grob("FACS", color = "black", size = 14), fig.lab = "c", fig.lab.face = "bold", fig.lab.size = 16)
```

### Figure S1
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
Fig_S1a
Fig_S1b
Fig_S1c
```

### Figure S2
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
Fig_S2a
Fig_S2b
Fig_S2c
```

### 2021-12-01 Figures/Paper_Figures_final.Rmd
Add files via upload

@@
 
-myeloma_all_signs["Mean", ] = colMeans(myeloma_all_signs, na.rm = T) %>% round(., 3)
-myeloma_all_signs_p["Mean", ] = colMeans(myeloma_all_signs_p, na.rm = T)
+myeloma_all_signs$Mean = rowMeans(myeloma_all_signs, na.rm = T) %>% round(., 3)
+myeloma_all_signs_p$Mean = rowMeans(myeloma_all_signs, na.rm = T)
+
+myeloma_all_signs = myeloma_all_signs[order(myeloma_all_signs$Mean, decreasing = T), ]
+myeloma_all_signs_p = myeloma_all_signs_p[rownames(myeloma_all_signs), ]
 ```
@@
 
-Melanoma_GSE72056_all_signs["Mean", ] = colMeans(Melanoma_GSE72056_all_signs, na.rm = T) %>% round(., 3)
-Melanoma_GSE72056_all_signs_p["Mean", ] = colMeans(Melanoma_GSE72056_all_signs_p, na.rm = T)
+Melanoma_GSE72056_all_signs$Mean = rowMeans(Melanoma_GSE72056_all_signs, na.rm = T) %>% round(., 3)
+Melanoma_GSE72056_all_signs_p$Mean = rowMeans(Melanoma_GSE72056_all_signs_p, na.rm = T)
+
+Melanoma_GSE72056_all_signs = Melanoma_GSE72056_all_signs[order(Melanoma_GSE72056_all_signs$Mean, decreasing = T), ]
+Melanoma_GSE72056_all_signs_p = Melanoma_GSE72056_all_signs_p[rownames(Melanoma_GSE72056_all_signs), ]
 ```
@@
                                                cor.test(meta$MCP_CD8_T_cells, meta_facs$CD8_Tcells)$p.value, NA),
-                               "EpiDISH (BPRNACan)" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$p.value, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$p.value,
+                               "EpiDISH BPRNACan" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$p.value, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$p.value,
                                                         cor.test(meta$Epidish_BPRNACan_CD4, meta_facs$CD4_Tcells)$p.value,
@@
                                                         cor.test(meta$Epidish_BPRNACan_cancer,meta_facs$Cancer_cells)$p.value),
-                               "EpiDISH (BPRNACanProMet)" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 
+                               "EpiDISH BPRNACanProMet" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 
                                                               cor.test(meta$Epidish_BPRNACanProMet_NK, meta_facs$NKcells)$p.value,
@@
                                                         cor.test(meta$Epidish_BPRNACanProMet_cancer,meta_facs$Cancer_cells)$p.value),
-                               "EpiDISH (BPRNACan3DProMet)" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,
+                               "EpiDISH BPRNACan3DProMet" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,
                                                                 cor.test(meta$Epidish_BPRNACan3DProMet_NK, meta_facs$NKcells)$p.value,
@@
                                                         cor.test(meta$Epidish_BPRNACan3DProMet_cancer,meta_facs$Cancer_cells)$p.value),
-                               "EpiDISH (Melanoma)" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,
+                               "EpiDISH Melanoma" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,
                                                       NA, cor.test(meta$Epidish_CBSX.melanoma_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
@@
                                                cor.test(meta$Epidish_CBSX.melanoma_Malignant, meta_facs$Cancer_cells)$p.value),
-                               "EpiDISH (HNSCC)" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,
+                               "EpiDISH HNSCC" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,
                                                      NA, cor.test(meta$Epidish_CBSX.HNSCC_T.cells.CD4, meta_facs$CD4_Tcells)$p.value,
@@
                                                cor.test(meta$Epidish_CBSX.HNSCC_Malignant, meta_facs$Cancer_cells)$p.value),
-                               "EpiDISH (NSCLC)" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,
+                               "EpiDISH NSCLC" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,
                                                      cor.test(meta$Epidish_CBSX.NSCLC_NK.cells, meta_facs$NKcells)$p.value, 
@@
 
-Melanoma_GSE93722_all_signs["Mean", ] = colMeans(Melanoma_GSE93722_all_signs, na.rm = T) %>% round(., 3)
-Melanoma_GSE93722_all_signs_p["Mean", ] = colMeans(Melanoma_GSE93722_all_signs_p, na.rm = T)
+Melanoma_GSE93722_all_signs$Mean = rowMeans(Melanoma_GSE93722_all_signs, na.rm = T) %>% round(., 3)
+Melanoma_GSE93722_all_signs_p$Mean = rowMeans(Melanoma_GSE93722_all_signs_p, na.rm = T)
+
+Melanoma_GSE93722_all_signs = Melanoma_GSE93722_all_signs[order(Melanoma_GSE93722_all_signs$Mean, decreasing = T), ]
+Melanoma_GSE93722_all_signs_p = Melanoma_GSE93722_all_signs_p[rownames(Melanoma_GSE93722_all_signs), ]
 ```

### 2021-12-01 Figures/Supp_figures.Rmd
update of supp figures
text size and description

@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(T_cell.)|(T.cell.)")) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(T_cell.)|(T.cell.)")) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Mono.*")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = mono, ncol = 3, top = textGrob("Monocytes", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = mono, ncol = 3, top = textGrob("Monocytes", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M1)|(_Macro.*)")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(Macrophage.)|(Macrophages.)")) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = m1, ncol = 3, top = textGrob("Macrophages M1", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = m1, ncol = 3, top = textGrob("Macrophages M1", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M2)|(_Macro.*)")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(Macrophage.)|(Macrophages.)")) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = m2, ncol = 3, top = textGrob("Macrophages M2", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = m2, ncol = 3, top = textGrob("Macrophages M2", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(B_cell.*)|(_B.cell.*)|(_B_lin.*)")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], ".cell.*")) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")))
 
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Neu.*")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = neutro, ncol = 3, top = textGrob("Neutrophils", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = neutro, ncol = 3, top = textGrob("Neutrophils", gp=gpar(fontsize=20,font=3,face="bold")))
 ```
@@
           axis.title.y= element_text(size = 12, face="bold") )  + 
-      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Macro.*")) +
+      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
       theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
-      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
+      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
+      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
   })
 }
-grid.arrange(grobs = macro, ncol = 3, top = textGrob("Macrophages", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
+grid.arrange(grobs = macro, ncol = 3, top = textGrob("Macrophages", gp=gpar(fontsize=20,font=3,face="bold")))
 

### 2021-12-02 Prediction_model/predict_from_deconv_revision.py
Add plot mode to the predict_from_deconv_revision analysis

@@ -76,6 +76,11 @@ TEST_CLOUG = True    # models trained on all datasets are tested on the Cloughes
 CV_ADAPT = False     # increase k, the number of CV folds, if training didn't converged with previous k
 CV_TRAIN = 5         # default number of splits for CV
 CV_MAX = 10          # max splits if previous training failed
+PLOT_MODE = False    # enable/disable plot figures on the screen
+
+def plot_figure(plt, PLOT_MODE):
+    if PLOT_MODE:
+        plt.show()
 
 path_interm = Path("../data/intermediate/Deconvolution_paper")
 data_version = 'all_deconvolutions_2021-08-10'
@@ -579,7 +584,7 @@ for l1_name, l1_ratios in l1_ratios_list:
                 score_split[clin_col + ' - diff ' + metric] = score_split[clin_col + ' - ' + metric] - score_split[test_name + ' - ' + metric]
                 
         score_condi[str_condi] = score_split
-        plt.show()
+        plot_figure(plt, PLOT_MODE)
 
     scores = pd.DataFrame.from_dict(score_condi, orient='index')
     scores.index.name = 'signature'
@@ -653,7 +658,7 @@ for score_label in score_labels:
         title = f"Gain in predictive power by {score_label} and feature importance of {clin_col}"
         ax.set_title(title)
         fig.savefig(dir_load / title, facecolor='white')
-        fig.show()
+        plot_figure(fig, PLOT_MODE)
 
 # %% [markdown] tags=[]
 # ### Cell types proportions
@@ -948,7 +953,7 @@ for l1_name, l1_ratios in l1_ratios_list:
             plt.title(param_string + f" l1_ratio {l1_ratio}, C {C}")
             plt.savefig(dir_save / f"coef_{param_string}.png", bbox_inches='tight', facecolor='white')
 
-            plt.show()
+            plot_figure(plt, PLOT_MODE)
             plt.close('all')
         
         if TEST_CLOUG:
@@ -1195,7 +1200,7 @@ plt.ylabel('coef')
 plt.title(param_string + f" l1_ratio {l1_ratio}, C {C}")
 # plt.savefig(dir_save / f"coef_{param_string}.png", bbox_inches='tight', facecolor='white')
 
-plt.show()
+plot_figure(plt, PLOT_MODE)
 plt.close('all')
 
 if TEST_CLOUG:

### 2021-12-02 Prediction_model/predict_from_deconv_revision.py
Fix minor crashes in predict_from_deconv_revision analysis

@@ -1282,7 +1282,7 @@ for comb in combinations(condis, 2):
 # ### Plot models coefficients and Odds Ratios
 
 # %%
-coefs.index
+# coefs.index
 
 # %%
 dir_load = r"../data/processed/Deconvolution_paper_revision/data_version-all_deconvolutions_2021-11-02/only_melanoma/drop_scores/cv-5/l1_ratios-advised/"
@@ -1383,7 +1383,7 @@ for signature in signatures:
 # ## Reorder models' performance data
 
 # %%
-filename = dir_save / ('l1_ratios-' + l1_name) / 'scores_signatures_deconv.csv'
+filename = os.path.join(dir_save, 'scores_signatures_deconv.csv')
 df = pd.read_csv(filename, index_col=0)
 df
 
@@ -1397,7 +1397,7 @@ for score_label in score_labels:
     df_select['mean all datasets'] = df_select.mean(axis=1)
     df_select.sort_values(by='mean lodo', ascending=False, inplace=True)
 
-    filename = dir_save / ('l1_ratios-' + l1_name) / ('scores_signatures_deconv_sorted-' + score_label + '.csv')
+    filename = os.path.join(dir_save, ('scores_signatures_deconv_sorted-' + score_label + '.csv'))
     df_select.to_csv(filename)
 
 # %%

### 2021-12-02 Figures/Supp_fig4.Rmd
Refactor Supp_fig4.Rmd

@@
 })
-knitr::opts_chunk$set(fig.width=15, fig.height=15) 
+knitr::opts_chunk$set(fig.width = 15, fig.height = 15)
 ```
@@
 
-tcga_deconv = read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_all_TCGA.txt", header=T)
+tcga_deconv <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/deconvolutions_pipeline/all_deconvolutions/all_deconvolutions_all_TCGA.txt", header = T)
 Aran_all_facs <- read.csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv", sep = "\t")
@@
 
-colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
-colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
-colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
-colnames(tcga_deconv) = colnames(tcga_deconv) %>% str_replace_all("CBSX__LM22_" , "CBSX.LM22")
+colnames(tcga_deconv) <- colnames(tcga_deconv) %>% str_replace_all("(CBSX__Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix_)|(CBSX_Fig2ab.NSCLC_PBMCs_scRNAseq_sigmatrix)", "CBSX.NSCLC")
+colnames(tcga_deconv) <- colnames(tcga_deconv) %>% str_replace_all("(CBSX__scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b_)|(CBSX_scRNA.Seq_melanoma_Tirosh_sigmatrix_SuppFig_3.b)", "CBSX.melanoma")
+colnames(tcga_deconv) <- colnames(tcga_deconv) %>% str_replace_all("(CBSX__sigmatrix_HNSCC_Fig2cd_)|(CBSX_sigmatrix_HNSCC_Fig2cd)", "CBSX.HNSCC")
+colnames(tcga_deconv) <- colnames(tcga_deconv) %>% str_replace_all("CBSX__LM22_", "CBSX.LM22")
 
@@
 
-Aran_all_facs$Sample_ID <- Aran_all_facs$Sample_ID %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")
-Aran_all_facs <- Aran_all_facs[Aran_all_facs$CPE != "NaN",]
+Aran_all_facs$Sample_ID <- Aran_all_facs$Sample_ID %>%
+  str_remove_all(., ".01A.*") %>%
+  str_replace_all(., "-", ".")
+Aran_all_facs <- Aran_all_facs[Aran_all_facs$CPE != "NaN", ]
 
-tcga_deconv$Samples <- tcga_deconv$Samples %>% str_remove_all(., ".01A.*") %>% str_replace_all(., "-", ".")
+tcga_deconv$Samples <- tcga_deconv$Samples %>%
+  str_remove_all(., ".01A.*") %>%
+  str_replace_all(., "-", ".")
 
@@
 
-Aran_all_facs <- Aran_all_facs %>% .[.$Sample_ID %in% Comm_samples, ] %>% .[order(.$Sample_ID), ]
-HE_all_TCGA <- HE_all_TCGA %>% .[.$ParticipantBarcode %in% Comm_samples, ] %>% .[order(.$ParticipantBarcode),]
+Aran_all_facs <- Aran_all_facs %>%
+  .[.$Sample_ID %in% Comm_samples, ] %>%
+  .[order(.$Sample_ID), ]
+HE_all_TCGA <- HE_all_TCGA %>%
+  .[.$ParticipantBarcode %in% Comm_samples, ] %>%
+  .[order(.$ParticipantBarcode), ]
 tcga_deconv <- tcga_deconv %>% .[.$Samples %in% Comm_samples, ]
@@
   group_by(Samples) %>%
-  summarise_all(mean)%>%
+  summarise_all(mean) %>%
   as.data.frame()
-tcga_deconv <- merge(tcga_deconv, Aran_all_facs[,1:2], by.x = "Samples", by.y = "Sample_ID")
-rownames(tcga_deconv) = tcga_deconv$Samples
-tcga_deconv <- tcga_deconv[,-1]
+tcga_deconv <- merge(tcga_deconv, Aran_all_facs[, 1:2], by.x = "Samples", by.y = "Sample_ID")
+rownames(tcga_deconv) <- tcga_deconv$Samples
+tcga_deconv <- tcga_deconv[, -1]
 
 # for each method_signature make a DF with all 3 cell type in H&E
-make_df <- function(met_sign, DF){
-  data = DF %>% select(colnames(DF)[grepl(met_sign, colnames(DF))])
-  lymph = data %>% 
-    select(colnames(data)[grepl("CD4", colnames(data))], colnames(data)[grepl("CD8", colnames(data))], 
-           colnames(data)[grepl("NK", colnames(data))]) %>% 
+make_df <- function(met_sign, DF) {
+  data <- DF %>% select(colnames(DF)[grepl(met_sign, colnames(DF))])
+  lymph <- data %>%
+    select(
+      colnames(data)[grepl("CD4", colnames(data))], colnames(data)[grepl("CD8", colnames(data))],
+      colnames(data)[grepl("NK", colnames(data))]
+    ) %>%
     replace(is.na(.), 0) %>%
     mutate(sum = rowSums(across(where(is.numeric))))
-  macro = data %>% 
-    select(colnames(data)[grepl("M0", colnames(data))], colnames(data)[grepl("M1", colnames(data))], 
+  macro <- data %>%
+    select(
+      colnames(data)[grepl("M0", colnames(data))], colnames(data)[grepl("M1", colnames(data))],
       colnames(data)[grepl("M2", colnames(data))], colnames(data)[grepl("Mono", colnames(data))],
-           colnames(data)[grepl("Macro", colnames(data))]) %>% 
+      colnames(data)[grepl("Macro", colnames(data))]
+    ) %>%
     replace(is.na(.), 0) %>%
     mutate(sum = rowSums(across(where(is.numeric))))
-  neutro = data %>% 
+  neutro <- data %>%
     select(colnames(data)[grepl("Neu", colnames(data))]) %>%
@@
 
-  final_df = data.frame(Lymphocytes = lymph$sum, Neutrophils = neutro$sum,
-                        Macrophages = macro$sum, row.names = rownames(data))
+  final_df <- data.frame(
+    Lymphocytes = lymph$sum, Neutrophils = neutro$sum,
+    Macrophages = macro$sum, row.names = rownames(data)
+  )
   final_df
@@
 
-colcol = c("darkslategrey", "green", "coral")
-make_plot <- function(data, method_data, method){
-  ploty = list()
+colcol <- c("darkslategrey", "green", "coral")
+make_plot <- function(data, data_HE, method, method_data, cancer_type) {
+  ploty <- list()
   for (i in 1:3) {
@@
       i <- i
-      x = ggplot(data, aes(x = data_HE[, i], y = method_data[, i])) +
+      ggplot(data, aes(x = data_HE[, i], y = method_data[, i])) +
         geom_point(colour = colcol[i]) +
-        stat_smooth(method = lm, size = 0.2, color = "black", se = F, fullrange = T) +
-        scale_x_continuous(limits = c(0, max(method_data[,i]))) +
-        scale_y_continuous(limits = c(0, max(method_data[,i]))) +
-        theme(axis.title.x= element_text(size = 12, face="bold"), 
-            axis.title.y= element_text(size = 12, face="bold") )  + 
-        ylab(method) + xlab("FACS") + ggtitle(colnames(method_data)[i]) +
+        stat_smooth(method = lm, formula = y ~ x, size = 0.2, color = "black", se = F, fullrange = T) +
+        scale_x_continuous(limits = c(0, max(method_data[, i]))) +
+        scale_y_continuous(limits = c(0, max(method_data[, i]))) +
+        theme(
+          axis.title.x = element_text(size = 12, face = "bold"),
+          axis.title.y = element_text(size = 12, face = "bold")
+        ) +
+        ylab(method) +
+        xlab("FACS") +
+        ggtitle(colnames(method_data)[i]) +
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
-        annotate("text", x = -Inf, y = Inf, hjust=-0.2, vjust=1, label = paste("italic(r)==", round(cor.test(method_data[, i], data_HE[, i])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
-        annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=3, label = paste("RMSE =", round(sqrt(mean((method_data[, i] - data_HE[, i])^2, na.rm = T)), 2)), parse = F, size = 6) 
+        annotate("text", x = -Inf, y = Inf, hjust = -0.2, vjust = 1, label = paste("italic(r)==", round(cor.test(method_data[, i], data_HE[, i])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
+        annotate("text", x = -Inf, y = Inf, hjust = -1, vjust = 3, label = paste("RMSE =", round(sqrt(mean((method_data[, i] - data_HE[, i])^2, na.rm = T)), 2)), parse = F, size = 6)
     })
@@
 
+make_plots <- function(tcga_deconv, signatures_list, HE_all_TCGA, cancer_type) {
+  cancer_type_data <- tcga_deconv %>% filter(Cancer_type == cancer_type)
+
+  cancer_type_data_HE <- HE_all_TCGA %>% filter(Study == cancer_type) %>% select(3:5)
+
+  for (signature in signatures_list) {
+    signature_data <- make_df(signature, cancer_type_data)
+    curated_signature <- str_remove(signature, fixed("^"))
+    make_plot(cancer_type_data, cancer_type_data_HE, curated_signature, signature_data, cancer_type)
+  }
+}
+```
+
+```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+signatures_list <- c("Quantiseq", "Epidish_BPRNACan", "DeconRNASeq_BPRNACan", "Epidish_BPRNACanProMet", "DeconRNASeq_BPRNACanProMet", "Epidish_BPRNACan3DProMet", "DeconRNASeq_BPRNACan3DProMet", "Epidish_CBSX.NSCLC", "DeconRNASeq_CBSX.NSCLC", "Epidish_CBSX_LM22", "DeconRNASeq_CBSX_LM22", "Epidish_CBSX.melanoma", "DeconRNASeq_CBSX.melanoma", "Epidish_CBSX.HNSCC", "DeconRNASeq_CBSX.HNSCC", "^CBSX.LM22", "^CBSX.NSCLC", "^CBSX.melanoma", "^CBSX.HNSCC")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "LUAD")
-data_HE = HE_all_TCGA %>% filter(Study == "LUAD")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "LUAD")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "LUSC")
-data_HE = HE_all_TCGA %>% filter(Study == "LUSC")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "LUSC")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "PRAD")
-data_HE = HE_all_TCGA %>% filter(Study == "PRAD")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "PRAD")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "BLCA")
-data_HE = HE_all_TCGA %>% filter(Study == "BLCA")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "BLCA")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "CESC")
-data_HE = HE_all_TCGA %>% filter(Study == "CESC")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "CESC")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "BRCA")
-data_HE = HE_all_TCGA %>% filter(Study == "BRCA")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "BRCA")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "UCEC")
-data_HE = HE_all_TCGA %>% filter(Study == "UCEC")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "UCEC")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "COAD")
-data_HE = HE_all_TCGA %>% filter(Study == "COAD")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "COAD")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "READ")
-data_HE = HE_all_TCGA %>% filter(Study == "READ")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "READ")
 ```
@@
 
-data = tcga_deconv %>% filter(Cancer_type == "SKCM")
-data_HE = HE_all_TCGA %>% filter(Study == "SKCM")
-data_HE = data_HE[, 3:5]
-
-QT = make_df("Quantiseq", data)
-make_plot(data, QT, "QuantiSeq")
-
-Epidish_BPRNACan = make_df("Epidish_BPRNACan", data)
-make_plot(data, Epidish_BPRNACan, "Epidish_BPRNACan")
-
-DeconRNASeq_BPRNACan = make_df("DeconRNASeq_BPRNACan", data)
-make_plot(data, DeconRNASeq_BPRNACan, "DeconRNASeq_BPRNACan")
-
-Epidish_BPRNACanProMet = make_df("Epidish_BPRNACanProMet", data)
-make_plot(data, Epidish_BPRNACanProMet, "Epidish_BPRNACanProMet")
-DeconRNASeq_BPRNACanProMet = make_df("DeconRNASeq_BPRNACanProMet", data)
-make_plot(data, DeconRNASeq_BPRNACanProMet, "DeconRNASeq_BPRNACanProMet")
-
-Epidish_BPRNACan3DProMet = make_df("Epidish_BPRNACan3DProMet", data)
-make_plot(data, Epidish_BPRNACan3DProMet, "Epidish_BPRNACan3DProMet")
-DeconRNASeq_BPRNACan3DProMet = make_df("DeconRNASeq_BPRNACan3DProMet", data)
-make_plot(data, DeconRNASeq_BPRNACan3DProMet, "DeconRNASeq_BPRNACan3DProMet")
-
-Epidish_CBSX.NSCLC = make_df("Epidish_CBSX.NSCLC", data)
-make_plot(data, Epidish_CBSX.NSCLC, "Epidish_CBSX.NSCLC")
-DeconRNASeq_CBSX.NSCLC = make_df("DeconRNASeq_CBSX.NSCLC", data)
-make_plot(data, DeconRNASeq_CBSX.NSCLC, "DeconRNASeq_CBSX.NSCLC")
-
-Epidish_CBSX_LM22 = make_df("Epidish_CBSX_LM22", data)
-make_plot(data, Epidish_CBSX_LM22, "Epidish_CBSX_LM22")
-DeconRNASeq_CBSX_LM22 = make_df("DeconRNASeq_CBSX_LM22", data)
-make_plot(data, DeconRNASeq_CBSX_LM22, "DeconRNASeq_CBSX_LM22")
-
-Epidish_CBSX.melanoma = make_df("Epidish_CBSX.melanoma", data)
-make_plot(data, Epidish_CBSX.melanoma, "Epidish_CBSX.melanoma")
-DeconRNASeq_CBSX.melanoma = make_df("DeconRNASeq_CBSX.melanoma", data)
-make_plot(data, DeconRNASeq_CBSX.melanoma, "DeconRNASeq_CBSX.melanoma")
-
-Epidish_CBSX.HNSCC = make_df("Epidish_CBSX.HNSCC", data)
-make_plot(data, Epidish_CBSX.HNSCC, "Epidish_CBSX.HNSCC")
-DeconRNASeq_CBSX.HNSCC = make_df("DeconRNASeq_CBSX.HNSCC", data)
-make_plot(data, DeconRNASeq_CBSX.HNSCC, "DeconRNASeq_CBSX.HNSCC")
-
-CBSX.LM22 = make_df("^CBSX.LM22", data)
-make_plot(data, CBSX.LM22, "CBSX.LM22")
-CBSX.NSCLC = make_df("^CBSX.NSCLC", data)
-make_plot(data, CBSX.NSCLC, "CBSX.NSCLC")
-CBSX.melanoma = make_df("^CBSX.melanoma", data)
-make_plot(data, CBSX.melanoma, "CBSX.melanoma")
-CBSX.HNSCC = make_df("^CBSX.HNSCC", data)
-make_plot(data, CBSX.HNSCC, "CBSX.HNSCC")
-
+make_plots(tcga_deconv, signatures_list, HE_all_TCGA, "SKCM")
 ```

### 2021-12-14 Final_methylation_RNAseq_signatures.Rmd
Add files via upload

  ---
title: "R Notebook"
output: html_notebook
---
### To do different gene expression by limma package

```{r}

  DGEs <- function(data, Phenotype, lFC, FDR, method){
      require(limma)
      require(dplyr)
      #require(dendextend)

      message("[===========================]")
      message("[<<<<<<< DGEs START >>>>>>>>>]")
      message("[<<<< Pairwise analysis >>>>>]")
      message("------------------------------")

      # This function creates the pairs for the pairwise matrices
      design.pairs <- function(levels) {
          n <- length(levels)
          design <- matrix(0,n,choose(n,2))
          rownames(design) <- levels
          colnames(design) <- 1:choose(n,2)
          k <- 0
          for (i in 1:(n - 1))
              for (j in (i + 1):n) {
                  k <- k + 1
                  design[i,k] <- 1
                  design[j,k] <- -1
                  colnames(design)[k] <- paste(levels[i], "-", levels[j],sep = "")
              }
          design
      }

      # This function creates the pairs for the pairwise matrices

      design <- model.matrix(~0 + Phenotype)
      contr.matrix <- design.pairs(levels(factor(Phenotype)))
      colnames(design) <- rownames(contr.matrix)

      # Removing heteroscedascity from data
      v <- voom(log2(data+1), design, plot = F)

    if (method == "Blood") {  
      # Fitting linear models for comparisons of interest
      Fit <- lmFit(v, design) %>%
          contrasts.fit(., contr.matrix) %>%
          eBayes(.)

    } else if (method == "Cancer") {

      Fit <- lmFit(v, design) %>%
          contrasts.fit(., contr.matrix) %>%
          eBayes(.) %>% treat(., lfc = lFC)

    }

      FitList <- list()
      for (i in 1:ncol(contr.matrix)) {
          FitList[[i]] <- topTreat(Fit[which(decideTests(Fit)[,i] != 0),], coef = i, adjust.method = "BH", number = nrow(v$E)) %>% mutate(ID = rownames(.)) %>% filter(adj.P.Val < FDR)

      }

      names(FitList) <- colnames(contr.matrix)
      message("thank you for you waiting")
      return(FitList)

  }

  Signfeature <- function(data_TPM, Phenotype, FitList, FCcuoff ,MaxDMRs) {
      require(dplyr)
      require(matrixStats)
      require(limma)

      message("[===========================]")
      message("[<<<< Signature START >>>>>]")
      message("-----------------------------")

      # design <- model.matrix(~0 + Phenotype)
      # v_expr <- voom(data, design, plot = FALSE)

      # using positive FC (=over-expressed in cell type of interest)
      # FitList is DGEs which calculate by DGEs function

      A1 <- list()
      for (i in 1:length(FitList)) {

          A1[[i]] <- filter(FitList[[i]],  abs(logFC) > FCcuoff) %>% arrange(., desc(logFC)) #%>% top_n(ceiling(n()*0.5), wt = logFC)
          if (nrow(A1[[i]]) > MaxDMRs) {
              A1[[i]] <- A1[[i]][1:MaxDMRs,]
          }
      }

      sig <- lapply(A1, function(x) dplyr::select(x,ID))
      sig <- do.call(rbind, sig)
      sig <- filter(sig, !duplicated(ID))
      data1 <- data_TPM[rownames(data_TPM) %in% sig$ID,]

      # Print number of selected probes (signature)
      nrow(data1)

      result <- getMedVal(data1, Phenotype)
      message("[===========================]")
      message("[<<<< Signature END >>>>>]")
      message("-----------------------------")
      return(result)
  }

getMedVal <- function(data, Phenotype){
  library(matrixStats)

  Trans <- data.frame(t(data))
  Mt.Split <- split(Trans, Phenotype)
  Mt.Split <- lapply(Mt.Split, function(x) colMedians(data.matrix(x)))
  Mt.Split <- do.call(cbind, Mt.Split)
  rownames(Mt.Split) <- rownames(data)
  return(Mt.Split)
}

### To choose suitable threshold of LogFC (save as PDF file)

DGEs.QC <- function(FitList, FDR) {

    require(ggpubr)

    p <- list()

    for (i in 1:length(FitList)) {
        p[[i]] <- ggplot(FitList[[i]][FitList[[i]]$adj.P.Val < FDR,], aes(x = logFC)) + geom_density(colour = "red") + labs(title = names(FitList)[i], x = "logFC", y = "Density") + theme(plot.title = element_text(hjust = 0.5))
    }
    return(do.call(ggarrange, p))
}

getExpMatrix <- function(geneList, expression){

    df_out <- expression[geneList, ]
    return(df_out)
}

```

### BPRNA signature

```{r}

blueprint_DGEs_blood <- DGEs(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,7178:7216], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[7178:7216], FDR = 0.05, method = "Blood")

Mediant_blueprint_blood <- getMedVal(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,7178:7216], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[7178:7216])

BPRNA <- Signfeature(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(7178:7216)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[c(7178:7216)], FitList = blueprint_DGEs_blood,  FCcuoff = 2.5, MaxDMRs = 200)

```

### BPRNACan signature

```{r}

TCGA_normal_cancer_WB_DGEs <- DGEs(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(1:7164)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[1:7164], lFC = 1.5, FDR = 0.05, method = "Cancer")

blueprint_DGEs <- DGEs(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,7165:7216], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[7165:7216], lFC = 2, FDR = 0.05, method = "Cancer")

TCGA_cancer_blueprint_DGEs <- DGEs(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(684:6778, 7165:7216)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[c(684:6778, 7165:7216)], lFC = 2, FDR = 0.05, method = "Cancer")

Mediant_TCGA_normal_cancer_WB <- getMedVal(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(1:7164)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[1:7164])

Mediant_TCGA_cancer_blueprint <- getMedVal(data = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(684:6778, 7165:7216)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[c(684:6778, 7165:7216)])

Tumor.sig <- Signfeature(data_TPM = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(1:7164)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[1:7164], FitList = TCGA_normal_cancer_WB_DGEs, FCcuoff = 3, MaxDMRs = 100)

TIL.sig <- Signfeature(data_TPM = TCGA_normal_cancer_WB_blueprint_TPM_normalization[,c(684:6778, 7165:7216)], Phenotype = TCGA_normal_cancer_WB_blueprint_phenotype[c(684:6778, 7165:7216)], FitList = blueprint_DGEs, FCcuoff = 2, MaxDMRs = 150)

Immune_Tumor_CpGs <- unique(c(rownames(Tumor.sig), rownames(TIL.sig)))

BPRNACan <- getExpMatrix(geneList = Immune_Tumor_CpGs, expression = Mediant_TCGA_cancer_blueprint)

```

### 2021-12-14 Final_methylation_DNAm_signatures.Rmd
Add files via upload

---
title: "R Notebook"
output: html_notebook
---

### import bigwig data  ###

```{r}

# Function for importing bigWig data

FeatureBigWig <- function(x) {
	coverage <- c()
	for (i in 1:length(x)) {
    coverage <- c(coverage, list(data.frame(import(x[[i]]))))
  }
	coverage
}

# Merge the same samples's data

combine <- function(x){
    k <- c()
    for (i in seq(from = 1, to = length(x), by = 2)) {
        k <- c(k, list(data.frame(merge(x[[i]], x[[i + 1]], by.x = c('seqnames', 'start', 'end'), by.y = c('seqnames', 'start', 'end')))))
  }
    k
}

# Discards bases that have coverage below 10X

filter <- function(cg){
    flt <- c()
        for (i in 1:length(cg)) { 
        flt <- c(flt, list(data.frame(cg[[i]][cg[[i]]$score.y <= quantile(cg[[i]]$score.y, .999) & cg[[i]]$score.y >= 10,])))
        }
    flt
}

# Merge the all samples

final_merge <- function(path) {

    library(rtracklayer)

    files <- dir(path,  full.names = TRUE)

    Feature.cell <- FeatureBigWig(files)

    merge.cell <- combine(Feature.cell)

    filter.merge.cell <- filter(merge.cell)

    names.files <- c(names(filter.merge.cell[[1]])[1:3],unique(gsub('.CPG.*', '', dir(path))))

    dat = filter.merge.cell[[1]]

for (i in 2:length(filter.merge.cell)) {
    dat <- merge(dat, filter.merge.cell[[i]], by.x = c('seqnames', 'start', 'end'), by.y = c('seqnames', 'start', 'end'))
    }
    a <- dat[,1:3]
    for (j in seq(from = 6, to = ncol(dat), by = 6)) {
        a <- cbind(a,dat[, j])
        }
    colnames(a) <- names.files 
    a
}

```

# Generate signatures codes

```{r}

# Find different methylation positions (DMPs)

  DMPs <- function(data, Phenotype, method){
      require(limma)
      require(dplyr)

      message("[===========================]")
      message("[<<<< DMPs START >>>>>]")
      message("-----------------------------")

      design.pairs <- function(levels) {
          n <- length(levels)
          design <- matrix(0,n,choose(n,2))
          rownames(design) <- levels
          colnames(design) <- 1:choose(n,2)
          k <- 0
          for (i in 1:(n - 1))
              for (j in (i + 1):n) {
                  k <- k + 1
                  design[i,k] <- 1
                  design[j,k] <- -1
                  colnames(design)[k] <- paste(levels[i], "-", levels[j],sep = "")
              }
          design
      }

          design <- model.matrix(~0 + Phenotype)
          contr.matrix <- design.pairs(levels(factor(Phenotype)))
          colnames(design) <- rownames(contr.matrix)

      Fit <- lmFit(data, design) %>%
          contrasts.fit(., contrasts = contr.matrix) %>%
          eBayes(.)

      if (method == "TM") {

        FitList <- list()
        for (i in 1:ncol(contr.matrix)) {
            FitList[[i]] <- topTable(Fit[which(decideTests(Fit)[,i] != 0),], coef = i, adjust.method = "BH", number = nrow(data)) %>% mutate(ID = rownames(.))
            message(paste0(i, " done"))
        }

        } else if (method == "TIL") {
            FitList <- list()
            for (i in 1:ncol(contr.matrix)) {
               FitList[[i]] <- topTable(Fit, coef = i, adjust.method = "BH", number = nrow(data)) %>% mutate(ID = rownames(.)) 
              message(paste0(i, " done"))

        }
      }
      names(FitList) <- colnames(contr.matrix)

      message("[<<<<< DMPs END >>>>>>]")
      message("[===========================]")
      return(FitList)
  }

  # Function to get median value of each gene from an input dataframe

  getMedVal <- function(data, Phenotype){
    library(matrixStats)
    Trans <- data.frame(t(data))
    Mt.Split <- split(Trans, Phenotype)
    Mt.Split <- lapply(Mt.Split, function(x) colMedians(data.matrix(x)))
    Mt.Split <- do.call(cbind, Mt.Split)
    rownames(Mt.Split) <- rownames(data)
    return(Mt.Split)
  }

  Signfeature <- function(data, Phenotype, FitList, FDR, FCcuoff, MaxDMRs, method) {
    require(dplyr)
    require(matrixStats)
    require(limma)

      message("[===========================]")
      message("[<<<< Signature START >>>>>]")
      message("-----------------------------")

  # Filter by thresholds
  if (method == "TM") {
       A1 <- list()
      for (i in 1:length(FitList)) {
           A1[[i]] <- filter(FitList[[i]], adj.P.Val < FDR & abs(logFC) > FCcuoff) #%>% arrange(., desc(logFC))
          if (nrow(A1[[i]]) > MaxDMRs) { 
            A1[[i]] <- A1[[i]][1:MaxDMRs,]
            }
      }
  } else if (method == "TIL") {
      A1 <- list()
      for (i in 1:length(FitList)) {
          A1[[i]] <- filter(FitList[[i]], adj.P.Val < FDR & abs(logFC) > FCcuoff) #%>% arrange(., desc(logFC))
          if (nrow(A1[[i]]) > MaxDMRs) { 
            A1[[i]] <- A1[[i]][1:MaxDMRs,]
            }
      }
  }

    sig <- lapply(A1, function(x) dplyr::select(x,ID))
    sig <- do.call(rbind, sig)
    sig <- filter(sig, !duplicated(ID))
    data1 <- data[rownames(data) %in% sig$ID,]

  # Print number of selected probes (signature)
   nrow(data1)

    result <- getMedVal(data1, Phenotype)
      message("[===========================]")
      message("[<<<< Signature END >>>>>]")
      message("-----------------------------")
     return(result)
  }

  # function to extract expression values of a list of CpGs

  getExpMatrix <- function(geneList, expression){

      df_out <- expression[geneList, ]
      return(df_out)
  }

DGEs.QC <- function(FitList, FDR) {

    require(ggpubr)

    p <- list()

    for (i in 1:length(FitList)) {
        p[[i]] <- ggplot(FitList[[i]][FitList[[i]]$adj.P.Val < FDR,], aes(x = logFC)) + geom_density(colour = "red") + labs(title = names(FitList)[i], x = "logFC", y = "Density") + theme(plot.title = element_text(hjust = 0.5)) + scale_x_continuous(breaks = seq(-1, 1, 0.2)) + theme(axis.text.x = element_text(size = 10, color = "Black"), axis.text.y = element_text(size = 10, color = "Black"))
    }
    return(do.call(ggarrange, p))
}

```

## BPmet signature ##

```{r}

FitList_IC_blood <- DMPs(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[, c(56:80, 93:105)], Phenotype = blueprint_pheno[c(1:25, 38:50)], method = "TIL")

Mediant_IC_blood <- getMedVal(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,c(56:80, 93:105)], Phenotype = blueprint_pheno[-c(26:37,51:52)])

BPmet <- Signfeature(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,c(56:80, 93:105)], Phenotype = blueprint_pheno[-c(26:37,51:52)], FitList = FitList_IC_blood, FDR = 0.05, FCcuoff = 0.2, MaxDMRs = 100, method = "TIL")

```

## BPmetCan signature ##

```{r}

  group <- c(rep("normal", 17), rep("cancer", 34), rep("wb", 4))

  Pheno2 <- c(as.character(group[18:51]), as.character(blueprint_pheno))

  FitList_TM <- DMPs(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,-c(56:107)], Phenotype = group, method = "TM")

  # FitList_IC <- DMPs(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,-c(1:55,81:92,106:107)], Phenotype = blueprint_pheno[-c(26:37,51:52)], method = "TIL")

  FitList_TIC <- DMPs(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,c(18:51,56:107)], Phenotype = Pheno2, method = "TIL")

Mediant_T <- getMedVal(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,-c(56:107)], Phenotype = group)

# Mediant_IC <- getMedVal(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,-c(1:55,81:92,106:107)], Phenotype = blueprint_pheno[-c(26:37,51:52)])

Mediant_TIC <- getMedVal(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,c(18:51, 56:107)], Phenotype = Pheno2)

Tumor.sig <- Signfeature(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,-c(56:107)], Phenotype = group, FitList = FitList_TM, FDR = 0.05, FCcuoff = 0.5, MaxDMRs = 100, method = "TM")

TIC.sig <- Signfeature(data = Normal_cancer_WB_blueprint_WGBS_genomic_numeric[,c(18:51,56:107)], Phenotype = Pheno2, FitList = FitList_TIC, FDR = 10e-6, FCcuoff = 0.3, MaxDMRs = 300, method = "TIL")

Immune_Tumor_CpGs <- unique(c(rownames(Tumor.sig), rownames(TIC.sig)))

BPmetCan <- getExpMatrix(geneList = Immune_Tumor_CpGs, expression = Mediant_TIC)

```

### 2022-01-26 Figures/Figure4.Rmd
Add Figure4.Rmd

---
title: "Figure 4"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 15, fig.height = 17, echo = FALSE, results = "hide", warning = FALSE, message = FALSE)
```

```{r}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(ggpubr)
library(grid)
library(gridExtra)
library(magrittr)
```

```{r}
plot_figure <- function(longer_merge, title) {
  longer_merge %<>%
    mutate(name = str_replace(name, "Avg_", "Average ")) %>%
    mutate(name = str_replace(name, "Met_", "Methylation "))
  ggplot(longer_merge, aes(sorted_type, fct_rev(name))) +
    geom_tile(aes(fill = cor), colour = "grey", size = 1) +
    scale_fill_gradient2(low = "#5C5DAF", mid = "white", high = "#EA2E2D") +
    geom_text(aes(label = text), col = "black", size = 8) +
    theme_minimal() +
    theme(
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.y = element_blank(),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 14),
      axis.text.x = element_text(
        angle = 90, hjust = 0.5, vjust = 0.5,
        size = 16, colour = "black", face = "bold"
      ),
      axis.text.y = element_text(size = 16, colour = "black", face = "bold")
    ) +
    labs(fill = str_c("Correlation")) +
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5, size = 16, face = "bold"))
}

prepare_table <- function(correlations, pvalues) {
  correlations %<>% select(...1, order(.[9,-1], decreasing = T))
pvalues %<>% dplyr::select(colnames(correlations))

longer_correlations <- correlations %>% pivot_longer(-1) %>% arrange(name)
longer_pvalues<- pvalues %>% pivot_longer(-1)

merged_all <- bind_cols(longer_correlations, longer_pvalues[, 3]) %>% dplyr::rename(cor=value...3, pvalue=value...4)
merged_all %>%
  mutate(text = case_when(
    is.na(pvalue) & is.na(cor) ~ str_c("NA"),
    is.na(pvalue) & (cor == 0) ~ str_c(cor, "\n"),
    pvalue >= 0.05 ~ str_c(cor),
    pvalue >= 0.01 & pvalue < 0.05 ~ str_c(cor, "\n*"),
    pvalue >= 0.001 & pvalue < 0.01 ~ str_c(cor, "\n**"),
    pvalue < 0.001 ~ str_c(cor, "\n***")
  )) %>% mutate(sorted_type = factor(...1, levels = unique(...1)))
}

```

# Table of correlation

### Lymphocytes
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
lymph_correlations <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/lymph.csv") 
lymph_pvalues <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/lymph_p.csv")

lymph_figure <- plot_figure(prepare_table(lymph_correlations, lymph_pvalues), "Lymphocytes")

#ggsave("lymph_figure.pdf", dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
```

### Macrophages
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
macro_correlations <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/macro.csv")
macro_pvalues <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/macro_p.csv")

macro_figure <- plot_figure(prepare_table(macro_correlations, macro_pvalues), "Macrophages")

```

### Neutrophils
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
neutro_correlations <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/neutro.csv")
neutro_pvalues <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/all_tcga_corr/neutro_p.csv")

neutro_figure <- plot_figure(prepare_table(neutro_correlations, neutro_pvalues), "Neutrophils")

```
```{r}
ggsave("all_figure4_heatmaps.pdf", arrangeGrob(grobs = list(lymph_figure, macro_figure, neutro_figure)), dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
```

### 2022-01-26 Figures/Figure4.Rmd
Fix style in Figure4.Rmd

@@
 prepare_table <- function(correlations, pvalues) {
-  correlations %<>% select(...1, order(.[9,-1], decreasing = T))
+  correlations %<>% select(...1, order(.[9, -1], decreasing = T))
   pvalues %<>% dplyr::select(colnames(correlations))
 
-longer_correlations <- correlations %>% pivot_longer(-1) %>% arrange(name)
-longer_pvalues<- pvalues %>% pivot_longer(-1)
+  longer_correlations <- correlations %>%
+    pivot_longer(-1) %>%
+    arrange(name)
+  longer_pvalues <- pvalues %>% pivot_longer(-1)
 
-merged_all <- bind_cols(longer_correlations, longer_pvalues[, 3]) %>% dplyr::rename(cor=value...3, pvalue=value...4)
+  merged_all <- bind_cols(longer_correlations, longer_pvalues[, 3]) %>% dplyr::rename(cor = value...3, pvalue = value...4)
   merged_all %>%
@@
       pvalue < 0.001 ~ str_c(cor, "\n***")
-  )) %>% mutate(sorted_type = factor(...1, levels = unique(...1)))
+    )) %>%
+    mutate(sorted_type = factor(...1, levels = unique(...1)))
 }
-
 ```
@@
 
-#ggsave("lymph_figure.pdf", dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
+# ggsave("lymph_figure.pdf", dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
 ```

### 2022-02-09 Figures/Figure2.Rmd
Add Figures2.Rmd
create functions to do plots of RNAseq methods vs H&E estimates like in
Fig 2. Finished scatterplot and rugplot but I need to implement the plot
saving and the last heatmaps

---
title: "Figure 2 and figure 2 supplementary material"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 15, fig.height = 17, echo = FALSE, results = "hide", warning = FALSE, message = FALSE)
```

# Imports

```{r}
library(tidyverse)
```

# Functions

```{r}
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot

    to_plot.cor <- rcorr(data.matrix(to_plot[c(x,y)]), type = "pearson")

  if (to_plot.cor$P[x,y] == 0){
    p.val = "< 2.2e-16"
    } else {
      p.val = paste("=", signif(to_plot.cor$P[x,y],2))
    }
    to_plot.rmse = sqrt(colMeans((to_plot[,y] - to_plot[,x])^2, na.rm = T))

  stats <- paste("Pearson: R = ", round(to_plot.cor$r[x,y], 2),
               ", pval ", p.val, "\n",
               "RMSE = ", round(to_plot.rmse, 2), sep = "")

  ## plot
  your_plot <- ggplot(to_plot) +
    aes_string(x = x, y = y) +
    geom_point(color = color) +
    labs(title = title, subtitle = stats, x = "", y = "") +
    geom_smooth(method=lm) +
    theme_classic() +
    theme(
      plot.title=element_text(family='', face='bold', colour='black', size=25, margin=margin(t=50,b=-40)),
      plot.subtitle=element_text(family='', face='italic', colour='black', size=18, margin=margin(t=50,b=-40)),
      text = element_text(size=15)
  )

  return(your_plot)
}

# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
# of a given method/signature.
# Works inside of ridgeplot_parse. it takes:
# -  'deconv_data': contains the deconvolution data to index and summarize. 
#
# -  'signature dictionary': contains the exact names of the method
#                           (if it works with one signature) or the signature
#                           (if it works with multiple methods). 
#
# - iterator: string to subscript the signatures_dict with either signature
#             or methods names depending where is it called
#
# - prefix: string to leave just celltype names when substracted to the columns
#             of deconv_data of the specified method (or method + signature).
#
# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"

ridgeplot_parse <- function(deconv_data, signatures_dictionary){

  results <- tibble(Samples = deconv_data$Samples)

  names_table <- deconv_data %>%
    dplyr::select(-c(Samples)) %>%
    names() %>%
    str_split_fixed("_", 2) %>%
    as_tibble(.name_repair = "unique")

  for (method in unique(names_table[,1,drop=T])){

    if (method %in% c("Epidish",
                      "DeconRNASeq",
                      "CBSX")){

      for (signature in names(signatures_dictionary)){ # iterates through all the signatures (the ones not present for the method will yield all 0)
        to_match <- paste(method, signature, sep = "_")

        for (celltype in names(signatures_dictionary[[signature]])){
          if (length(signatures_dictionary[[signature]][[celltype]]) > 0){
            name_of_summary <- paste(to_match, celltype, sep = "_")
            columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".")
            # print(name_of_summary)
            # deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% colnames() %>% print()
            # cat("-------------------------\n")
            deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
          }
        }
  }
    } else{

    to_match <- method

    for (celltype in names(signatures_dictionary[[method]])){
      if (length(signatures_dictionary[[method]][[celltype]]) > 0){
          name_of_summary <- paste(to_match, celltype, sep = "_")
          columns_to_summarize <- paste(to_match, signatures_dictionary[[method]][[celltype]], sep = ".")

          deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
      }
    }
  }
  }
  results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
}

plot_ridgeplot <- function(data, ct){

  # calculate correlations
  data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table

  # select strings to remove from signature names
  substring_remove <- c(paste("_",ct, sep=""),
    "_Tirosh_sigmatrix_SuppFig_3-b",
    "_scRNA-Seq",
    "Fig2ab-",
    "_PBMCs_scRNAseq_sigmatrix",
    "sigmatrix_",
    "_Fig2cd")

  # filter correlations
  deconv_ct_names <- data %>% dplyr::select(matches(ct), -ct) %>% names()
  cor.table[["r"]][ct,deconv_ct_names] %>% sort() -> cor.ct.sorted
  names(cor.ct.sorted) <- str_remove_all(names(cor.ct.sorted), paste(substring_remove, collapse = "|"))
  cor.ct.sorted["H&E"] = 1

  # ridgeplot perse
  cols <- c("H&E" = "red", "CBSX" = "yellow", "Epidish" = "blue", "Quantiseq" = "pink", "DeconRNASeq" = "green")

  ct_subset = data %>%
    dplyr::select(matches(ct)) %>%
    rename("H&E" = ct) %>%
    gather() %>%
    mutate(key = str_remove_all(key, paste(substring_remove, collapse = "|")),
           key=factor(key, levels=names(cor.ct.sorted)),
           method = as.factor(str_extract(key, "[^_]+")))

ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
  geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                       point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
  theme_ridges() + ggtitle(ct) +
  annotate("text", x = 1, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
  scale_colour_manual(values = cols) +
   theme(axis.text.x = element_text(color = "black", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 20, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "black", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.title = element_text(color = "black", size = 20)) +
  ylab("") + xlab("% of cell type")

}

summary_corrplots

```

# Data loading

```{r}
read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
  mutate_at("Samples", str_remove_all, ".01A*") %>%
  mutate_at("Samples", str_replace_all, "-", ".") %>% 
  group_by(Samples) %>%
  summarise_all(mean) -> tcga_deconv

read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
  mutate_at("Sample_ID", str_remove_all, ".01A*") %>%
  mutate_at("Sample_ID", str_replace_all, "-", ".") -> Aran_all_facs

read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
  dplyr::select(-c(...1)) %>%
  mutate_at("ParticipantBarcode", str_remove_all, ".01A*") %>%
  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") -> HE_all_TCGA

```

# Figure
## A) Tumor Purity
```{r}
Aran_all_facs %>% dplyr::filter(Cancer_type == "LUAD", CPE != "NaN") %>% 
  arrange(factor(Sample_ID, levels = Sample_ID))  -> Facs_LUAD_

Comm_samples <- Reduce(intersect, list(tcga_deconv$Samples,
                                       Facs_LUAD_$Sample_ID))
Facs_LUAD_ %>% 
  dplyr::filter(Sample_ID %in% Comm_samples) %>% 
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_LUAD

tcga_deconv %>% 
  dplyr::filter(Samples %in% Comm_samples) %>% 
  arrange(factor(Samples, levels = Comm_samples)) -> LUAD_RNA_decon

# Scatterplot CCLE_TIL10 LUAD
identical(Facs_LUAD$Sample_ID, LUAD_RNA_decon$Samples) %>% stopifnot()
 Facs_LUAD %>% bind_cols(LUAD_RNA_decon) -> LUAD_merged

title = "ESTIMATE vs CCLE TIL10 Cancer"
color = "black"
scatterplot_truevsestimate(LUAD_merged, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color)

# Scatterplot BPRNACan LUAD
title = "ESTIMATE vs BPRNACan Cancer"
color = "black"
scatterplot_truevsestimate(LUAD_merged, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color)
```

## B) 3 Celltypes ridge plots
### Create aggregation dictionaries to compare with Lymphocites, Macrophages and Neutrophils FACs

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
signature_dict <- list()
signature_dict[["BPRNACan"]] <- list(Lymphocytes = c("B", "CD4", "CD8", "NK"),
                    Macrophages = c("Mono", "M0", "M1", "M2"),
                    Neutrophils = c("Neu"))

signature_dict[["BPRNACanProMet"]] <- signature_dict[["BPRNACan"]]
signature_dict[["BPRNACan3DProMet"]] <- signature_dict[["BPRNACan"]]

signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4","NKT.cells" ,"B.cells", "NK.cells"),
                                                                         Macrophages = c("Monocytes"),
                                                                         Neutrophils = c())

signature_dict[["CBSX_LM22"]] <- list(Lymphocytes = c("B.cells.naive", "B.cells.memory",  "T.cells.CD8",
                                                        "T.cells.CD4.naive", "T.cells.CD4.memory.resting",
                                                        "T.cells.CD4.memory.activated", 
                                                        "T.cells.regulatory..Tregs.", "NK.cells.resting",
                                                        "NK.cells.activated"),
                                        Macrophages = c("Monocytes", "Macrophages.M0", "Macrophages.M1", "Macrophages.M2",),
                                        Neutrophils = c("Neutrophils")) # skipped , "Plasma.cells" "T.cells.follicular.helper", "T.cells.gamma.delta" in Lymphos, as well as "Dendritic.cells.resting", "Dendritic.cells.activated" for macros

signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4",
                                                                                                   "NK.cells", "B.cells"),
                                                                                   Macrophages = c("Macrophages"),
                                                                                   Neutrophils = c())

signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells"),
                                                          Macrophages = c("Macrophages", "Dendritic.cells"),
                                                          Neutrophils = c())

signature_dict[["CCLE_TIL10"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells", "NK.cells", "Tregs"),
                    Macrophages = c("Macrophages.M1", "Macrophages.M2", "Monocytes", "Dendritic.cells"),
                    Neutrophils = c("Neutrophils"))

signature_dict[["Quantiseq"]] <- list(Lymphocytes = c("B.cell", "T.cell.CD4+.(non-regulatory)", "T.cell.CD8+", "T.cell.regulatory(Tregs)", "NK.cell"),
                    Macrophages = c("Macrophage.M1", "Macrophage.M2", "Myeloid.dendritic.cell", "Monocyte"),
                    Neutrophils = c("Neutrophil"))

# signature_dict[["MCP"]] <- list(Lymphocytes = c("T.cells", "CD8.T.cells", "Cytotoxic.lymphocytes","B.lineage" ,"NK.cells"),
#                     Macrophages = c("Myeloid.dendritic.cells", "Monocytic.lineage"),
#                     Neutrophils = c("Neutrophils")) # Based in enrichment so cant sum celltype estimates

# signature_dict[["XCELL"]] <- list(Lymphocytes = c(".B-cells", "CD4+.", "CD8+.", "CLP", "NK.", "Th1_cells", "Tgd_cells", "Th2_cells", "Tregs"),
#                     Macrophages = c("aDC", "cDC", "iDC", "pDC", "DC", "Macrophages.", "Monocytes"),
#                     Neutrophils = c("Neutrophils")) # Not in the paper in theory

```

### Data processing & ridge plot

```{r}
HE_all_TCGA %>% dplyr::filter(Study == "LUAD") %>%  na.exclude() %>%
  arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))  -> HE_LUAD_

Comm_samples <- Reduce(intersect, list(tcga_deconv$Samples,
                                       HE_LUAD_$ParticipantBarcode))
HE_LUAD_ %>% 
  dplyr::filter(ParticipantBarcode %in% Comm_samples) %>% 
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_LUAD

tcga_deconv %>%
  rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) %>%
  dplyr::filter(Samples %in% Comm_samples) %>% 
  arrange(factor(Samples, levels = Comm_samples)) -> LUAD_RNA_decon

LUAD_summarized <- ridgeplot_parse(deconv_data = LUAD_RNA_decon, signatures_dictionary = signature_dict)

# Ridgeplot
identical(HE_LUAD$ParticipantBarcode, LUAD_summarized$Samples) %>% stopifnot()
 HE_LUAD %>% bind_cols(LUAD_summarized) %>% select(-c(Samples)) -> LUAD_merged

for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
 print(plot_ridgeplot(data = LUAD_merged, ct = ct))
 }
# Suplementary idea: apply the above to all TCGA and add dataset as a plot argument

```

## Summary Corrplot

```{r}

```

# Suplementary figure

```{r}

```

### 2022-02-09 Figures/Figure2.Rmd
add option to do Fig2B of any TCGA
add dependencies + wrapper_ridgeplot so you can run the code to do teh
ridgeplot in any of TCGA cancer types

@@
 library(tidyverse)
+library(Hmisc)
+library(ggridges)
 ```
@@
 
-plot_ridgeplot <- function(data, ct){
-
-  # calculate correlations
+plot_ridgeplot <- function(data){
  data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table
-
+  final_plot <- list()
+  for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
     # select strings to remove from signature names
@@
 
-ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
+  final_plot[[ct]] <- ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
     geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
@@
     scale_colour_manual(values = cols) +
-   theme(axis.text.x = element_text(color = "black", size = 20, angle = 90, hjust = .5, vjust = .5, face = "plain"),
-        axis.text.y = element_text(color = "black", size = 20, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
-        axis.title.x = element_text(color = "black", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
-        axis.title.y = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
+     theme(axis.text.x = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
+          axis.text.y = element_text(color = "black", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
+          axis.title.x = element_text(color = "black", size = 10, angle = 0, hjust = .5, vjust = 0, face = "plain"),
+          axis.title.y = element_text(color = "black", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
           plot.title = element_text(color = "black", size = 20)) +
     ylab("") + xlab("% of cell type")
+  }
+  return(final_plot)
+}
 
+wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){
+
+  # build the data
+  true_estimates %>% dplyr::filter(Study == cancer_abreviation) %>%  na.exclude() %>%
+    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))  -> true_subset_
+
+  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
+                                         true_subset_$ParticipantBarcode))
+  true_subset_ %>% 
+    dplyr::filter(ParticipantBarcode %in% Comm_samples) %>% 
+    arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> true_subset
+
+  deconv_data  %>%
+    dplyr::filter(Samples %in% Comm_samples) %>% 
+    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
+
+  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+
+  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
+  true_subset %>% bind_cols(deconv_subset_summary) %>% select(-c(Samples)) -> data_toplot
+
+  # calculate correlations
+ return(plot_ridgeplot(data_toplot))
 }
@@
   mutate_at("ParticipantBarcode", str_remove_all, ".01A*") %>%
-  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") -> HE_all_TCGA
+  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") %>%
+  distinct(ParticipantBarcode, .keep_all= TRUE) -> HE_all_TCGA # for the READ samples TCGA.AG.5 & TCGA.AG.3
 
@@
                                                         "NK.cells.activated"),
-                                        Macrophages = c("Monocytes", "Macrophages.M0", "Macrophages.M1", "Macrophages.M2",),
+                                        Macrophages = c("Monocytes", "Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
                                         Neutrophils = c("Neutrophils")) # skipped , "Plasma.cells" "T.cells.follicular.helper", "T.cells.gamma.delta" in Lymphos, as well as "Dendritic.cells.resting", "Dendritic.cells.activated" for macros
@@
 ```{r}
-HE_all_TCGA %>% dplyr::filter(Study == "LUAD") %>%  na.exclude() %>%
-  arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))  -> HE_LUAD_
-
-Comm_samples <- Reduce(intersect, list(tcga_deconv$Samples,
-                                       HE_LUAD_$ParticipantBarcode))
-HE_LUAD_ %>% 
-  dplyr::filter(ParticipantBarcode %in% Comm_samples) %>% 
-  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_LUAD
 
@@
   rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
-  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) %>%
-  dplyr::filter(Samples %in% Comm_samples) %>% 
-  arrange(factor(Samples, levels = Comm_samples)) -> LUAD_RNA_decon
+  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) -> tcga_deconv_ridge
 
-LUAD_summarized <- ridgeplot_parse(deconv_data = LUAD_RNA_decon, signatures_dictionary = signature_dict)
+ridgeplots_by_cancer <- list()
+for (cancer in unique(HE_all_TCGA$Study)){
+ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
+}
 
-# Ridgeplot
-identical(HE_LUAD$ParticipantBarcode, LUAD_summarized$Samples) %>% stopifnot()
- HE_LUAD %>% bind_cols(LUAD_summarized) %>% select(-c(Samples)) -> LUAD_merged
-
-for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
- print(plot_ridgeplot(data = LUAD_merged, ct = ct))
- }
-# Suplementary idea: apply the above to all TCGA and add dataset as a plot argument
+# pdf_name <- paste("test", "ridges", ".pdf", sep = "")
+#   ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
+#
 

### 2022-02-11 Figures/Figure2.Rmd
wrap tumour purity scatterplot + fix ridgeplot text adjust + loop through cancers

@@
              method = as.factor(str_extract(key, "[^_]+")))
-
-  final_plot[[ct]] <- ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
+  adjust_x <- max(ct_subset$value)
+  final_plot[[ct]] <- print(ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
     geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
@@
     theme_ridges() + ggtitle(ct) +
-    annotate("text", x = 1, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
+    annotate("text", x = adjust_x, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
+    scale_x_continuous(limits = c(0, (adjust_x + adjust_x*0.2))) +
     scale_colour_manual(values = cols) +
@@
           plot.title = element_text(color = "black", size = 20)) +
-    ylab("") + xlab("% of cell type")
+    ylab("") + xlab("% of cell type"))
   }
@@
  return(plot_ridgeplot(data_toplot))
+}
+
+wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
+  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
+    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_
+
+  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
+                                         true_subset_$Sample_ID))
+  true_subset_ %>% 
+    dplyr::filter(Sample_ID %in% Comm_samples) %>% 
+    arrange(factor(Sample_ID, levels = Comm_samples)) -> true_subset
+
+  deconv_data %>% 
+    dplyr::filter(Samples %in% Comm_samples) %>% 
+    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
+
+  # Scatterplot CCLE_TIL10
+  identical(true_subset$Sample_ID, deconv_subset$Samples) %>% stopifnot()
+   true_subset %>% bind_cols(deconv_subset) -> merged_subset
+
+  final_plot = list()
+  color = "black"
+
+  title = "ESTIMATE vs CCLE TIL10 Cancer"
+  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color)
+
+  # Scatterplot BPRNACan
+  title = "ESTIMATE vs BPRNACan Cancer"
+  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color)
+
+  return(final_plot)
 }
@@
 ```{r}
-Aran_all_facs %>% dplyr::filter(Cancer_type == "LUAD", CPE != "NaN") %>% 
-  arrange(factor(Sample_ID, levels = Sample_ID))  -> Facs_LUAD_
-
-Comm_samples <- Reduce(intersect, list(tcga_deconv$Samples,
-                                       Facs_LUAD_$Sample_ID))
-Facs_LUAD_ %>% 
-  dplyr::filter(Sample_ID %in% Comm_samples) %>% 
-  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_LUAD
-
-tcga_deconv %>% 
-  dplyr::filter(Samples %in% Comm_samples) %>% 
-  arrange(factor(Samples, levels = Comm_samples)) -> LUAD_RNA_decon
-
-# Scatterplot CCLE_TIL10 LUAD
-identical(Facs_LUAD$Sample_ID, LUAD_RNA_decon$Samples) %>% stopifnot()
- Facs_LUAD %>% bind_cols(LUAD_RNA_decon) -> LUAD_merged
-
-title = "ESTIMATE vs CCLE TIL10 Cancer"
-color = "black"
-scatterplot_truevsestimate(LUAD_merged, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color)
-
-# Scatterplot BPRNACan LUAD
-title = "ESTIMATE vs BPRNACan Cancer"
-color = "black"
-scatterplot_truevsestimate(LUAD_merged, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color)
+wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, cancer_abreviation = "LUAD")
 ```
@@
 ridgeplots_by_cancer <- list()
+tpurity_by_cancer <- list()
+blank  <- ggplot() + theme_void()
+
 for (cancer in unique(HE_all_TCGA$Study)){
   ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
+  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
+        },
+        error = function(cond) {
+          message(paste("not enough FACs samples for ", cancer, "no scatterplot will be generated"))
+          return(list(ccle = blank, bprna = blank))
+        }
+  )
+  tpurity_by_cancer[[cancer]]$extra = blank
 }
 
-# pdf_name <- paste("test", "ridges", ".pdf", sep = "")
-#   ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
+ridges <- ggarrange(plotlist = ridgeplots_by_cancer[["LUAD"]], ncol = 3, common.legend = T, legend = "bottom")
+scater <- ggarrange(plotlist = tpurity_by_cancer[["LUAD"]], ncol = 3, common.legend = T)
+blank  <- ggplot() + theme_void()
+fullplot <- ggarrange(plotlist = list(scater, ridges, blank), nrow = 3, heights = c(0.15, 0.3, 0.45))
+annotate_figure(fullplot, top = text_grob("LUAD", color = "black", size = 30))
+pdf_name <- paste("test", "ridges", ".pdf", sep = "")
+ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 3)
+# for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
+#    annotate_figure(print(ridgeplots_by_cancer[[cancer]][[ct]]),
+#                              top = text_grob("Test", color = "black", size = 30),
+#                              left = text_grob("Estimated fractions", color = "black", size = 20, rot = 90),
+#                              bottom = text_grob("H&E estimates", color = "black", size = 20))
+# }
+
 #

### 2022-02-16 Figures/Figure2.Rmd
code organization and Sup.fig2.pdf generation
also did a change in the scatterplot axis labels and select and relocate
dplyr name conflicts

@@
 # Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
-scatterplot_truevsestimate <- function(merged_data, x, y, title, color){
+scatterplot_truevsestimate <- function(merged_data, x, y, title, color, x_lab = "", y_lab = ""){
     merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
@@
     geom_point(color = color) +
-    labs(title = title, subtitle = stats, x = "", y = "") +
+    labs(title = title, subtitle = stats, x = x_lab, y = y_lab) +
     geom_smooth(method=lm) +
@@
       dplyr::select(matches(ct)) %>%
-      rename("H&E" = ct) %>%
+      dplyr::rename("H&E" = ct) %>%
       gather() %>%
@@
   identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
-  true_subset %>% bind_cols(deconv_subset_summary) %>% select(-c(Samples)) -> data_toplot
+  true_subset %>% bind_cols(deconv_subset_summary) %>% dplyr::select(-c(Samples)) -> data_toplot
 
@@
   color = "black"
+  x_lab = "ESTIMATE"
 
   title = "ESTIMATE vs CCLE TIL10 Cancer"
-  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color)
+  y_lab = "CCLE TIL10 Cancer"
+  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
 
@@
   title = "ESTIMATE vs BPRNACan Cancer"
-  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color)
+  y_lab = "BPRNACan Cancer"
+  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
 
@@
 }
-
-summary_corrplots
 
@@
 
+wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = "LUAD")
+```
+
+## Summary Corrplot
+
+```{r}
+
+```
+
+# Suplementary figure
+
+```{r}
 ridgeplots_by_cancer <- list()
@@
   tpurity_by_cancer[[cancer]]$extra = blank
-}
 
-ridges <- ggarrange(plotlist = ridgeplots_by_cancer[["LUAD"]], ncol = 3, common.legend = T, legend = "bottom")
-scater <- ggarrange(plotlist = tpurity_by_cancer[["LUAD"]], ncol = 3, common.legend = T)
+  ridges <- ggarrange(plotlist = ridgeplots_by_cancer[[cancer]], ncol = 3, common.legend = T, legend = "bottom")
+  scater <- ggarrange(plotlist = tpurity_by_cancer[[cancer]], ncol = 3, common.legend = T)
   blank  <- ggplot() + theme_void()
   fullplot <- ggarrange(plotlist = list(scater, ridges, blank), nrow = 3, heights = c(0.15, 0.3, 0.45))
-annotate_figure(fullplot, top = text_grob("LUAD", color = "black", size = 30))
-pdf_name <- paste("test", "ridges", ".pdf", sep = "")
-ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 3)
-# for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
-#    annotate_figure(print(ridgeplots_by_cancer[[cancer]][[ct]]),
-#                              top = text_grob("Test", color = "black", size = 30),
-#                              left = text_grob("Estimated fractions", color = "black", size = 20, rot = 90),
-#                              bottom = text_grob("H&E estimates", color = "black", size = 20))
-# }
-
-#
-
+  annotate_figure(fullplot, top = text_grob(cancer, color = "black", size = 40))
+  pdf_name <- paste("Sup.fig2_", cancer, ".pdf", sep = "")
+  ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2.5)
+}
+system("pdfunite Sup.fig2_*.pdf Sup.fig2.pdf")
 ```
-
-## Summary Corrplot
-
-```{r}
-
-```
-
-# Suplementary figure
-
-```{r}
-
-```

### 2022-03-09 Figures/Figure2.Rmd
reorganize figures

@@
 ```{r}
+################################################################################
 # Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
@@
 }
+################################################################################
 
+################################################################################
+wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
+  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
+    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_
+
+  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
+                                         true_subset_$Sample_ID))
+  true_subset_ %>% 
+    dplyr::filter(Sample_ID %in% Comm_samples) %>% 
+    arrange(factor(Sample_ID, levels = Comm_samples)) -> true_subset
+
+  deconv_data %>% 
+    dplyr::filter(Samples %in% Comm_samples) %>% 
+    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
+
+  # Scatterplot CCLE_TIL10
+  identical(true_subset$Sample_ID, deconv_subset$Samples) %>% stopifnot()
+   true_subset %>% bind_cols(deconv_subset) -> merged_subset
+
+  final_plot = list()
+  color = "black"
+  x_lab = "ESTIMATE"
+
+  title = "ESTIMATE vs CCLE TIL10 Cancer"
+  y_lab = "CCLE TIL10 Cancer"
+  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
+
+  # Scatterplot BPRNACan
+  title = "ESTIMATE vs BPRNACan Cancer"
+  y_lab = "BPRNACan Cancer"
+  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
+
+  return(final_plot)
+}
+################################################################################
+
+################################################################################
 # This function returns the Lymphocytes, Macrophages and Neutrophils summarized
@@
 }
+################################################################################
 
+################################################################################
 wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){
@@
 }
-
-wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
-  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
-    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_
-
-  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
-                                         true_subset_$Sample_ID))
-  true_subset_ %>% 
-    dplyr::filter(Sample_ID %in% Comm_samples) %>% 
-    arrange(factor(Sample_ID, levels = Comm_samples)) -> true_subset
-
-  deconv_data %>% 
-    dplyr::filter(Samples %in% Comm_samples) %>% 
-    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
-
-  # Scatterplot CCLE_TIL10
-  identical(true_subset$Sample_ID, deconv_subset$Samples) %>% stopifnot()
-   true_subset %>% bind_cols(deconv_subset) -> merged_subset
-
-  final_plot = list()
-  color = "black"
-  x_lab = "ESTIMATE"
-
-  title = "ESTIMATE vs CCLE TIL10 Cancer"
-  y_lab = "CCLE TIL10 Cancer"
-  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
-
-  # Scatterplot BPRNACan
-  title = "ESTIMATE vs BPRNACan Cancer"
-  y_lab = "BPRNACan Cancer"
-  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
-
-  return(final_plot)
-}
-
+################################################################################
 ```
@@
 ```{r}
-wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, cancer_abreviation = "LUAD")
+wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = , cancer_abreviation = "LUAD")
 ```

### 2022-03-09 Figures/Figure2.Rmd
add to wrapper_tpurity choose estimate

@@
 ################################################################################
-wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
+wrapper_tpurity <- function(deconv_data, true_estimates, estimate, cancer_abreviation){
   true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
@@
   color = "black"
-  x_lab = "ESTIMATE"
+  x_lab = estimate
 
-  title = "ESTIMATE vs CCLE TIL10 Cancer"
+  title = paste0(estimate, " vs CCLE TIL10 Cancer")
   y_lab = "CCLE TIL10 Cancer"
-  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
+  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
 
   # Scatterplot BPRNACan
-  title = "ESTIMATE vs BPRNACan Cancer"
+  title = paste0(estimate, " vs BPRNACan Cancer")
   y_lab = "BPRNACan Cancer"
-  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
+  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
 
@@
 ```{r}
-wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = , cancer_abreviation = "LUAD")
+wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = "ABSOLUTE" , cancer_abreviation = "LUAD")
 ```
@@
   ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
-  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
+  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, estimate = "ABSOLUTE", cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
         },

### 2022-03-09 Figures/Figure2.Rmd
add wrapper_corrplots

@@
 ```{r}
+################################################################################
+# Customizable corrplot functions (modified from https://www.khstats.com/blog/corr-plots/corr-plots/)
+cors <- function(df, cor.stat) {
+  M <- Hmisc::rcorr(as.matrix(df), type = cor.stat)
+  Mdf <- map(M, ~data.frame(.x))
+  return(Mdf)
+}
+
+formatted_cors <- function(df, cor.stat){
+  cors(df, cor.stat) %>%
+    map(~rownames_to_column(.x, var="measure1")) %>%
+    map(~pivot_longer(.x, -measure1, "measure2")) %>%
+    bind_rows(.id = "id") %>%
+    pivot_wider(names_from = id, values_from = value) %>%
+    dplyr::rename(p = P) %>%
+    mutate(sig_p = ifelse(p < .05, T, F),
+           p_if_sig = ifelse(sig_p, p, NA),
+           r_if_sig = ifelse(sig_p, r, NA)) 
+}
+################################################################################
+
 ################################################################################
@@
 }
+################################################################################
 
+################################################################################
 plot_ridgeplot <- function(data){
@@
 ################################################################################
+
+################################################################################
+wrapper_corrplots <- function(deconv_data, true_estimates, cancer_abreviation){
+  # build the data
+  true_subset_ <- true_estimates %>%  na.exclude() %>%
+    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))
+
+  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
+                                         true_subset_$ParticipantBarcode))
+
+  true_subset <-dplyr::filter(true_subset_, ParticipantBarcode %in% Comm_samples) %>% 
+    arrange(factor(ParticipantBarcode, levels = Comm_samples))
+
+  deconv_subset <- dplyr::filter(deconv_data, Samples %in% Comm_samples) %>% 
+    arrange(factor(Samples, levels = Comm_samples))
+
+  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
+
+  to_corr <- bind_cols(true_subset, deconv_subset_summary) %>% dplyr::select(-c(Samples))
+  ct_corrplots <- list()
+   for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
+    # select strings to remove from signature names
+    substring_remove <- c(paste0("_",ct),
+      "_Tirosh_sigmatrix_SuppFig_3.b",
+      "_scRNA.Seq",
+      "Fig2ab.",
+      "_PBMCs_scRNAseq_sigmatrix",
+      "sigmatrix_",
+      "_Fig2cd")
+
+    store_corrs <- tibble(measure1 = character(),
+                          measure2 = character(),
+                          r = numeric(),
+                          n = numeric(),
+                          p = numeric(),
+                          sig_p = logical(),
+                          p_if_sig = numeric(),
+                          r_if_sig = numeric())
+    # segregate by cancer type
+    for (st in unique(to_corr$Study)){
+      deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
+        # segregate by ct
+        dplyr::select(matches(ct)) %>%
+        formatted_cors(cor.stat = "pearson") %>%
+        # reduce to corrs just to ground truth
+        dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
+        # rename ground truth as cancer type
+        dplyr::mutate(measure1 = st)
+      #add to the rest of cancer type correlations
+      store_corrs <- add_row(store_corrs , deconv_ct_names)
+    }
+
+    # Plot
+    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|"))) %>% 
+    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
+    geom_tile() +
+      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
+         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
+    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
+    geom_text() +
+    theme_classic() +
+    scale_x_discrete(expand=c(0,0)) +
+    scale_y_discrete(expand=c(0,0)) +
+    rotate_x_text(angle = 45)
+   }
+  return(ct_corrplots)
+}
+
 ```
@@
 ```{r}
-
+wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
 ```

### 2022-03-10 Figures/Figure2.Rmd
order Figure2 corrplot by mean

@@
     # Plot
-    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|"))) %>% 
+    store_corrs <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|")))
+
+    order <- store_corrs %>% group_by(measure2) %>% dplyr::summarize(meanr = mean(r)) %>% arrange(desc(meanr))
+    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange( factor(measure2, levels = order$measure2)) %>%
     ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +

### 2022-03-10 Figures/Figure2.Rmd
add Figure2 corrplot average row

@@
 
-    order <- store_corrs %>% group_by(measure2) %>% dplyr::summarize(meanr = mean(r)) %>% arrange(desc(meanr))
-    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange( factor(measure2, levels = order$measure2)) %>%
+    order <- store_corrs %>% 
+      group_by(measure2) %>%
+      dplyr::summarize(r = mean(r)) %>% 
+      arrange(desc(r)) %>% 
+      mutate(measure1 = "Average",
+             p = NA,
+             sig_p = TRUE,
+             p_if_sig = NA,
+             r_if_sig = r ) %>%
+      dplyr::relocate(measure1, .before = measure2)
+
+    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
     ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +

### 2022-03-10 Figures/Figure2.Rmd
fix Figure2 corrplot mean with NANs

@@
     order <- store_corrs %>% 
+      drop_na(r) %>% # Epidish_CBSX_LM22 dont work for UVM in Neutrophils and mean dont work with NANs
       group_by(measure2) %>%

### 2022-03-15 Figures/Figure2.Rmd
Save corrplot Figure2.Rmd

@@
 library(ggridges)
+library(ggtext)
+library(glue)
 ```
@@
 
+    ## Function to highlight the "average" row
+    highlight = function(x, pat, color="black", family="") {
+  ifelse(grepl(pat, x), glue("<b style='font-family:{family}; color:{color}'>{x}</b>"), x)
+}
+
     ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
@@
     scale_x_discrete(expand=c(0,0)) +
-    scale_y_discrete(expand=c(0,0)) +
-    rotate_x_text(angle = 45)
+    scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
+    rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())
    }
@@
 ```{r}
-wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
+corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
+corrplots$Macrophages <- summary_corr$Macrophages + rremove("y.text")
+corrplots$Neutrophils <- summary_corr$Neutrophils + rremove("y.text")
+summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
+
+ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
 ```
@@
 # Suplementary figure
-
 ```{r}

### 2022-04-28 Prediction_model/predict_from_deconv_revision.py
remove XCELL from prediceted model input

@@ -224,7 +224,7 @@ if data_version == 'all_deconvolutions_2021-11-02':
     conditions = [
         'quanTIseq',
         'MCP',
-        'XCELL',
+        #'XCELL',
         'EpiDISH_BPRNACan_',
         'DeconRNASeq_BPRNACan_',
         'EpiDISH_BPRNACanProMet_',
@@ -248,7 +248,7 @@ else:
     conditions = [
         'quanTIseq',
         'MCP',
-        'XCELL',
+        #'XCELL',
         'EpiDISH_BPRNACan_',
         'DeconRNASeq_BPRNACan_',
         'EpiDISH_BPRNACanProMet_',

### 2022-04-29 Figures/Figure2.Rmd
minor fix

@@
 corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
-corrplots$Macrophages <- summary_corr$Macrophages + rremove("y.text")
-corrplots$Neutrophils <- summary_corr$Neutrophils + rremove("y.text")
+corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
+corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
 summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")

### 2022-04-29 Figures/Figure3.Rmd
add Figure3.Rmd

--- 2022-04-29 Figures/Figure2.Rmd
@@
 ---
-title: "Figure 2 and figure 2 supplementary material"
-output:
+title: "Figure 3 and figure 3 supplementary material"
+output: html_notebook
   pdf_document: default
@@
 ```{r, echo=FALSE, warning=FALSE, message=FALSE}
-knitr::opts_chunk$set(fig.width = 15, fig.height = 17, echo = FALSE, results = "hide", warning = FALSE, message = FALSE)
+#knitr::opts_chunk$set(fig.width = 15, fig.height = 17, echo = FALSE, results = "hide", warning = FALSE, message = FALSE)
 ```
@@
 
-  title = paste0(estimate, " vs CCLE TIL10 Cancer")
-  y_lab = "CCLE TIL10 Cancer"
-  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
+  title = paste0(estimate, " vs MethylCBS Cancer")
+  y_lab = "MethylCBS Cancer"
+  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "EpiDISH_MethylCBS_cancer", title, color,  x_lab, y_lab)
 
   # Scatterplot BPRNACan
-  title = paste0(estimate, " vs BPRNACan Cancer")
-  y_lab = "BPRNACan Cancer"
-  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
+  title = paste0(estimate, " vs BPmetCan Cancer")
+  y_lab = "BPmetCan Cancer"
+  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "EpiDISH_BPmetCan_cancer", title, color, x_lab, y_lab)
 
@@
     # select strings to remove from signature names
-    substring_remove <- c(paste("_",ct, sep=""),
-      "_Tirosh_sigmatrix_SuppFig_3-b",
-      "_scRNA-Seq",
-      "Fig2ab-",
-      "_PBMCs_scRNAseq_sigmatrix",
-      "sigmatrix_",
-      "_Fig2cd")
+    # substring_remove <- c(paste("_",ct, sep=""),
+    #   "_Tirosh_sigmatrix_SuppFig_3-b",
+    #   "_scRNA-Seq",
+    #   "Fig2ab-",
+    #   "_PBMCs_scRNAseq_sigmatrix",
+    #   "sigmatrix_",
+    #   "_Fig2cd")
+    substring_remove <- c("nothing")
 
@@
     # ridgeplot perse
-    cols <- c("H&E" = "red", "CBSX" = "yellow", "Epidish" = "blue", "Quantiseq" = "pink", "DeconRNASeq" = "green")
+    cols <- c("H&E" = "red", "CIBERSORT" = "yellow", "EpiDISH" = "blue")
 
@@
 
-  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+  #deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+  deconv_subset_summary <- dplyr::select(deconv_subset, matches("Samples|Lymphocytes|Macrophages|Neutrophils"))
 
@@
 
-  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+  #deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
+  deconv_subset_summary <- dplyr::select(deconv_subset, matches("Samples|Lymphocytes|Macrophages|Neutrophils"))
   identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
@@
     # select strings to remove from signature names
-    substring_remove <- c(paste0("_",ct),
-      "_Tirosh_sigmatrix_SuppFig_3.b",
-      "_scRNA.Seq",
-      "Fig2ab.",
-      "_PBMCs_scRNAseq_sigmatrix",
-      "sigmatrix_",
-      "_Fig2cd")
+    # substring_remove <- c(paste0("_",ct),
+    #   "_Tirosh_sigmatrix_SuppFig_3.b",
+    #   "_scRNA.Seq",
+    #   "Fig2ab.",
+    #   "_PBMCs_scRNAseq_sigmatrix",
+    #   "sigmatrix_",
+    #   "_Fig2cd")
+    substring_remove <- c(paste0("_",ct))
 
@@
 ```{r}
-read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
+tcga_deconv <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/TCGA_EpiDISH_CIBERSORT_BPmetCan_MethylCBS.csv") %>%
+  dplyr::select(-Sample) %>%
+  dplyr::rename(Samples = ...1) %>%
+  rename_with(stringr::str_replace, 
+              pattern = "Neutrophiles$", replacement = "Neutrophils", matches("Neutrophiles")) %>%
   mutate_at("Samples", str_remove_all, ".01A*") %>%
@@
   group_by(Samples) %>%
-  summarise_all(mean) -> tcga_deconv
+  summarise_all(mean)
 
-read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
+Aran_all_facs <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
   mutate_at("Sample_ID", str_remove_all, ".01A*") %>%
-  mutate_at("Sample_ID", str_replace_all, "-", ".") -> Aran_all_facs
+  mutate_at("Sample_ID", str_replace_all, "-", ".")
 
-read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
+HE_all_TCGA <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
   dplyr::select(-c(...1)) %>%
@@
   mutate_at("ParticipantBarcode", str_replace_all, "-", ".") %>%
-  distinct(ParticipantBarcode, .keep_all= TRUE) -> HE_all_TCGA # for the READ samples TCGA.AG.5 & TCGA.AG.3
+  distinct(ParticipantBarcode, .keep_all= TRUE) # for the READ samples TCGA.AG.5 & TCGA.AG.3
 
@@
 ```{r}
-# Lists of celltypes of each signature
+# Lists of celltypes of each signature ( NO NEED IN THIS CASE)
 ## signature dictionary construction (can use . as regexp!)
@@
 signature_dict <- list()
-signature_dict[["BPRNACan"]] <- list(Lymphocytes = c("B", "CD4", "CD8", "NK"),
-                    Macrophages = c("Mono", "M0", "M1", "M2"),
-                    Neutrophils = c("Neu"))
+signature_dict[["BPmetCan"]] <- list(Lymphocytes = c("_B$", "CD4", "CD8", "NK", "Treg", "Lymphocytes"),
+                    Macrophages = c("Mono", "M0", "M1", "M2", "Macrophages"),
+                    Neutrophils = c("Neutrophiles"))
 
-signature_dict[["BPRNACanProMet"]] <- signature_dict[["BPRNACan"]]
-signature_dict[["BPRNACan3DProMet"]] <- signature_dict[["BPRNACan"]]
-
-signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4","NKT.cells" ,"B.cells", "NK.cells"),
-                                                                         Macrophages = c("Monocytes"),
+signature_dict[["MethylCBS"]] <- list(Lymphocytes = c("_B", "CD4", "CD8", "NK", "Treg", "Lymphocytes"),
+                                                                         Macrophages = c("Mono", "Macrophages"),
                                                                          Neutrophils = c())
@@
 
-tcga_deconv %>%
-  rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
-  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) -> tcga_deconv_ridge
+# tcga_deconv_ridge <- tcga_deconv %>%
+#   rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
+#   rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_"))
+tcga_deconv_ridge <- tcga_deconv
 
@@
 
-ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
+ggsave("Fig3_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 1)
 ```
@@
 
-for (cancer in unique(HE_all_TCGA$Study)){
+unique_cancers <- dplyr::filter(HE_all_TCGA, ParticipantBarcode %in% tcga_deconv_ridge$Samples) %>% distinct(Study) %>% deframe()
+for (cancer in unique_cancers){
   ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
@@
   annotate_figure(fullplot, top = text_grob(cancer, color = "black", size = 40))
-  pdf_name <- paste("Sup.fig2_", cancer, ".pdf", sep = "")
+  pdf_name <- paste("Sup.fig3_", cancer, ".pdf", sep = "")
   ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2.5)
 }
-system("pdfunite Sup.fig2_*.pdf Sup.fig2.pdf")
+system("pdfunite Sup.fig3_*.pdf Sup.fig3.pdf")
 ```

### 2022-06-22 Figures/Figure2.Rmd
simplify wrapper corrplots input

@@
 ################################################################################
-wrapper_corrplots <- function(deconv_data, true_estimates, cancer_abreviation){
+wrapper_corrplots <- function(deconv_data, true_estimates){
   # build the data

### 2022-06-23 Figures/Figures_nonTCGA.Rmd
add Figures_nonTCGA.Rmd
corrected teh celltype estimations~ground truth equivalences. Yet to fix
the corrplot function

--- 2022-06-22 Figures/Figure2.Rmd
@@
 ################################################################################
-wrapper_tpurity <- function(deconv_data, true_estimates, estimate, cancer_abreviation){
-  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
-    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_
-
-  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
-                                         true_subset_$Sample_ID))
-  true_subset_ %>% 
-    dplyr::filter(Sample_ID %in% Comm_samples) %>% 
-    arrange(factor(Sample_ID, levels = Comm_samples)) -> true_subset
-
-  deconv_data %>% 
-    dplyr::filter(Samples %in% Comm_samples) %>% 
-    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
-
-  # Scatterplot CCLE_TIL10
-  identical(true_subset$Sample_ID, deconv_subset$Samples) %>% stopifnot()
-   true_subset %>% bind_cols(deconv_subset) -> merged_subset
-
-  final_plot = list()
-  color = "black"
-  x_lab = estimate
-
-  title = paste0(estimate, " vs CCLE TIL10 Cancer")
-  y_lab = "CCLE TIL10 Cancer"
-  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)
-
-  # Scatterplot BPRNACan
-  title = paste0(estimate, " vs BPRNACan Cancer")
-  y_lab = "BPRNACan Cancer"
-  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)
-
-  return(final_plot)
-}
-################################################################################
-
-################################################################################
-# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
-# of a given method/signature.
-# Works inside of ridgeplot_parse. it takes:
-# -  'deconv_data': contains the deconvolution data to index and summarize. 
-#
-# -  'signature dictionary': contains the exact names of the method
-#                           (if it works with one signature) or the signature
-#                           (if it works with multiple methods). 
-#
-# - iterator: string to subscript the signatures_dict with either signature
-#             or methods names depending where is it called
-#
-# - prefix: string to leave just celltype names when substracted to the columns
-#             of deconv_data of the specified method (or method + signature).
-#
-# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"
-
-ridgeplot_parse <- function(deconv_data, signatures_dictionary){
-
-  results <- tibble(Samples = deconv_data$Samples)
-
-  names_table <- deconv_data %>%
-    dplyr::select(-c(Samples)) %>%
-    names() %>%
-    str_split_fixed("_", 2) %>%
-    as_tibble(.name_repair = "unique")
-
-  for (method in unique(names_table[,1,drop=T])){
-
-    if (method %in% c("Epidish",
-                      "DeconRNASeq",
-                      "CBSX")){
-
-      for (signature in names(signatures_dictionary)){ # iterates through all the signatures (the ones not present for the method will yield all 0)
-        to_match <- paste(method, signature, sep = "_")
-
-        for (celltype in names(signatures_dictionary[[signature]])){
-          if (length(signatures_dictionary[[signature]][[celltype]]) > 0){
-            name_of_summary <- paste(to_match, celltype, sep = "_")
-            columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".")
-            # print(name_of_summary)
-            # deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% colnames() %>% print()
-            # cat("-------------------------\n")
-            deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
-          }
-        }
-  }
-    } else{
-
-    to_match <- method
-
-    for (celltype in names(signatures_dictionary[[method]])){
-      if (length(signatures_dictionary[[method]][[celltype]]) > 0){
-          name_of_summary <- paste(to_match, celltype, sep = "_")
-          columns_to_summarize <- paste(to_match, signatures_dictionary[[method]][[celltype]], sep = ".")
-
-          deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
-      }
-    }
-  }
-  }
-  results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
-}
-################################################################################
-
-################################################################################
-plot_ridgeplot <- function(data){
- data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table
-  final_plot <- list()
-  for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
-    # select strings to remove from signature names
-    substring_remove <- c(paste("_",ct, sep=""),
-      "_Tirosh_sigmatrix_SuppFig_3-b",
-      "_scRNA-Seq",
-      "Fig2ab-",
-      "_PBMCs_scRNAseq_sigmatrix",
-      "sigmatrix_",
-      "_Fig2cd")
-
-    # filter correlations
-    deconv_ct_names <- data %>% dplyr::select(matches(ct), -ct) %>% names()
-    cor.table[["r"]][ct,deconv_ct_names] %>% sort() -> cor.ct.sorted
-    names(cor.ct.sorted) <- str_remove_all(names(cor.ct.sorted), paste(substring_remove, collapse = "|"))
-    cor.ct.sorted["H&E"] = 1
-
-    # ridgeplot perse
-    cols <- c("H&E" = "red", "CBSX" = "yellow", "Epidish" = "blue", "Quantiseq" = "pink", "DeconRNASeq" = "green")
-
-    ct_subset = data %>%
-      dplyr::select(matches(ct)) %>%
-      dplyr::rename("H&E" = ct) %>%
-      gather() %>%
-      mutate(key = str_remove_all(key, paste(substring_remove, collapse = "|")),
-             key=factor(key, levels=names(cor.ct.sorted)),
-             method = as.factor(str_extract(key, "[^_]+")))
-  adjust_x <- max(ct_subset$value)
-  final_plot[[ct]] <- print(ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
-    geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
-                         point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
-    theme_ridges() + ggtitle(ct) +
-    annotate("text", x = adjust_x, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
-    scale_x_continuous(limits = c(0, (adjust_x + adjust_x*0.2))) +
-    scale_colour_manual(values = cols) +
-     theme(axis.text.x = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
-          axis.text.y = element_text(color = "black", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
-          axis.title.x = element_text(color = "black", size = 10, angle = 0, hjust = .5, vjust = 0, face = "plain"),
-          axis.title.y = element_text(color = "black", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
-          plot.title = element_text(color = "black", size = 20)) +
-    ylab("") + xlab("% of cell type"))
-  }
-  return(final_plot)
-}
-################################################################################
-
-################################################################################
-wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){
-
-  # build the data
-  true_estimates %>% dplyr::filter(Study == cancer_abreviation) %>%  na.exclude() %>%
-    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))  -> true_subset_
-
-  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
-                                         true_subset_$ParticipantBarcode))
-  true_subset_ %>% 
-    dplyr::filter(ParticipantBarcode %in% Comm_samples) %>% 
-    arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> true_subset
-
-  deconv_data  %>%
-    dplyr::filter(Samples %in% Comm_samples) %>% 
-    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset
-
-  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
-
-  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
-  true_subset %>% bind_cols(deconv_subset_summary) %>% dplyr::select(-c(Samples)) -> data_toplot
-
-  # calculate correlations
- return(plot_ridgeplot(data_toplot))
-}
-################################################################################
-
-################################################################################
-wrapper_corrplots <- function(deconv_data, true_estimates){
+benchmark_corrplots <- function(deconv_data, true_estimates){
   # build the data
@@
   ct_corrplots <- list()
-   for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
-    # select strings to remove from signature names
-    substring_remove <- c(paste0("_",ct),
-      "_Tirosh_sigmatrix_SuppFig_3.b",
-      "_scRNA.Seq",
-      "Fig2ab.",
-      "_PBMCs_scRNAseq_sigmatrix",
-      "sigmatrix_",
-      "_Fig2cd")
 
-    store_corrs <- tibble(measure1 = character(),
-                          measure2 = character(),
-                          r = numeric(),
-                          n = numeric(),
-                          p = numeric(),
-                          sig_p = logical(),
-                          p_if_sig = numeric(),
-                          r_if_sig = numeric())
-    # segregate by cancer type
-    for (st in unique(to_corr$Study)){
+    for (st in unique(celltypes)){
       deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
@@
     rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())
-   }
+
   return(ct_corrplots)
@@
 ```{r}
-read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
-  mutate_at("Samples", str_remove_all, ".01A*") %>%
-  mutate_at("Samples", str_replace_all, "-", ".") %>% 
-  group_by(Samples) %>%
-  summarise_all(mean) -> tcga_deconv
+deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt")
 
-read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
-  mutate_at("Sample_ID", str_remove_all, ".01A*") %>%
-  mutate_at("Sample_ID", str_replace_all, "-", ".") -> Aran_all_facs
-
-read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
-  dplyr::select(-c(...1)) %>%
-  mutate_at("ParticipantBarcode", str_remove_all, ".01A*") %>%
-  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") %>%
-  distinct(ParticipantBarcode, .keep_all= TRUE) -> HE_all_TCGA # for the READ samples TCGA.AG.5 & TCGA.AG.3
+ground_truth <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")
 
@@
 # Figure
-## A) Tumor Purity
-```{r}
-wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = "ABSOLUTE" , cancer_abreviation = "LUAD")
-```
-
 ## B) 3 Celltypes ridge plots
@@
 signature_dict <- list()
-signature_dict[["BPRNACan"]] <- list(Lymphocytes = c("B", "CD4", "CD8", "NK"),
-                    Macrophages = c("Mono", "M0", "M1", "M2"),
-                    Neutrophils = c("Neu"))
+signature_dict[["BPRNACan"]] <- list(B = c("B"),
+                                     CAFs = c(""),
+                                     CD4 = c("CD4"),
+                                     CD8 = c("CD8"),
+                                     Endothelial = c(""),
+                                     Macrophages = c("M0", "M1", "M2"),
+                                     NK = c("NK"),
+                                     Th = c(""),
+                                     Treg = c(""),
+                                     Cancer = c("cancer"),
+                                     Other = c("Mono", "Neu"))
 
@@
 
-signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4","NKT.cells" ,"B.cells", "NK.cells"),
-                                                                         Macrophages = c("Monocytes"),
-                                                                         Neutrophils = c())
+signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
+                                     CAFs = c(""),
+                                     CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c(""),
+                                     Macrophages = c(""),
+                                     NK = c("NK.cells"),
+                                     Th = c(""),
+                                     Treg = c(""),
+                                     Cancer = c(""),
+                                     Other = c("Monocytes","NKT.cells"))
 
-signature_dict[["CBSX_LM22"]] <- list(Lymphocytes = c("B.cells.naive", "B.cells.memory",  "T.cells.CD8",
-                                                        "T.cells.CD4.naive", "T.cells.CD4.memory.resting",
-                                                        "T.cells.CD4.memory.activated", 
-                                                        "T.cells.regulatory..Tregs.", "NK.cells.resting",
-                                                        "NK.cells.activated"),
-                                        Macrophages = c("Monocytes", "Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
-                                        Neutrophils = c("Neutrophils")) # skipped , "Plasma.cells" "T.cells.follicular.helper", "T.cells.gamma.delta" in Lymphos, as well as "Dendritic.cells.resting", "Dendritic.cells.activated" for macros
+signature_dict[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
+                                     CAFs = c(""),
+                                     CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c(""),
+                                     Macrophages = c("Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
+                                     NK = c("NK.cells.resting", "NK.cells.activated"),
+                                     Th = c("T.cells.follicular.helper", "T.cells.gamma.delta"),
+                                     Treg = c("T.cells.regulatory..Tregs."),
+                                     Cancer = c(""),
+                                     Other = c("Monocytes", "Dendritic.cells.resting", "Dendritic.cells.activated", "Mast.cells.resting", "Mast.cells.activated", "Eosinophils", "Neutrophils"))
 
-signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4",
-                                                                                                   "NK.cells", "B.cells"),
+signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
+                                     CAFs = c("CAF"),
+                                     CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c("Endothelial.cells"),
                                      Macrophages = c("Macrophages"),
-                                                                                   Neutrophils = c())
+                                     NK = c("NK.cells"),
+                                     Th = c(""),
+                                     Treg = c(""),
+                                     Cancer = c("Malignant"),
+                                     Other = c(""))
 
-signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells"),
-                                                          Macrophages = c("Macrophages", "Dendritic.cells"),
-                                                          Neutrophils = c())
+signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
+                                     CAFs = c("CAFs"),
+                                     CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c("Endothelial.cells"),
+                                     Macrophages = c("Macrophages"),
+                                     NK = c(""),
+                                     Th = c(""),
+                                     Treg = c(""),
+                                     Cancer = c("Malignant.cells"),
+                                     Other = c("Dendritic.cells", "Mast.cells", "Myocytes"))
 
-signature_dict[["CCLE_TIL10"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells", "NK.cells", "Tregs"),
-                    Macrophages = c("Macrophages.M1", "Macrophages.M2", "Monocytes", "Dendritic.cells"),
-                    Neutrophils = c("Neutrophils"))
+signature_dict[["Quantiseq"]] <- list(B = c("B.cell"),
+                                     CAFs = c(""),
+                                     CD4 = c("T.cell.CD4+.(non-regulatory)"),
+                                     CD8 = c("T.cell.CD8+"),
+                                     Endothelial = c(""),
+                                     Macrophages = c("Macrophage.M1", "Macrophage.M2"),
+                                     NK = c("NK.cell"),
+                                     Th = c(""),
+                                     Treg = c("T.cell.regulatory(Tregs)"),
+                                     Cancer = c(""),
+                                     Other = c("Monocyte", "Neutrophil", "Myeloid.dendritic.cell", "uncharacterized.cell"))
 
-signature_dict[["Quantiseq"]] <- list(Lymphocytes = c("B.cell", "T.cell.CD4+.(non-regulatory)", "T.cell.CD8+", "T.cell.regulatory(Tregs)", "NK.cell"),
-                    Macrophages = c("Macrophage.M1", "Macrophage.M2", "Myeloid.dendritic.cell", "Monocyte"),
-                    Neutrophils = c("Neutrophil"))
+# signature_dict[["CCLE_TIL10"]] <- list(B = c("B"),
+#                                      CAFs = c(""),
+#                                      CD4 = c(""),
+#                                      CD8 = c(""),
+#                                      Endothelial = c(""),
+#                                      Macrophages = c(""),
+#                                      NK = c(""),
+#                                      Th = c(""),
+#                                      Treg = c(""),
+#                                      Cancer = c(""),
+#                                      Other = c(""))
 
-# signature_dict[["MCP"]] <- list(Lymphocytes = c("T.cells", "CD8.T.cells", "Cytotoxic.lymphocytes","B.lineage" ,"NK.cells"),
-#                     Macrophages = c("Myeloid.dendritic.cells", "Monocytic.lineage"),
-#                     Neutrophils = c("Neutrophils")) # Based in enrichment so cant sum celltype estimates
-
-# signature_dict[["XCELL"]] <- list(Lymphocytes = c(".B-cells", "CD4+.", "CD8+.", "CLP", "NK.", "Th1_cells", "Tgd_cells", "Th2_cells", "Tregs"),
-#                     Macrophages = c("aDC", "cDC", "iDC", "pDC", "DC", "Macrophages.", "Monocytes"),
-#                     Neutrophils = c("Neutrophils")) # Not in the paper in theory
+# signature_dict[[""]] <- list(B = c(""),
+#                                      CAFs = c(""),
+#                                      CD4 = c(""),
+#                                      CD8 = c(""),
+#                                      Endothelial = c(""),
+#                                      Macrophages = c(""),
+#                                      NK = c(""),
+#                                      Th = c(""),
+#                                      Treg = c(""),
+#                                      Cancer = c(""),
+#                                      Other = c(""))
 
 ```
-
-### Data processing & ridge plot
-
-```{r}
-
-tcga_deconv %>%
-  rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
-  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) -> tcga_deconv_ridge
-
-wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = "LUAD")
-```
-
 ## Summary Corrplot
@@
 ```{r}
-corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
+corrplots <- benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth)
 corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
@@
 ```
-
-# Suplementary figure
-```{r}
-ridgeplots_by_cancer <- list()
-tpurity_by_cancer <- list()
-blank  <- ggplot() + theme_void()
-
-for (cancer in unique(HE_all_TCGA$Study)){
-  ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
-  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, estimate = "ABSOLUTE", cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
-        },
-        error = function(cond) {
-          message(paste("not enough FACs samples for ", cancer, "no scatterplot will be generated"))
-          return(list(ccle = blank, bprna = blank))
-        }
-  )
-  tpurity_by_cancer[[cancer]]$extra = blank
-
-  ridges <- ggarrange(plotlist = ridgeplots_by_cancer[[cancer]], ncol = 3, common.legend = T, legend = "bottom")
-  scater <- ggarrange(plotlist = tpurity_by_cancer[[cancer]], ncol = 3, common.legend = T)
-  blank  <- ggplot() + theme_void()
-  fullplot <- ggarrange(plotlist = list(scater, ridges, blank), nrow = 3, heights = c(0.15, 0.3, 0.45))
-  annotate_figure(fullplot, top = text_grob(cancer, color = "black", size = 40))
-  pdf_name <- paste("Sup.fig2_", cancer, ".pdf", sep = "")
-  ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2.5)
-}
-system("pdfunite Sup.fig2_*.pdf Sup.fig2.pdf")
-```

### 2022-06-27 Figures/Figures_nonTCGA.Rmd
Fix corrplot for GSE72056

@@
 ---
-title: "Figure 2 and figure 2 supplementary material"
+title: "Figure Extra"
 output:
@@
 ################################################################################
-benchmark_corrplots <- function(deconv_data, true_estimates){
+# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
+# of a given method/signature.
+# Works inside of ridgeplot_parse. it takes:
+# -  'deconv_data': contains the deconvolution data to index and summarize. 
+#
+# -  'signature dictionary': contains the exact names of the method
+#                           (if it works with one signature) or the signature
+#                           (if it works with multiple methods). 
+#
+# - iterator: string to subscript the signatures_dict with either signature
+#             or methods names depending where is it called
+#
+# - prefix: string to leave just celltype names when substracted to the columns
+#             of deconv_data of the specified method (or method + signature).
+#
+# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"
+
+ridgeplot_parse <- function(deconv_data, signatures_dictionary, key){
+
+    results <- tibble(Samples = deconv_data[[key]])
+
+    names_table <- deconv_data %>%
+      dplyr::select(-any_of(key)) %>%
+      names() %>%
+      str_split_fixed("_", 2) %>%
+      as_tibble(.name_repair = "unique")
+
+    for (method in unique(names_table[,1,drop=T])){
+
+      if (method %in% c("Epidish",
+                        "DeconRNASeq",
+                        "CBSX")){
+
+        for (signature in names(signatures_dictionary)){ # iterates through all the signatures (the ones not present for the method will yield all 0)
+          to_match <- paste(method, signature, sep = "_")
+
+          for (celltype in names(signatures_dictionary[[signature]])){
+            if (length(signatures_dictionary[[signature]][[celltype]]) > 0){
+              name_of_summary <- paste(to_match, celltype, sep = "_")
+              columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".")
+
+              print(paste0("Truth: ", name_of_summary))
+              deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% colnames() %>% paste0("Est: ",.) %>% print()
+              cat("-------------------------\n")
+              deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
+            }
+          }
+    }
+      } else{
+
+      to_match <- method
+
+      for (celltype in names(signatures_dictionary[[method]])){
+        if (length(signatures_dictionary[[method]][[celltype]]) > 0){
+            name_of_summary <- paste(to_match, celltype, sep = "_")
+            columns_to_summarize <- paste(to_match, signatures_dictionary[[method]][[celltype]], sep = ".")
+
+            deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
+        }
+      }
+    }
+    }
+    results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
+}
+################################################################################
+
+################################################################################
+benchmark_corrplots <- function(deconv_data, true_estimates, key, title){
   # build the data
   true_subset_ <- true_estimates %>%  na.exclude() %>%
-    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))
+    arrange(factor(get(key), levels = get(key)))
 
-  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
-                                         true_subset_$ParticipantBarcode))
+  common <- Reduce(intersect, list(deconv_data[[key]],
+                   true_subset_[[key]]))
 
-  true_subset <-dplyr::filter(true_subset_, ParticipantBarcode %in% Comm_samples) %>% 
-    arrange(factor(ParticipantBarcode, levels = Comm_samples))
+  true_subset <- dplyr::filter(true_subset_, get(key) %in% common) %>% 
+    arrange(factor(get(key), levels = common))
 
-  deconv_subset <- dplyr::filter(deconv_data, Samples %in% Comm_samples) %>% 
-    arrange(factor(Samples, levels = Comm_samples))
+  deconv_subset <- dplyr::filter(deconv_data, get(key) %in% common) %>% 
+    arrange(factor(get(key), levels = common))
 
-  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)
-  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
+  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict, key = key)
+  identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()
 
-  to_corr <- bind_cols(true_subset, deconv_subset_summary) %>% dplyr::select(-c(Samples))
+  to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
   ct_corrplots <- list()
+  store_corrs <- tibble(measure1 = character(),
+                          measure2 = character(),
+                          r = numeric(),
+                          n = numeric(),
+                          p = numeric(),
+                          sig_p = logical(),
+                          p_if_sig = numeric(),
+                          r_if_sig = numeric())
 
-    for (st in unique(celltypes)){
-      deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
+    for (ct in unique(dplyr::select(true_estimates, -any_of(key)) %>% names())){
+
+      substring_remove <- c(paste0("_",ct,"$"),
+      "_Tirosh_sigmatrix_SuppFig_3.b",
+      "_scRNA.Seq",
+      "Fig2ab.",
+      "_PBMCs_scRNAseq_sigmatrix",
+      "sigmatrix_",
+      "_Fig2cd")
+
+      deconv_ct_names <- to_corr %>%
         # segregate by ct
-        dplyr::select(matches(ct)) %>%
+        dplyr::select(matches(paste0(ct, "$"))) %>%
         formatted_cors(cor.stat = "pearson") %>%
@@
         # rename ground truth as cancer type
-        dplyr::mutate(measure1 = st)
+        dplyr::mutate(measure2 = str_remove_all(measure2,  paste(substring_remove, collapse = "|")))
       #add to the rest of cancer type correlations
@@
     # Plot
-    store_corrs <- dplyr::mutate(store_corrs, measure2=stringr::str_remove_all(measure2, paste(substring_remove, collapse = "|")))
 
     order <- store_corrs %>% 
-      drop_na(r) %>% # Epidish_CBSX_LM22 dont work for UVM in Neutrophils and mean dont work with NANs
+      drop_na(r) %>% 
       group_by(measure2) %>%
@@
     ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
-    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
+    ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
     geom_tile() +
-      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
+      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, 
          subtitle="Only significant correlation coefficients shown (95% I.C.)") +
@@
     theme_classic() +
-    scale_x_discrete(expand=c(0,0)) +
+    scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
     scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
-    rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())
+    rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown())
 
@@
 
-# Data loading
-
+# GSE72056
+## Data loading
 ```{r}
-deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt")
+deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
+fix naming of deconv results
 
@@
 
-# Figure
-## B) 3 Celltypes ridge plots
-### Create aggregation dictionaries to compare with Lymphocites, Macrophages and Neutrophils FACs
+## Signature Dictionary construction
 
@@
 signature_dict[["BPRNACan"]] <- list(B = c("B"),
-                                     CAFs = c(""),
+                                     CAFs = c(),
                                      CD4 = c("CD4"),
                                      CD8 = c("CD8"),
-                                     Endothelial = c(""),
+                                     Endothelial = c(),
                                      Macrophages = c("M0", "M1", "M2"),
                                      NK = c("NK"),
-                                     Th = c(""),
-                                     Treg = c(""),
+                                     Th = c(),
+                                     Treg = c(),
                                      Cancer = c("cancer"),
@@
 signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
-                                     CAFs = c(""),
+                                     CAFs = c(),
                                      CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
-                                     Endothelial = c(""),
-                                     Macrophages = c(""),
+                                     Endothelial = c(),
+                                     Macrophages = c(),
                                      NK = c("NK.cells"),
-                                     Th = c(""),
-                                     Treg = c(""),
-                                     Cancer = c(""),
+                                     Th = c(),
+                                     Treg = c(),
+                                     Cancer = c(),
                                      Other = c("Monocytes","NKT.cells"))
@@
 signature_dict[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
-                                     CAFs = c(""),
+                                     CAFs = c(),
                                      CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"),
                                      CD8 = c("T.cells.CD8"),
-                                     Endothelial = c(""),
+                                     Endothelial = c(),
                                      Macrophages = c("Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
@@
                                      Treg = c("T.cells.regulatory..Tregs."),
-                                     Cancer = c(""),
+                                     Cancer = c(),
                                      Other = c("Monocytes", "Dendritic.cells.resting", "Dendritic.cells.activated", "Mast.cells.resting", "Mast.cells.activated", "Eosinophils", "Neutrophils"))
@@
                                      NK = c("NK.cells"),
-                                     Th = c(""),
-                                     Treg = c(""),
+                                     Th = c(),
+                                     Treg = c(),
                                      Cancer = c("Malignant"),
-                                     Other = c(""))
+                                     Other = c())
 
@@
                                      Macrophages = c("Macrophages"),
-                                     NK = c(""),
-                                     Th = c(""),
-                                     Treg = c(""),
+                                     NK = c(),
+                                     Th = c(),
+                                     Treg = c(),
                                      Cancer = c("Malignant.cells"),
@@
 signature_dict[["Quantiseq"]] <- list(B = c("B.cell"),
-                                     CAFs = c(""),
+                                     CAFs = c(),
                                      CD4 = c("T.cell.CD4+.(non-regulatory)"),
                                      CD8 = c("T.cell.CD8+"),
-                                     Endothelial = c(""),
+                                     Endothelial = c(),
                                      Macrophages = c("Macrophage.M1", "Macrophage.M2"),
                                      NK = c("NK.cell"),
-                                     Th = c(""),
+                                     Th = c(),
                                      Treg = c("T.cell.regulatory(Tregs)"),
-                                     Cancer = c(""),
+                                     Cancer = c(),
                                      Other = c("Monocyte", "Neutrophil", "Myeloid.dendritic.cell", "uncharacterized.cell"))
 
-# signature_dict[["CCLE_TIL10"]] <- list(B = c("B"),
-#                                      CAFs = c(""),
-#                                      CD4 = c(""),
-#                                      CD8 = c(""),
-#                                      Endothelial = c(""),
-#                                      Macrophages = c(""),
-#                                      NK = c(""),
-#                                      Th = c(""),
-#                                      Treg = c(""),
-#                                      Cancer = c(""),
-#                                      Other = c(""))
+# signature_dict[["CCLE_TIL10"]] <- list(B = c(),
+#                                      CAFs = c(),
+#                                      CD4 = c(),
+#                                      CD8 = c(),
+#                                      Endothelial = c(),
+#                                      Macrophages = c(),
+#                                      NK = c(),
+#                                      Th = c(),
+#                                      Treg = c(),
+#                                      Cancer = c(),
+#                                      Other = c())
 
-# signature_dict[[""]] <- list(B = c(""),
-#                                      CAFs = c(""),
-#                                      CD4 = c(""),
-#                                      CD8 = c(""),
-#                                      Endothelial = c(""),
-#                                      Macrophages = c(""),
-#                                      NK = c(""),
-#                                      Th = c(""),
-#                                      Treg = c(""),
-#                                      Cancer = c(""),
-#                                      Other = c(""))
+# signature_dict[[""]] <- list(B = c(),
+#                                      CAFs = c(),
+#                                      CD4 = c(),
+#                                      CD8 = c(),
+#                                      Endothelial = c(),
+#                                      Macrophages = c(),
+#                                      NK = c(),
+#                                      Th = c(),
+#                                      Treg = c(),
+#                                      Cancer = c(),
+#                                      Other = c())
 
 ```
-## Summary Corrplot
+## Corrplot
 
 ```{r}
-corrplots <- benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth)
-corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
-corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
-summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
-
-ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
+benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth,  key = "Samples", title = "GSE72056")
+# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
+# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
+# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
+# 
+# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
 ```

### 2022-07-15 Figures/Figures_nonTCGA.Rmd
add Thomas benchmark

@@
 ################################################################################
-benchmark_corrplots <- function(deconv_data, true_estimates, key, title){
+benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
   # build the data
@@
 
-  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict, key = key)
+  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = dict, key = key)
   identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()
@@
 ```{r}
-deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
+deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
 fix naming of deconv results
 
-ground_truth <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")
+truth_GSE72056 <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")
 
@@
 ## non matching signatures/methods (all 0) are removed.
-signature_dict <- list()
-signature_dict[["BPRNACan"]] <- list(B = c("B"),
+dict_GSE72056 <- list()
+dict_GSE72056[["BPRNACan"]] <- list(B = c("B"),
                                      CAFs = c(),
@@
 
-signature_dict[["BPRNACanProMet"]] <- signature_dict[["BPRNACan"]]
-signature_dict[["BPRNACan3DProMet"]] <- signature_dict[["BPRNACan"]]
+dict_GSE72056[["BPRNACanProMet"]] <- dict_GSE72056[["BPRNACan"]]
+dict_GSE72056[["BPRNACan3DProMet"]] <- dict_GSE72056[["BPRNACan"]]
 
-signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
+dict_GSE72056[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
                                      CAFs = c(),
@@
 
-signature_dict[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
+dict_GSE72056[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
                                      CAFs = c(),
@@
 
-signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
+dict_GSE72056[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
                                      CAFs = c("CAF"),
@@
 
-signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
+dict_GSE72056[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
                                      CAFs = c("CAFs"),
@@
 
-signature_dict[["Quantiseq"]] <- list(B = c("B.cell"),
+dict_GSE72056[["Quantiseq"]] <- list(B = c("B.cell"),
                                      CAFs = c(),
@@
 
-# signature_dict[["CCLE_TIL10"]] <- list(B = c(),
+# dict_GSE72056[["CCLE_TIL10"]] <- list(B = c(),
 #                                      CAFs = c(),
@@
 
-# signature_dict[[""]] <- list(B = c(),
+# dict_GSE72056[[""]] <- list(B = c(),
 #                                      CAFs = c(),
@@
 ```{r}
-benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth,  key = "Samples", title = "GSE72056")
+benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
 # corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
@@
 ```
+
+# Thomas RNAseq #! Change name!
+## Data loading
+```{r}
+deconv_Thomas <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
+  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
+  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results
+
+load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
+truth_Thomas <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))
+
+```
+
+## Signature Dictionary construction
+
+```{r}
+# Lists of celltypes of each signature
+## signature dictionary construction (can use . as regexp!)
+## uncoment print of functions to check that you detect what you want.
+## non matching signatures/methods (all 0) are removed.
+dict_Thomas <- list()
+dict_Thomas[["BPRNACan"]] <- list(CD4 = c("CD4"),
+                                     CD8 = c("CD8"),
+                                     NK = c("NK"))
+
+dict_Thomas[["BPRNACanProMet"]] <- dict_Thomas[["BPRNACan"]]
+dict_Thomas[["BPRNACan3DProMet"]] <- dict_Thomas[["BPRNACan"]]
+
+dict_Thomas[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     NK = c("NK.cells"), #"NKT.cells"?
+                                     )
+
+dict_Thomas[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
+                                     CD8 = c("T.cells.CD8"),
+                                     NK = c("NK.cells.resting", "NK.cells.activated"))
+
+dict_Thomas[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     NK = c("NK.cells"))
+
+dict_Thomas[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     NK = c())
+
+dict_Thomas[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
+                                   CD8 = c("T.cell.CD8+"),
+                                   NK = c("NK.cell"))
+
+```
+## Corrplot
+
+```{r}
+benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas,  key = "Samples", title = "Thomas")
+# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
+# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
+# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
+# 
+# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
+```

### 2022-07-15 Figures/Figure2.Rmd
new deconvolution result location

@@
 ```{r}
-read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
+read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/data/deconvolution_for_gemdecan/all_deconvolutions_all_TCGA.txt") %>%
   mutate_at("Samples", str_remove_all, ".01A*") %>%

### 2022-07-15 Figures/Figures_nonTCGA.Rmd
new deconvolution result location

@@
 ```{r}
-deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
+deconv_GSE72056 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
 fix naming of deconv results
@@
 ```{r}
-deconv_Thomas <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
+deconv_Thomas <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
   dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%

### 2022-09-05 Figures/Figures_nonTCGA.Rmd
add TIL10 and CCLE_TIL10 signatures to Non TCGA
validated by hand

@@
 ```{r}
-deconv_GSE72056 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
+deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_not_metastatic.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #!
 fix naming of deconv results
@@
 ## non matching signatures/methods (all 0) are removed.
+## validated by jacobo 05/09/2022
+
 dict_GSE72056 <- list()
@@
 
-# dict_GSE72056[["CCLE_TIL10"]] <- list(B = c(),
-#                                      CAFs = c(),
-#                                      CD4 = c(),
-#                                      CD8 = c(),
-#                                      Endothelial = c(),
-#                                      Macrophages = c(),
-#                                      NK = c(),
-#                                      Th = c(),
-#                                      Treg = c(),
-#                                      Cancer = c(),
-#                                      Other = c())
+dict_GSE72056[["TIL10"]] <- list(B = c("B.cells"),
+                                     CAFs = c(),
+                                     CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c(),
+                                     Macrophages = c("Macrophages.M1", "Macrophages.M2"),
+                                     NK = c("NK.cells"),
+                                     Th = c(),
+                                     Treg = c("Tregs"),
+                                     Cancer = c(),
+                                     Other = c("Monocytes", "Neutrophils", "Dendritic.cells"))
+
+dict_GSE72056[["CCLE_TIL10"]] <- list(B = c("B.cells"),
+                                     CAFs = c(),
+                                     CD4 = c("T.cells.CD4"),
+                                     CD8 = c("T.cells.CD8"),
+                                     Endothelial = c(),
+                                     Macrophages = c("Macrophages.M1", "Macrophages.M2"),
+                                     NK = c("NK.cells"),
+                                     Th = c(),
+                                     Treg = c("Tregs"),
+                                     Cancer = c("Cancer.cells"), #the only diff respect Til10
+                                     Other = c("Monocytes", "Neutrophils", "Dendritic.cells"))
+
+dict_GSE72056[["CD226"]] <- list(B = c("B"),
+                                     CAFs = c(),
+                                     CD4 = c("CD4"),
+                                     CD8 = c("CD8"),
+                                     Endothelial = c(),
+                                     Macrophages = c("M1", "M2"),
+                                     NK = c("NK"),
+                                     Th = c(),
+                                     Treg = c(),
+                                     Cancer = c(),
+                                     Other = c("Mono", "Neu"))
 

### 2022-09-08 Figures/Figures_nonTCGA.Rmd
Spliting corrplot fuction

@@
 library(ggtext)
+library(reshape2)
 library(glue)
@@
 ################################################################################
+```
+
+```{r}
 benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
@@
 }
+```
 
+```{r}
 ```
@@
 
-dict_GSE72056[["CD226"]] <- list(B = c("B"),
-                                     CAFs = c(),
-                                     CD4 = c("CD4"),
-                                     CD8 = c("CD8"),
-                                     Endothelial = c(),
-                                     Macrophages = c("M1", "M2"),
-                                     NK = c("NK"),
-                                     Th = c(),
-                                     Treg = c(),
-                                     Cancer = c(),
-                                     Other = c("Mono", "Neu"))
+# dict_GSE72056[["CD226"]] <- list(B = c("B"),
+#                                      CAFs = c(),
+#                                      CD4 = c("CD4"),
+#                                      CD8 = c("CD8"),
+#                                      Endothelial = c(),
+#                                      Macrophages = c("M1", "M2"),
+#                                      NK = c("NK"),
+#                                      Th = c(),
+#                                      Treg = c(),
+#                                      Cancer = c(),
+#                                      Other = c("Mono", "Neu"))
 
@@
 ## Corrplot
+```{r}
+corr <- benchmark_corr(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples")
+p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "GSE72056")
+p
 
+```
+
+## Test without function
 ```{r}
-benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
-# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
-# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
-# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
-# 
-# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
+
+deconv_data = deconv_GSE72056
+true_estimates = truth_GSE72056
+dict = dict_GSE72056
+key = "Samples"
+title = "GSE72056"
+
+# build the data
+true_subset_ <- true_estimates %>%  na.exclude() %>%
+  arrange(factor(get(key), levels = get(key)))
+
+common <- Reduce(intersect, list(deconv_data[[key]],
+                 true_subset_[[key]]))
+
+true_subset <- dplyr::filter(true_subset_, get(key) %in% common) %>% 
+  arrange(factor(get(key), levels = common))
+
+deconv_subset <- dplyr::filter(deconv_data, get(key) %in% common) %>% 
+  arrange(factor(get(key), levels = common))
+
+deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = dict, key = key)
+identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()
+
+to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
+ct_corrplots <- list()
+store_corrs <- tibble(measure1 = character(),
+                        measure2 = character(),
+                        r = numeric(),
+                        n = numeric(),
+                        p = numeric(),
+                        sig_p = logical(),
+                        p_if_sig = numeric(),
+                        r_if_sig = numeric())
+
+for (ct in unique(dplyr::select(true_estimates, -any_of(key)) %>% names())){
+
+    substring_remove <- c(paste0("_",ct,"$"),
+    "_Tirosh_sigmatrix_SuppFig_3.b",
+    "_scRNA.Seq",
+    "Fig2ab.",
+    "_PBMCs_scRNAseq_sigmatrix",
+    "sigmatrix_",
+    "_Fig2cd")
+
+    deconv_ct_names <- to_corr %>%
+      # segregate by ct
+      dplyr::select(matches(paste0(ct, "$"))) %>%
+      formatted_cors(cor.stat = "pearson") %>%
+      # reduce to corrs just to ground truth
+      dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
+      # rename ground truth as cancer type
+      dplyr::mutate(measure2 = str_remove_all(measure2,  paste(substring_remove, collapse = "|")))
+    #add to the rest of cancer type correlations
+    store_corrs <- add_row(store_corrs , deconv_ct_names)
+  }
+
+  # Plot
+
+  order <- store_corrs %>% 
+    drop_na(r) %>% 
+    group_by(measure2) %>%
+    dplyr::summarize(r = mean(r)) %>% 
+    arrange(desc(r)) %>% 
+    mutate(measure1 = "Average",
+           p = NA,
+           sig_p = TRUE,
+           p_if_sig = NA,
+           r_if_sig = r ) %>%
+    dplyr::relocate(measure1, .before = measure2)
+
+  corr_df <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2))
+  write.csv( corr_df, paste0('Spearmans_Correlation_',title,'.csv') )
+  corr_df %>% ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
+              geom_tile() +
+              labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
+              scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
+              geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
+              scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
+              scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) 
+  # order columns by number of NA (push empty columns to the right)
+corr_matrix <- corr_df %>%
+    dcast(measure2~measure1, value.var = "r") 
+corr_matrix_sorted <- corr_matrix[order(rowSums(is.na(corr_matrix))), ]
+corr_matrix_sorted2 <- corr_matrix_sorted[,order(colSums(is.na(corr_matrix_sorted))) ]
+
+melt(data = corr_matrix_sorted2) %>% ggplot(aes(measure2, variable, fill=value, label=round(value,2))) +
+            geom_tile() + 
+            labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
+            scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1), na.value = 'white') +
+            geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
+            scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
+            scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red"))
+
+corr_matrix_sorted2
+
 ```
@@
 ```{r}
-benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas,  key = "Samples", title = "Thomas")
+
+corr <- benchmark_corr(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_GSE72056, key = "Samples")
+p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "Thomas")
+p
 # corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")

### 2023-07-24 Figures/Figure2.Rmd
minor fix dplyr Figure2.Rmd

@@
     map(~rownames_to_column(.x, var="measure1")) %>%
-    map(~pivot_longer(.x, -measure1, "measure2")) %>%
+    map(~pivot_longer(.x, -measure1, names_to = "measure2")) %>%
     bind_rows(.id = "id") %>%

### 2023-07-24 Figures/Figure4.Rmd
minor fix dplyr Figure4.Rmd

@@
 prepare_table <- function(correlations, pvalues) {
-  correlations %<>% select(...1, order(.[9, -1], decreasing = T))
-  pvalues %<>% dplyr::select(colnames(correlations))
+  order <- pivot_longer(correlations, -`...1`) %>%
+    dplyr::filter(`...1` == "Mean") %>%
+    dplyr::arrange(desc(value)) %>%
+    .$name
+
+    correlations %<>% dplyr::select(...1, all_of(order))
+    pvalues %<>% dplyr::select(...1, all_of(order))
 

### 2023-07-24 Figures/Figures_nonTCGA.Rmd
minor fixes dplyr Figures_nonTCGA.Rmd

@@
 library(glue)
+library(ggpubr)
 ```
@@
 ```{r}
-corr <- benchmark_corr(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples")
-p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "GSE72056")
-p
-
+corr <- benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
+corr
 ```

### 2023-07-31 Figures/Figures_nonTCGA.Rmd
clean and fix Thomas RNAseq part Figures_nonTCGA.Rmd

@@
 
-## Test without function
-```{r}
-
-deconv_data = deconv_GSE72056
-true_estimates = truth_GSE72056
-dict = dict_GSE72056
-key = "Samples"
-title = "GSE72056"
-
-# build the data
-true_subset_ <- true_estimates %>%  na.exclude() %>%
-  arrange(factor(get(key), levels = get(key)))
-
-common <- Reduce(intersect, list(deconv_data[[key]],
-                 true_subset_[[key]]))
-
-true_subset <- dplyr::filter(true_subset_, get(key) %in% common) %>% 
-  arrange(factor(get(key), levels = common))
-
-deconv_subset <- dplyr::filter(deconv_data, get(key) %in% common) %>% 
-  arrange(factor(get(key), levels = common))
-
-deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = dict, key = key)
-identical(true_subset[[key]], deconv_subset_summary[[key]]) %>% stopifnot()
-
-to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
-ct_corrplots <- list()
-store_corrs <- tibble(measure1 = character(),
-                        measure2 = character(),
-                        r = numeric(),
-                        n = numeric(),
-                        p = numeric(),
-                        sig_p = logical(),
-                        p_if_sig = numeric(),
-                        r_if_sig = numeric())
-
-for (ct in unique(dplyr::select(true_estimates, -any_of(key)) %>% names())){
-
-    substring_remove <- c(paste0("_",ct,"$"),
-    "_Tirosh_sigmatrix_SuppFig_3.b",
-    "_scRNA.Seq",
-    "Fig2ab.",
-    "_PBMCs_scRNAseq_sigmatrix",
-    "sigmatrix_",
-    "_Fig2cd")
-
-    deconv_ct_names <- to_corr %>%
-      # segregate by ct
-      dplyr::select(matches(paste0(ct, "$"))) %>%
-      formatted_cors(cor.stat = "pearson") %>%
-      # reduce to corrs just to ground truth
-      dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
-      # rename ground truth as cancer type
-      dplyr::mutate(measure2 = str_remove_all(measure2,  paste(substring_remove, collapse = "|")))
-    #add to the rest of cancer type correlations
-    store_corrs <- add_row(store_corrs , deconv_ct_names)
-  }
-
-  # Plot
-
-  order <- store_corrs %>% 
-    drop_na(r) %>% 
-    group_by(measure2) %>%
-    dplyr::summarize(r = mean(r)) %>% 
-    arrange(desc(r)) %>% 
-    mutate(measure1 = "Average",
-           p = NA,
-           sig_p = TRUE,
-           p_if_sig = NA,
-           r_if_sig = r ) %>%
-    dplyr::relocate(measure1, .before = measure2)
-
-  corr_df <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2))
-  write.csv( corr_df, paste0('Spearmans_Correlation_',title,'.csv') )
-  corr_df %>% ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
-              geom_tile() +
-              labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
-              scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
-              geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
-              scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
-              scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) 
-  # order columns by number of NA (push empty columns to the right)
-corr_matrix <- corr_df %>%
-    dcast(measure2~measure1, value.var = "r") 
-corr_matrix_sorted <- corr_matrix[order(rowSums(is.na(corr_matrix))), ]
-corr_matrix_sorted2 <- corr_matrix_sorted[,order(colSums(is.na(corr_matrix_sorted))) ]
-
-melt(data = corr_matrix_sorted2) %>% ggplot(aes(measure2, variable, fill=value, label=round(value,2))) +
-            geom_tile() + 
-            labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
-            scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1), na.value = 'white') +
-            geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
-            scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
-            scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red"))
-
-corr_matrix_sorted2
-
-```
-
 # Thomas RNAseq #! Change name!
@@
                                      CD8 = c("T.cells.CD8"),
-                                     NK = c("NK.cells"), #"NKT.cells"?
+                                     NK = c("NK.cells") #"NKT.cells"?
                                      )
@@
                                      CD8 = c("T.cells.CD8"),
-                                     NK = c())
+                                     NK = NULL)
 
@@
 
-corr <- benchmark_corr(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_GSE72056, key = "Samples")
-p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "Thomas")
-p
-# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
-# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
-# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
-# 
-# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
+corr <- benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas, key = "Samples", title = "test")
+corr
 ```

### 2023-07-31 Figures/Figures_nonTCGA.Rmd
change naming script from Thomas RNAseq to Nakamura2018

@@
 
-# Thomas RNAseq #! Change name!
+# Nakamura2018 RNAseq #! Change name!
 ## Data loading
 ```{r}
-deconv_Thomas <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
+deconv_Nakamura2018 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
   dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
@@
 load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
-truth_Thomas <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))
+truth_Nakamura2018 <- as_tibble(FACS_Nakamura2018_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))
 
@@
 ## non matching signatures/methods (all 0) are removed.
-dict_Thomas <- list()
-dict_Thomas[["BPRNACan"]] <- list(CD4 = c("CD4"),
+dict_Nakamura2018 <- list()
+dict_Nakamura2018[["BPRNACan"]] <- list(CD4 = c("CD4"),
                                      CD8 = c("CD8"),
@@
 
-dict_Thomas[["BPRNACanProMet"]] <- dict_Thomas[["BPRNACan"]]
-dict_Thomas[["BPRNACan3DProMet"]] <- dict_Thomas[["BPRNACan"]]
+dict_Nakamura2018[["BPRNACanProMet"]] <- dict_Nakamura2018[["BPRNACan"]]
+dict_Nakamura2018[["BPRNACan3DProMet"]] <- dict_Nakamura2018[["BPRNACan"]]
 
-dict_Thomas[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
+dict_Nakamura2018[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
@@
 
-dict_Thomas[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
+dict_Nakamura2018[["CBSX_LM22"]] <- list(CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"), # "T.cells.follicular.helper", "T.cells.gamma.delta", "T.cells.regulatory..Tregs."?
                                      CD8 = c("T.cells.CD8"),
@@
 
-dict_Thomas[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
+dict_Nakamura2018[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
@@
 
-dict_Thomas[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
+dict_Nakamura2018[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(CD4 = c("T.cells.CD4"),
                                      CD8 = c("T.cells.CD8"),
@@
 
-dict_Thomas[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
+dict_Nakamura2018[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
                                    CD8 = c("T.cell.CD8+"),
@@
 
-corr <- benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas, key = "Samples", title = "test")
+corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "test")
 corr

### 2023-07-31 Figures/Figures_nonTCGA.Rmd
corrrect change of name Figures_nonTCGA.Rmd

@@
 load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
-truth_Nakamura2018 <- as_tibble(FACS_Nakamura2018_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))
+truth_Nakamura2018 <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))
 
@@
 
-corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "test")
+corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "Nakamura et al. 2018")
 corr

### 2023-12-14 Figures/Figures_nonTCGA.Rmd
add Vanderbilt + try fix bug parse
given the complex naming of this cohort ground truth I have some
problems when cleaning the correlation table.

I try and fix this by changing processing of ground truth and add some
comments for ease of ussage

@@
 
+  # Create a tibble to store equivalences
     results <- tibble(Samples = deconv_data[[key]])
@@
 
+    # Iterate throughout methods and their signatures, saving with standard notation
     for (method in unique(names_table[,1,drop=T])){
@@
             if (length(signatures_dictionary[[signature]][[celltype]]) > 0){
-              name_of_summary <- paste(to_match, celltype, sep = "_")
-              columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".")
+              name_of_summary <- paste(to_match, celltype, sep = "_") # New name
+              columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".") # Columns to sum of the deconv to have the new name
 
@@
     }
+    # remove empty signatures
     results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
@@
 benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
-  # build the data
+  # build the data to parse all the estimations to ground truth
   true_subset_ <- true_estimates %>%  na.exclude() %>%
-    arrange(factor(get(key), levels = get(key)))
+    arrange(factor(get(key), levels = get(key))) %>%
+    dplyr:::rename_with(~str_replace(.,"_", ".")) %>%
+    dplyr:::rename_with(~str_replace(.," ", "."))
 
@@
 
+  # summarize those predictions constituting each ground truth celltype and standardize naming
   deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = dict, key = key)
@@
 
+  # Correlate predictions to ground truth
   to_corr <- inner_join(true_subset, deconv_subset_summary) %>% dplyr::select(-any_of(key))
@@
 
-    for (ct in unique(dplyr::select(true_estimates, -any_of(key)) %>% names())){
+    for (ct in unique(dplyr::select(true_subset, -any_of(key)) %>% names())){
 
@@
         formatted_cors(cor.stat = "pearson") %>%
-        # reduce to corrs just to ground truth
+        # reduce to just to ground truth on one side, deconv on the other
         dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
@@
 ```
+
+# Vanderbilt
+## Data loading
+```{r}
+deconv_Vanderbilt <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/Vanderbilt_08122023/all_deconvolutions_TPM_Counts_Van.txt") %>%
+  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
+  dplyr::rename_with(~str_replace_all(.,"\\.", "_")) %>%
+  dplyr::rename_with(~str_replace_all(.,"__", "_"))#! fix naming of deconv results
+
+truth_Vanderbilt <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/Vanderbilt_08122023/Cell_proportions.csv") %>%
+  rename(Samples = "...1")
+
+```
+
+## Signature Dictionary construction
+
+```{r}
+# Lists of celltypes of each signature
+## signature dictionary construction (can use . as regexp!)
+## uncoment print of functions to check that you detect what you want.
+## non matching signatures/methods (all 0) are removed.
+dict_Vanderbilt <- list()
+dict_Vanderbilt[["BPRNACan"]] <- list(`B cells` = c("B"),
+                                      CD4 = c("CD4"),
+                                      CD8 = c("CD8"),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c("cancer"),
+                                      Fibroblasts = c(),
+                                      `M1 Macrophages` = c("M1"),
+                                      `M2 macrophages` = c("M2"),
+                                      `Mast cells` = c(),
+                                      `Mural cells` = c(),
+                                      NK = c("NK"),
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c()) # Missing Monocytes, M0 and Neutrophils
+
+dict_Vanderbilt[["BPRNACanProMet"]] <- dict_Vanderbilt[["BPRNACan"]]
+dict_Vanderbilt[["BPRNACan3DProMet"]] <- dict_Vanderbilt[["BPRNACan"]]
+
+dict_Vanderbilt[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(`B cells` = c("B_cells"),
+                                      CD4 = c("T.cells.CD4"),
+                                      CD8 = c("T.cells.CD8"),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c(),
+                                      Fibroblasts = c(),
+                                      `M1 Macrophages` = c(),
+                                      `M2 macrophages` = c(),
+                                      `Mast cells` = c(),
+                                      `Mural cells` = c(),
+                                      NK = c("NK"), # NKT.cells?
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c()) # Missing Monocytes and NKT.cells
+
+dict_Vanderbilt[["CBSX_LM22"]] <- list(`B cells` = c("B.cells.memory", "B.cells.naive"),
+                                      CD4 = c("T.cells.CD4.memory.activated", "T.cells.CD4.memory.resting", "T.cells.CD4.naive"),
+                                      CD8 = c("T.cells.CD8", "T.cells.gamma.delta"),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c(),
+                                      Fibroblasts = c(),
+                                      `M1 Macrophages` = c("Macrophages.M1"),
+                                      `M2 macrophages` = c("Macrophages.M2"),
+                                      `Mast cells` = c("Mast.cells.activated", "Mast.cells.resting"),
+                                      `Mural cells` = c(),
+                                      NK = c("NK.cells.activated", "NK.cells.resting"), 
+                                      `Plasma B cells` = c("Plasma.cells"),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c("T.cells.follicular.helper"),
+                                      `T reg.
+cells` = c("T.cells.regulatory..Tregs.")) # Missing Dendritic.cells.activated, Dendritic.cells.resting, Eosinophils, Macrophages.M0, , Monocytes, Neutrophils
+
+dict_Vanderbilt[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(`B cells` = c("B.cells"),
+                                      CD4 = c("T.cells.CD4"),
+                                      CD8 = c("T.cells.CD8"),
+                                      `Endothelial cells` = c("Endothelial.cells"),
+                                      Cancer = c("Malignant"),
+                                      Fibroblasts = c("CAF"),
+                                      `M1 Macrophages` = c(),
+                                      `M2 macrophages` = c(),
+                                      `Mast cells` = c(),
+                                      `Mural cells` = c(),
+                                      NK = c("NK.cells"), 
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c()) # Missing Macrophages
+
+list(`B cells` = c(),
+                                      CD4 = c(),
+                                      CD8 = c(),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c(),
+                                      Fibroblasts = c(),
+                                      `M1 Macrophages` = c(),
+                                      `M2 macrophages` = c(),
+                                      `Mast cells` = c(),
+                                      `Mural cells` = c(),
+                                      NK = c(), 
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c())
+
+dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
+                                      CD4 = c("T.cells.CD4"),
+                                      CD8 = c("T.cells.CD8"),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c("Malignant.cells"),
+                                      Fibroblasts = c("CAFs"),
+                                      `M1 Macrophages` = c(),
+                                      `M2 macrophages` = c(),
+                                      `Mast cells` = c("Mast.cells"),
+                                      `Mural cells` = c(),
+                                      NK = c(), 
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c()) # Missing Dendritic.cells Macrophages
+
+dict_Vanderbilt[["Quantiseq"]] <- list(`B cells` = c("B_cell"),
+                                      CD4 = c("T_cell_CD4+_(non-regulatory)"),
+                                      CD8 = c("T_cell_CD8+"),
+                                      `Endothelial cells` = c(),
+                                      Cancer = c(),
+                                      Fibroblasts = c(),
+                                      `M1 Macrophages` = c("Macrophage_M1"),
+                                      `M2 macrophages` = c("Macrophage_M2"),
+                                      `Mast cells` = c(),
+                                      `Mural cells` = c(),
+                                      NK = c("NK_cell"), 
+                                      `Plasma B cells` = c(),
+                                      `T cells proliferative` = c(),
+                                      `T helper cells` = c(),
+                                      `T reg. cells` = c("T_cell_regulatory_(Tregs)")) # Missing Monocyte Myeloid_dendritic_cell Neutrophil uncharacterized_cell
+
+dict_Vanderbilt[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
+                                   CD8 = c("T.cell.CD8+"),
+                                   NK = c("NK.cell"))
+
+```
+## Corrplot
+
+```{r}
+corr <- benchmark_corrplots(deconv_data = deconv_Vanderbilt, true_estimates = truth_Vanderbilt, dict = dict_Vanderbilt, key = "Samples", title = "Vanderbilt scRNAseq")
+corr
+
+```

### 2023-12-15 Figures/Figures_nonTCGA.Rmd
Fix problem Macrophage naming. Stupid bug

@@
     arrange(factor(get(key), levels = get(key))) %>%
-    dplyr:::rename_with(~str_replace(.,"_", ".")) %>%
-    dplyr:::rename_with(~str_replace(.," ", "."))
+    dplyr:::rename_with(~str_replace_all(.,"_", ".")) %>%
+    dplyr:::rename_with(~str_replace_all(.," ", "."))
 
@@
   ct_corrplots <- list()
+
+  ## Build matrix to store correlations 
   store_corrs <- tibble(measure1 = character(),
@@
                                    NK = c("NK.cell"))
-
 ```
@@
                                       Fibroblasts = c(),
-                                      `M1 Macrophages` = c("M1"),
+                                      `M1 macrophages` = c("M1"),
                                       `M2 macrophages` = c("M2"),
@@
                                       Fibroblasts = c(),
-                                      `M1 Macrophages` = c(),
+                                      `M1 macrophages` = c(),
                                       `M2 macrophages` = c(),
@@
                                       Fibroblasts = c(),
-                                      `M1 Macrophages` = c("Macrophages.M1"),
+                                      `M1 macrophages` = c("Macrophages.M1"),
                                       `M2 macrophages` = c("Macrophages.M2"),
@@
                                       Fibroblasts = c("CAF"),
-                                      `M1 Macrophages` = c(),
+                                      `M1 macrophages` = c(),
                                       `M2 macrophages` = c(),
@@
 
-list(`B cells` = c(),
-                                      CD4 = c(),
-                                      CD8 = c(),
-                                      `Endothelial cells` = c(),
-                                      Cancer = c(),
-                                      Fibroblasts = c(),
-                                      `M1 Macrophages` = c(),
-                                      `M2 macrophages` = c(),
-                                      `Mast cells` = c(),
-                                      `Mural cells` = c(),
-                                      NK = c(), 
-                                      `Plasma B cells` = c(),
-                                      `T cells proliferative` = c(),
-                                      `T helper cells` = c(),
-                                      `T reg. cells` = c())
-
 dict_Vanderbilt[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(`B cells` = c("B.cells"),
@@
                                       Fibroblasts = c("CAFs"),
-                                      `M1 Macrophages` = c(),
+                                      `M1 macrophages` = c(),
                                       `M2 macrophages` = c(),
@@
                                       Fibroblasts = c(),
-                                      `M1 Macrophages` = c("Macrophage_M1"),
+                                      `M1 macrophages` = c("Macrophage_M1"),
                                       `M2 macrophages` = c("Macrophage_M2"),
@@
 
-dict_Vanderbilt[["Quantiseq"]] <- list(CD4 = c("T.cell.CD4+.(non-regulatory)"), # "T.cell.regulatory(Tregs)"
-                                   CD8 = c("T.cell.CD8+"),
-                                   NK = c("NK.cell"))
-
 ```

### 2023-12-15 Figures/Figures_nonTCGA.Rmd
Fix problem Plasma B cell by overriding nomenclature

@@
 
-      substring_remove <- c(paste0("_",ct,"$"),
+      substring_remove <- c(paste0("_",unique(dplyr::select(true_subset, -any_of(key)) %>% names()),"$"),
       "_Tirosh_sigmatrix_SuppFig_3.b",
@@
 truth_Vanderbilt <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/Vanderbilt_08122023/Cell_proportions.csv") %>%
-  rename(Samples = "...1")
+  rename(Samples = "...1", `Plasma cells` = `Plasma B cells`)
 
@@
                                       NK = c("NK"),
-                                      `Plasma B cells` = c(),
+                                      `Plasma cells` = c(),
                                       `T cells proliferative` = c(),
@@
                                       NK = c("NK"), # NKT.cells?
-                                      `Plasma B cells` = c(),
+                                      `Plasma cells` = c(),
                                       `T cells proliferative` = c(),
@@
                                       NK = c("NK.cells.activated", "NK.cells.resting"), 
-                                      `Plasma B cells` = c("Plasma.cells"),
+                                      `Plasma cells` = c("Plasma.cells"),
                                       `T cells proliferative` = c(),
@@
                                       NK = c("NK.cells"), 
-                                      `Plasma B cells` = c(),
+                                      `Plasma cells` = c(),
                                       `T cells proliferative` = c(),
@@
                                       NK = c(), 
-                                      `Plasma B cells` = c(),
+                                      `Plasma cells` = c(),
                                       `T cells proliferative` = c(),
@@
                                       NK = c("NK_cell"), 
-                                      `Plasma B cells` = c(),
+                                      `Plasma cells` = c(),
                                       `T cells proliferative` = c(),

### 2023-12-15 Figures/Figures_nonTCGA.Rmd
Fix problem NK cells by correcting dictionary

@@
                                       `Mural cells` = c(),
-                                      NK = c("NK"),
+                                      `NK cells` = c("NK"),
                                       `Plasma cells` = c(),
@@
                                       `Mural cells` = c(),
-                                      NK = c("NK"), # NKT.cells?
+                                      `NK cells` = c("NK"), # NKT.cells?
                                       `Plasma cells` = c(),
@@
                                       `Mural cells` = c(),
-                                      NK = c("NK.cells.activated", "NK.cells.resting"), 
+                                      `NK cells` = c("NK.cells.activated", "NK.cells.resting"), 
                                       `Plasma cells` = c("Plasma.cells"),
@@
                                       `Mural cells` = c(),
-                                      NK = c("NK.cells"), 
+                                      `NK cells` = c("NK.cells"), 
                                       `Plasma cells` = c(),
@@
                                       `Mural cells` = c(),
-                                      NK = c(), 
+                                      `NK cells` = c(), 
                                       `Plasma cells` = c(),
@@
                                       `Mural cells` = c(),
-                                      NK = c("NK_cell"), 
+                                      `NK cells` = c("NK_cell"), 
                                       `Plasma cells` = c(),
